% universal settings
\documentclass[smalldemyvopaper,11pt,twoside,onecolumn,openright,extrafontsizes]{memoir}
\usepackage[T1]{fontenc}
\usepackage[osf]{Alegreya,AlegreyaSans}

% COMMAND
\newcommand{\chapdesc}[1]{
    \begin{flushright}
    \emph{{#1}}
    \end{flushright}
    \vspace{26pt}
}

% PACKAGE DEFINITION
% typographical packages
\usepackage{microtype} % for micro-typographical adjustments
\usepackage{setspace} % for line spacing
\usepackage{lettrine} % for drop caps and awesome chapter beginnings
\usepackage{titlesec} % for manipulation of chapter titles

% for placeholder text
\usepackage{lipsum} % to generate Lorem Ipsum

% other
\usepackage{calc}
\usepackage{hologo}
\usepackage[hidelinks]{hyperref}
%\usepackage{showframe}

% PHYSICAL DOCUMENT SETUP
% media settings
\setstocksize{8.5in}{5.5in}
\settrimmedsize{8.5in}{5.5in}{*}
\setbinding{0.175in}
\setlrmarginsandblock{0.611in}{1.222in}{*}
\setulmarginsandblock{0.722in}{1.545in}{*}

% defining the title and the author
%\title{\LaTeX{} ePub Template}
%\title{\textsc{How I Started to Love {\fontfamily{cmr}\selectfont\LaTeX{}}}}
\title{Tales of the Southside Chillers: Volume I}
\author{Galadriel Moonwater \& Co.}
\newcommand{\press}{Cool Books for Very Cool Boys Press}

% custom second title page
\makeatletter
\newcommand*\halftitlepage{\begingroup % Misericords, T&H p 153
  \setlength\drop{0.1\textheight}
  \begin{center}
  \vspace*{\drop}
  \rule{\textwidth}{0in}\par
  {\Large\textsc\thetitle\par}
  \rule{\textwidth}{0in}\par
  \vfill
  \end{center}
\endgroup}
\makeatother

% custom title page
\thispagestyle{empty}
\makeatletter
\newlength\drop
\newcommand*\titleM{\begingroup % Misericords, T&H p 153
  \setlength\drop{0.15\textheight}
  \begin{center}
  \vspace*{\drop}
  \rule{\textwidth}{0in}\par
  {\HUGE\textsc\thetitle\par}
  \rule{\textwidth}{0in}\par
  {\Large\textit\theauthor\par}
  \vfill
  {\Large\scshape\press}
  \end{center}
\endgroup}
\makeatother

% chapter title manipulation
% padding with zero
\renewcommand*\thechapter{\ifnum\value{chapter}<10 0\fi\arabic{chapter}}
% chapter title display
\titleformat
{\chapter}
[display]
{\normalfont\scshape\huge}
{\HUGE\thechapter\centering}
{0pt}
{\vspace{18pt}\centering}[\vspace{10pt}]

% typographical settings for the body text
\setlength{\parskip}{0em}
\linespread{1.09}

% HEADER AND FOOTER MANIPULATION
  % for normal pages
  \nouppercaseheads
  \headsep = 0.16in
  \makepagestyle{mystyle} 
  \setlength{\headwidth}{\dimexpr\textwidth+\marginparsep+\marginparwidth\relax}
  \makerunningwidth{mystyle}{\headwidth}
  \makeevenhead{mystyle}{}{\textsf{\scriptsize\scshape{Tales of the Southside Chillers: Vol. I}}}{}
  \makeoddhead{mystyle}{}{\textsf{\scriptsize\scshape\leftmark}}{}
  \makeevenfoot{mystyle}{}{\textsf{\scriptsize\thepage}}{}
  \makeoddfoot{mystyle}{}{\textsf{\scriptsize\thepage}}{}
  \makeatletter
  \makepsmarks{mystyle}{%
  \createmark{chapter}{left}{nonumber}{\@chapapp\ }{.\ }}
  \makeatother
  % for pages where chapters begin
  \makepagestyle{plain}
  \makerunningwidth{plain}{\headwidth}
  \makeevenfoot{plain}{}{}{}
  \makeoddfoot{plain}{}{}{}
  \pagestyle{mystyle}
% END HEADER AND FOOTER MANIPULATION

% table of contents customisation
\renewcommand\contentsname{\normalfont\scshape Contents}
\renewcommand\cftchapterfont{\normalfont}
\renewcommand{\cftchapterpagefont}{\normalfont}
\renewcommand{\printtoctitle}{\centering\Huge}

% layout check and fix
\checkandfixthelayout
\fixpdflayout

% BEGIN THE DOCUMENT
\begin{document}
\pagestyle{empty}
% the half title page
\halftitlepage
\cleardoublepage
% the title page
\titleM
\clearpage

% dedication

% begin front matter
\frontmatter
\pagestyle{mystyle}
% preface
% \chapter*{Preface}
% \lipsum[100-104]
% acknowledgements
%   \chapter*{Acknowledgements}
% \lipsum[1-9]
% table of contents
\clearpage
\tableofcontents*

% begin main matter
\mainmatter

\chapter{Lunar Rumours}
\chapdesc{Astrological trouble brews as our adventure begins.}

Our story begins as all quests must: with a chance encounter between
three strangers in a tavern. \href{/characters/hanamir/}{Hanamir} (a
half-orc monk), \href{/characters/harlan/}{Harlan} (a human cleric of
the storm god \href{/characters/kord/}{Kord}), and
\href{/characters/galadriel/}{Galadriel} (a half-elf bard) are
separately enjoying their beverages of choice in this tavern when the
mayor of town, \href{/characters/frunk/}{Frunk}, begins drunkenly
ranting about a man, \href{/characters/hjun/}{H'Jun}, who owes him an
eel brain. Our heroes learn that the eel brain is a necessary component
for an ``invention'' that the mayor was planning to build in preparation
for the town's famous Moon Festival , in honor of the town's patron
goddess. He also needs red glass for the invention, but the focus was
definitely on this missing eel brain. The takeaway from our conversation
was that H'Jun was entrusted to bring the eel brain to Mayor Frunk, but
fell asleep on the job and was robbed.

Hanamir, Harlan, and Galadriel decide to visit the would-be co-creator
of this invention, someone named \href{/characters/bryn/}{Bryn} who
lives on top of a hill near town. Bryn informs them that the invention
was supposed to be something that would allow him to inspect the moon.
He is very worried about his inability to inspect the moon--he won't
divulge too many details to avoid causing panic, but he says he fears
something is very wrong with the moon, which might prevent the Moon
Festival from taking place, and worse, might devastate the entire town.
(By the way, the forest right outside town is on fire? And has been on
fire for a hundred years? But this seems to be unrelated? )

Our heroes then make their way to the home of H'Jun, the failed eel
brain procurer. After peeking in the window to see that he's passed out
on the floor, they break into his house and awaken him. In a very
intoxicated stupor, he tells them the tale of how he was robbed of the
eel brain by (he claims) an orc and a goblin. He pursued them as far as
a well , and is embarrassed to say that he was too scared to follow them
down into the well because he's afraid of the dark.

But the intrepid adventurers have no such fears. They descend into the
well to find a large open space with two balconies, a gated staircase
descending somewhere farther down, a pile of armor, and a pile of bones
. As they attempt to inspect the pile of bones, two vicious goblins jump
down from the balconies and attack them. Hanamir starts off strong,
injuring one of the goblins and forcing him to retreat back onto one of
the balconies. The other goblin attacks Galadriel with a scimitar and
gravely injures her. Harlan uses magic to try to heal Galadriel. Though
he sustains injuries, Hanamir kills the second goblin with a shortsword
. Galadriel then uses her crossbow to shoot and kill the first goblin on
the balcony. As he collapses, something can be heard falling out of his
pocket.


\chapter{Red Glass}
\chapdesc{Our heroes seek answers...and valuable non-crystalline amorphous solids.}

After the goblin's death the heroes scramble for the fallen object: a
brass key. It did not fit the gate nearby, for no lock was present, but
noises were heard down the stairs behind it. Before another step could
be taken a large dwarf descends rapidly down the well, loudly coming to
rest at the bottom of the well shaft. As the heroes are checking the
health of the newcomer, they find \href{/characters/hanamir/}{Hanamir}
in an unresponsive state. After some quick introductions, the dwarven
barbarian \href{/characters/tannin/}{Tannin} McBitters agrees to join
the party, replacing the newly catatonic Hanamir. Not wanting to abandon
her half-orc friend to the elements,
\href{/characters/galadriel/}{Galadriel} uses a spell of minor illusion
to disguise Hanamir as the most realistic pond any of the adventurers
has ever seen. A truly stunning display of magical artistry.

Having hidden their friend securely, the party sets to work getting down
the stairs. Tannin takes the first shot at breaking down the gate, but a
last second stumble results in a stubbed toe and a bruised ego.
\href{/characters/harlan/}{Harlan} then brings his maul to bear on the
rusty gate, sending it clattering down the stairs along with a hobgoblin
who was ascending at the time. At the bottom of the stairs they
valiantly face an angry orc and the dazed hobgoblin. Minutes later,
after sustaining only minor wounds, the heroes have knocked the two foes
unconscious and tied them up. After searching his person, Galadriel
finds on the orc a holy symbol of Shargaas, a devious orcish god. A
foreboding sign of things to come.

During questioning the orc proves surly and unwilling to cooperate,
bragging that he had eaten the eel brains he'd stolen from
H'Jun.~Hesitant to seek another source of eel brain, Tannin figures a
more direct route is necessary. Unleashing a fearsome roar, Tannin
terrifies the bound orc into spilling his lunch all over the floor of
the well. Fortunately, more than 80\% of the eel brain was left
undigested, so the heroes can still return victorious. After several
unsuccessful attempts to extract further information, the heroes decide
these captives can't be left alive to hatch future plots, and dispatch
them with little fanfare. A quick search of the upper level reveals some
gold, arrows, a hand-held battering ram, and a new orcish maul, but the
biggest surprise is the absence of Hanamir. After carefully verifying
that they aren't still being fooled by the best pond illusion ever, they
discover that their half-orc friend has woken up and wandered away.
Unnerved, the heroes return to town.

Back at the inn, the heroes find Mayor \href{/characters/frunk/}{Frunk}
nursing a drink, but less besotted than last time. In celebration of an
adventure completed, Tannin buys the inn a round of drinks, but that
happy mood will not last. Galadriel lets slip that something is wrong
with the moon, a worrisome prospect in the elven city, which eventually
leads the adventures to share news of the orcish menace. In an effort to
recruit reinforcements, Galadriel takes up her lute and improvises a
truly catchy tune about the orcs that will be vanquished and the
townsfolk that will rise to the occasion and defend their city from
attack. Buoyed by song, the townspeople grab nearby weapons and torches
and spill out into the street, focused on investigating the well and
finding the intruding orcs.

Having rallied the people of the inn, Tannin, Harlan, and Galadriel seek
out \href{/characters/bryn/}{Bryn} to discuss the second needed piece of
the invention: red glass. Craftable only with sand from a far desert and
fire from a dragon, the heroes decide that procuring some existing red
glass would be a better bet. Unfortunately, Bryn tells them that the
only red glass available is found in the stained glass window at the
local temple of \href{/characters/eilistraee/}{Eilistraee}, or perhaps
from a farther orcish temple cloaked in mystery and danger. The heroes
decide to investigate the elven temple first thing in the morning, and
gratefully accept Bryn's offer of food and board for the evening.

Awaking refreshed, they set off for the temple, mulling over different
strategies for obtaining an audience. They are stopped by Mayor Frunk
who had left the inn the previous evening before Galadriel's
performance. Apparently a number of townsfolk were asking after their
loved ones, loved ones that never returned from the bar the previous
evening. After telling him that they recruited the townsfolk to help
fight the orcs, the heroes proceed confidently to the temple.

Since she has elvish ancestry, Galadriel is appointed the spokesperson
and raps on the gate. A nervous looking figure in dark robes urges them
to leave immediately, but Galadriel will not be deterred. She insists on
coming inside, and is granted entrance, but her companions are forbidden
from joining her. As they sputter their protests, Galadriel leaves
Tannin and Harlan outside and enters the temple. She soon realizes her
mistake when she sees four elven bodies lying motionless on the floor.
Before she knows it, she is bound and gagged, able to cry out only
briefly for help. Tannin and Harlan, already nervous from the
gatekeeper's demeanor, spring into action upon hearing Galadriel's
scream. Tannin pulls out his new acquisition, the hand-held battering
ram from the well, and with barbarian rage begins assaulting the
imposing gates of the temple.


\chapter{The Annunciation of Chanto}
\chapdesc{A confrontation with sinister forces in a holy place.}

We left our heroes on a terrifying cliffhanger. While
\href{/characters/harlan/}{Harlan} and
\href{/characters/tannin/}{Tannin} face a shower of arrows from above
the temple, \href{/characters/galadriel/}{Galadriel} has been taken
hostage by four orc cultists and a vicious bugbear within. The temple
attendants have been brutally murdered.

Tannin, in a barbarian rage, breaks down the temple door with his
portable ram. Battle commences, but it's a weird one: there's a lot of
swinging at each other and missing. The two cultists in front come at
Harlan and Tannin with scimitars and whiff the air. Tannin hits one with
his battle axe and Harlan finishes the job with his orcish maul.

Out of nowhere, our most pond-resembling compatriot,
\href{/characters/hanamir/}{Hanamir}, emerges from his hiding place and
frees Galadriel from the bugbear. He then strikes at the bugbear and
misses; Galadriel, thrilled to be rescued, takes a swipe at the
bugbear's exposed thigh with her rapier and hits. The bugbear retaliates
with a swing of his deadly morning star and deals considerable damage to
both Hanamir and Galadriel.

Meanwhile, Tannin and Harlan battle the second and third cultists at the
front of the temple. There's more swinging and missing, and the fourth
cultist rushes to the front to join the fray. Tannin succeeds in killing
the second one with his battle axe. The third cultist mysteriously
sacrifices himself while the fourth starts chanting and shrouds himself
in flames---alas! A mage!

Hanamir and Galadriel knock the bugbear unconscious. The chanting mage,
affectionately known as Chanto, conjures a floating hand above the
bugbear's body, and uses magic to disappear and reappear in the corner
of the temple. When Hanamir confronts him, Chanto demands to know our
heroes' purpose. ``To learn what threatens the moon!'' Hanamir replies.
Chanto retorts, ``Shargaas threatens the moon!'' and conjures three
darts that hit Hanamir, Galadriel, and Harlan.

Sensing that the floating hand is trying to revive the bugbear,
Galadriel puts the creature out of its misery. Tannin intimidates the
mage, who backs down and urges the party to leave---``We were in the
middle of something!'' Harlan heals Galadriel, who then heals Hanamir.
Hanamir uses sleight-of-hand to attack the mage, but he disappears.

Our heroes are now alone in the temple. Tannin smashes the window
containing the precious red glass, taking it. Hanamir has the clever
idea to position the dead bugbear in the broken window to explain the
damage.

Perceiving a staircase underneath one column, Hanamir leads the party
downstairs. It's pitch black. Using their combined powers of perception,
darkvision, and stealth, the group avoids several pressure traps in the
darkened corridor. \emph{Slam!} The mage from upstairs jumps out from
underneath a cot and strikes Hanamir with his staff. Hanamir perceives a
sleeping bugbear in another cot close by, and elects to stab-then-punch
the bugbear in rapid succession.

Tannin swiftly cuts down the mage with his battle axe. Harlan lights his
holy symbol to provide some light in the darkened basement. Galadriel
shoots the bugbear in the head, killing it. The party is alone once
more.

Hanamir notices another cot around the corner covered in blood---some
poor temple attendant perished there, it seems. Tannin checks the mage's
body and recovers 20 gold pieces, which the party splits evenly. The
mage also has a map of the area west of town, including the burning
woods, with a spot marked in the woods. Tannin keeps the map.

Galadriel perceives that there is another trap on the ground and advises
the party to avoid it. The group inspects one last cot and the bookshelf
next to it. The books are all about the goddess of the temple,
\href{/characters/eilistraee/}{Eilistraee}, and contain information
about her lineage. She is the daughter of a lawful good father (elf?)
and of Lolth, the spider goddess. They read that the town, Eillin, once
had many followers of Lolth, but they were driven out. Galadriel takes
two of the most interesting-looking books with her.

Tannin shoves the bookshelf aside and finds a ladder behind it. Before
climbing the ladder, the group decides to inspect the corpses they've
left behind. The bugbear only has a mace, of no interest to anyone. The
cultists upstairs have several symbols of Shargaas, their orc god, which
the party decides to take. Galadriel finds an enchanted shawm and adds
it to her collection of instruments.

The party returns to the ladder downstairs and climbs it. It leads to a
platform with a locked door, marked by the symbol of a harp. Galadriel
first checks the door for magic, finding none. She then tries the key
she collected from the body of an orc in the well to open the door. It
fits!

Inside, they find one book, also marked with the symbol of a harp.
Galadriel decides to keep it, but doesn't tell the party why. There's
also a chest, full of nice weapons and gold, which the individuals of
the party take according to their interest.

For now, our heroes decide to return to town to take a long rest. They
all dream sweet dreams of leveling up.


\chapter{Porcine Comity}
\chapdesc{Discoveries with unforeseen consequences, and a new friend?}

After their night's rest, each member of the party finds that their
dreams have come true! They all feel \emph{amazing} --- not only
well-rested, but measurably more proficient at a variety of skills
important to them.

They decide to hit up the marketplace in town to do a little shopping,
since they're in such a great mood. \href{/characters/tannin/}{Tannin}
decides he needs a new portable ram. His old one, he feels, is unlucky,
and he spies a particularly gorgeous one that he simply must have. He
doesn't have the gold for it, but the seller makes him a deal: if Tannin
will run a series of grueling errands for him, the ram is his. Tannin
agrees. He gives the party the red glass from the temple and goes on his
way.

\href{/characters/harlan/}{Harlan} has a hankering for a good bargain.
He strikes up a conversation with another shopkeeper and purchases a
magic orb that, when wielded, allows him to cast a cantrip of poison
spray. He also buys a set of one thousand ball-bearings, which he gifts
to \href{/characters/hanamir/}{Hanamir}, just 'cause he's feeling
generous. He inspects a ring inscribed with a ``B.'' It's a little too
pricey, however, so he leaves it alone.

Harlan, Hanamir, and \href{/characters/galadriel/}{Galadriel} make their
way back to \href{/characters/bryn/}{Bryn}'s observatory to deliver the
red glass. Bryn looks frazzled and sleep-deprived, but he's very excited
to receive the glass. He says he'll get started right away on his
machine, but it will take him 3 or 4 hours to complete it.

Our heroes decide to head back toward the well to try and catch up with
the missing townsfolk. On the way out of town, they encounter a human
traveler. He looks world-weary, about 60 years old, and wears armor that
he has modified himself. He's called \href{/characters/the-savage/}{the
Savage}, and he says he's on his way into Eillin for the Moon Festival,
having just passed through the Town of the Undead. Hanamir notices that
he's wearing a ring inscribed with a ``B,'' just like the one from the
marketplace. He also looks about half as old, when Hanamir really takes
a good look at him. The ring doesn't seem to be magical, but when the
Savage notices Hanamir's gaze, he tries to cover up his hand. When the
group presses him on it, and mentions that there's a matching ring in
town, he is unnerved and hurries away.

The party moves onward and makes it to the well. Galadriel yells down,
but there's no response. They decide to go in and check. It looks just
how they left it, but there's a spear on the ground in the first
chamber. They proceed down the stairs and find that the grate in the
floor has been moved. They can't see anything down there, even with
darkvision.

Curiosity wins out. They decide to climb down into the narrow shaft,
Hanamir going first, then Harlan, then Galadriel. There's a whole lot of
nothing, until they're about 120 feet down, and then\ldots{} Hanamir is
caught! In a web! Of a giant spider!

Harlan lights his holy symbol, catching the spider's eyes. Galadriel
shoots at the spider and misses, but casts Bardic Inspiration on Harlan
to help him with close-range tasks. The spider attacks Hanamir, doing
damage, but failing to poison him. Harlan tries to cut Hanamir free from
the web but can't quite get it. He switches places on the rope with
Galadriel, who tries slashing at the web with her rapier. Hanamir
wriggles free! He climbs onto the spider's ledge.

Behind the spider, Hanamir can see 50 or 60 silk-wrapped shapes. He
attacks the spider and misses. The spider shoots webbing at Galadriel,
binding her against the wall. Harlan jumps down to the platform and
attacks the spider with his maul in a heroic fashion that could only be
described as ``a natural 20.'' Hanamir follows up with a fatal blow, and
the spider is no more.

They free Galadriel from the web and rescue the townspeople who were not
yet spider chow. Galadriel is wracked with guilt for having led them
here. In the spider's lair, the party finds 5 gold pieces each, as well
as a pig. In her distress, Galadriel bonds with the pig immediately and
decides to keep it as a pet. Harlan inspects the rest of the cave and
throws an illuminated rock down the remainder of the shaft, but all
seems empty. They leave the well, carrying the pig with them.

They journey back to town, having effectively killed a few hours on this
mini quest. Galadriel now leads the pig on a leash. Hanamir has some
skill in animal handling and decides to inspect the pig, and notices
that it's heavier than a pig ought to be. He concludes it has consumed
something of note. Though the idea of killing the pig is pitched,
Galadriel protests in the strongest terms. Hanamir tries to give it a
special pig Heimlich maneuver, but no dice. Galadriel serenades the pig
with a traditional elven Song of Voiding, inducing the gentlest possible
vomit in her dear new friend. The pig coughs up a magical gauntlet with
the red spider insignia of the goddess Lolth. The gauntlet grants its
wearer the power of blindsight and a spider-like climbing ability.
Galadriel doesn't put it on, but keeps it.

Back at the observatory, Bryn presents the party with his newly-crafted
pair of eel-brain-powered red glass goggles. He can see through the
smoke with them, but he thinks it won't be enough to see the moon
tonight. He asks if the party would be willing to take the goggles up to
a mountaintop for a better view, or if not that, to extinguish the
source of the smoke in the burning woods. Directing the goggles toward
the woods, they can all see a tower of about 6 or 7 stories' height.

Undecided on their next move, the party returns to the marketplace.
Harlan asks the shopkeeper from that morning about the ``B'' ring he saw
earlier, but the man is reluctant to acknowledge it. With some
persuasion, he admits that he saw ``the Savage'' earlier and that he
accepted a large sum of money for the ring. He implies that the ring may
have been stolen from the grave of a man known around town as Uncle. The
shopkeeper recalls Uncle's address was 1122 Boogie Woogie Avenue, but he
had no relatives, and there's another family living there now.

The party heads to 1122 Boogie Woogie Avenue. While Galadriel asks the
man of the house what he knows about Uncle, Hanamir sneaks around the
side and breaks into the cellar. He sees casks of ale, old farming
tools, and some books about the town. On the bookshelf, he notices
``TANNIN WAS HERE!'' carved into the wood. He chuckles, knowing that
despite having separate adventures today, somehow his friend's penchant
for bookshelf destruction led him to the same place. He decides not to
steal anything, and sneaks back out.

Galadriel learns that 1122 Boogie Woogie Avenue was a frequent meeting
place for Uncle and his group of friends, including Mayor
\href{/characters/frunk/}{Frunk}, and that after his death, the group
would sometimes come back to the house to honor Uncle's memory. Hanamir,
hearing this, reconsiders. He sneaks back into the basement and steals
the most informative book. He comes back around front, looking eager to
leave, and the group bids the man farewell. They decide to take another
rest before deciding what their next move should be.


\chapter{Toward the Flame}
\chapdesc{An entry to hostile territory: the only way out is through.}

It's another beautiful day in the town of Eillin.
\href{/characters/tannin/}{Tannin} is still on his personal side quest,
but \href{/characters/harlan/}{Harlan},
\href{/characters/hanamir/}{Hanamir}, and
\href{/characters/galadriel/}{Galadriel} are eager to solve the problem
of the burning forest, and they're running out of time before the Moon
Festival. Their only choice is to press on.

They return to \href{/characters/bryn/}{Bryn}'s observatory for some
information before they leave town. Galadriel hands him the enchanted
gauntlet and asks if he knows anything about it. ``Where did you get
this?'' Bryn asks, concerned. ``The symbol of Lolth is most unwelcome in
town.'' He reminds them that Lolth, the spider goddess, once had many
followers in \href{/characters/eilistraee/}{Eilistraee}, but they were
driven out. Galadriel asks him if he can detect any curses on the
gauntlet. ``It would be a curse to wear it here,'' he replies.

They ask him what to expect if they succeed in viewing the moon with the
red glass goggles. His theory, he says, is that the moon has been cut in
two. If this is the case, it would be a sign that something deeply wrong
has happened to Eilistraee, and the town would need to evacuate.

The team lets him know that the orcs they've encountered have claimed
responsibility via their god, Shargaas, for the threat to the moon.
``Shargaas?!'' Bryn exclaims, with a pointed look toward Hanamir.

``My only god is the written word,'' says Hanamir. ``But there is an orc
temple to Shargaas not far from here, according to
\href{/characters/the-savage/}{the Savage}.''

``Oh! He's around? I'm surprised he hasn't made himself known,'' says
Bryn, his tone changing. ``The Savage is an old friend of the town. I
haven't seen him since I was a boy, but he's a famous warrior. Utterly
devoted to the pursuit of valor. He's saved us from more than one
disaster in the past.'' Bryn considers this, and frowns. ``I know not if
his presence now be an omen of good or ill.''

The party thanks Bryn for his insight and returns to the inn, in the
hopes of running into Mayor \href{/characters/frunk/}{Frunk}. They
suspect that the Mayor might be able to tell them more.
\href{/characters/fleck/}{Fleck} the bartender greets them with a
twinkle in his gold-coin eyes. Sure enough, among the surviving
townsfolk, Mayor Frunk sits in his familiar spot at the bar.

``The Savage? Sure I know him. He just left the inn, in fact,'' says
Frunk. ``The man's an inspiration. He was born here, and though he
travels far and wide, he always comes back when we need him. You won't
believe this, but when he was just sixteen, he slew a dragon.''

``Is he still in town? What's he doing here?'' asks Harlan.

``He said he had to check on something, and then he was on his way.
Didn't waste time leaving.''

``Hey, you wouldn't happen to know anything about a man who went by
`Uncle', would you?'' says Galadriel.

Frunk doesn't know why, but he feels comfortable sharing, though he
usually wouldn't. ``Oh, yes. He was known as Uncle because I called him
that first. I don't know his real name. He was like an uncle to me.''

``Did Uncle and the Savage know each other?'' Galadriel says, sensing
she may be pushing her luck.

``Um, they might have,'' says Frunk. ``But uh, sorry, the King is coming
into town for the Moon Festival and I really need to go prepare for
that. Get\ldots{} supplies. King stuff. Stuff that kings like.''

Hanamir stealthily watches where Frunk goes when he leaves. It appears
he's headed to the house of \href{/characters/hjun/}{H'Jun}---his friend
who was robbed of the eel brain during the first chapter of this quest.

Our heroes strike out for the burning forest. Hanamir wears the red
glass goggles, leading the pack. Galadriel puts on the gauntlet of
Lolth, hoping that the blindsight and climbing ability will come in
handy. Harlan can't see through the smoke, but he hangs back with
Galadriel.

With the goggles, Hanamir senses that a wall of fire in their path is
actually fake, and leads them through it. They come to a pond, which has
effectively sheltered its surrounding trees from the fire. Galadriel
tests out her new spiderlike climbing skills by quickly scaling a tree
and surveying their options. There's a fork in the path ahead, and to
the left there is a hut, untouched by fire. To the right, she sees
nothing but dense woods, and the suggestion of faint movement within.

They go left and investigate the hut. Hanamir tries to sneak through the
door, but stumbles on his way in, surprising an elderly tiefling inside.
The tiefling reaches for a trident. ``Oops, pardon me,'' says Hanamir.

``How did you get in here?'' says the tiefling. ``I haven't seen anyone
in ages! The fire's driven everyone away. I can't even get out. I'm so
lonely! The name's \href{/characters/magick/}{Magick}, by the way. I
make potions. Healing potions, potions that'll make you impervious to
magic, all kinds of potions. I'm even working on one that lets you plane
shift at will, but so far all it does is bring me back to the center of
my hut. I have a lot of it, if you guys want some. You'll have to let me
know how it affects each of you, being different types of creatures than
little ol' me.'' They each accept a vial of the plane shifting potion,
just in case it comes in handy later. ``I can sell you some of the other
potions, but I only take electrum. No interest in gold. Or I'll barter
you for 'em. Do you have anything I could wear that might make me feel
fancy? That would keep me from being bored for a good couple of days, I
think.''

The party inspects their inventory, but they don't have anything that
would fit the bill for fanciness.

``I hear rope can be considered a fancy accessory in some cultures,''
Hanamir suggests.

``Oh\ldots{} no thanks,'' says Magick, looking put out.

``What if we show you the way out of the forest in exchange for three
vials of your magic imperviousness potion?'' Harlan asks, ever the
bargain hunter.

``Sounds good!'' says Magick.

As they lead the tiefling out of the forest, past the fake fire, they
try to glean more information about their surroundings.

``Do you know who is in the tower?'' asks Hanamir.

``No one, I suspect,'' says Magick. ``Once the red dragon set this fire,
it went back to sleep, I think. No one left in the forest now except for
me and old Grizzleby. That's the dragon's name. It's a very common
dragon name.''

They bid the tiefling farewell and return down the left-side fork in the
path, past the hut this time. They come to a rocky clearing that leads
to a cave. There is a great heat emanating from the cave, and it looks
unnaturally dark inside. Galadriel, using the gauntlet's blindsight,
peers inside. ``It looks great in here!'' she says. ``Lots of spider
webs. Tons of them on all the walls. I am feeling really good about
exploring in here.''

Hanamir lights a torch, catching the attention of two giant spiders
inside. The first one approaches him and tries to bite him, but he
dodges. The second one shoots a web, Spider-Man-style, at Galadriel, but
she jumps out of the way. ``Friends, fear not!'' Galadriel addresses the
spiders and displays the insignia on her gauntlet. ``I come in the name
of Lolth!''

The second spider pauses a moment, then shoots another web at her,
binding her to the wall. Galadriel is trapped and indignant.

Hanamir attacks the first spider with his shortsword and misses. Harlan
follows up with his maul, and makes a solid hit. At that point, two much
smaller spiders---about fist-sized---scurry in from the deeper part of
the cave. They try to bite Harlan, but he swats them away. The first
spider takes advantage of his distraction and successfully attacks him.
Harlan hits back with Wrath of the Storm, bloodying the spider.

The second spider rounds on Hanamir and bites him with its huge pincers.
He's not poisoned, but he sustains heavy damage. Meanwhile, Galadriel
struggles to free herself from the web, but is so ineffective at doing
so that she sprains her wrist. Still, she can at least help by healing
Hanamir from across the cave. Hanamir then casts the fatal blow to the
first spider.

Harlan swings at the second spider with his maul but misses. The two
smaller spiders creep up on still-stuck Galadriel and start biting her.
Galadriel tries to free herself \emph{again} and fails \emph{again}.
There's a bloody back-and-forth between Hanamir, Harlan, and the
remaining giant spider, while the smaller spiders focus on nibbling
Galadriel. The giant spider is wounded, and after one last attempt at
biting Harlan, it flees to the back of the cave. Harlan and Hanamir try
to hit it with their ranged weapons, but it gets away, disappearing into
a crevice similar to the one they saw in their last spider battle.

Galadriel tries a third time to escape the web and damages herself doing
so. It's a bad scene. Hanamir and Harlan come over and each squash one
of the smaller spiders. Hanamir then uses his torch to free Galadriel,
who is a bit embarrassed, but still in a weirdly good mood.

They explore the cave. There are silk-wrapped shapes in various stages
of being eaten, but none of them appear to be humanoid this time around.
There are 200-300 spider eggs.

Galadriel climbs up the walls and hangs out on the ceiling. She is
loving the abilities the gauntlet has given her! She feels so alive, so
agile, so arachnoid!

``I feel VERY good and normal!'' she shouts down at her compatriots.

``Hmm. What happens if you take off the gauntlet, Galadriel?'' says
Hanamir. She tries, but cannot. It is fused with her arm.

``So what do you think?'' says Harlan. ``Should we take some spider
eggs? Or just burn the whole thing?'' Galadriel jumps down from the
ceiling and claws at his eyes.

After that scuffle subsides, they leave the cave, and Galadriel feels
suddenly able to share with them that there were no fewer than 900 other
spiders hiding deeper in the cave. The gauntlet prevented her from
saying this. She realizes it would take a priest of Lolth to remove the
gauntlet from her arm, and if they encounter any more spiders in the
forest, she might unintentionally take their side. They try to exit the
forest the way they came, but they find that the fake fire is now
real---they are trapped.

There is no choice but to venture onward toward the tower and hope the
bonds of their friendship can withstand the sinister forces that
surround them.


\chapter{Axe and Claw}
\chapdesc{The pack descends, and the peril deepens.}

\href{/characters/harlan/}{Harlan},
\href{/characters/hanamir/}{Hanamir}, and
\href{/characters/galadriel/}{Galadriel} return to the pond in the
burning woods. They are still reeling from their encounter in the spider
cave, but after Galadriel performs a short Song of Rest, they feel a bit
stronger.

``Shall we explore this pond?'' asks Harlan, peering at it. The water is
dark, and he can't see beneath the surface.

Hanamir needs no encouragement and dives right in. He sees about ten
skeletons lying in the pond's murky depths. ``Dead tieflings down there,
it looks like,'' he reports back.

Just then, they hear a loud noise from the woods beside them. Before
anyone can prepare for attack, someone crashes through the trees,
wielding a battering ram and smoldering faintly. It's
\href{/characters/tannin/}{Tannin}!

The group welcomes their dwarven friend back and tells him the tale of
their recent adventures. Tannin shows off the new ram he spent all that
time earning, and then takes notice of the pig. ``Who brought the
snack?'' he asks.

``RUDE,'' says Galadriel. ``He's not a snack, he's my precious little
\href{/characters/buddy/}{buddy}. His name\ldots{} is Buddy.''

``Agree to disagree,'' shrugs Tannin.

Together, they decide to return to \href{/characters/magick/}{Magick}'s
hut and look around. Under a loose floorboard, they find a blade
inscribed with some Draconic script. Galadriel, using Comprehend
Languages, interprets that the blade belonged to a tiefling warrior
named Valonius, and that he fought with it in many battles. The blade
does not seem to be endowed with any magical properties.

``Ooh, let's take this with us,'' says Harlan. ``It's not like the
tiefling's coming back for it.'' But Hanamir feels strongly that they
shouldn't take it. The group argues and eventually decides to just leave
it. ``Fine,'' mumbles Harlan.

They return to the pond and then take the path that forks to the right.
Hanamir perceives a group of twigblights ahead, along with other
assorted woodland creatures. None have noticed the travelers approaching
their quiet habitat yet.

Tannin changes all that by jumping ahead in a Reckless Attack, killing a
twigblight in one blow. Harlan smashes another one with his warhammer.
Galadriel smites one more with her rapier. Hanamir snuffs out another
with his darts.

With four rapidfire twigblight murders out of the way, the party is
caught unawares by two stirges swooping down from above. One latches
onto Galadriel's back and starts draining her blood with its hideous
proboscis. The other attempts to do the same to Hanamir, but it misses
him and hits the ground.

At the same moment, a wolf jumps out at Tannin and bites him. Tannin,
still in Reckless Attack mode, lays waste to the wolf with his battle
axe. A second snarling wolf bites Hanamir.

Harlan thinks quickly and casts Sacred Flame on the stirge that is stuck
on Galadriel, killing it in a blaze of fire. Galadriel wastes no time
loosing an arrow at the second wolf, wounding it and breaking its hold
on Hanamir. She casts Healing Word on Hanamir.

The second wolf then turns and lunges at Tannin. Its teeth dig in, but
Tannin uses his battle axe to split a wolf in half for the second time
in minutes.

Partially healed from his wolf bite, Hanamir hasn't forgotten the stirge
that tried to make a meal out of him. He punches it so hard it makes a
dent in the ground. A third stirge flies down to attack him, misses, and
retreats 40 feet into the air again.

The two remaining twigblights come at Harlan with their shrubby little
claws. He dispatches them straight to hell with a thunderous blast of
Wrath of the Storm. Then he rounds on the stirge Hanamir just punched
and crushes it with the business end of his maul.

Galadriel shoots an arrow at the third stirge circling above them, but
misses. She casts Healing Word on herself and feels a little less
lightheaded from all the blood loss.

The third stirge swoops down at Tannin and latches on, but Hanamir
quickly stabs it to death and removes it from Tannin's neck. But between
the wolf bites and the stirge, Tannin has had a rough go of it. Harlan
casts Healing Word on him.

They all take a moment to reflect on the carnage before moving on. But
as they do, they hear howling from somewhere close by. It's not over
yet\ldots{}

A small wolf appears before the party, blocking their path. A much
larger wolf---a direwolf, in fact---makes itself known behind them. The
direwolf bares its teeth and charges at Harlan, who dodges it. The
smaller wolf takes a bite out of Hanamir.

Tannin flies into a barbarian rage and attacks the direwolf for some
significant damage. Harlan swings at it with his maul but misses, and
then brings out his orb of poison spray, but that too misses its target.

Galadriel runs up to Hanamir and stabs the small wolf. She then looks
behind her and casts Bardic Inspiration on Tannin. Hanamir frees himself
from the wolf's jaws and kills it. At that moment, the direwolf leaps
over Harlan and Tannin to confront Galadriel and Hanamir. It digs its
teeth into Hanamir in apparent anguish over the death of the little
wolf.

Galadriel sinks an arrow into the dire wolf's hide, Tannin Attacks it
Recklessly, and Harlan takes a swing at it with his maul. Galadriel hits
it with another arrow; Hanamir recovers enough to hit it with some
darts. Enraged, the direwolf rounds on Tannin and gores him savagely,
knocking him down and rendering him unconscious.

In shock, the remainder of the group tries several ineffective attacks
on the direwolf. Finally, Hanamir brings it down with a carefully-aimed
dart to the head. Harlan uses his medicine kit to stabilize Tannin. They
push onward into the forest, dragging Tannin beside them.

They come to a clearing around the roots of a giant tree. Harlan,
Hanamir, and Galadriel each do some exploring. They conclude that this
might be a safe place to rest.

Galadriel has a hunch that the tower may lie to the east. She takes
advantage of her spider skills and scales the tree. To her comrades on
the ground, she reports: ``There's a river on fire to the west---nothing
beyond that. Just a rocky clearing to the north. There's another tall
tree in the distance, but I don't know how we'd get there. And I can't
see the tower at all from here!''

She comes down, and the group decides to set up camp. Tannin is still
grievously wounded but feels confident about his camping skills. ``Guys,
I got this. Seriously,'' he assures them, swaying on his feet. He
proceeds to build a mediocre campsite. ``See?''

The others thank him and tuck him in, and he passes out instantly,
clutching his enchanted battering ram. Galadriel strums a lullaby on her
lute and curls up with Buddy the pig. Harlan conjures a fluffy cloud for
a pillow. Hanamir wears the red glass goggles for some bedtime reading
before nodding off. They all take a long, refreshing rest and wake up in
the morning feeling stronger than ever.

As the party began to wake from its slumber, Harlan gathers everyone up,
and over breakfast reveals that he had not been entirely truthful about
his past. He is most definitely a cleric of
\href{/characters/kord/}{Kord}, but he was not raised a pirate, as he
had let slip before. Now that he has gotten to know his companions
better, he feels he can tell his true story:

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\hypertarget{the-ballad-of-harlan-stormborne}{%
\subsection{The Ballad of Harlan
Stormborne}\label{the-ballad-of-harlan-stormborne}}

Growing up deep in the wilderness, Harlan gained an affinity for nature
at a young age. His parents, who had instilled in him a respect for the
wrath of the natural world, passed away during a hurricane when he was a
teen.

Harlan channeled his fury and sense of loss into clerical training under
Kord's auspices. This god, known to Harlan's family his whole life,
embodied the strength and resilience of nature that he wanted to
emulate.

After completing his training, and gaining Kord's favor, in his early
twenties, Harlan was appointed guardian of the Cave of Storms. Hidden in
a remote area, the Cave looks simple enough from the outside, but true
mysteries lay within. Though it shares no ecosystem with the world above
ground, save through a system of underground rivers and lakes, the Cave
nevertheless maintains a roiling, furious thunderstorm wholly beneath
the surface of the land. As Harlan discovered during his more than ten
years of service at the Cave, the storm never abates, and even entering
is an invitation for destruction.

Why a thunderous storm exists permanently below ground was beyond
Harlan's comprehension, but he knew he must protect it nonetheless. He
spent these years mostly alone, foraging and studying what scholarly
tomes he could convince those he met to part with. It was not uncommon
for travelers to pass through the area, but Harlan ensured that they
never lingered long. He would spin wild stories about the dangers of the
forest, the monsters that lurk in the streams or the trees, anything but
the truth of the Cave, the secret he was sworn to protect at all costs.

He may have spent his entire life as the Cave's guardian, were it not
for the strange dreams he began to receive. Always very vivid, these
dreams place him in the sky, floating among the clouds. He wasn't
himself, but neither was he able to identify what form he had taken. He
was simply among the clouds, peering down at images that resonated in
his mind. An army marching through a now-barren field. A cult of
fanatics setting fire to a forest. A band of goblins turning a stream
into a sewer. Harlan assumed these cloud dreams were sent by Kord
himself, and began making plans to take arms against those who would so
callously defile the natural world.

One dream in particular called to Harlan as no other had. A band of
travelers was converging on a far-away Elven city, ready to defend it
from an unnamed evil. Harlan knew he must join this group, or put
everything he believed in at risk. After consulting with the few members
of his order he was able to reach, he located a new initiate able to
keep watch on the Cave of Storms, and began his journey as soon as he
was able.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

In the pre-dawn mist, Galadriel takes the red glass goggles with her and
climbs up the tree again to see if she can observe the moon. There are
two things occluding the moon, she realizes, but she doesn't know where
they're coming from. She comes back down, disappointed, and attempts to
remove the gauntlet of Lolth, but it's still stuck firmly to her arm.

The group heads east. They come upon the burned ruins of a tiefling
village. They don't find any valuables right away, but after digging
through the rubble, they each find 25 electrum. More interesting still:
they find the bones of a single creature, much larger than a tiefling,
with fearsome claws. Could it be the remains of a small dragon?

Galadriel senses that the villagers tried to protect themselves with a
fire repelling spell, but it has long since stopped working. Hanamir
inspects the bones again and notes that the clawed arm appears to have
been hacked off.

Harlan is eager to move on and check out the flaming river to the west.
They go, and find that the river is not naturally on fire: it is like a
magical vein of lava, carving out a slight path to the south. Galadriel
again senses something arcane; she understands that the river is the
source of the entire forest fire. The river runs north to south, and so
the origin of the flames must be to the north. In fact\ldots the incline
to the north is a red dragon's lair. The dragon has constructed a false
volcano as its nest!

Hanamir decides to at least check the path leading south, but it only
goes back to the spider cave and Magick's hut. So the group ventures
north, past the roots of the giant tree to the rocky clearing. At first,
all they see is a gate in the clearing, standing alone like an altar.

But when they notice the little spiders emerging from underneath the
rocks ahead, it is already too late. A massive spider, larger than any
they've encountered thus far, appears behind them. It rubs its pincers
together, and the smaller spiders shriek with excitement. It is time to
feed\ldots{}


\chapter{A Silken Kord}
\chapdesc{Divine wisdom, and entry to a dark tower.}

The giant spider blinks its uncountable eyes. Two swarms of tiny spiders
flank it on either side, waiting for a signal to attack.
\href{/characters/galadriel/}{Galadriel} takes a step back. Will the
gauntlet of Lolth prevent her from fighting? Or worse: will it cause her
to turn against her friends? She feels an unnatural bond with the
smaller spiders, but no such tenderness for the monstrous blue creature.
This, at least, is a hopeful sign.

\href{/characters/tannin/}{Tannin} and
\href{/characters/harlan/}{Harlan} charge forward at the spider and
batter its shimmering hide with axe and maul. Harlan dodges a
retaliatory attack from the spider, and, as if embarrassed, it
disappears into thin air. Alas! It appears the adventurers are in battle
with a \emph{phase spider}.

Meanwhile, \href{/characters/hanamir/}{Hanamir} is using his fists to
smash as many small spiders as he can. He leaves one swarm badly
depleted. Galadriel is still hesitant about joining the fray lest she
become an unwilling ally of the spiders. She decides to help indirectly
by casting Faerie Fire on the second swarm of spiders and endowing
Hanamir with Bardic Inspiration as he continues crushing critters right
and left.

Tannin develops a brutally effective attack against the swarms: the
``axe blender.'' Spider limbs fly in all directions from his spinning
blade. Harlan reduces a number of spiders to a paste with his hammer.
But in a flash of blue, the phase spider reappears and bites Harlan. He
is poisoned to within an inch of death, and falls to the ground,
unconscious.

Galadriel readies her crossbow and shoots the phase spider. The arrow
hits, and the spider disappears again. Hanamir and Tannin wipe out one
swarm of spiders entirely and use the axe blender technique to great
effect on the other swarm. As Hanamir kills the last of the small
spiders, the phase spider reappears and attempts to poison Tannin, who
strikes a damaging blow with his axe. But Galadriel is ready. She shoots
one more arrow at the massive spider and it collapses, dead, and then
flickers out of existence.

Harlan stirs and opens his eyes. He's still woozy, but he's able to heal
himself enough to stand up and inspect the gate-like altar that sits in
the clearing. Sure enough, it's a monument to his beloved storm deity.
``Praise \href{/characters/kord/}{Kord}!'' he cries.

The Voice of Kord praises Harlan's valor in battle and offers him divine
wisdom. Harlan asks for something to help the party find its way. Kord
reveals that the dragon nest is only accessible from the river of fire.
In the opposite direction, the tower is marked with a red hourglass, and
there is no way to reach it on foot---they must go ``above or below'' if
they wish to venture there.

After a short, restorative rest, Hanamir decides to take the red glass
goggles and climb the spider silk to the top of the tree. He sees that
one source of the moon's distress is very close, and the other is far to
the east. (When he mentions this to the group, Harlan remembers from his
clerical studies that there is some connection between Lolth and
Shargaas, the orc god---could the eastern source be the Shargaas
temple?) Hanamir also looks at the dragon crater, but there's no sign of
the dragon itself.

The party decides to climb the spider silk and attempt an approach to
the tower from above, per Kord's recommendation. Tannin attaches the
spider silk to his javelin and launches it at the tree next to the
tower. Miraculously, this works. Galadriel secures
\href{/characters/buddy/}{Buddy} the pig to herself with rope in a
makeshift baby bjorn, and then they each zipline down the spider silk to
the other tree, landing in the clearing next to the tower.

The tower is a stone octagon with a red hourglass embedded in its
windowless walls. Galadriel senses that this tower intersects with other
planes, and that Lolth followers from other planes come here to worship.
It is, indeed, one of the sources of the moon's occlusion. She knocks on
the door, but there is no response.

Hanamir perceives that the door is unlocked and that there are no traps
waiting for them immediately inside, so the group enters. They find a
large empty room covered in blood stains---sacrifices to Lolth.
Galadriel notes eight small divots around the central Lolth symbol and
intuits that they have a ritualistic purpose. She feels the power of
Lolth flooding through her, as if the gauntlet knows it is home.

As the group ascends to the second story, Tannin sets a bear trap behind
them in case they are followed. Hanamir leads them down a hallway lined
with arrow traps, all previously triggered. They step through more
puddles of blood, but no bodies.

The hallway leads them to a room with four large, wounded spiders. A
pool of water has collected on the floor from a leak in the ceiling.
Galadriel senses that the spiders were attacked in the last hour.
Hanamir sneaks into the room and silently kills one. Galadriel is
wracked with pain and feels her power diminish noticeably.

Harlan and Tannin both enter the room, not bothering to be stealthy. In
fact, Tannin tries to intimidate the spiders with a roar, but his voice
cracks instead. The spiders are not intimidated. They bite Harlan and
Tannin. Hanamir sneaks up to disable one of the spiders, and Harlan
knocks out another. They are careful not to kill them so as to avoid
harming Galadriel.

Frustrated with her own uselessness, Galadriel tries to shoot the last
spider, but some unseen force makes her hand slip, and the arrow hits
Hanamir. Tannin is still shaken from his unsuccessful roar. He tries to
punch a spider but hits himself in the face instead. Hanamir keeps his
cool in spite of the friendly fire lodged in his shoulder and knocks out
the last spider.

In the aftermath of this bungled battle, Harlan discovers a hole in the
floor hidden by one of the spiders. It contains a green orb of unknown
religious significance. He picks it up. In a brief vision, he sees a
troglodyte---a fearsome reptilian creature.


\chapter{Slaad Meets World}
\chapdesc{In the tower of spiders, can a one-armed man be king?}

After describing his brief vision of a troglodyte,
\href{/characters/harlan/}{Harlan} pockets the mysterious verdant orb,
and the party continues on through the tower of Lolth.

\href{/characters/hanamir/}{Hanamir} leads them down the next corridor.
It is lined with five flaming torches and one unlit torch. A staircase
at the end of the hallway is dripping with blood. Though Harlan and
\href{/characters/galadriel/}{Galadriel} inspect the torches and the
staircase for any signs of magical tampering, they find nothing, and
continue onward. What's a little blood in a spider tower? C'mon!

They proceed up the stairs to another torchlit hallway, but this time,
there's a door at the end, and they can hear voices echoing behind it.
It's a calm discussion in what sounds like Common. Harlan opens the
door---sneakily---and the party sees two goblins standing next to a
treasure chest.

``You been to Chez Goblin? Back in Goblintown? Best buffalo chicken
totchos in my entire life,'' one says. He's dressed in heavy dwarven
armor, clearly not made for him, and carries an enormous golden axe.

``No way, really?'' says the other. This one is dressed like a typical
goblin and carries a short sword.

``Yeah way. You really gotta go sometime.''

Our heroes bicker amongst themselves about what to do for several
minutes. Finally, Hanamir throws a dart and hits the normal-looking
goblin in the neck.

``Ow!'' says Dart Neck, and confers briefly with his friend in Goblin.
Then he shrugs. Heavy Armor reaches for his axe.

``Stop right there,'' says \href{/characters/tannin/}{Tannin}.

``Or what?'' says Heavy Armor.

Tannin indicates his javelin, and Heavy Armor chuckles.

``Are you sure about that? Don't you recognize this axe?''

``Nope!'' Harlan butts in. ``Should we recognize it?''

The goblin approaches and shows them the inscription on the golden axe:
it belongs to Abathor, the dwarven god of greed.

``Ohhhh, Abathor! Much respect for Abathor,'' says Harlan, trying to
whip up a rapport. ``Sorry about that dart. Our friend isn't quite
himself. Now, who are you fine gentlemen? What brings you to this Lolth
tower today?''

``We're adventurers,'' says Dart Neck. He plucks the dart out of his
gristly nape and regains some dignity. ``We procure fine and interesting
things and connect them to discerning buyers throughout the Forgotten
Realms. \href{/characters/sanford/}{Sanford} \& Son. I'm Sanford. He's
my son.''

Harlan's interest is piqued; the bargaining begins posthaste. The
goblins' inventory includes a set of playing cards, a robe, a blue hat,
a clear orb, some shackles, various potions, a silver breastplate, and a
ring.

``This ring? Grants protection to the wearer. 350 gold pieces. Can't
hurt,'' says Sanford. He points to the playing cards. ``Or perhaps for
any magically-inclined among you, a Deck of Illusions---nearly complete,
very rare, 500 gold.''

``What about those shackles?'' says Harlan.

``Dimensional Shackles,'' says the Son. ``Keeps a plane-shifting
creature stuck in one plane.''

``How much?'' says Harlan.

``Got anything you might want to sell to us for it?''

In an odd, disorienting moment, Tannin, Hanamir, and Galadriel find
themselves persuaded to leave Harlan alone with the goblins. They return
after a short while to learn that Harlan has sold a ``private heirloom''
to the goblins for enough gold to purchase the Dimensional Shackles.
Harlan doesn't elaborate on what went down, and the rest of the party is
just like, ``okay.''

``Nice doing business with you,'' says Harlan. ``Where are you headed?''

``Town of the Undead next,'' says Sanford. ``But before we go\ldots{}
any chance you'd want to sell us that pretty jade orb? Or that gauntlet?
Because if it's enchanted or cursed, we're very, very interested. You
might have seen our billboards along the forest path? WE BUY CURSED
GOODS?''

``Sorry,'' says Galadriel. ``I quite literally cannot remove it from my
body.'' Harlan also politely declines to part with the troglodyte orb,
even though they say they'd pay ten platinum pieces for it.

``All right, then,'' says Sanford. ``But if you change your mind, or
find any other orbs you might want to sell for a good price, you can
find us using this.'' He gives Harlan a plain-looking ring, and then the
two goblins pick up their treasure chest and head out.

The party continues up the stairs to a large cavernous room. There's
blood on the floor---some of it fresh, some of it old, some of it green.
There are two large metal doors on opposite walls. The floor slopes
upward in a staggered fashion, sort of like amphitheatre seating. At the
end of the room, there's another staircase up to the next floor. In one
corner, there is a pile of rags and six levers in the wall, all
different colors: white, black, gold, green, blue, and red. The gold one
is pulled down.

\emph{CRASH!} From another plane, a Death Slaad appears, roaring and
bleeding from a freshly-chopped-off arm. There is someone riding on its
back---it's \href{/characters/the-savage/}{the Savage}! And he's impaled
on a spike on the Slaad's back! Tannin throws his spear at the Slaad,
but misses and knocks the Savage to the ground instead.

``Stand back!'' shouts the Savage. Hanamir throws a dart, but it bounces
off the Slaad's hide.

In each of their minds, they hear a voice saying:
\texttt{GIVE\ UP\ NOW\ AND\ ILL\ SPARE\ YOU\ AFTER\ I\ EAT\ THIS\ ONE.}

The Slaad then shoots four fireballs at the Savage, but somehow misses.
The Savage swings his sword back and also misses. The Slaad chuckles and
then casually bites off the Savage's hand with the sword still clutched
in its grasp.

Galadriel casts Detect Thoughts on the Slaad. It is thinking about how
it is going to kill this guy and then kill everyone else, despite its
earlier psychic reassurance. She also learns it has been imprisoned a
long time, and is now freed, with one mission only: to kill. And it has
a gem in its brain that, if captured, would put the Slaad under the
capturer's control.

Harlan tries flipping the gold lever back upright, but it doesn't stay
put---once triggered, it's broken, it seems. Harlan then casts a fog
cloud that envelops the Slaad and the Savage in the middle of the room.

Tannin pulls down the white lever. One of the metal doors opens. From
that room, a Wyrmling appears---a baby red dragon, perhaps 15 years old.
``Dang!'' Tannin, having not learned his lesson, then pulls the green
lever. An ominous gear clicking sound starts coming from the ceiling.

The Savage does something in the fog cloud with the Death Slaad, but no
one can see what he does.

The Wyrmling stretches its heavy wings and approaches Hanamir. It snaps
its neck forward to bite him, but just misses. Boldly, Hanamir darts
forth and takes a quick stab at the Wyrmling with his short sword,
nicking its hide.

Galadriel starts Viciously Mocking the dragon, but it has no effect. She
then pulls the red lever impulsively and the lights come on.

Abruptly, the clicking noise stops, and ten arrows shoot down from the
ceiling. The Slaad and Harlan are each struck with two arrows, but
everyone else is spared.

``Welp, guess I'm doing this,'' says Harlan. He pulls the blue
lever\ldots{} and the floor in the center of the room drops away. For an
eerie moment, the Wyrmling and Hanamir float above the darkness before
falling down to a watery pit below.


\chapter{Hook, Line and Sinker}
\chapdesc{A battle of wits...and wyrms.}

Chaos reigns in the stone arena. The sound of the newly-amputee Savage's
struggle with the Death Slaad from within the fog does not inspire
confidence. The Wyrmling lets out a furious roar as it hits the water.

``\href{/characters/hanamir/}{Hanamir}!'' the party cries in unison,
dreading the horrible sound of dragon jaws ripping through armor like so
much metal cotton candy. But all they hear, for now, is splashing.

Each non-submerged member of the party leaps into action in a different
direction. \href{/characters/tannin/}{Tannin} rushes to the edge of the
pit, unrolling his rope down to give Hanamir a lifeline.
\href{/characters/galadriel/}{Galadriel}, by unnatural instinct, scales
the wall and perches on the ceiling. She casts a blindness spell on the
Wyrmling to buy them some time to regroup.
\href{/characters/harlan/}{Harlan} moves toward the fog cloud he
summoned, but turns his magic against the dragon, hurling a Sacred Flame
in its direction.

The Wyrmling is shocked and enraged. It unfurls its enormous wings and
beats the air in powerful bursts, rising from the water to hover in
mid-air. Steam surrounds its body like a shimmering veil. Still blind,
it falls silent in an attempt to locate its adversaries. It hears Tannin
say ``Almost there!'' as he pulls Hanamir up over the edge of the pit.
And then it hears two identical voices, rising in volume and
desperation.

Two people stumble out of the fog cloud, locked in a very well-matched
tussle. They both appear to be \href{/characters/the-savage/}{the
Savage}.

``That's the Slaad! I'm the real Savage! Kill it!'' says the one on the
left.

``No! No! It's taking my form, it's a shape shifter! Kill the other
one!'' says the one on the right.

Hanamir wrings out quite a bit of water from one of his sleeves and
assesses the two Savages calmly.

``Tell us about the last interaction you had with us,'' he challenges
them. ``Tell us about the ring.''

Before the Savage on the right can utter a word, the Savage on the left
tackles him. Hanamir rushes toward Harlan, and they both prepare to
intervene.

But the Wyrmling has heard enough. It blasts fire straight down upon
Harlan and Hanamir. The two adventurers fall to the ground and lie
there, motionless and smoldering.

This could be the end for our heroes, and Tannin and Galadriel know it.
From the ceiling, Galadriel fires an arrow at the dragon and pierces it
just behind its shoulder. It whips its head around, struggling to
pinpoint Galadriel's location.

Back on the floor, the real Savage shoots a lightning bolt from his hand
at the fake Savage, which instantly returns to its true Slaad form. It
is mortally injured, but it bites back at the Savage, who is bleeding
heavily from multiple grievous wounds himself. Tannin tosses his last
javelin at the Slaad and skewers it. It laughs its hideous laugh. It may
be close to death, but it makes sure to indicate its scorn for everyone
in the room.

The Wyrmling perks up at the sound of the javelin flying through the air
and snaps its teeth at the space right next to Tannin. He jumps out of
the way, but the dragon knows it got close.

Another arrow from Galadriel's crossbow hits the Wyrmling, but falls to
the ground. She scurries across the ceiling so the Wyrmling can't locate
her. From a new roost, she casts Healing Word on the Savage, whose
bleeding seems to slow. He uses his remaining arm to slice the Slaad,
and for a moment, it looks like it might be over for the Aberrant beast.
But then it summons a spiteful burst of energy and cold K.O.s the Savage
with a swing of its claw.

The Wyrmling's demeanor changes abruptly---it can see again. Tannin
turns to face it. He won't be roasted without a fight. At the same
moment, Tannin and the dragon both lunge at each other and miss.

Galadriel shoots one last arrow at the Slaad. It slumps to the floor,
finally dead. Nearby, Harlan groans. He's alive!

Tannin and the Wyrmling stare each other down in silence. It's maybe the
most badass moment in the quest so far, and Galadriel gets goosebumps
just watching from above. She makes a mental note to write a really cool
bard poem about it later, if she lives. In the meantime, she casts
Bardic Inspiration on Tannin.

The barbarian moves first, landing a mighty blow against the Wyrmling
with his battle axe. In retaliation, it takes a bite out of Tannin and
comes back with a bloody mouthful of dwarf armor.

Galadriel crawls along the ceiling to sit on the chandelier directly
above the action. She reaches behind herself to rummage through her
backpack, and gives \href{/characters/buddy/}{Buddy} the Pig a
reassuring pat on the head before taking out her lute. She starts
strumming a fast-paced, rhythmic tune, and the atmosphere in the battle
chamber shifts noticeably. Magically, in fact.

She addresses the Wyrmling and begins singing to it in Elvish. It's a
song so insulting, it's nigh untranslatable. There simply aren't
profanities obscene enough to express in Common what Galadriel sings to
this baby dragon---and if there were, you'd have to take a shower
afterward to wash off the shame of what you just heard. Imagine the most
humiliating and demeaning thing you could say to a juvenile fire
dinosaur, right to its face. It's shocking and, honestly, it's a bit
much. The Wyrmling suffers two points of psychic damage.

Galadriel's vicious mockery of the Wyrmling seems to help Harlan wake
up. Through the agonizing pain, he casts Healing Word on his very crispy
body and then brushes off some charcoal dust that used to be his outer
layer of skin. Good as new, sort of. He busies himself with the medicine
kit from his backpack and sets to work stabilizing the ultra-well-done,
char-broasted Hanamir beside him.

``We've got a pulse!'' reports Harlan after a few moments of vague
ministrations.

Hanamir sits up. He says nothing. His limbs make a disturbing crackling
sound as he rises to his feet, draws his sword, and straight up stabs
the Wyrmling. The dragon's blood spurts freely from the incision, but it
seems almost too surprised by the turn of events to react. Hanamir, now
drenched in dragon blood, lands two follow-up punches before the
Wyrmling finally recoils away from him. It hisses something in Draconic,
which Harlan promptly translates: \emph{The only way is to burn these
guys to a crisp.}

Galadriel now transitions her psychic assault on the Wyrmling from
mockery to something more sinister. There is no more musical
accompaniment; there is only a whispered spell that makes the dragon
shudder with anguish. Its eyes glow red.

Harlan takes the opportunity to slam the Wyrmling with his maul, dealing
serious damage. Tannin lodges his axe in the dragon's back. The Wyrmling
is losing control over its movements, but its eyes burn even brighter.
Its breath rattles in its throat, a rumble of flames building within.

But before it can exhale, Hanamir's sword cuts clean through its heart.
The Wyrmling falls to the floor, dead, a tendril of smoke rising from
its mouth.

---

No one says anything for a good long while. From the ceiling, Galadriel
coughs and brushes smoke away from her face. Hanamir is still sizzling
faintly. Over by the corpse of the Slaad, the Savage has woken up and
casts a healing spell on himself.

``So,'' he says, ``how'd you all find me?''

Galadriel creeps down the wall to join the group. ``Coincidence,
actually,'' she says. ``We're here to help save the Moon Festival.
Something in this tower is exerting an unholy influence on the moon.
Isn't that why you're here, too?''

``Not really,'' the Savage says, surprised. ``I heard there was a temple
of Lolth in this forest. I'm interested in what happened to the
followers of Lolth after they were driven from Eillin. Seems a few of
them ended up here.''

``Ahem. Aren't you going to thank us for saving you?'' says Harlan.

``Uh, thank you, I guess,'' says the Savage. ``But I had it under
control when you got here. You kind of\ldots{} made things
worse\ldots{}'' He looks directly at Tannin. ``And now I don't have an
arm. But we lived\ldots{} so.''

``You're welcome!'' says Tannin.

``I fought my way up through this tower. You probably saw the blood.
Killed some priests. Kept fighting until they took me here and threw the
gold switch and set this guy on me.'' He indicates the dead Slaad.

Hanamir finally speaks, his voice tight, as if pushing through an almost
unbearable amount of pain to form words. He smells like really good
barbecue, and everyone's thinking it but no one says it. He says:
``What's behind the other door?''

``I don't know,'' says the Savage. ``All I know is, I killed eight
priests. The two I didn't kill dragged me here and thought they'd let
the Aberration do their work for them. But of course, they didn't know
who I am.'' He smirks. ``So, the moon, huh? What's going on?''

``That's what we've been trying to determine,'' says Galadriel. She has
taken Buddy the Pig out of her backpack and holds him on her lap,
feeding him pieces of a granola bar that she accidentally smushed at the
bottom of the bag. ``It's being attacked on two fronts---one here and
one somewhere to the east. But here's what I don't get. Isn't Lolth the
mother of \href{/characters/eilistraee/}{Eilistraee}? The moon goddess?
Why would Lolth's followers be doing this to the daughter of their
goddess?''

``Ah, but Lolth \emph{hates} her daughter,'' says the Savage, as if this
were common knowledge. ``Anyway, I don't think Lolth is a powerful
enough deity to really do damage to the moon. If the Lolth priests are
in league with someone else, though, it's possible. Somewhere to the
east, you said?''

``Yes. Shargaas temple, we think,'' says Hanamir. A puddle of dragon
blood is forming at his feet, still dripping steadily from his hair.

``That'd do it,'' agrees the Savage. ``Interesting. I forget if I
mentioned this to you when we first met, but there's a city out that way
that was sealed up long ago to trap the undead inside. The Shargaas
folks keep trying to unseal the damn thing. This type of thing, the moon
thing, would be right up their alley.''

``Want to help us defeat them?'' says Galadriel. It might just be the
smoke in the air, but she kind of bats her eyelashes at him. ``We could
really use your help. You're like\ldots{} really strong and good at
fighting and stuff. Even with one arm, I'm sure you could take them all
down\ldots{}''

The Savage knows she's flattering him, but he is into it. ``Ahhhh, I
don't know about all that,'' he chuckles smugly. ``But here's what I can
tell you. Before they brought me to this arena, they kept me upstairs in
their barracks. There are probably six of them up there right now,
sleeping, if you want to take them by surprise.'' His eyes flicker to
the door. ``But listen, I really gotta get going. I need to, um, talk to
some people.''

``Wait,'' says Harlan, and takes the green orb out from his pocket.
``Before you go, do you know what this is?''

``Oh,'' nods the Savage. He digs in his own pockets. ``Yeah, I found two
more orbs just like that here. Onyx and pink pearl. Want them?''

``Yes,'' says Tannin. He reaches out to grab them from the Savage, but
the taller man holds them over Tannin's head, giving the black orb to
Harlan and the pink orb to Hanamir.

In a flash, Harlan sees a fish-like person. Hanamir sees Grumsh, the orc
god of storms.

``Aw, cool,'' says Tannin, obviously annoyed that he didn't get to have
a vision.

``Hey, one more thing,'' says the Savage. ``If the mother of this
Wyrmling ever finds out you killed her child\ldots{}'' He looks at
Hanamir head to toe. ``I just mean\ldots{} you definitely wouldn't be so
lucky in that encounter.''

Harlan wanders to the room where the dragon was held prisoner. The walls
are etched with the claw marks of a truly livid animal. The floor is
deeply cracked.

``What should we do with it?'' asks Galadriel. ``Hide it? Or are there
any uses for dragon scales, or\ldots?''

``I've fought a mature dragon and lived to tell the tale. Most people do
not. Dragons are very intelligent; they understand things we don't. If
this dragon finds you and you try to pull anything shady, it will almost
certainly know. If you could somehow convince it that the priests of
Lolth were responsible for the Wyrmling's death, you'd be off the hook.
But I don't recommend trying.'' He pauses. ``Just make sure it's never
found.''

``Is there nothing we can say to convince you to stay and help us?''
says Harlan. ``Any kind of a trade you might make?''

``What do you have?'' says the Savage.

``A sword,'' says Hanamir. ``We could tell you the location of a
sword.''

``What kind of sword?''

``A tiefling sword!'' says Galadriel. ``Owned by some warrior named
Valorius.''

``Wait. Valorius?'' The Savage sounds incredulous. ``How do you know?''

``Inscription on the blade,'' says Galadriel. ``Why, is it something
you'd want?''

``I mean, uhhhhhhh,'' sputters the Savage, ``if there were any chance
that's \emph{really} Valorius's sword, it's---I mean, it's a legendary
treasure. Value upwards of two hundred platinum.''

``Huh, really?'' says Tannin. ``It wasn't even enchanted or anything.''

``Doesn't need to be. You guys have never heard of Valorius? Where is
this thing?''

``It's in this hut, we met a tiefling---`` Galadriel starts, but Harlan
interrupts.

``Say you'll help us, and we'll tell you,'' says Harlan.

``A tiefling? Here? Alive? Did you all not notice the abundance of
deceased tieflings all over the place in this forest?'' The Savage looks
skeptical now. ``There are no living tieflings here. And no sword of
Valorius, either.''

``It's real,'' says Hanamir, and his stern quietude makes the Savage
interested again.

``Look, you don't have to come with us,'' concedes Harlan. ``But what if
we traded you the location of the sword for some more information, or
for a favor from that secret order you won't tell us about?''

The Savage hesitates, then says nothing. Galadriel is growing impatient.
She casts Detect Thoughts on the Savage.

``He really wants us to leave,'' she tells the party. ``He killed all
but \emph{one} priest of Lolth---there aren't six of them upstairs. He's
obsessed with this sword. He really wants to bargain with us for it but
doesn't want to betray his order if the sword's not really there.''

``Okay, fine,'' says the Savage, glaring at Galadriel. ``You tell me the
location of the sword. If I go, and find it, then sure, I'll tell you
something about my order or do you a favor or whatever. But if I go and
it's not there? My order will come to you. And you will not like it.''

``It was there when we left it,'' says Tannin. ``But someone could have
taken it by now.''

``Do we have a deal or not?'' says the Savage.

The party considers this a moment too long. The Savage gets impatient
himself and casts Detect Thoughts on them all.

``Huh,'' he says softly. ``How very interesting. Three of you seem
willing to make this trade with me in good faith. And one of you knows
the sword is not there. In fact, one of you sold it. And was going to
lead me on a wild goose chase---and have me betray my \emph{order} ---
for \emph{nothing}.''

He lets the news wash over them. There are murmurs of confusion and
surprise.

``Okay, look,'' starts Harlan. ``I was just---''

``What?!'' says Galadriel. ``You took it? That was your `private
heirloom' you sold?''

``It was just going to sit there under a floorboard!'' cries Harlan. ``I
mean, come on!''

``We agreed not to take it,'' says Hanamir, who---amazingly---is visibly
flushed with anger on top of his already gruesome burns.

``It got us the Dimensional Shackles!''

``Which we didn't use,'' says Tannin, who seems the least fazed by this
revelation.

``Yeah, but we \emph{might},'' says Harlan. ``I did it for us, and I
don't regret it! \href{/characters/magick/}{Magick} is never coming
back.''

``Congratulations, you played yourself,'' hisses the Savage through his
teeth. ``And you tried to play the Savage. And that just don't fly.''

``Oh, please,'' scoffs Harlan, starting to lose his own patience. He
straightens his back and stares down the Savage. ``I'm not trying to get
you to betray your order---you won't even tell us what your order
\emph{is}. And frankly, I think you would do well to consider us your
allies, because we just fought with you against two hellacious beasts
who wanted us all dead. I'm trying to be practical while \emph{all} of
you are being foolish, and meanwhile, our enemies get closer and closer
to reaching their goal of destroying the moon. And then we'll all be
sorry. There is a bigger picture here. So think about that, Savage!''

This quiets the party, but the Savage is unconvinced. He goes to the
body of the Slaad and slices open its stomach.

``I sold it to \href{/characters/sanford/}{Sanford} and Son,'' says
Harlan. ``They just left here with it earlier today. See? Is that a sign
of good faith?''

``That's nice,'' says the Savage. ``But it's too late.'' He rummages
inside the Slaad's guts until he finds what he's looking for: his
severed arm, still holding his sword. He waves it at them. ``Bye.''

Galadriel and Hanamir stand there, fuming---Hanamir literally---while
Tannin checks out the remaining locked door.

``Blah blah blah, bye forever, the Savage,'' he says. ``Anybody curious
what's behind this door?''

He puts his ear to it and knocks. An Orcish voice responds:

``WHEN ARE YOU GOING TO LET ME OUT OF HERE?!?!''


\chapter{Questions in the Dark}
\chapdesc{The Chillers stealthily ascend...into danger.}

\textbf{INT. LOLTH TOWER -- NIGHT}

The body of a wyrmling dragon lies dead on the stone floor, The remains
of a death slaad not far away. Our heroes stand outside the last closed
door. It is 1 a.m. on the day before the moon festival.

\textbf{Orc}: When are you going to let me out of here?!

\textbf{\href{/characters/hanamir/}{Hanamir}}: What do you think? Should
we rest, or talk to the orc?

\textbf{\href{/characters/harlan/}{Harlan}}: We should talk to the orc
first and then deal with the priest upstairs.

\textbf{\href{/characters/tannin/}{Tannin}}: Let's release the orc and
tell him to go upstairs and kill the priest while we take a rest.

the group ignores this idea.

\textbf{\href{/characters/galadriel/}{Galadriel}}: Orc first, then rest,
then priest.

\textbf{Hanamir}: All right. Here goes. (in Orcish) How ya doin',
brother?

\textbf{Orc}: I said, let me out of here.

\textbf{Hanamir}: Well, compadre, I need to know first who you're
working for and what brings you here.

\textbf{Orc}: I think you can tell I'm not working for these fools. So
just let me go and we'll sort this out when I'm out of here.

\textbf{Hanamir}: Are you interested in revenge?

\textbf{Orc}: Whatever! Just let me out!

\textbf{Hanamir}: I'll make a deal with you: there are some priests
upstairs, the guys who locked you up\ldots{}

\textbf{Orc}: I'm not going head to head with a priest of Lolth. How do
you think I wound up in here?

\textbf{Harlan}: Ask if there is anything he can offer us in exchange
for letting him out.

\textbf{Hanamir}: Yeah. Is there anything you can offer us in exchange
for letting you out?

\textbf{Orc}: I'm your fellow orc! Let me out!

\textbf{Hanamir}: Ahem. My friends and I will discuss it. Thanks for
your time.

The orc can be heard punching the wall.

\textbf{Hanamir}: (in Common) I see no reason to let him out.

\textbf{Tannin}: We should totally let him out.

\textbf{Galadriel}: I think we should at least try and do more talking
first. Maybe get to know him, ask him his name\ldots{} relate to him on
a personal level! You're brothers!

\textbf{Hanamir}: Half-brothers. And the orcs we've met so far have all
been antagonists. This guy is coy about who he's working for, and I
don't trust him.

\textbf{Harlan}: Maybe ask him how he got here, and see what his side of
the story is. Do a good cop bad cop scenario.

\textbf{Hanamir}: (in Orcish) So what's your story? I'm a loose cannon,
myself.

\textbf{Orc}: I was doing some favors for these people, so I was working
for them at one point\ldots{} and look, things went south, and I just
need to get back to where I came from. That's all I ask.

\textbf{Hanamir}: Do you know about any books?

\textbf{Orc}: \ldots\ldots\ldots..what kind of books?

\textbf{Hanamir}: Any kind of books. Maybe books getting picked up off a
caravan?

\textbf{Orc}: Okay\ldots{} I didn't realize they belonged to the
university. I don't have the books. I can tell you what happened to them
if you let me out.

\textbf{Hanamir}: I'll let you out. And you're gonna walk free, and
you'll tell your boss that Hanamir wants his books back. Hanamir's
comin'.

\textbf{Orc}: It's a deal.

\textbf{Hanamir}: (in Common) Will the rest of you find a good place to
stand so you can ambush him in case he turns on me?

the group readies itself. Galadriel climbs up the wall to sit above the
door.

\textbf{Harlan}: You know what I'll do? I'll cast Locate Object on the
Shargaas amulet. You give it to him, and we can track him that way.

\textbf{Hanamir}: Good idea.

Hanamir arranges the scene so that he's standing with one foot casually
resting on the body of the slaad. He pulls the last lever to open the
door, releasing the orc.

A somewhat bloodied orc emerges. He wears armor; he's a warrior.

\textbf{Orc}: Here's the situation. We had to sacrifice some of your
books. As you may know, Shargaas demands tribute of stolen goods, and we
figured it was an easy way to sacrifice something to him.

\textbf{Hanamir}: You figured wrong, brother.

\textbf{Orc}: Are we going to hold to the bargain?

\textbf{Hanamir}: Yes. Hanamir keeps his word. (he throws the orc the
amulet.) Take this and remember to tell your boss\ldots{} Hanamir's
coming.

\textbf{Orc}: Where did you get this?

\textbf{Hanamir}: It doesn't matter.

\textbf{Orc}: Well, you held up your end of the deal, I'll hold up mine
and be on my way\ldots Good luck with \href{/characters/cazna/}{Cazna}.
\emph{(he leaves)}

The group checks the orc's cell. It smells pretty bad. Some rat
bones\ldots not too much else in there worthy of reporting. It seems he
had been in there a week or two.

The group takes a short rest, restoring some energy and vitality.
Hanamir is still not feeling his best, but the rest of the party is much
better.

Looking down into the pit, Harlan notices something shiny. Hanamir dives
in to retrieve it.

\textbf{Hanamir}: \emph{(voice echoing in the water)} Aha. I can easily
identify this as a piece of azurite.

Hanamir climbs back up.

\textbf{Hanamir}: Check this out. Showed me a shark guy. \emph{(he
refers to a sahuagin, a shark-like creature)}

\textbf{Harlan}: I'm nervous about what we're supposed to do with these
orbs.

\textbf{Hanamir}: I think they're related to planes\ldots{} Gruumsh
lives in another plane, shark people in the water plane\ldots{}

\textbf{Galadriel}: Why does water get its own plane?

\textbf{Hanamir}: There are planes for lots of elements. This is common
knowledge.

\textbf{Galadriel}: Sounds fake, but ok.

\textbf{Harlan}: Can we deal with this priest please??

\textbf{Tannin}: First let's hide the dragon. Are we all in on this
murder? Everyone's fingerprints should be on it so that we're bound to
it. And no stealing any scales.

They look pointedly at Harlan.

The group pushes the dragon into the watery pit and then closes it. They
are aware that this may have been the water supply of the residents of
the tower and that the water will now be contaminated with dragon
cholera, also known as flaming dysentery.

The group heads upstairs. Hanamir sneaks up first, as usual. They enter
a long, straight hallway. There are several doors: the ones on immediate
left and right are closed. There is an open door further down the
hallway.

Hanamir goes to nearest door and tries to perceive any obvious traps. No
traps; the area is well-trafficked; the floor is grooved from lots of
people walking around.

Hanamir then opens the door on the right. It opens easily. He uses swat
team hand signals that they went over during the short rest to encourage
the group to follow him.

The room is a bedroom with cots and a bathroom in the back. Otherwise,
the room is empty and unremarkable.

\textbf{Harlan}: \emph{(whispering)} Let's close the door and search
this room.

\textbf{Galadriel}: Or, close the door and take a long rest for the
entire night. I need my spells back.

\textbf{Harlan}: That's risky\ldots{} we could get interrupted.

\textbf{Hanamir}: Yeah, we should keep going.

\textbf{Tannin}: We should try and silently murder everyone on this
floor.

They search the room, only finding some drow clothing. Hanamir puts on a
drow robe. It's tight.

\textbf{Hanamir}: What's a good thing to say to somebody in the dark
that would make them think you're an elf?

\textbf{Galadriel}: \emph{I amar prestar aen. Han mathon ne nen.} ``The
world has changed. I can feel it in the water.''

\textbf{Hanamir}: Cool.

The group discusses the origin of drow, or dark elves, and concludes
it's a description of their alignment. They are mostly devoted to lolth,
but some are not. They generally speak elvish and common. Some drow
speak undercommon, and when they do, it is with a heavy australian
accent.

Hanamir goes to the next closed door. He nudges it open. It's a smaller
room, single bed in it, with a drow sleeping in it.

She wakes up and notices Hanamir. Hanamir pulls the drow robe up over
his face as much as he can.

\textbf{Hanamir}: \emph{(in Elvish)} The world has changed. I can feel
it in the water.

\textbf{Drow}: \emph{(in Elvish)} What?

Hanamir attempts to knock her out. He hits her but she's still
conscious, though bloodied. He hits her again and succeeds in
restraining her. The group closes the door.

\textbf{Tannin}: How many of you are on this floor?

\textbf{Drow}: Twelve of us in this tower.

\textbf{Tannin}: How many on this floor?

\textbf{Drow}: \ldots How many have you killed?

\textbf{Tannin}: No one yet. Are you a priest?

Galadriel, looking around, determines that this drow is a powerful
figure.

\textbf{Galadriel}: \emph{(in Elvish)} We don't have to hurt you. But we
need to know what's going on with the moon.

\textbf{Drow}: You're far too late to interfere.

\textbf{Galadriel}: Why's that?

\textbf{Drow}: We've already cast the binding magic.

\textbf{Galadriel}: What kind of magic?

\textbf{Drow}: Why should I cooperate with you?

\textbf{Tannin}: How many priests do we need to kill to stop this magic?

\textbf{Drow}: I thought you hadn't killed anyone yet?

\textbf{Tannin}: \ldots How many more priests do we need to kill to stop
this magic?

\textbf{Drow}: Look, what do you want?

\textbf{Galadriel}: We're here to save the moon.

\textbf{Drow}: I told you, you're too late for that. If that's what
you're here for, just kill me.

\textbf{Galadriel}: At least describe to us what you did to the moon.

\textbf{Drow}: I didn't do it.

\textbf{Galadriel}: Then who did?

\textbf{Drow}: Again, why should I cooperate? I'm not afraid to die at
this point. I've fulfilled my mission.

\textbf{Galadriel}: (she casts charm person on the drow priestess, but
it doesn't work.) Okay, fine. I need you to help me out, sister. I've
got a gauntlet that might belong to you.

\textbf{Drow}: (interested) Where'd you get that?

\textbf{Galadriel}: From my pig.

\textbf{Drow}: What?

\textbf{Galadriel}: (turns around to show
\href{/characters/buddy/}{buddy} peeking out of her backpack, chewing on
the drawstrings) This is Buddy. He had eaten the gauntlet, I don't know
where he got it. We made him throw up, and then I put it on.

\textbf{Drow}: So that pig ate a priest of Lolth???

\textbf{Galadriel}: No, I don't think Buddy ate a person.

\textbf{Drow}: These are only worn by priests of Lolth.

\textbf{Galadriel}: Yeah, but he probably ate it off the ground
somewhere.

\textbf{Drow}: I'm not sure that pig is what you think it is.

\textbf{Galadriel}: I'm pretty sure he's an adorable pig and I'm pretty
sure he's my best friend.

\textbf{Drow}: Okay, well, I'll take the gauntlet. If you don't want it.

\textbf{Galadriel}: I do want it! I just don't like being able to not
fight spiders when necessary. Is there anything you can do about that?

\textbf{Drow}: Yeah, absolutely.

\textbf{Galadriel}: What can you do?

\textbf{Drow}: If you just take it off, I'll fix it.

\textbf{Galadriel}: I can't take it off.

\textbf{Drow}: Oh, I can take it off you no problem.

Galadriel notices that the drow is fidgeting with something and staring
at the gauntlet, clearly coveting it. Tannin, Hanamir, and Harlan make
moves to draw their weapons.

\textbf{Galadriel}: Hey, one more thing, is there anything you can tell
me about these orbs? (she indicates the azurite, onyx, pink pearl, and
jade.)

\textbf{Drow}: Again, I understand I'm being held hostage, but what
exactly am I getting out of this if I tell you anything?

\textbf{Harlan}: What about your life?

\textbf{Drow}: What guarantee do I have that you won't just kill me
anyway?

\textbf{Harlan}: We let the orc go.

\textbf{Drow}: You let him go?! All right, then, you might as well kill
me.

\textbf{Galadriel}: Who was he? Give us the deets!

\textbf{Drow}: He was a spy for Shargaas.

\textbf{Galadriel}: Aren't you in league with Shargaas?

\textbf{Drow}: We were\ldots until they double crossed us.

\textbf{Galadriel}: So now Shargaas is\ldots protecting the moon?

\textbf{Drow}: No, they're still going through with that, but they
double crossed us. \emph{(she pauses)} You guys are in over your heads.

\textbf{Harlan}: She's onto us.

\textbf{Drow}: Cazna and the followers of Shargaas both needed
\href{/characters/eilistraee/}{Eilistraee} out of the way.

\textbf{Galadriel}: Who's Cazna?

\textbf{Drow}: The high priestess of this temple.

\textbf{Galadriel}: That's not you?

\textbf{Drow}: No.

\textbf{Harlan}: And where is she?

\textbf{Drow}: In her chambers.

\textbf{Galadriel}: Or she's dead.

\textbf{Tannin}: You think? I think she's at the top of the tower.

\textbf{Drow}: Yeah, she's at the top. In her chambers. \emph{(she
pauses)} If you all let out that spy\ldots{} there are gonna be orcs
here in a matter of hours.

\textbf{Tannin}: Aw.

\textbf{Harlan}: And you don't want to be here when that happens. So
tell us what we want to know, and we'll let you live. We'll let you go.

\textbf{Drow}: \ldots We had a plan. We thought the Shargaas followers
wanted to destroy the city so that they could unseal the city of the
dead. We wanted the city for ourselves again because we were run out of
town. We discovered that they were infiltrating this tower so that as
soon as Eilistraee was destroyed, they would kill us before we could
take the town, because apparently that interferes with their plans.

\textbf{Harlan}: And these orbs?

\textbf{Drow}: They have religious meaning to us. They represent false
gods.

\textbf{Harlan}: What do you do with them?

\textbf{Drow}: We stole them from followers of false gods as proof of
our superiority over them. You can sell them on the black market. You
can have them.

\textbf{Galadriel}: We have them already, lol.

\textbf{Drow}: Let me go now.

\textbf{Harlan}: Any other information? This is the time.

\textbf{Galadriel}: What do you think my pig is?

\textbf{Drow}: Something that could've eaten a high priest of Lolth.

\textbf{Galadriel}: Like what? What are the main predators of high
priests of Lolth? Where on the food chain do they fall?

\textbf{Drow}: I really don't know, but I'm concerned.

Hanamir tries to knock out the priestess, but she plane-shifts outta
here. She had apparently been fidgeting with a plane-shifting fidget
spinner.

The group quickly searches the room. There is a chest containing: 4
carved bone statuettes (a spider, a drow, a dragon, some trees), a
copper chalice with silver filigree, and 2 embroidered silk
handkerchiefs. Galadriel considers checking these items for magic, rolls
a 1, and thinks to herself ``it's magical that there are bones inside
all of us,'' and forgets to do an actual check. Buddy sniffs the
statues.

They each take a statue and divvy up the handkerchiefs and chalice
(Galadriel takes none because gauntlet). Hanamir suggests Galadriel
steal a priestess robe; she does.

They go back to the hallway and enter the next room with the open door.
it's set up like a jail cell, not decorated like the other rooms. this
is a place for prisoners, but there's no one inside.

Down the hallway, there's an archway leading to another room, and there
are two more closed doors on the left. they check out the archway. it
leads to a dining hall with two long wooden tables. at the end there's a
stone altar with three lit torches above it. other than that, it's
empty. Hanamir encourages Galadriel to check the altar for magic. she
determines that the pot roast that they serve there is pretty magical.
Hanamir eats some and it's delicious. is it made of human? we don't
know.

They move on to the next door, which is locked. Hanamir tries to pick
the lock with his thieves' tools. Harlan casts guidance of
\href{/characters/kord/}{kord} on him. Hanamir succeeds in picking the
lock.

Inside the room, there are three people sleeping: two drow dressed in
shabby clothes, and one non-drow elf. it's hard to tell if they're
prisoners or there by choice. one drow is dressed in white, the other in
a black robe. the non-drow elf is dressed in rags.

They notice a lute under the bed. Galadriel tries to see if it's cool,
or at least better than the one she already has, but can't tell.
Hanamir, with elaborate hand gestures, to team: kill them, or just keep
them locked up?

\textbf{Galadriel}: Let's dimensional-shackle two of the prisoners
together, so they can't plane shift and it's harder for them to fight
us.

\textbf{Harlan}: Let's check out the one remaining room first.

So they leave and check the other door. Hanamir picks the lock on the
door.

In this room, there are two drow sleeping. On the wall there is a
shortsword, and in a pile at the foot of the bed, there's some armor.
Hanamir checks out the sword to see if it is cool. It is not.

\textbf{Hanamir}: (with silent hand signals) Murder time?

\textbf{Galadriel}: (with silent hand signals) I think these two are
wardens, the other three are prisoners.

\textbf{Hanamir}: (with silent hand signals) Okay, when I give the
signal, you sneak in and murder one of these guys with me.

Galadriel stealths in, leaving buddy in the hallway. Tannin is giving
buddy the major side-eye.

Galadriel stabs one of the drow wardens in the neck with her shortsword
and kills him. Hanamir tries but fails to kill the other one. He then
tries to put the warden in a half-nelson, but the warden breaks free.

Galadriel tries to stab him, but misses. She casts bardic inspiration on
Tannin. Tannin enters the room with a reckless attack and wallops the
warden with his battle axe. Harlan charges in after and hits him with
his hammer.

The drow warrior levitates out of the bed, 20 feet up.

\textbf{WARRIOR}: \emph{(to Galadriel)} Why are you doing this?

\textbf{Galadriel}: `Cause we're trying to save the moon, man! (she
remembers she is dressed as a priestess.) I mean, because I'm bad to the
bone!

\textbf{Hanamir}: \emph{(in Elvish)} The world has changed. I can feel
it in the water.

Hanamir throws a dart at the warrior. Galadriel climbs up the wall and
stabs him with her shortsword, killing him. he falls back into his bed.
a ring of keys falls out of his pocket.

Hanamir takes the keys.

They leave the room. Hanamir uses the keys to lock the door where the
other three are sleeping. The group heads back to the dining hall and
inspects a locked iron door inside. Hanamir uses the keys to open it. It
leads to a store room containing yet more pot roast, and also treasure.

Hanamir opens a chest. It contains roughly 650 gold pieces' worth of
small gems.

Galadriel opens the next one. She finds a ioun stone of protection. When
tossed in the air, it orbits one's head and increases one's armor class.

Harlan opens a chest to find 1400 copper pieces and 35 electrum. It's
super heavy and now he has to drag it around. Is it karma? who can say?

Tannin opens the last one. Inside is an exquisite collection of
treasures: an enormous gold bracelet, a trident of fish command, and an
ever-smoking bottle. Tannin wears the gold chain as a necklace and
marvels at his new aquaman powers. He tosses the smoke bottle to
Hanamir, since sneaking's not really his style.

Back in the dining hall, a voice can be heard.

\textbf{VOICE}: Hello?


\chapter{The Disappearing Dwarf}
\chapdesc{Our heroes once more become a triad.}

\href{/characters/galadriel/}{Galadriel} is tuning her lute. She looks
up.

``Oh! Lolth's legs!''

You intuit that this is a new exclamation of surprise that she's trying
out.

``Didn't see you there. Yes, please, come in. Pour yourself a tankard of
\href{/characters/fleck/}{Fleck}'s finest Eillin ale.''

She takes a sip.

``Folks, I'm glad you turned up just now. It has been COUGHcough weeks
since the last time I recounted our tale. But I think it's time, don't
you? Pull up a chair. I invite you to come with me on a journey of
danger and delights---and reminisce with me on some of the more recent
highlights of our quest.''

She conjures a wavy flashback border before your eyes and begins to
strum her lute.

``Who could forget where we left off? Surely not I!'' She thinks for a
long moment. ``Oh, yup. We were in the Tower of Lolth\ldots{}''

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

The wavy flashback border expands, and within it you see
\href{/characters/hanamir/}{Hanamir},
\href{/characters/harlan/}{Harlan}, \href{/characters/tannin/}{Tannin},
and Galadriel in the dining hall, each inspecting their new treasures.
Tannin puts on his sick new chunky gold chain necklace and brandishes
his trident. Harlan stares sullenly at his burlap sack full of copper
pieces. The smell of that exquisite pot roast is in the air.

``Hello?'' comes a voice from down the hall.

Our heroes spring into pantomime. Hanamir disappears behind the treasure
room door. Harlan and Tannin pretend to be shackled together, while
Galadriel, still dressed in drow robes, pushes them ahead of her as if
she has just captured them. They confront two guards in the hallway.

``What's going on here?'' one of them, dressed in leather studded armor,
asks.

``I found these two miscreants desecrating our temple. I am taking them
to the arena to face justice,'' says Galadriel, using her best ``stern
priestess'' voice.

``Nice. Can we watch?'' asks the other one.

``Uh, yes,'' says Galadriel. ``It'll be really gross. You'll love it.''

``Cool,'' says the armored guard. ``Where's Drada?''

``Oh, she's fine,'' says Galadriel. ``She\ldots{} went out to run an
errand.''

Somehow, the guards buy this.

``Let's bring the other prisoners, too,'' one of them suggests.

``Yes! The more the merrier. I mean, the more the bloodier,'' says
Galadriel, chuckling. ``Lolth will be pleased with this tribute.''

When the guards turn away to unlock the prisoners' room, Galadriel
signals to Harlan and Tannin that it's time to attack. Hanamir emerges
from his hiding place as if materializing out of the ether.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

The wavy flashback border around this scene grows thicker and hazier
before your eyes. You can see Galadriel in the present again, and she
smiles, though a tinge of pain is in her eyes.

``Ah, a great battle! And a terrible one,'' she sighs. ``It was in this
confrontation that our dwarven friend, Tannin, fell unconscious.
And\ldots we didn't get a chance to speak to him after that.''

She gazes at the floor, maybe feeling a little guilty.

``We spared one of the guards. I took his super sweet leather studded
armor for myself, and he gave us information about the rest of the tower
in exchange for his life. He told us that there's a floor of eternal
darkness above us, and a prayer room above that, which can only be
accessed by manipulating the lights in other levels of the tower. And he
let us know that the priestess who got away probably just made herself
invisible.''

Galadriel plays a minor chord on the lute.

``But when we finished fleecing this jabroni, we saw that Tannin had
disappeared. There was an empty vial of
\href{/characters/magick/}{Magick}'s plane-shifting potion lying on the
floor where he had been.''

She raises her tankard of Fleck's Eillin ale in a toast.

``To Tannin! A loyal friend and fearsome barbarian. Wherever he is, may
he be doing what he loves: holding dominion over all marine life, and
flying into a destructive rage whenever necessary.''

She drinks deeply, then gestures back at the original flashback window.

``After that, we spoke to the three prisoners who had been locked away
by the fiendish followers of Lolth.''

``We met Tallis, \href{/characters/feld/}{Feld}, and Hillbloo. They
seemed nice. We learned that Feld is the cousin of H'Jun, the drunkard
from Eillin. He has a lot of heart, but he's not a very good bard. We
let them go on their way, and decided to search the tower for anything
we'd missed.''

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

In the flashback portal, you then see the adventurers roaming through
the tower, looking for clues in the places they'd fought through. They
find a key fashioned of bone underneath the bed of one of the guards
they killed. Hanamir finds a red garnet orb in a statue of a bugbear on
the wall of the arena where they fought the Wyrmling. He also suffers
intense chills from the white pearl orb he is holding. They extinguish
the torches in the lower floors of the tower, following the instructions
of the guard whose life they spared. They continue on to the Eternal
Darkness floor and start following a murky maze.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

``Oh, and here's one of my favorite parts!'' Galadriel grins.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

You watch as Hanamir tosses Galadriel into the impenetrable blackness
alongside the path. Galadriel lets out a victorious ululation when she
lands, unharmed, on the wall, and climbs up to the ceiling to survey the
maze from above. She guides them safely to the other side, and an entire
booby-trapped level of dangerous gameplay is skipped entirely.

``Next we take a long rest, so I'm going to fast-forward through that
part.'' With a wave of her hand, the flashback portal zips through
several hours of footage in which the trio struggle to get comfortable
on the icy floors of the Lolth tower. ``Now, okay, we're about to enter
the Prayer Room, which is this asterisk-shaped room where each point is
a hallway ending with a statue of a god.''

You see Harlan approach the statue of the Troglodyte god with the jade
orb. He communes with the god, who asks for his orb back in exchange for
some information. Harlan demurs, and consults with the party.

All the gods seem to be evil-aligned. The party decides to have
Galadriel talk with the shark god, who at least is lawful evil. She
returns with some fairly banal advice, which is that there are eight
gods in the room, and that they must find them all to do what they seek.
So, they need to find all the orbs.

You watch as they search the tower a second time. They return to the
arena and retrieve the body of the Wyrmling. It's a grisly scene as they
hack the corpse apart searching for the final orb to complete their
collection, and they don't even find anything except a deeper sense of
shame.

When they finally make their way to the floor with all the bedrooms,
they find a secret compartment that is unlocked by the bone key they
found earlier. Harlan looks inside and finds the last orb, belonging to
a fire giant god.

They return to the prayer room. The Troglodyte god is angry with Harlan.

``I'm tired of waiting,'' he says, invading Harlan's mind with a voice
like ancient stone. ``You said we could make a deal.''

``What can you give us that will help us save the moon?'' says the
cleric.

``I am the God of Hunger. I will give you this satchel. Each day, you
may take food from this satchel, and it will heal you of your wounds.''

Harlan takes it, and places the jade orb in the mouth of the Troglodyte
statue. It disappears.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

The flashback portal fades from sharp color to hazy desaturation, and
Galadriel waves it away.

``A dangerous trade? Who can say?'' she shrugs. ``Join me after these
messages for the next chapter of our adventure. Until then, I will be
here, knitting a sweater for my adorable best friend,
\href{/characters/buddy/}{Buddy} the Pig.''

At the sound of his name, Buddy waddles over to Galadriel from another
room. She scoops him up and sets him in her lap, and he proceeds to lick
her face.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

Commercial break. Two goblins in ill-fitting suits address the camera.

``You got potions? We buy potions.''

``You got cursed amulets? We love cursed amulets.''

``Don't want to deal with the hassle of an arcane inheritance? We will
take that mess off your hands, no questions asked.''

``Good credit, bad credit, bad credit from another dimension, we don't
care. We will make you a deal that will leave you saying: `Look at this
cool stuff I bought.'\,''

``Just ask for \href{/characters/sanford/}{Sanford} \& Son. Buyers and
sellers of the most fascinating antiques, collectibles, and magical
artifacts on the continent.''

``Sanford \& Son: If you need to find us, we'll probably be somewhere.''

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}


\chapter{The Matriarch and the Handmaiden}
\chapdesc{A deal is struck...at what cost?}

``Welcome back,'' says \href{/characters/galadriel/}{Galadriel}. ``It is
now time for us to tell the tale of what happened in the final hours
before the Moon Festival. The culmination of all that our humble
questing party has worked for, thus far. The showdown that would become
legendary amongst the gods.''

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

She conjures a new flashback window. In it, you can see
\href{/characters/hanamir/}{Hanamir},
\href{/characters/harlan/}{Harlan}, and Galadriel standing in the Prayer
Room, discussing their course of action. You see Hanamir take the pink
pearl orb and approach the statue of the orc god, Gruumsh. He falls into
a trance. Harlan and Galadriel stand in the center of the room and peer
at him cautiously. After a few moments, Hanamir places the pink pearl
orb in the statue, and it evaporates. He returns to his companions and
presents a book.

``Gruumsh gave me this,'' he says, pleased as punch.

``Was he nice? Was he dreamy?'' asks Harlan.

``Yes. Very strong looking. I felt safe.'' Hanamir flips through the
book's pages.

``And books are your favorite! An unlikely gift from an orc god,'' says
Galadriel.

``Yes. He doesn't quite understand, but he knows I am particular about
my books,'' says Hanamir. ``I told him Shargaas is attacking the moon.
He didn't know, and he was displeased. I asked him what we can do to
help. His advice was to kill the priestess,
\href{/characters/cazna/}{Cazna}, and not to trust Tiamat.''

``The dragon god?'' says Harlan. ``That's not one of our orbs.''

``What does the book say?'' says Galadriel.

``It's all about planes,'' Hanamir says, skimming pages. The book is
called The Big Book of Planes. ``Some places exist between planes. `Have
fun,' it says.''

``So what now?'' says Harlan. ``Another orb, another god, hopefully
another piece of information?''

``I don't know that we have any other options,'' says Galadriel.

Harlan takes the fire giant orb to its corresponding statue and returns
with nothing in his hands.

``I didn't get a material gift this time, but I did get some
information,'' he says. ``This fire giant god---very intimidating
guy---really hates Lolth. He is very much rooting for us and against
her. He says that Cazna is protected by a barrier that is impenetrable
by force or magic. It will hold as long as she concentrates on her
spell. So he advised us not to waste our energy trying to break down the
barrier.'' He pauses. ``I also asked him how to get to the top of the
tower. He said we'd need to speak to Tiamat about that.''

``But---'' starts Galadriel, eyes wide.

``I know. Who do we trust on the topic of the evil dragon god? The evil
orc god or the evil fire giant god?'' muses Harlan.

``Hard to say,'' says Hanamir, though he seems unfocused on the
conversation, as he's still skimming his book on planes.

``If we were to try and speak to Tiamat,'' says Harlan, ``how might we
do that? Through the divot in the center of the room? And without an
orb, what would we offer up to him?''

His eyes drift toward Galadriel's backpack, where
\href{/characters/buddy/}{Buddy}'s face can be seen peeking out of the
top. The pig snorts contentedly.

``Watch it,'' snaps Galadriel. ``Don't you have a god of your own you
could ask for wisdom?''

``That's true,'' says Harlan. ``Worth a try, anyway.''

Harlan kneels and begins to pray. Hanamir and Galadriel aren't sure if
it's their imagination, or if they are hearing distant claps of thunder
from beyond the tower walls. A faint mist rises around Harlan,
condensing into a cloud above all of them that flickers with
electricity.

``Didn't we just talk?'' comes a voice from within the cloud. It sounds
like heavy rainfall and roaring wind.

``O Stormy Father,'' says Harlan, head bowed, ``I thank you. I do not
take your time and wisdom for granted. I have been following your
instructions, and I find myself stymied at this juncture. I beseech you
to bless us with any wisdom you might possess regarding our path
forward.''

Thunder rattles the entire room. Galadriel and Hanamir share a nervous
look.

``I sense many trapped souls where you are,'' says the Voice of
\href{/characters/kord/}{Kord}. ``Souls of evil beings.''

``Yes, we found them encased in gemstone orbs, littered throughout this
tower,'' says Harlan.

``And what have you been doing with them?'' booms Kord.

``Well, we thought that, uh, perhaps\ldots{}''

``Remember, I am your god,'' says Kord.

``We've, uh, we've returned a few of them\ldots{}''

``\ldots To their evil owners.''

``In furtherance of our quest! To save the Moon!'' Harlan bows even
deeper.

``Hm,'' snorts Kord, with a crackle of lightning. ``I'm not really a
Moon guy.''

``Well, hey, the Moon has an impact on the tides, affecting the
weather\ldots{}''

``I have an impact on the tides and the weather!'' roars Kord.

``Absolutely, your Holiness, I just thought maybe you got a bit of an
assist from the Moon---''

``I don't need a Moon assist! I'm the God of Storms!'' The tower itself
seems to vibrate in another roll of thunder.

``Of course, my lord. Of course. I humbly ask your forgiveness. And if I
am misinterpreting any of your guidance, I would like to be corrected. I
only pray that you give us direction toward the successful completion of
our quest. The Moon is in peril, and its absence would affect all who
inhabit this land.''

There is a long silence, punctuated only with flickers of light from
within the cloud.

``My advice? These orbs you possess are worth a great deal of human
gold. Go sell them and be prosperous. Do not give them back to evil
gods.''

``Understood. Understood,'' says Harlan. ``And how might we reach the
top of the tower? And kill Cazna?''

``I know nothing of that.''

``Anything about Tiamat?'' Harlan tries.

``Tiamat? The god of the chromatic dragons?''

``That's the one,'' says Harlan. ``We were told to seek help from him.''

``Who told you to seek the aid of Tiamat?!'' Kord's voice smacks into
them all like a freezing ocean wave. ``What kind of sadistic joke were
they playing on you?''

``One of the other gods here,'' says Harlan.

``An evil god.''

``We've had conflicting reports from multiple evil gods, sir,'' Harlan
mutters.

``Well, listen to your god now. If there is a follower of Tiamat here,
do not give their soul back to Tiamat. Do not do that.''

``Understood, my lord,'' says Harlan. ``And what about this divot in the
floor here? Is there a god here crying out for souls?''

``What divot?'' asks Kord.

A great hissing sound erupts from the cloud, and it disappears into a
trail of vapor. Before their eyes, the party sees that there is no
longer an indentation in the center of the room. In its place, there is
a statue of a five-headed dragon. It is Tiamat.

``Thank you, my lord!''

``Hmph. I wish you had more parents I could kill,'' the voice of Kord
echoes near the ceiling. ``I thought it would teach you not to rely on
others.''

``I, uh, wish that too, your holiness,'' says Harlan.

``Thanks for groveling. I have some things I gotta go doooo\ldots{}''
Kord's absence is immediate and smells like tall grass after the rain.

Letting a solemn silence pass, Galadriel approaches the statue of Tiamat
and senses its arcane power.

``It wants a soul very badly,'' she murmurs. ``Any soul will do.''

``Well, I hate to sound callous,'' says Harlan, dusting himself off as
he stands, ``but if we don't want to give it an orb, and none of us want
to be sacrificed\ldots{}''

``Yes?'' prompts Hanamir, genuinely not following.

``Well\ldots{}'' says Harlan, glancing again at Buddy in Galadriel's
backpack.

``Oh, are you suggesting we murder my best friend again?'' she snarls.

``I would never!'' Harlan feigns shock. ``But since you brought it
up\ldots{}''

``Would a pig have a soul that would satisfy a dragon god?'' Hanamir
wonders.

``As a cleric, I---''

``If it comes down to it, Harlan, I will fight you.'' Galadriel clenches
her fists and stares him down.

``I was going to say, as a cleric, I can check to see if pigs even have
souls.''

He holds out a hand over Buddy's sweet noggin. Upon grazing the
baby-soft peachfuzz atop Buddy's precious noodle, Harlan suddenly
understands the eternal struggle of what it is to be a pig; he has seen
all of the porcine condition in its infinite shades of meaning. He jumps
back, utterly repulsed by the idea of sacrificing this creature.

``Pigs really super do have souls,'' he concludes, a bit shaken.

``Damn right,'' says Galadriel.

``So what now?'' says Hanamir. They stare at each other.

``I\ldots{} could talk to Lolth,'' Galadriel says, finally, holding out
her gauntleted wrist like a foreign object. They all look at it in
silence.

Without further discussion, Galadriel kneels to the ground and addresses
the spider goddess.

``Lolth,'' she says. ``Mother. Speak to me.''

The light in the room dims. A shadow, darker than a moonless night,
descends as if on a silk string from the ceiling and settles in the air
above Galadriel's head. Galadriel's eyes fill with black smoke, and then
the shadow sinks down to swallow her completely.

``If she comes back possessed,'' says Harlan, ``what's our plan?''

``I think I have an idea,'' says Hanamir.

It doesn't take long. The shadow lifts with a softly clicking sigh.

``I spoke to her,'' says Galadriel. ``And she can show me how to get to
the top of the tower.''

``Hey, Gals,'' says Hanamir, affecting a casual air, ``while you were
praying, we thought we might just give up and go home.''

``Yeah,'' says Harlan, catching on. ``We thought we could go back to
Eillin and actually burn it down instead? And maybe make some bacon out
of the pig?''

``What?!'' she gasps. ``Oh---I see. No, I would still rather not do any
of those things.''

Hanamir holds eye contact with her for a long moment, then assures
Harlan, ``It's true.''

``I told Lolth that I killed her followers,'' says Galadriel. ``I told
her I did it to prove that I alone am worthy of being her high
priestess. I asked her how to unseat Cazna.''

``And?'' says Harlan.

``She asked me if I think I am truly worthy. And she asked me why I had
not bound myself to my holy relic.'' She gulps. ``I told her I was
waiting to do it in her presence. And so now I\ldots{} I'm bound to her.
I can never take the gauntlet off.''

Galadriel's eyes fill with black smoke again, and a terrible voice comes
from her mouth.

``Do you want to come to the top of the tower now?''

Galadriel's eyes clear and a door appears in the wall in front of them.
Before they proceed, she casts invisibility on Hanamir. He leads them
through the door and up the stairs in unseen silence.

They emerge on the roof. The moon shines weakly overhead, as if
struggling; much of its light is dampened by a malevolent shadow. Its
voice, distant but beautiful, addresses Galadriel:

``Are you a follower of my accursed mother?''

``Y-yes,'' says Galadriel.

``Then I have nothing to say to you. For accepting the help of Lolth,
you are doomed.''

Tears spring into Galadriel's eyes.

``But is there anything I---''

``I have nothing to say.'' The shadow seems to gain ground over the
moon's waning light. At the opposite end of the rooftop, behind a
shimmering web, they see Cazna, who seems not to have noticed them.

``Remember, we learned she's protected by a barrier,'' says Harlan.
``Probably the web.''

``Do you think it extends around the other side?'' says Hanamir.

``Galadriel, perhaps you could check?'' suggests Harlan. ``You can climb
along the side of the tower. Leave Buddy here if you want.''

``He's staying in my backpack, thank you,'' says Galadriel, wiping away
tears. ``I will never trust you with him in a million years.'' She
climbs down over the side of the tower, trying to remain calm, but
trembling with grief. Buddy nuzzles the back of her neck and oinks
reassuringly.

The side of the tower is smooth and cold. She creeps along the side
until she is at the edge beneath Cazna. The priestess remains deeply
entranced in her ritual\ldots{} and there is no web on this side.

Galadriel climbs closer. She lifts herself up to stand on the roof
behind Cazna. Through the web, she can see Harlan rush forward, trying
to create a distraction. Cazna looks up and notices him, and with a
flick of her wrist, she conjures a phase spider and sets it upon him.
She is still engrossed in her spell.

Galadriel breathes as quietly as she can and tiptoes even closer. The
priestess smells like incense and witch hazel. She sees the phase spider
lunge at Harlan and miss. The time to do it---if she's going to do
it---is now.

She draws her short sword and, without hesitating further, plunges it
into Cazna's back.

``I'm the high priestess now, biiitch!'' cries Galadriel.

Cazna howls in pain and the magical web around her evaporates like steam
into the night sky. Harlan's hammer is already raised; he dodges another
attack from the phase spider, runs through the disintegrating barrier,
and slams Cazna with it, knocking her to the ground.

Hanamir, still invisible, swings for the phase spider and makes a dent
in its prickly blue hide. Shrieking in confusion, it advances on the foe
it can see. It sinks its teeth into Harlan's side and rips a
mortal-looking chunk of flesh right out of him. Meanwhile, Cazna picks
herself up, wounded and enraged.

Galadriel gathers up all the magic she can muster and casts Healing Word
on Harlan. His arteries stop gushing quite so terminally onto the
rooftop. He reaches for the satchel the hunger god gave him and, in
desperation, takes a bite of bread. Immediately---and a little
eerily---he is restored to perfect health.

Galadriel then whips back around and casts Tasha's Hideous Laughter on
Cazna. The priestess is overcome with giggles, then full-bellied
laughter, then hysterics, and falls to her knees.

``You see, Lolth?'' Galadriel cries. ``She is weak! She is not worthy of
your favor! She is not fit to wipe the crust from your multitudinous
eyes!''

Harlan feels Hanamir's invisible arms lifting him back to his feet.
``Use the storm,'' he whispers. ``Now's your shot.''

``On it,'' says Harlan. He summons a gust of wind and blasts it straight
at Cazna.

Convulsing, she flies backward off the roof.

Everyone, even the phase spider, rushes to the edge. The priestess,
screaming not with fear but with amusement, falls. And then the laughter
stops.

``Is she\ldots{}'' says Harlan.

``Yes,'' says Hanamir. ``Dead. Completely. Exactly.''

The moon emerges, full and bright and unnaturally large. The phase
spider blinks out of existence.

A plume of smoke from the ground rises up to the edge of the roof. It is
in the shape of Cazna's body, but its edges are blurred, and moonlight
shines through it, so bright that the adventurers shield their eyes. The
shadow Cazna does not laugh.

The tower goes hazy; things that were once solid might not be. A black
curtain sweeps to one side out of the nothingness, and an arachnid, all
enormous legs and glittering obsidian eyes, appears. It picks up Cazna's
lifeless body. Suddenly the arachnid is a drow, Lolth in her humanoid
form, twelve feet tall and even more terrifying to behold. She cradles
Cazna like a child and kisses her face, and then, with a snap of her
jaw, bites off the priestess's legs.

Cazna's severed torso falls to the ground. Lolth grabs the corpse's hand
and drags her back through the black curtain. The black curtain
disappears.

The party exhales. They have no words for their disbelief. They are
standing alone at the top of the tower. Before them, they see three
other curtains billowing gently, though there is no breeze.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

Commercial break. An aerial shot of the town of Eillin. Then the camera
pans down main street to stop and focus on the famous tavern in the town
square. A man with coins for eyes opens the door. The audio is muffled
and polluted with background noise.

``Welcome to \href{/characters/fleck/}{Fleck}'s! I'm Fleck, and the
locals know Fleck's is the best spot in town to get your pre-game on
before the Moon Festival this weekend.'' He waves an arm. ``Follow me!''

A star wipe introduces a new shot of the tavern interior. It is mostly
empty, but H'Jun is passed out face down on the bar. Fleck is behind the
bar cleaning tankards with a questionable-looking rag.

V.O. (Fleck): ``Meet the regulars. Stop and say hi. I may not be able to
see you, but I sure can serve you the finest ale in Eillin!''

A diagonal wipe to a shot of a stock room full of kegs.
\href{/characters/frunk/}{Frunk} Thunderstruck wanders into the shot,
fiddling with his ring, then jumps out of the way when he notices the
camera.

V.O. (Fleck): ``Fleck's Tavern. Eillin's hottest bar, restaurant, inn,
and part-time club. Open 24 hours the weekend of the Moon Festival.
Moon-themed drink specials and half off totchos all weekend.''

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}


\chapter{Moonlight Sonata}
\chapdesc{A lunar interlude, and a hero's welcome...but peril never sleeps.}

``Welcome back,'' whispers \href{/characters/galadriel/}{Galadriel}.
\href{/characters/buddy/}{Buddy} is now napping in her lap, and she
strokes his head. ``That was a dramatic finale to our quest, wasn't
it?''

Buddy oinks a little in his sleep, and she looks down at him with pure
adoration.

``I bet you're wondering how dope this party is going to be,'' says
Galadriel. ``Don't worry. You'll find out soon. We rejoin our heroes
back at the top of the tower, looking at three mysterious curtains.''

You see in the flashback window that
\href{/characters/hanamir/}{Hanamir} is perusing the Big Book of Planes
that Gruumsh gave him.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

``I think the turquoise curtain is the one we want, team,'' he says,
chewing on his lip thoughtfully.

``Onward, then,'' says \href{/characters/harlan/}{Harlan}. They pass
through it one by one and the nature of reality does a few backflips.
They land near the base of the hill outside of Eillin. They look up at
the observatory and see that \href{/characters/bryn/}{Bryn}'s lights are
on. The sun is setting, and an enormous full moon glows over the town.

``Shall we check in with dear old Bryn?'' says Hanamir.

``Yes. I can't wait to tell him those glasses were completely useless,''
says Galadriel.

``Not completely,'' says Hanamir, who still has them propped atop his
head. He brings them down to rest on his nose and the look is undeniably
fierce.

When they reach the top of the hill, Bryn is already at the door to
welcome them in.

``It's you guys!'' he exclaims. ``Come in, come in. We weren't sure what
happened. It was the strangest thing. The occlusion of the moon---it
disappeared all of a sudden! And
\href{/characters/eilistraee/}{Eilistraee} arrived in town for the
festival!''

``Yes, well, we tracked down the source of the problem. A rogue
priestess of Lolth was responsible,'' says Harlan. ``Do you know the
name \href{/characters/cazna/}{Cazna}?''

``Cazna, of course,'' says Bryn. ``She was the culprit? She fled the
town years ago. We didn't know she was alive!''

``Oh, she's dead now,'' says Galadriel.

``And she was being helped by the orcs to take down Eilistraee. The
followers of Shargaas, specifically,'' Harlan clarifies quickly, with a
glance at Hanamir.

``Well, the town is deeply in your debt,'' says Bryn. ``I don't know how
to thank you. Would you like a book on the History of Eillin?''

Hanamir takes it with a quick bow.

``Want to come with us to the Moon Festival?'' says Galadriel.

``We'll buy you a drink!'' says Harlan.

``Oh! I couldn't,'' tuts Bryn. ``I have so much studying to do. I would
rather stay up on my hill.''

``Anything we can do for you in town?'' asks Hanamir.

``Actually,'' says Bryn, ``there's a wizard friend of mine who usually
comes to visit me during the festival. He hasn't come by yet, so if you
see him in town, send him up my way.''

``Any distinguishing characteristics?'' says Harlan.

``He's an elf\ldots{} and he's a wizard\ldots{} he's about 700 years
old\ldots{} you'll know when you see him,'' says Bryn. ``I really look
forward to seeing him each year. He's the only visitor I usually have,
present company excluded.''

``Come on, Bryn,'' wheedles Galadriel. ``Science is fun and all, but you
can let loose once in awhile!''

``Science is all the fun I need,'' says Bryn, appearing to mean it.

The adventurers leave this huge unbelievable nerd to his books and
scamper on down the hill toward town. But before joining the
festivities, they decide to seek out
\href{/characters/sanford/}{Sanford} \& Son to offload their remaining
orbs.

``Why aren't you guys partying in town?'' Sanford asks after greeting
them as warmly as goblins can do.

``We need some drinking money, and it so happens that we have some hot
items we'd like to run by you,'' says Hanamir.

``All right. Whaddya got?'' asks the Son.

``Check this thing out.'' Hanamir hands him the pearl orb.

``Very nice,'' says Sanford, rotating it.

``There's a trapped soul inside, too,'' says Harlan. ``Frost giant.''

``Trapped soul of a frost giant in a pearl\ldots{} um, I'll say three
hundo for the pearl and three hundo for the frost giant.'' The Son makes
a note in a small ledger.

``You've got a deal, my man,'' says Hanamir. They shake.

``Got any cool new magical items yourselves?'' asks Harlan.

``Well, it really hasn't been very long since we last saw you,'' says
Sanford. ``It was\ldots{} two days ago, I think.''

``It does not feel that way,'' says Galadriel. ``Anything, though?''

``We do have something you might like, adventurers such as yourselves.''
He reaches into his inventory and holds up a long robe. Galadriel
squints in the low light to see if it's at all goth, but it's not. It's
covered in colorful, oddly-shaped patches. ``Interesting things happen
when you remove the patches on this fashion-forward piece. You might get
a helpful item for each one. Two thousand gold.''

``A little steep,'' says Hanamir. ``We'll pass on it for now.''

``Anything else you want to sell, then?''

The adventurers rummage through their belongings and produce the
chalice, the bone key, the silk handkerchiefs, the gems, and the
figurines they found in the tower. Sanford \& Son pay them a reasonable
amount of gold.

``Oh, before we go,'' says Hanamir. ``Can you take a look at this
plane-shifting potion?''

Sanford takes the proffered vial and sniffs it, frowning deeply.
``Where'd you get this? It's very unstable.''

``Our friend drank some of this and we don't know what happened to
him,'' Harlan says.

``Frankly, I would pour this on the ground, if I were you,'' says
Sanford.

``Really? The tiefling seemed very confident,'' says Harlan.

``A tiefling gave it to you?'' Sanford looks surprised.

``Yes, her name was \href{/characters/magick/}{Magick}. Making potions
was her whole deal,'' says Galadriel.

``Well, their names are aspirational\ldots{}'' says Sanford. ``This
potion is dangerous. Your friend drank this? How much of him
plane-shifted?''

``What? He was completely gone,'' says Galadriel.

``Oh, okay. That's lucky.'' Sanford raises his eyebrows and sets about
packing up his new purchases.

Harlan, Hanamir, and Galadriel laugh nervously.

``Nice doing business with you,'' says the Son. ``See you around.''

The party turns and heads toward the town.

``Oh, we're going into town too,'' says Sanford. ``Haha, awkward.''

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

The flashback window fades from view, and you're back with Galadriel and
Buddy in the cozy TV studio.

``Now the fun part. The adventurers head to Eillin to enjoy their
success and finally let go of all that questing stress at the Moon
Festival. The libations are flowing freely among the townspeople, who
are making merry around a great bonfire in the center of town. I present
to you the highlights of the night, in the comedic mockumentary style of
The Office.''

You see a close-up window of \href{/characters/frunk/}{Frunk}
Thunderstruck, dwarf mayor of Eillin, addressing the camera directly.
He's sitting on a bench outside \href{/characters/fleck/}{Fleck}'s
Tavern. The noise of celebrants can be heard all around him.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

``I was excited for tonight because\ldots{} well, to be quite honest,
this has been the most stressful couple of weeks in my life. Trying to
put together this festival with this whole moon crisis going on, and not
even being able to tell people about it\ldots{}'' Frunk rolls his eyes.
``Just, let me say, I'm glad it's over. And I'm glad I ran into those
random people that day and convinced them to check out the situation
with the red glass---hey, speaking of which, that's them!'' He points
past the camera. ``Hey! Adventurers!'' He waves them over. Hanamir,
Harlan, and Galadriel shuffle into the frame. Frunk tugs on the sleeve
of a man standing nearby.

``\href{/characters/slee/}{Slee}! These are the ones I was telling you
about,'' says Frunk.

The man, a human of about sixty years old, turns to face the party. He
has a salt-and-pepper beard and a vibe of total gravitas.

``Oh my god, it's the king,'' Galadriel stage-whispers.

``Your highness,'' says Hanamir, kneeling. Harlan bows deeply and
Galadriel curtsies (oh yeah, and she's no longer dressed as a Lolth
priestess and has put on a sick party outfit, by the way. Oh and it's
long-sleeved and it covers up the gauntlet). King Slee lets them express
their deference for a bit of a long moment, then addresses them.

``It's an honor to meet heroes such as yourselves. Frunk tells me that
the festival would not have happened for the first time in centuries if
not for your help,'' says the king. ``Please, tell us how you did it.''

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

The cameraman gets distracted by a very intoxicated human woman who has
climbed onto a signpost and released a large quantity of flying
golf-ball-sized creatures into the night air. They fly in circles and
emit some impressive colored sparks for about thirty seconds. The camera
pans back to our group.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

``Anyway, we killed her exactly dead,'' Galadriel is explaining
animatedly to King Slee, whose brow is furrowed.

``I'm sure Eilistraee is very grateful,'' he says diplomatically. ``She
is here tonight, you know. She likes to spend most of the festival
dancing. You could go see her.''

``Oh, um.'' Galadriel turns redder than a Wyrmling and glances
uncomfortably at the camera for a second. She tugs at her sleeve, as if
checking that the gauntlet is still hidden. ``Maybe in a little while.''

``Hey, speaking of being grateful,'' says Frunk, lowering his voice. ``I
belong to an ancient order that is charged with protecting the town.
After your success on this, we'd be interested in hiring you all on a
permanent basis to help defend us against outside threats.''

``We'd be open to that,'' says Harlan. ``Do you know anything of Regent
\href{/characters/khargol/}{Khargol}? He seems like the most likely next
threat. Apparently he and the followers of Shargaas were working in
conjunction with Cazna and the Lolth followers to destroy Eilistraee.''

``That surprises me. As orcs go, Khargol is pretty reasonable.'' Frunk
gives Hanamir an apologetic look. ``He fights with honor, I mean. We
have a tense relationship with the orcs of this region, and if they're
plotting against us, it might be time to break the unspoken truce.''

H'Jun strides confidently in front of the camera.

``Moon Festival forever,'' he slurs. He spills some ale on himself.
``HA!''

``Hey, buddy,'' says Harlan. ``Having fun?''

Frunk moves away to talk with Slee, looking worried. H'Jun lumbers over
to talk with the adventurers.

``Did you all see the dragon?'' he whispers.

``Pardon?'' says Hanamir.

``The dragon in the woods,'' he says. ``No one believes me.''

``Oh, um, nope, we didn't,'' says Galadriel. ``But we believe you.''

``You should tell them all about the dragon!'' H'Jun seems to
misunderstand.

``Okay, bud.'' Harlan pats him on the shoulder. ``Hey, I think we met
someone you know during our quest. Goes by the name of
\href{/characters/feld/}{Feld}?''

``Feld! You know Feld? Feld's my cousin,'' hiccups H'Jun.~``He's over
there!'' He swivels around to point at Feld and smacks an elderly
half-elf in the face.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

The footage now cuts to a series of short interviews with partygoers,
starting with the aforementioned Feld. Harlan, Hanamir, and Galadriel
are present but not on camera.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

``Oh, H'Jun? Yeah, he's wasted again,'' says Feld, shrugging. ``It is
what it is. He's a good guy, and he's letting me stay with him in town
while I get back on my feet again after the kidnapping.''

He is proud to show off that he can now play Rock Me, Mama, Like a Wagon
Wheel on the lute, if haltingly.

``I got a job here in town playing live for the outdoor brunch crowd on
weekends,'' he says. ``And I said to myself, as soon as I got it, that
I'd reward you guys for saving me. Thank you so much.'' He gives the
adventurers some gold. What a guy!

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

The camera cuts to the interior of the tavern. Two young drow women
stare at the camera, unimpressed. ``She said she saw a tiefling. Yeah,
here at the party. Pretty cool I guess.''

``I mean, not really. They're just not that common around here.'' The
other one shrugs. ``Anyway, it looked like a demon, very ugly\ldots{}
hated it. Smelled weird, hated it. Oh, and it kept talking about
revenge! So creepy.''

``Yeah, seriously creepy.''

``It kept trying to get me to come with it to the forest or something.
Like, no, idiot, there's monsters in there. But it was talking about how
it needed to head north for revenge. Toward the mountains.
Against\ldots{} some name\ldots{} Baberuth? Babyruth? No, Bameryth.''

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

Cut to Fleck behind the bar, coin eyes glittering in the light from the
bonfire outside.

``I pretty much just serve drinks,'' he says serenely. ``But I did get
to be part of the planning of it, yeah. And before he had to go,
\href{/characters/the-savage/}{the Savage} gave me this note to read at
the celebration. I think he forgot that I\ldots{} can't anymore.'' A
pregnant pause. ``He did say he was sorry he can't be here for the
festivities. He has business to attend to. It's a shame, because
everyone in town loves him.''

Galadriel, off camera, asks: ``Any idea where he went?''

``Nah, I didn't see him leave,'' says Fleck. ``But, to be fair\ldots{} I
don't see anything.'' He smiles at what he thinks is the camera, but is
actually the wall. ``Life is hard.'' The camera pans to what looks like
a lot of broken glass behind the bar.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

Back outdoors, two dwarves argue heatedly with one another. ``It's a
secret dwarf treasure, that's what makes it so cool, what is wrong with
you?''

``It's just not as cool if I can't tell people about it, you know?''

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

Cut to a human man wearing a large purple hat and double fisting two
tankards of ale. He peers into the camera conspiratorially. ``I heard
the orcs fled. I heard they're really shook up, yeah. No one knows why.
But my money's on chemtrails.''

Hanamir, off camera, expresses skepticism.

``No, really! One of my friends went out there, and\ldots{} he was
trying to just get a look at the forbidden city. And he had to sneak
around the orc encampment to do that. And it just looked completely
abandoned! Nothing inside, no clue where they'd gone. The chemtrails
overhead were clear as day, though.''

``Did your\ldots{} friend\ldots{} happen see any books in the orc
encampment?'' says Hanamir's voice.

``My friend doesn't like to read much,'' says purple hat. ``But as a
matter of fact, he did see some books. But that's even weirder. Why did
orcs even have books, right?''

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

Cut to the adventurers sipping their drinks (a seltzer with lime for
Hanamir, ale for the other two) near the dance floor.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

``She's right over there,'' says Hanamir. ``You could go try and make
amends.''

Behind them, a twelve-foot-tall drow woman can be seen dancing in a
rapturous crowd of people. She looks so much like Lolth that the
cameraman does a double take---but it's Eilistraee.

``I don't know,'' whines Galadriel, holding her Groucho Marx disguise,
weighing whether to go incognito and avoid confronting the goddess
again.

``We'll be your wingmen!'' says Harlan. ``If you pass up this
opportunity to make things right, you probably won't get another one.''

``Fine,'' sighs Galadriel, folding up the disguise and putting it back
in her bag. Harlan drags her toward the goddess.

Eilistraee notices them and stops dancing. She leaves the dance floor
and approaches them.

``Greetings,'' she says. If voices could glow, hers would. ``I've been
awaiting your arrival. I appreciated what you all did back there.''
Despite her words, Eilistraee looks at Galadriel with a bit of side-eye.

Galadriel sinks to her knees and bows her head. Realizing that she is
not about to say anything, Harlan pipes up.

``Truly, it was our honor to help defeat Cazna,'' he says.

``Yes. Did you catch it, by the way?'' adds Hanamir. ``It was pretty
sweet.''

``The word got out,'' says Eilistraee with a slight smile. ``The God of
Laughter is telling everybody. Truly, I owe you all my life and the life
of this town.''

``Well,'' says Hanamir, ``we couldn't have done it at all without our
friend Galadriel here.''

``She made a great sacrifice to do what we did, to save the Moon, and we
didn't want to let tonight pass without at least acknowledging that
sacrifice,'' says Harlan.

Galadriel looks up at her friends, very touched, and already ugly
crying.

``May I read your thoughts?'' Eilistraee asks Galadriel.

``Yes,'' she sniffs. ``Of course.''

``I see that you did not try to deceive me,'' she says. ``And I see that
you are just another victim of my mother's curse.''

Galadriel nods vigorously.

``I reacted badly before. Forgive me. You are, of course, forgiven
yourself. And although there is nothing I can do to lift the curse she's
put upon you, you should know that what she said about it being
permanent is not true.'' Eilistraee pauses. ``She aims to sow despair.
But if you were to obtain the blessing of a god of her stature or
higher, they would be able to lift the curse.''

``\href{/characters/kord/}{Kord}?'' asks Hanamir, glancing at Harlan.

``Kord perhaps. I don't know for sure. One person I know could do it
would be my father, Korellon, creator of the elves, who vastly outranks
my mother. Unfortunately, I can't help you with that.''

``You have already helped me.'' Galadriel wipes her nose on her sleeve;
it's undignified. ``Thank you.''

The goddess leans down and touches Galadriel's head in blessing. ``I
think there is hope for you. I still see goodness in you. Be careful.''

Eilistraee is silent for a moment.

``I am going to give you a gift. It is a precious and dangerous thing to
wield, and I need you to understand the gravity of it.''

She holds a pendant. It emanates a soft light in her hand.

``This will let you use a spell known as a Wish. When you use it, you
may tell me your wish and I will grant it.''

``Why is it dangerous?'' says Hanamir.

``Depending on your wish\ldots{} you could level a city with it. It's
not cursed. But it will change the course of history when you decide to
use it.''

``We understand. We will not take this honor lightly,'' says Harlan.

``Any of you may use it, but it may only be used once.'' Eilistraee
hands the pendant to Galadriel.

``It's so beautiful,'' she sobs. Eilistraee smiles.

``So, how are you feeling, godwise?'' asks Hanamir as Galadriel takes a
moment to collect herself.

``I'm proud to see this festival happening. It's unusual that I walk on
this plane, but I always enjoy it. I'm glad to see the drow who have
rejected my mother living here in harmony with half-elves.''

``What do you know of the orc threat?'' asks Harlan.

``Shargaas is a lesser deity of the orcs, less powerful than Gruumsh,
and Shargaas can't stand that,'' Eilistraee says. ``He's the god of the
new moon, so we tend not to see each other.''

``Do you know what this satchel of bread is going to do to me? An evil
god gave it to me.'' Harlan holds up the Bread of Eternal Hunger.
Eilistraee gives him a grim look.

``Just\ldots{} think about where the bread comes from. There's no such
thing as free bread. Be careful with it.''

There is an uncomfortable silence while Harlan sits with this.

``By the way, Harlan's deity Kord did aid us in saving you, just so you
know,'' says Hanamir. ``I hope the two of you are on good terms.''

``Not all gods know each other, you know,'' says Eilistraee, smirking.
She walks back to the dance floor and resumes breaking it down to the
slammin' tunes.

The trio wander away from the dance floor, back to where they first
chatted with Frunk and King Slee. The two leaders are standing not far
off, speaking in hushed tones. Frunk looks gravely worried.

``Shall we eavesdrop?'' says Hanamir.

Galadriel responds by casting invisibility on him and giving him bardic
inspiration; Harlan follows up by casting enhance ability and gives him
the guidance of Kord. It's overkill, but they want to be sure.

Hanamir tiptoes up to the two leaders until he can just barely hear what
they're saying. Something about ``Been''---something about unsealing a
city, whether that will be necessary if someone's gotten in---something
about a betrayal---they'll need ``all the Been\ldots{}''

It's not clear what they mean yet, but that night, the adventurers
discuss it as they settle into their rickety twin beds at the inn.
Hanamir struggles to get his blanket to cover his whole body.

``It's that ring with the B on it, the one the Savage has,'' says
Harlan. ``The B must stand for Been, and if you have a ring, you're a
member.''

``So, we know Frunk and the Savage and King Slee are members,'' says
Hanamir. He wears an adorable nightcap and matching pajamas with little
bespectacled worms reading books on them. ``Who else?''

``The ring we found in the market---the one the Savage ended up
buying,'' says Harlan. ``I think that one belonged to Uncle, right?''

``We'll figure it out tomorrow,'' yawns Galadriel. She and Buddy are
spooning and already half asleep.

The flashback footage speeds up through the ensuing long rest. They
sleep soundly, even with the increasingly intrusive sounds coming from
outside as the sun rises on a very hungover town.

Finally, the noise wakes Harlan. He stomps over to the window groggily
to see what's causing all the ruckus.

``Uh, guys?'' he says, snapping to alertness. ``There's a sheep running
around the town square knocking things over, and also the town crier is
ringing a bell and saying that\ldots Bryn is dead?''

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

This final flashback window dissolves into air. Galadriel puts down her
lute and smiles.

``Ending on a cliffhanger here, I know, I know,'' she says. ``But join
me next time for Part Two of our clip show, where we'll see the party
take on a wacky murder mystery with lots of wild animals, including a
talking sheep! It's a whole different vibe. You'll love it!''

She places her lute in its case delicately and winks.

``This has been Galadriel T. Moonwater with your recap. Good night!''

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\hypertarget{the-true-history-of-eillin}{%
\section{The True History of Eillin}\label{the-true-history-of-eillin}}

\hypertarget{founding-governance}{%
\subsection{Founding \& Governance}\label{founding-governance}}

Eillin was founded in the year 325 by Veneyphe and Bynrize. Veneyphe was
a Half-Elf and Bynrize was a Drow and while little is known about their
history or how they came to meet it is known that they founded the town
as an homage to Eillistrae and as a symbol of peace between the Drow and
Half-Elves.

Eileen has little need of formal governance, the town elects an informal
``mayor,'' the title mostly a tribute to the nickname of Venephye for
the first 86 years of the town's existence. After her death there was no
formal leader, but the co-founder of the town, Bynrize, served roughly
the same role of settling disputes. In his old age he delegated this to
an outsider and dear friend, Frunk Thunderstruck the Dwarf. This
decision was made at a time of great tension between the Half-Elf and
Drow populations, and eased some of the tensions.

The recent death of Bynrize leaves the young town faced with a choice,
will it continue in the tradition of its now departed founders or will
it forge a new path in the modern world?

\hypertarget{the-moon-festival}{%
\subsection{The Moon Festival}\label{the-moon-festival}}

In 330, with a small population the town saw its first moon festival. On
this day Ellistrae appeared in her Drow form and walked among the town
and all in the town celebrated her presence. Since then she has appeared
once every year while locals throw a feast in her honor.

The festival has grown so large that people come from all over to
attend. In many years even the Human Rulers of nearby Aberith come to
pay homage to her holiness and celebrate the beautiful spectacle of a
24-hour full moon.

\hypertarget{war-peace}{%
\subsection{War \& Peace}\label{war-peace}}

The history of Ellistrae has not always been peaceful, Orcs sacked the
town in 389 and again in 534.

After the first raid several factions were created to defend Eillin,
though they were opposed by Veneyphe as she felt that they would lead
their followers to violate the town's unspoken principle of neutrality.

Starting in 633 the southern half of the continent, which includes
Eillin saw undead hordes descend on cities periodically. During this
period many left Eillin to live in the city of Aberith. Eventually this
led to an alliance between the two, with Aberith pledging protection in
exchange for goods from Eillin. After about 50 years, the hordes
eventually subsided and peace blossomed again.

The next threat that Eillin would face would nearly tear it apart. A
long-extant cult of Drow made an attempt on the life of Bynrize on the
eve of the moon festival. They felt that the alliance with the Half-Elf
had gone on long enough and wanted to return the town to the Drow.

The leaders were defeated and their supporters were driven out of town.
This led to continued strife between the Drow and Half-Elf population
for many years, but that tension is mostly forgotten.

\hypertarget{local-geography}{%
\subsection{Local Geography}\label{local-geography}}

Eillin is on the southern coast of Ivrend, a continent comprised
primarily of Elves, Humans, and Half-Elves with the occasional Orc and
Dwarf settlement. The town is bordered on the north by the anomalous
``mountains of greed'' a visual siren song of jewels from which it is
said none return and on the south by the enchanting Moon Sea.

Surrounding the town there are several small hamlets and farms. Three
main roads lead out of the town: east, west, and northeast.

To the west of the town there is a forest in which it was long rumored
that evil dwelled. Young children used to play on the edge of the forest
hoping to get a glimpse at the evil that lurked there but it is widely
believed these were just the occasional wild animal or lost wanderer.

To the northeast there is the road that leads to the city of Aberith,
the largest city on the eastern half of the continent. It is several
day's journey but some make the journey on a regular basis to trade
goods in the cosmopolitan city of Aberith.

To the immediate east are the ruins of an ancient city. Not much is
known about the history of the city but it is believed to have been
destroyed well before the creation of Eillin. Visiting the city is
banned by the Crown of Aberith.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}


\chapter{Ovine Arbitration}
\chapdesc{Sad tidings, and a ruminant client.}

``Adventurers? Open up!'' the voice of \href{/characters/frunk/}{Frunk}
Thunderstruck can be heard through the door of their room. He knocks
forcefully. ``It's an emergency!''

\href{/characters/hanamir/}{Hanamir} leaps to the doorway like an
elegant-but-burly gazelle and opens it.

``Mayor Frunk,'' he says. ``We just heard about
\href{/characters/bryn/}{Bryn}.'' His voice is solemn.

``What happened?'' asks \href{/characters/harlan/}{Harlan}.

``He's dead! Murdered!'' says Frunk, bustling past Hanamir into the
room. ``Adventurers\ldots{} I cannot overstate the gravity of this
situation.''

``Who did it?'' \href{/characters/galadriel/}{Galadriel} sits up
groggily.

``We don't know, of course,'' says Frunk. He snaps his fingers at her.
``Wake up! This is serious!''

``Sorry,'' she says. ``I liked Bryn. Can we help?''

``Yes,'' says Frunk. ``Come with me.''

``We'll get ready and meet you---'' starts Hanamir, but Frunk interrupts
him.

``No time! No time for that! I need you to help me solve the murder,''
says Frunk, and he drags Hanamir out the door.

``Mayor, sir! Wait!'' says Harlan, scurrying after them. Galadriel and
\href{/characters/buddy/}{Buddy} bring up the rear, thumping down a few
stairs before switching to a more coordinated spider-climb along the
wall.

The town square is in chaos: decorations from the Moon Festival litter
the ground and horses sip from puddles of beer between the cobblestones.
But the most prominent disruption is a sheep, bleating incessantly and
knocking over barrels of trash in an apparent bid for attention. It
notices the pajama-clad adventurers exiting the inn and crashes headlong
into Harlan, dropping a scroll at his feet.

Harlan stumbles, then picks it up.

``Looks like a Speak with Animals spell,'' he says. ``And I think
through the act of reading it, it's been cast on me, and I can---''

``Hello? Hello? Can you understand me?'' bleats the sheep. Harlan
glances at Hanamir and Galadriel, who look bewildered. Frunk crosses his
arms, fuming at this new delay.

``Yes,'' Harlan says.

``Thank goodness,'' says the sheep. ``My name is Finethur
\href{/characters/shinebright/}{Shinebright}, and I'm a wizard, and I am
in dire need of your aid!''

``Oh dear,'' says Harlan, trying to stifle a giggle. He translates this
information for his friends. ``What caused your transformation?''

``I've been turned into this form by my traitorous apprentice. We need
to go get my wand back from him. I'm afraid of what he's doing with
it,'' says the sheep urgently. ``He's kept me as his prisoner for
months. This has been my first opportunity to break free.''

Harlan translates again, then has a sudden realization. ``Is this
related to the death of your friend Bryn?''

The sheep looks on the verge of a heart attack. ``Bryn is dead?!''

``Sadly, yes,'' says Harlan. ``We just found out. He was murdered.
Stabbed to death in his observatory.''

Shinebright baas mournfully. Buddy hops down from Galadriel's arms and
nuzzles him a bit.

``Please, follow me,'' says Shinebright, after taking a moment to
collect himself. ``I'll lead you to my tower and we can reclaim what he
took from me.''

``Of course. Any friend of Bryn's is a friend of ours.'' Harlan explains
all this to Hanamir and Galadriel.

``Hmm, I'd like to take a quick gander at the crime scene\ldots{}'' says
Hanamir, with a gesture at Frunk, who is tapping his foot.

``Maybe we split up?'' says Galadriel, scooping Buddy up and into her
backpack.

``Fine by me,'' says Harlan.

The adventurers part ways. Shinebright trots ahead of Galadriel and
Harlan toward the path northward out of town, while Hanamir and Frunk
head west to Bryn's place.

---

The path up to Bryn's observatory is blocked off by a line of thin
yellow parchment reading ``TAKE HEEDE! THYS YS THE SCENE OF A
KYLLYNGE.'' With a heavy sigh, Frunk steps over it and waves Hanamir
along, trudging up the hill to the observatory. Its wide windows sparkle
in the morning light.

Hanamir has always admired the observatory. He sees it as a hybrid of a
temple and a library---a quiet sanctuary for a fellow man of letters.
Now, as he enters the front door, he feels a level of grief that
surprises him. The once-serene place is overrun with armed guardsmen
poking at Bryn's instruments and rifling through his documents. Hanamir
puts on a brave face and approaches one of the guards.

``What's the good word, gentlemen? What happened here?'' he asks.

``Oh, it's you,'' a guard says, checking something on a clipboard.
``Hanamore, the half-orc.''

``Hanamir,'' says Hanamir.

``Sure. We were told that your party was seen departing this observatory
last night. You may have been the last to see Mr.~Starloft alive. Did
you notice anything unusual?'' asks the guard, peering up at Hanamir,
clearly trying to read murderous intent in his face.

``No, but he did say he was hoping to see a friend of his, a wizard,
whom he hadn't seen in awhile. And we invited him to come to the Moon
Festival with us, but he declined,'' says Hanamir.

``We know he wasn't one for parties,'' says the guard, smirking a little
bit. ``It's not suspicious that he stayed behind. But this is the first
we're hearing of this wizard friend.''

``Do you have any leads so far?'' asks Hanamir.

``We had two intoxicated witnesses say they saw three humanoids heading
out of Bryn's place near the beginning of the festival,'' the guard
says, ``and we know that was you and your friends. Later on, there were
reports of one more humanoid seen on the path toward the observatory.''

``Mind if I take a look around?'' says Hanamir.

``Go ahead. But we've searched this place top to bottom,'' says the
first guard. He points at Bryn's living room, which is full of jumbled
piles of books, some splayed open on the ground.

Hanamir winces.

He excuses himself politely and circles the exterior of the observatory.
Bryn's garden is blooming with flowers and odd-looking fruits. A sheen
of dew makes the surface of a large stone sundial glitter in the
sunlight. Hanamir feels a swell of un-monkish anger rising in his
throat. Someone so careful, so thoughtful---such a conscientious steward
of knowledge---murdered! All the science, history, and magic he
mastered---gone! And for what? Who could want someone like Bryn dead?
And want it enough to stab him to death, in his home?

Hanamir stands where the edge of Bryn's garden begins to slope down in a
grassy hillside. Interesting. Some indentations in the soft ground here.

``Looks like a pair of tracks,'' he murmurs to himself. ``Heading
north\ldots{} toward the mountains.''

He squints ahead at the gems that dot the distant cliffs. Whoever killed
Bryn might have left these tracks. And if so, Hanamir decides, he would
find them. He strides down the hill adjacent to the tracks, filled with
a new sense of purpose.

---

Meanwhile, Harlan and Galadriel have followed the sheep out beyond the
town walls on a road lined with tall grass and wildflowers. The morning
has ripened into a beautiful afternoon. If it weren't for the anxious
chatter (or unintelligible bleating, if you're Galadriel) of Shinebright
the sheep, the adventurers might have enjoyed their stroll in the lush
countryside. Galadriel tries to lighten the mood with an upbeat walking
song on her lute, but Shinebright maintains his grim demeanor.

``For many years, I lived and worked out of the tower up the road
here,'' he explains. ``I was a transmutation wizard. People would seek
me to perform polymorph spells for them, and I made a living that way.''
He looks back at them impatiently, waiting for them to catch up to his
four-legged scamper. ``Bryn was one of my good friends, though we didn't
see each other much. Only about once a year, but that was enough for us.
I'd visit him during the Moon Festival. I'm sure he was wondering why I
didn't show up this year. I hate to think that before he died, he might
have felt that I'd forgotten about him---''

But Shinebright's monologue is cut short by a sudden, piercing wolf howl
coming from somewhere beyond a turn in the road next to a small thicket.
A half-orc, bulkier and surlier than Hanamir, swaggers toward the group
from around the bend. He is flanked by three wolves in iron collars, and
behind him stomps a hulking figure in a dirty brown cloak.

``That sheep is Master Noke's. He desires to have it back,'' says the
half-orc. His hand rests on the hilt of his greatsword.

``Well,'' says Harlan levelly, ``this sheep claims to be his own
person.''

``It belongs to Master Noke,'' repeats the half-orc.

Shinebright backs up and circles behind Hanamir and Galadriel, visibly
quaking with fear.

``Who is Master Noke?'' Galadriel pipes up, stowing her lute in its
case.

``Only the best and greatest wizard and boss of all time,'' says the
half-orc aggressively. ``Just a generous and great and tremendous and
wonderful and terrific person that I love VERY much.''

``Hmm,'' says Harlan.

``And he sent me to get his sheep,'' says the half-orc.

``How long have you been working for him?'' asks Galadriel.

``Four months, give or take,'' says the half-orc.

``Hmmmmmm,'' Harlan says again, eyebrows raised.

Harlan casts Detect Magic to see if this dude is ensorcelled. He's not.
However, some other creatures are. A faint pink aura of magic appears
around the three wolves and the hulking figure in the cloak. Same with
Shinebright the sheep. And same with Buddy. Harlan's eyebrows nearly pop
off of his face with how intensely he's raising them, staring at
Galadriel.

``I always knew he was a special boy!'' she chuckles.

``We will come back to this later,'' says Harlan in a restrained tone,
rolling his eyes. He turns back to the half-orc. ``But sir, can I ask
about your wolf compatriots here? They look fearsome.''

``They were sent to help me on my mission to bring back Master Noke's
sheep,'' says the half-orc.

``Why haven't we heard of this Master Noke, if he's as great and
powerful as you say?'' says Galadriel. ``You'd think the word would get
out.''

The half-orc scowls.

``Are you going to turn over the sheep or not?!'' he roars.

``The sheep is a friend of a friend, so we have some responsibility to
him,'' says Galadriel. ``He asked for our help.''

``Maybe I haven't made myself clear. We're here to get the sheep, and
then you can be on your way. Hand over the sheep so I can return it to
Master Noke.''

``What will you do for us if we give you the sheep?'' asks Harlan.

Shinebright is baaing ruefully and bumping his head against Harlan's
legs.

``Please don't give me over to Guz,'' says Shinebright, though Harlan is
studiously ignoring him. ``He's Noke's enforcer. Noke is my old
apprentice. Please, please don't give me back. I'll be imprisoned
again.''

``Hey, we'll protect you, little guy,'' says Galadriel, seeing his
distress. ``Don't worry.''

``I'm an extremely powerful elven wizard!'' baas Shinebright. ``I'm
centuries older than you!''

Galadriel smiles at him and pats his head. The half-orc, Guz, draws his
sword, and his hench-animals growl. Harlan turns toward a nearby tree
and emits some startling bird sounds.

``Hey, you! Bird!'' the sounds, if translated, would mean.

A small robin tilts its head to the side, surprised to hear intelligible
speech coming from a human.

``Yeah?'' replies the bird.

``Go find Hanamir and tell him to get over here as soon as he can,''
says Harlan. ``He's a half-orc. He'll be somewhere near the hill with
the observatory on it, just outside town.''

``Okay, but you owe me,'' chirps the bird. It flutters off.

Harlan nods at it and then swiftly casts Shatter on Guz, smacking him to
the ground with thunder damage. The hood of the ratty cloak on the
hulking creature behind him falls off, revealing a bear. Galadriel nocks
an arrow and shoots the bear in its shoulder. It makes a pitiful noise
and lumbers off to climb the nearby tree.

One of the wolves approaches Harlan, snarling and snapping. Harlan
brings down his hammer in a brutally effective swing and crushes the
wolf's skull. He then casts Thunderwave and a second wolf is killed
instantly.

Just then, Hanamir bursts in on the scene from seemingly out of
nowhere---that guy sure is sneaky! The bird circles above him, and
Harlan hears its majestic cry:

``Breadcrumbs\ldots{} you owe me breadcrumbs now\ldots{} toasted
sourdough if you have it\ldots{}''

``Good thing I have bread,'' says Harlan to himself, darkly.

Hanamir leaps at Guz and they cross swords, neither landing a hit, but
giving Harlan time to think. The bear still sits in the tree, licking
its arrow wound. It doesn't look particularly threatening. Nevertheless,
Harlan casts Command on it, telling it to leave, and it acquiesces,
trundling off toward a larger thicket of trees.

``We'll offer you a deal,'' says Galadriel, watching as Guz pushes
Hanamir away from him. ``There are three of us now against you and one
wolf. We'll let you live if you go on your way, and the sheep stays with
us.''

``It's a good deal, brother,'' adds Hanamir in Orcish, and then in
Common, ``you'll want to think about it.''

Guz does think about it, and then decides to continue fighting.

The last wolf pounces on Shinebright and grabs him by the scruff of his
wooly neck. In response, Galadriel casts her trademark Tasha's Hideous
Laughter on the wolf. It lets go of Shinebright, falling to the ground
and barking with hilarity. Shinebright flees to stand behind Galadriel.
She approaches the laughing wolf and stabs it in the neck with her short
sword, killing it.

Harlan joins Hanamir in his battle against Guz, knocking him to the
ground with his maul, and then Hanamir deals the final blow. Guz is
dead.

``Oh, thank you,'' bleats Shinebright. ``Thank you kindly. As you can
see, I'm doomed without your help. Noke has many other transmuted guards
who work for him, and eventually, they will find me. The only way I'll
be safe is if we go and retrieve my wand from him.''

Harlan translates.

``We trust you,'' says Galadriel. ``Do you mind telling us how he got
your wand?''

``I have an incredibly rare wand of true polymorph,'' says Shinebright.
``One fateful night, I ended my wizard's trance, and I found my
apprentice standing above me. He was clutching my wand. I demanded to
know what the boy was doing, but the only noise I could
produce\ldots{}'' He pauses for a moment to gather himself, or just for
dramatic effect. ``I could only baa.'' He demonstrates pitifully. ``So
he kept me in the garden for months, and I only ate grass and
buttercups, and he kept me contained by hungry wolves and other beasts
that he had polymorphed. He was terrified of my escaping. He stole my
life! He told everyone I had died and that he was my successor. He began
doing polymorph magic for anyone who needed it, just like me.''

``Were there any warning signs? Did you suspect him of resenting you
during his training?'' asks Harlan, after relating this expository
baa-ackstory to his friends.

``Well\ldots{}'' says Shinebright. ``He was always frustrated with me.
He's human, and humans are impatient. I would always tell him `You're
still young! Don't worry about it,' and, you know\ldots{} maybe it had
been sixty or so years. But I'm an elf, and that's not a very long
time.''

``Are you familiar with the human lifespan?'' says Harlan earnestly.

``It's hard to remember! I'm not a zoologist,'' says Shinebright. ``He
wasn't ready to wield a wand. I was teaching him the way I was taught.
He was just impatient, and I told him to wait, and he didn't like
that.''

``So when you say `boy', you really mean he was an elderly man?''
prompts Galadriel.

``He was seventy, at most!'' bleats Shinebright.

``I see,'' says Galadriel, and she can't help but laugh. She casts Zone
of Truth. ``I hope you understand this is just a precaution. We've been
hurt before, and, well, I'd just like it if you would repeat the story
you just recounted for us while this spell is in effect.''

Shinebright repeats his story faithfully, but sounds guiltier this time.
He knows he was a bad teacher.

``All right,'' says Harlan, sighing. ``So we head to the tower next.
What of Guz and his wolves?'' The messenger bird has returned and is
sitting on Harlan's shoulder, demanding breadcrumbs. Harlan rummages in
the Eternal Hunger satchel and procures a few bread nubbins. The bird
eats them and its plumage grows fuller and shinier instantly. It trills
happily and flies away.

``I guess let's find out what the wolves really are,'' says Galadriel.
She takes the collars off the wolves, expecting them to shift back to
their original un-polymorphed forms, but nothing happens. She puts one
collar around Buddy's neck and fashions him a little name tag, though,
and it's cute.

Hanamir inspects Guz's corpse. He doesn't have much of value on him, but
he is wearing a pretty neat pair of denim jorts. Hanamir decides to take
those. ``These'll be great for summertime,'' he says, sounding excited.
``And they're in my size!''

Harlan now takes the opportunity to address Buddy, who is snorting and
sniffing the grass. He still shimmers with an arcane aura from Harlan's
Detect Magic spell.

``Buddy,'' he says, ``we haven't spoken up until now. Would you do us
the favor of---''

``Ask him if he loves me!'' giggles Galadriel.

``We'll---um, we'll get there. Would you do us the favor of---''

``It's okay, I know he does,'' she grins.

``Ahem,'' says Harlan. ``Would you do us the favor of introducing
yourself, now that I can understand you?''

Buddy oinks, blinking at him.

``We know very well that you are not a pig, although you are very
cute,'' he says carefully. ``We have no desire to tear you away from
Galadriel; I can see you've become very attached. But I need you to
speak to me.''

Buddy oinks again. He plucks a piece of clover and nibbles on it.
Galadriel coos.

``Come on. Aren't you curious?'' Harlan turns to Galadriel.

``I feel like when Buddy wants me to know who he is, he'll let me know
in his own time,'' she shrugs.

``So you're not worried that Peter Pettigrew is pulling one over on
you?'' says Harlan.

``I don't understand that reference,'' says Galadriel. ``But no, I'm not
worried. He's been good to me.'' She pauses and remembers that Zone of
Truth is still active. ``Hey, you still want to eat him?''

``I do enjoy the taste of bacon,'' says Harlan. ``But I'm more concerned
for our safety in the presence of Buddy than I am interested in eating
him.''

``Fair enough,'' says Galadriel.

Shinebright nudges Harlan, who is still squatting in the grass trying to
engage Buddy.

``I'll transmute this pig for you as soon as you get me my wand back!''
he offers.

``I'd be interested in that,'' says Harlan. ``Can you identify its true
form?''

``Not yet. I'd need my wand. But yes.''

``Sounds like it's up to you, Gals,'' says Hanamir.

``I won't force him to reveal himself,'' she maintains. ``I don't care
what his true form is. I love him so much.''

``What if---what if Shinebright whispered in my ear what his true form
is, once we get his wand back?'' says Harlan. ``And that way I can be
satisfied in knowing he's not a threat, if he isn't. But if he is, we
take action.''

``Yeah, Gals,'' says Hanamir. ``I gotta tell you. I don't want to kill
your pig. But if he proves to be a danger, I will.''

``That is fair,'' says Galadriel. ``I don't approve of anyone who would
try to harm my companions. But I honestly believe Buddy has been one of
those companions---a friend to us all. We don't know why he changed
forms, whether he's in hiding, or whether it was even his choice. I
don't want to force him to do anything he's uncomfortable with. But if
it turns out\ldots{}'' she trails off, shaking her head. ``I trust you
two to do what's right. You know that.''

During this chat, Shinebright has wandered off to eat buttercups. He
saunters back when he senses the drama has reached a conclusion.

``You guys done?'' he asks. ``Cool. So, the tower. There are three
platforms. The lowest is a garden, the middle is the main living area,
with a library and my workshop. The tallest platform is my bedroom.
There are guards surrounding the tower---at least one more bear, and I
don't know what else.''

Once they are in sight of the tower, they decide to take a long rest.
However, they do not hide themselves well enough, and a group of apes
acting as guards discover their campsite. The guards subdue them and
bring them to the garden platform of the tower. A man's silhouette
appears in the window of the tallest platform above them.

``I'll take it from here,'' says the shadow to the ape guards, and they
leave. He then addresses the adventurers. ``Greetings, trespassers. It
appears you have something of mine. Give it back.''

``It is our understanding that you wrongfully transmuted a wizard,
Finethur Shinebright, into this sheep,'' says Harlan.

``Wrongfully? Hah!'' says the man in the window. His face comes into the
light, and he is indeed an elderly man. ``Shinebright was my hero. I
dreamed of studying under him. And I did---for decades! And he treated
me like a child. Always said I wasn't ready. All he ever let me do was
cook and clean and recite answers from books! I'm old now. I had to
stand up to him.'' He clears his throat, apparently to shake off his
feelings. ``He wasn't even a good wizard, I learned. He just had this
wand. So yes, I took it from him, and I turned him into a sheep. I'm
doing what he used to do, and I'm doing it better!''

While he speaks, Hanamir sneaks closer to the door and starts fiddling
with the lock.

``I'm sympathetic to your story,'' says Harlan. ``I'm a human myself.
There is no question that you were wronged. But you sent your goon to
kill us---he was ready to slaughter us in cold blood over this sheep. We
cannot condone this wanton use of deadly force, nor the unchecked
release of transmuted animals to do your bidding. So, I propose an
alternative: you keep the sheep and everything in the tower, and we take
the wand.''

Noke doesn't say anything. Harlan continues.

``We take it to the King of Aberith, and ensure that it is stored in a
safe place, and never used by anyone again.''

``No deal,'' says Noke, finally. ``I am nothing without the wand. I'm an
old man who never learned much magic. But the wand makes me powerful.
I'll give you the tower if you let me keep the wand.''

``And the sheep?'' says Galadriel.

``I also get to keep the sheep,'' says Noke.

``No offense, but this seems like kind of a shitty deal,'' says
Galadriel.

``Well, it is a pretty nice structure. Good tall tower, interesting
layout,'' considers Harlan.

``That's just not what I'm out here for,'' says Galadriel, ``you know?
We told the sheep we'd protect him.''

``I do not plan to slaughter the sheep,'' clarifies Noke. ``All I want
is to see Shinebright live out the rest of his years stripped of his
power. Knowing that I took everything from him.''

``Well, what about your ambition?'' says Harlan. ``You say that's all
you want, but\ldots{}''

``Oh, yeah, well I also want to get rich by doing spells of true
polymorph for people.''

``Mmhmm, mmhmm,'' says Harlan. Hanamir is very close to figuring out the
lock. Harlan stalls for time. ``Would you mind showing us the wand?''

Noke holds it up. It has several odd-looking pieces grafted onto it, and
it is sparking and fizzing in a way that makes everyone instantly
uncomfortable.

``Whoa,'' says Harlan. ``I do not think you should be using that wand.''

With a click, Hanamir succeeds at picking the lock. The door swings
open. Galadriel immediately casts Invisibility on herself. Noke casts
Thunderwave and blasts Hanamir backward, inflicting some damage. Noke
also casts Slowness on the party, but Galadriel dodges it.

The party enters Noke's living quarters. In a rush of flapping sheets
and snapping bedposts, they see that the wizard has transmuted his bed
into a Wyrmling dragon.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

Commercial break. Grainy black-and-white footage of a female gnome in a
kitchen, looking bored, sighing inaudibly.

``Are you TIRED of your USUAL household objects and REGULAR
possessions?''

The gnome holds up a nondescript wooden spoon and sighs again.

``Do you wish that something you own\ldots{} was actually something
ELSE?''

The gnome nods eagerly, then holds her arms in a shrug, as if to say:
``But how?!''

``Take that plain old item from drab to fab with the help of
transmutation wizard Finethur Shinebright!''

A puff of magical pink smoke obscures the wooden spoon, and, in an
instant, the gnome is holding a live owl the size of her entire torso.
She is thrilled, but topples under its weight, and the owl flaps its
wings in distress. A slickly-designed logo appears overtop of the scene,
reading SHINEBRIGHT: POLYMORPHING SINCE THE REIGN OF GERIL II.

``Shinebright! He'll polymorph anything into anything else, at a price
that you won't BELIEVE. Conveniently located on route 2 north out of
Eillin.''

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}


\chapter{Careless Gibber}
\chapdesc{Aberrant blobs have got no rhythm.}

Having made herself invisible, \href{/characters/galadriel/}{Galadriel}
spider-climbs up the wall of Noke's living room and perches on the
ceiling. \href{/characters/hanamir/}{Hanamir} hides behind a set of
barrels. Only \href{/characters/harlan/}{Harlan} is out in the open,
fixing his gaze on the Bed Dragon with equal measures of surprise and
consternation. Noke has come down the stairs from his bedroom and now
sits on the dragon's back.

``I'll give you one more chance to turn over the sheep,'' says Noke.

``We didn't want this to end in violence, but I guess that's how it's
going to have to be,'' sighs Harlan, readying his maul.

``Hand it over, or I'll end you all!'' says Noke.

``In your dreams!'' says Galadriel.

The Bed Dragon grunts, and its voice sounds like cracking wood. Then it
roars with something called Splinter Breath, which is as bad as it
sounds, and blasts everything in a fifteen-foot cone in front of it with
splinters. Galadriel, though invisible, is pricked with millions of tiny
pieces of wood, and feels that she has immediately lost 84\% of her
overall health.

``Ow,'' she says. She shoots an arrow at the dragon and hits, but it's
not much revenge, as it is excruciatingly painful to move, what with all
the splinters. ``Can I have some bread?''

``If you're sure,'' says Harlan. He tosses the satchel containing the
Bread of Eternal Hunger toward her voice and she catches it.

``Yeah, I'm already screwed anyway, what with Lolth and all,'' she says,
and eats a piece of bread. She only gains back 13\% of her health,
though, if she had to quantify it. ``Damn, that was not even worth my
eternal soul.''

Harlan casts Command on Noke. ``Come down off of the dragon,'' he says,
his voice magically amplified. Noke has no choice but to obey. As he
does, Hanamir leaps out from his hiding place behind the barrels and
punches him in the face. The Bed Dragon takes the opportunity to snap
its splintery teeth at Harlan, taking a substantial chunk out of
Harlan's thigh.

``Can I have my bread back now?'' Harlan quips, ripping a spare bit of
bedsheet wing into a tourniquet.

``Not unless I do my Song of Voiding and vomit it into your mouth like a
baby bird,'' says Galadriel. ``I wonder if that would work!''

``No thank you,'' says Harlan. He opts to cast Cure Wounds on himself
instead, but it takes the last of his magical ability.

``Hanamir, we're counting on you, bud,'' says Galadriel. ``This dragon
is getting the best of us.''

``Change your focus from the dragon to the wizard, I think,'' says
Hanamir, barely breaking a sweat as he pummels Noke again.

``Wise,'' says Galadriel, and she releases an arrow that hits Noke in
the arm---not very damaging, but breaking his concentration. The Bed
Dragon collapses into a pile of wood and sheets.

Noke manages to break away from Hanamir and, not seeing a lot of
options, pulls out the wand of true polymorph. It's still sparking and
fizzing. He turns it toward himself. The adventurers watch in
slow-motion horror as the old man begins to melt into a pile of flesh,
eyes, and teeth, babbling and screaming incoherently. He has turned
himself, they realize, into a Gibbering Mouther, and it cannot have been
on purpose. The wand falls to the floor, smoking.

One of the creature's mouths spits some unfathomably disgusting fluid at
Hanamir, blinding him instantly. One of its other mouths then manages to
bite him, bringing Hanamir down to a similar level of injury as
Galadriel and Harlan. This is the closest the three of them have been to
being completely defeated, and boy howdy, what a way to go it would be.

``Move backward, Hanamir,'' Galadriel guides him from the ceiling. ``It
looks like when you get too close, the ground
gets\ldots squishy\ldots and gross\ldots{}''

``Any idea how to fight this thing?'' Harlan yells at
\href{/characters/shinebright/}{Shinebright}, who has been cowering in
the doorway the entire battle.

``It's very slow!'' baas Shinebright. ``Very slow, very dumb, very easy
to hit. Just don't get close to it.'' He stares at the Gibbering Mouther
in what looks like disappointment, but it's hard to tell on a sheep's
face. ``Oh, young Noke. What have you done?''

Hanamir makes a successful attack at the Mouther with his sword, and
uses the momentum to push himself backward and out of the monster's
gooey influence. ``Bad energy if you get too close to that thing,'' he
concludes, shuddering. ``Those voices\ldots not good.''

The critically wounded adventurers each take turns launching their
ranged weapons at the Gibbering Mouther. No matter how poor their aim,
they can't seem to miss it. After one last arrow from Galadriel, the
creature takes multiple final breaths from its many mouths and dies, at
least freed from its evident torment.

``That was a really close one,'' she says.

``Even closer than when we fought the dragon in the Lolth tower,'' says
Harlan.

``Much too close,'' says Hanamir.

Shinebright is leaping in the doorway, baaing his appreciation.

``You did it! I can't believe it! You defeated him!'' he bleats. He is
peering at the wand, which sits on the floor next to the hideous pile of
flesh. ``Now pick it up and turn me back!''

Harlan translates.

``Wait,'' says Galadriel, ``you're not worried about turning into one
of\ldots those?''

``Might be a little unsafe,'' says Hanamir.

``Look, this wand originally only had three charges of true polymorph in
it, but I've been able to make it last for years,'' Shinebright
explains. The wand is still emitting a heck of a lot of black smoke. ``I
don't want to be a sheep anymore!''

``Okay, but even if we succeed in turning you back, you agree that this
wand should be, um, retired, right?'' asks Harlan. ``Like\ldots if it
can accidentally turn things into that\ldots{}''

``Oh, there's always that chance,'' scoffs Shinebright. ``I know how to
use it. Please just turn me!''

``We promise to try,'' says Harlan. ``But we'll need to compromise on
the wand---and set your expectation for the fact that it just can't be
used anymore. It's too dangerous.''

``If you want to see if it works, try it out on your pig friend here,''
says Shinebright, waving a hoof at \href{/characters/buddy/}{Buddy}.
``Turn him back to what he really is, too.''

``You know, that's an idea,'' Harlan says, giving Galadriel a look.

``Harlan, I swear on my life, if you turn Buddy into a Gibbering Mouther
I will never---'' Galadriel starts, but Harlan interrupts.

``What are the odds of it malfunctioning? Like how often have you seen
things turn into Mouthers?'' Harlan considers.

``Oh, it's pretty unlikely,'' baas Shinebright.

``It just happened,'' says Galadriel. ``We just saw that happen.''

``Yeah, so, lightning doesn't strike the same place twice!'' says
Shinebright. Galadriel shakes her head.

``Can we at least take a long rest before we try anything?'' she asks.
``I'm sure we'll have a better shot at success if we're back at our full
capacity. Thinking clearly. Feeling powerful.''

``I like that idea,'' says Hanamir, who has wandered into the library
area and has begun checking out the titles. ``More romance novels in
here than you'd expect. You a romance novel guy, Shinebright?'' He picks
out one that looks interesting.

``Yes,'' agrees Harlan. ``Let's just take the rest of the day easy, and
tomorrow we'll turn you back to your true self.''

Shinebright is not happy about this, but retreats to the garden to eat
flowers and sulk. It's still fairly early in the afternoon, but the
adventurers have been through the wringer and are eager to rest.
Galadriel finds a pair of tweezers and begins removing the Bed Dragon
splinters from her face. Hanamir spends the evening breezing through two
novels: The Time Traveler's Tiefling and The Opposite of Rage is Love: A
Barbarian Romance. Harlan finds some earplugs and tries to ignore the
conversations of every bird that has found a nesting spot in the tower's
many crevices (with limited success).

All in all, they spend a pleasant night in the tower, and emerge the
next morning feeling good as new. Galadriel even manages to find the
time to bedazzle Buddy's collar and polish his hooves.

``All right,'' says Shinebright, with Harlan translating for him. ``Now,
one of you, please, please, please, turn me back into an elf.''

``I'll try,'' says Galadriel. ``But I just\ldots I'm worried for you.
You're not worried?!''

The sheep baas at her insistently.

``Okay,'' she says. ``If you're super sure\ldots{}''

She picks up the wand and takes a closer look. It is in truly terrible
shape, with lots of foreign objects apparently fused into it and glued
to its surface. It shudders with unstable magic in her hand.

She points it at Shinebright and, squinting and turning away, gives it a
wave. For a hopeful moment, they see the sheep turn into a
distinguished-looking elf of indeterminate age---but then the elf starts
to bubble and melt, and in another moment, Shinebright too has become a
Gibbering Mouther, shrieking and drooling. He seems to absorb the parts
of the dead Mouther that was sitting right next to him.

``Well,'' sighs Galadriel, ``I tried.''

``Okay, yeah, I'm so done with this,'' says Harlan. ``Let's leave.''

They turn toward the door. What's left of Shinebright gurgles something
that sounds like ``hey waaaait\ldots{}'' and it seems to give Galadriel
an idea.

``Hey,'' she says, pulling out her vial of
\href{/characters/magick/}{Magick}'s plane-shifting potion, ``what if we
plane-shifted this guy?''

``You'd have to throw it,'' says Hanamir. ``Trust me, you do not want to
get close to that thing.''

Harlan just shrugs.

``Yeah, do it,'' he says with a dismissive wave of his hands. ``I'm over
it.''

Galadriel lobs the vial of potion across the room at the mass of skin,
hair, mouths, and eyeballs. It's not even a good throw, but the glass
breaks. In an instant, the Gibbering Mouther that was once a noble elf
wizard vanishes from existence.

``Wow,'' she says. ``I wonder where it went.''

``Wherever \href{/characters/tannin/}{Tannin} went, probably,'' muses
Hanamir.

With all the Mouthers gone, the room is quiet.

``You know, this place is nice,'' says Harlan. ``For all his faults,
Shinebright had great taste in interior decor.'' He walks a wide circle
around the room and runs a hand across the surface of a shiny oak table.
``I didn't really notice before.''

``It's true,'' says Galadriel. She approaches the pile of sheets and
wood that was once a bed (and then a transmuted dragon), and casts Mend
Object on it. The shattered bedposts spring back together to form a
handsome frame, while the ripped textile elements sew themselves up. The
result is a supremely cozy-looking queen-size bed, neatly made up and
topped with fat pillows. ``I'd sleep in that.''

``And these books!'' says Hanamir, wandering back to the shelves,
sounding giddy. ``I've never read anything like them. There were a few
more titles I wanted to check out\ldots but I don't know if anything can
stack up to The Time Traveler's Tiefling!''

``Want to hang out here, then?'' says Harlan. ``Just for one more night?
We deserve a break.''

The adventurers stay another night in the wizard's tower. Hanamir reads
Wuthering Underdark and cries a little at the end. Harlan plants an herb
garden. Galadriel builds Buddy a mini pig palace.

``Okay, just one more night,'' says Galadriel, tucking Buddy into his
little bed.

The next day, they discover a secret compartment in Shinebright's
bedroom wall. Inside is a spellbook written in a language none of them
is familiar with---the first item that actually indicates Shinebright
had an academic interest in magic beyond the use of his polymorph wand.
There's also 120 gold pieces and a few spell scrolls, which they divide
among themselves.

Another day turns into a few more days, and soon the adventurers forget
exactly how long they've spent at Shinebright's tower. Harlan's garden
is thriving (basil, chives, mint, spring peas, heirloom tomatoes) and
Galadriel spends most of her days writing songs and taking naps with
Buddy in front of the Net of Flyx (Shinebright's arcane portal into
other universes). Hanamir reads every item in Shinebright's vast romance
novel collection (he says it's hard to rank them, but if he had to pick
a favorite, it would be Eventide).

At one point, Harlan empties his metric ton of copper coins into an
antechamber and dives right in. It's the first time he's felt like maybe
he didn't get a raw deal when he opened that treasure chest in the Lolth
tower. It changes his perspective on life, really---and afterward, he
approaches Galadriel and Hanamir, who are finishing up an intense game
of Ye Olde Fantasy Wordmatch in the kitchen.

``Do you guys think we should head back to town soon?'' Harlan asks. He
pours himself a cup of coffee and looks around for a snack.

``Sure,'' says Galadriel, attempting a triple word score with
``Blibdoolpoolp.''

``That's a proper noun,'' says Hanamir. ``Doesn't count.''

``But it's so good,'' she cries.

``Too bad,'' says Hanamir. He checks his points. ``Looks like I win.''

``Ugh, fine,'' says Galadriel. ``Okay, one more round, and then we'll
head back to town.''

Galadriel learns the hard way that playing Wordmatch with a librarian is
a losing game. She packs her things up in a bit of a foul mood, but once
they're back on the road, she's back to her usual self.

``That was fun, you guys,'' she says. ``I feel like we bonded a lot over
there.''

``Yeah, and we really turned that place into a home,'' says Harlan. ``I
wonder if we could try renting it out? Having a little bit of extra gold
wouldn't hurt us on our adventures. And it's not like Shinebright's
coming back for it.''

``We'd need to find a property manager,'' says Hanamir. ``Someone to
handle the tenants when we're traveling. But I agree.''

As they approach the outskirts of Eillin, they notice that guards are
posted at each entrance to the town.

``A half-orc, half-elf, and human traveling together?'' says a guard.
``What is your business in Eillin?''

``You haven't heard of us?'' Galadriel says, miffed. ``We're local
heroes.''

``The mayor can attest to this,'' says Hanamir. ``As can King
\href{/characters/slee/}{Slee} of Aberith.'' He pauses and then shouts
confidently, ``Send for the king!''

``Uh, that won't be necessary,'' says the guard. ``But fine, if
\href{/characters/frunk/}{Frunk} can vouch for you, come in.''

The vibe in town is tense. Frunk meets them at the tavern, looking
harried.

``Where have you three been?'' he snaps at them. ``You left with that
sheep and didn't say anything for weeks. We've been on lockdown. Can't
find \href{/characters/bryn/}{Bryn}'s killer.''

``We're sorry,'' says Harlan. ``We lost track of time. The sheep turned
out to be Bryn's friend, a wizard.''

``Oh, Shinebright?'' says Frunk. ``How's he doing?''

``Bad,'' says Galadriel. ``We accidentally---''

``Uhhh, due to a harrowing series of events, started by his renegade
apprentice, he was unfortunately turned into a horrific monster and
plane-shifted out of reality,'' says Harlan.

``It's been a chaotic time,'' says Hanamir.

``Yes, chaotic,'' agrees Harlan. ``So chaotic that it's hard to say
who's responsible for what. But he's gone.''

``Hmm,'' says Frunk, not following. ``So Shinebright's not living at
that tower on route 2 anymore?''

``No, and we wanted to ask you about that,'' says Harlan. ``Do you know
where we might find someone experienced at managing real estate? We did
a bit of work refurbishing the place and are thinking of renting it
out.''

``We could put a flyer up in the tavern, I suppose,'' says Frunk. ``Or
you could just ask H'Jun.~He needs something else to do besides drink.
He could be your guy.'' He gestures to the end of the bar, where H'Jun
is loudly telling his dragon encounter story to
\href{/characters/fleck/}{Fleck}.

``We'll consider it!'' says Harlan brightly. ``Anyway, have you found
out any more details about the murder?''

``Not much. But we do know this: Shinebright was considered a person of
interest in the case due to his relationship to Bryn. Now, you say he
was turned into a sheep at this time, so it seems unlikely to me that he
could stab a man. A humanoid figure was seen leaving the premises the
night of the murder, so it could really have been anyone. Maybe one of
the orcs, as they passed through the area. But no one knows where they
went, so their motive is inscrutable.'' Frunk scratches his head. ``It's
been a hell of a time in Eillin. We really could use your help
investigating this. The guards won't admit that, but I will.''

``Did Bryn make anyone angry?'' asks Galadriel.

``Or was he perhaps studying something dangerous?'' asks Hanamir.

``That's the thing, we don't know,'' says Frunk. ``There was one book of
his that did get stolen; we know that based on his organizing system,
but we're not sure which one. His interests were so varied, I guess it's
possible he worked on some controversial things\ldots{}''

``Who were his known associates? I know he was a shy person, but surely
he knew some people in town,'' says Harlan.

``Well,'' says Frunk, lowering his voice. ``You know about\ldots the
order I mentioned? The order that is tasked with protecting the town?
Bryn was a member.'' He pauses. ``But I don't know who would be aware
that he's one of us. We keep that information under wraps.''

``If someone does know who's in the order, and is trying to take people
out\ldots who do you speculate would be the next target?'' says Hanamir.

Frunk is silent, chewing on his lip.

``I don't think I can tell you the members of the order,'' he says.

``We don't wish to breach your privacy, but we do wish to protect the
town,'' says Harlan. ``We promise to be careful custodians of any
sensitive information you provide us with.''

Frunk nods, then sighs.

``You've proven yourselves trustworthy in the matter of the Moon
Festival,'' he says. ``King Slee and I did want to hire you to help out
the order when necessary\ldots telling you things on a need-to-know
basis\ldots but maybe it's time we tell you everything.''

The adventurers are silent, their drinks untouched, waiting for him to
continue.

``So. We're known as the Order of the Been,'' says Frunk. ``King Slee
and I are the only two surviving first order members. Uncle was the
founder.'' He sips his ale. ``Bryn was a second order member, along with
\href{/characters/the-savage/}{the Savage}, and
\href{/characters/feld/}{Feld}---you may have met him at the Moon
Festival. H'Jun's cousin.''

``We actually met him in the Lolth priestesses' tower,'' says Galadriel.
``He was imprisoned there. But go on.''

``H'Jun is a member too, but only fourth-order. Same with our bartender
here, Fleck.''

``So who do you think would be next in line as a target, if Bryn was the
first?'' asks Harlan.

``Well, Bryn was the most isolated of all of us. So it makes sense they
went after him first,'' says Frunk. ``I think I'd worry about H'Jun
next. His problem with drinking makes him, um\ldots{}''

``Easy to poison,'' Galadriel finishes as he trails off.

``Fleck is blind, so he's also vulnerable. But I can't imagine anyone
knowing he's a member,'' says Frunk. ``It's safe to say people know that
myself and the King are in some form of allegiance, and maybe they know
enough to connect us to the Savage. But Fleck is not an obvious
associate of ours.''

``Perhaps the book that was stolen contained information about the
identities of the people in the order,'' suggests Galadriel.

``Nothing about the order has ever been put to paper,'' says Frunk.
``We're very serious about that.''

``How long is the king planning to keep his guards here?'' asks Hanamir.

``As long as it takes,'' sighs Frunk. ``Until we can be confident we're
safe. This is the first real murder we've had, you know---lots of orc
raids in the past, but no crimes of passion, really. The king pledged
his troops as long as the threat persists.''

``So, would you give us your blessing to speak to the other members of
the order about this?'' says Harlan.

``It's not technically allowed,'' says Frunk. ``But I believe in this
case it is necessary. I will give you this ring, and if you show it to a
member of the Been, he will be permitted to speak to you on matters
pertaining to the order.''

He hands Harlan a simple gold ring inscribed with a ``B.''

``This was Bryn's ring,'' says Frunk. ``And it's interesting to me that
whoever killed him did not take this ring. It was still on his finger
when we found his body. It may mean that his murderer did not know about
the Been after all.''

``We saw a ring like this in the market once,'' says Galadriel. ``We
told the Savage about it the first time we met him, since we saw that he
was wearing the same thing. And when we went to see if it was still
there, it was gone. We think it was Uncle's, and that the Savage bought
it.''

``Interesting,'' says Frunk. ``I was unaware of this. If he has two
rings, he hasn't made that known to us.''

The group is silent, taking sips from their drinks and pondering what
the Savage's behavior might indicate.

``Well, I think our next step should be going back to the crime scene,''
says Hanamir. ``We should see if we can deduce what book from Bryn's
collection was stolen. It might be a clue to the murderer's identity.''

``Yes,'' says Harlan. ``And we should also ask around about starting our
property empire.''

They leave a generous tip for Fleck, who is still being forced to listen
to H'Jun's intoxicated ramblings, and head out into the town square. The
sun is settling over Eillin, and it would be a gorgeous evening if not
for the nervous energy pervading the place.

``What a strange adventure that was,'' says Hanamir. ``With the sheep, I
mean.''

``Yeah,'' says Galadriel. ``Do you think we did it right?''

``You mean like, did we do the right thing?'' asks Harlan.

``Yeah, like, was there any other way that could have gone?'' she
wonders. ``We tried to help, and we did, but it turned into a whole mess
with the Gibbering Mouthers\ldots and then we sort of stole his
house\ldots{}''

``We tried,'' says Harlan. ``And we learned some interesting things.
Such as the fact that our little friend here is not really a pig.'' He
tilts his head toward Buddy, who is adorably peeking out of the top of
Galadriel's backpack.

Galadriel reaches back and gives Buddy a gentle noogie on his fuzzy
little head.

``Yeah! They keep trying it, my sweet baby boy!'' she giggles. ``They
keep trying to turn me against you, but they can't. I don't care what
you are. You and me, friends forever!''

Harlan groans. Hanamir just goes ``hmm'' in a disapproving manner. Buddy
licks the back of Galadriel's neck and oinks.

Galadriel suddenly acknowledges the camera again, bringing the story
back to this weird meta place where it's a TV special and she's the
host. She winks.

Roll credits.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\hypertarget{pantheon-of-the-gods}{%
\section{Pantheon of the Gods}\label{pantheon-of-the-gods}}

by Malon Magris

We have spent many years studying the gods, their comings and goings and
their power struggles in an attempt to better understand the forces that
shape our world.

While there are countless entities wielding godlike power, is widely
believed that there are 13 supreme entities.

As you know, the gods are often categorized into 8 domains.

There are two domains that are the sole domain of good. The domains of
Life and Light, overseen by \textbf{Pelor} and \textbf{Photos}
respectively.

\begin{itemize}
\tightlist
\item
  \textbf{Pelor} is the god of the Sun, responsible for the creation of
  good in this world.
\item
  \textbf{Pholtus} is a close ally of \textbf{Pelor}'s and associated
  with Law and Light.
\end{itemize}

Just as \textbf{Pelor} and \textbf{Photos} lay claim to the domains most
associated with good in the world, the evil-aligned Death and Trickery
domains are the dominion of \textbf{Nerull} and \textbf{Tharizdun}.

\begin{itemize}
\tightlist
\item
  \textbf{Nerull} is the god of Death, Darkness, Murder, and the
  Underworld
\item
  \textbf{Tharizdun} is the creator of the Abyss, god of eternal
  darkness.
\end{itemize}

Just as war can be just and unjust, fought for good or evil purpose,
there are two sides of the War domain.

\begin{itemize}
\tightlist
\item
  \textbf{Erythnul} represents destruction, envy, and slaughter
\item
  \textbf{Trithereon} represents liberty and retribution
\end{itemize}

Likewise, the Tempest domain has a light and dark component. Both
\href{/characters/kord/}{**Kord}** and \textbf{Gruumsh} lay claim to
storms, and are closely aligned with their war-god counterparts.

Unique among the domains of gods is the Knowledge domain in being
represented by three gods.

\begin{itemize}
\tightlist
\item
  \textbf{Boccob}, the god of magic whose gift has allowed magic to
  flourish.
\item
  \textbf{Istus}, is the goddess of fate and destiny, her knowledge is
  neutral, she is only concerned with the fate of the cosmos, not petty
  squabbles between good and evil.
\item
  \emph{-page missing-}
\end{itemize}

And finally the Nature domain. \textbf{Obad-Hai} is the god of Nature
and \textbf{Beory} is thought of by her druidic followers as the avatar
of the planet itself. Their unwillingness to take a side has earned them
the ire of their fellow gods.

\hypertarget{ranking-the-gods}{%
\subsection{Ranking the Gods}\label{ranking-the-gods}}

It seems mortals are obsessed with understanding the relative power of
the gods. In a sense this is a fruitless endeavor, the true extent of
their powers are unknown. A mortal seeking to determine the difference
between \textbf{Pelor} and \textbf{Pholtus}' might would be akin to
asking whether or a a longsword or a great axe is more likely to slay a
rat. That said, our publisher demands we provide this information as it
moves parchment.

\hypertarget{power-rankings}{%
\subsubsection{Power Rankings}\label{power-rankings}}

\begin{itemize}
\tightlist
\item
  It is fair to say that \textbf{Pelor}, \textbf{Tharizdun}, and
  \textbf{Istus} have no known peers in their respective areas of
  interest.
\item
  Little is known of \textbf{Beory}'s power but if what her followers
  believe is true, she would surely be more powerful than most other
  deities.
\item
  As close allies of \textbf{Pelor} and \textbf{Tharizdun} and owners of
  entire domains in their own right, \textbf{Nerull} and \textbf{Photus}
  are formidable beings that control forces as powerful as death and
  light itself.
\item
  \textbf{Erythnul}, \textbf{Trithereon}, \textbf{Kord}, and
  \textbf{Gruumsh} have never solidified control over their domains and
  as such are seen as slightly less formidable than their peers. That
  said, to underestimate them would be a mistake as they are possibly
  the most ambitious of the gods.
\item
  Little is known of the power of \textbf{Obad-Hai}, \textbf{Boccob},
  and \emph{-torn-}
\end{itemize}

And of course, each of the gods has their demigod accomplices and there
are the gods that create and protect their own kind.

\hypertarget{other-gods-of-note}{%
\subsection{Other Gods of Note}\label{other-gods-of-note}}

\begin{itemize}
\tightlist
\item
  \textbf{Surtur} - god of Fire Giants
\item
  \textbf{Thrym} - god of Frost Giants
\item
  \textbf{Laoggzed} - god of Troglodytes
\item
  \textbf{Hruggek} - god of Bugbears
\item
  \textbf{Sekolah} - god of Sahuagin
\item
  \textbf{Corellon} - creator of the Elves
\item
  \textbf{Lolth} - goddess of the Drow
\item
  \textbf{Shargaas} - Orc Diety of Thieves and Night
\item
  \textbf{Tiamat} - God of Trickery and Queen of the Chromatic Dragons
\item
  \textbf{Blibdoolpoolp} - kuo-toa goddess of death
\item
  \textbf{Moradin} - dwarf god of creation
\item
  \textbf{Yondalla} - halfling goddess of fertility and protection
\item
  \textbf{Sehanine} - elf goddess of the moon
\item
  \textbf{Maglubiyet} - goblinoid god of war
\item
  \textbf{Grolantor} - hill giant god of war
\item
  \textbf{Bahamut} - deity of metallic dragons
\end{itemize}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}


\chapter{Forensic Orcaeology}
\chapdesc{Two cold cases get a bit warmer.}

The next morning, the adventurers awaken in their beds at the inn to the
sound of steady rain on the windows. Only a dull glow indicates that
it's time to get up, and \href{/characters/galadriel/}{Galadriel} is
still skeptical on that point when \href{/characters/harlan/}{Harlan}
tries shaking her to consciousness.

``Come on,'' he says. ``They're reading \href{/characters/bryn/}{Bryn}'s
will soon, and we don't want to be late.''

``I'll skip it,'' she says, pulling her blankets over her head.

``No, you won't,'' says Harlan, shaking her again.

On the other side of the room, \href{/characters/hanamir/}{Hanamir} is
whistling while he makes up his bed with a monk's precision. Galadriel
is only convinced to rise when \href{/characters/buddy/}{Buddy} nudges
her with his li'l snout and offers some encouraging oinks. The party
trudges toward the hill outside town in a chilly rain that makes each
footfall heavy with mud.

Bryn's observatory is no longer bustling with guards and investigators.
Now, it is empty except for a small group of close associates gathered
in the late scholar's library. \href{/characters/fleck/}{Fleck} the
bartender greets the adventurers as they enter and instructs them to set
their horrendously dirty shoes by the door.

``I've been named the executor of Bryn's estate, apparently,'' he
explains, looking a little flustered. ``I guess he must have done that
before the incident with the---well, you remember---the coins.''

He holds up a roll of parchment that must be Bryn's will.

``I can't read this, of course, and I was wondering if one of you
might\ldots?''

He unrolls the parchment, upside-down, and thrusts it in what happens to
be Harlan's direction.

``Yes, certainly,'' Harlan says, taking it from him. ``Not to worry.''

Harlan adopts a dignified stance and walks to the front of the group
gathered in the library.

``Friends of Bryn Starloft,'' he begins, ``we are here today to read the
last will and testament of an extraordinary person. Let us take this
time to honor his passing.''

They all bow their heads for a moment of silence. H'Jun hiccups.

``Now, let's see\ldots{}'' Harlan scans the parchment. ``Bryn Starloft
leaves his observatory to the town of Eillin, in the name of Mayor
\href{/characters/frunk/}{Frunk} Thunderstruck. The mayor shall use his
judgment on what to do with it---it may be made into a public space, or
he may sell it to benefit the town in another way.''

Frunk nods, and lowers his eyes contemplatively. Harlan continues
reading.

``Bryn says his inventions, many of which are `dangerous or incomplete',
shall be destroyed.''

``What?! No!'' Galadriel gasps. Harlan gives her a stern look and reads
on.

``His scrolls, he leaves to his wizard friend, Finethur
\href{/characters/shinebright/}{Shinebright}.'' Harlan pauses and feigns
pondering. ``Have I met him? Not sure.''

``Yes, he was that sheep, from last time,'' says Hanamir, not getting
it.

``Ah, yes,'' says Harlan.

Galadriel looks at both of them shiftily.

``Let's keep reading,'' says Harlan. ``Bryn leaves the top shelf of his
book collection to Fleck, the most voracious reader he knows\ldots{}''
He clears his throat. ``Fleck, we'll get these into Braille for you,
don't worry. There's gotta be a spell out there.''

Fleck's eyes and smile both gleam, and he gives a thumbs up.

``All books on animals go to Finethur Shinebright, to inspire him with
his polymorphs. Yes, yes, he'll certainly need those.''

Galadriel disguises a giggle as a sneeze.

``Books on various schools of magic should go to Ahmed Noke,
Shinebright's worthy apprentice. Also a very reasonable bequeathing.
Bequeathal? Bequeathment? Yes.'' He clears his throat again. ``I hear
the young upstart loves magic. May he read these in good health.''

Harlan takes a sip of something from his flask.

``Ahem. Books on religion should be left with that up-and-coming cleric
of \href{/characters/kord/}{Kord} who has recently passed through
town.'' He pauses, smiling. ``He must be talking about me!''

``Yes, we've set those aside for you already,'' says Frunk.

``And finally\ldots the book beginning with the letter `V' should be
destroyed, immediately, before it falls into the wrong hands,'' he says
slowly.

``Already taken care of,'' says Frunk. ``We burned it along with the
inventions, as he wished.''

``Do we know why he thought this book might be dangerous?'' asks
Hanamir.

``No, we just followed his instructions. Bryn was a very learnd man,
and none of us could read the language this book was written in. Nothing
we could even recognize,'' says Frunk.

``And one is missing, right? Stolen by the murderer?'' says Galadriel.
``How many does that leave?''

``Twenty-four, now, after destroying one and another being stolen,''
says Frunk.

Hanamir has been peering at the piles of books.

``I think the missing book is about animals. According to the number of
books he left Shinebright, there should be one more animal book than
there is,'' Hanamir says.

``Well, we can at least take what's meant for Shinebright and Noke to
the wizard's tower,'' says Galadriel, winking obviously at Harlan, who
turns pink and looks a little sweaty.

``So what now?'' asks Harlan, too loudly. ``What will happen to the
town? And to the observatory?''

``We'll stay locked down until the threat has passed,'' says Frunk.
``And, if you were to bring his murderer to justice, I'd say Bryn might
want the observatory left in your capable hands. If not, perhaps we'll
turn it into a public library---a monument to his legacy, and a gift to
the people of Eillin.''

``A fitting tribute,'' says Harlan. ``Say, can you enlighten us as to
Bryn's system? How did you know that one book in his collection was
missing?''

``Bryn went through many books, never keeping more than 26 at a time in
this particular bookshelf. If he got a new one he wanted to place there,
he was adamant about removing another one first. We never quite
understood why. The `V' book must have been important if it made it into
his group of 26.''

``Why 26?'' asks Hanamir. ``One for each letter of the alphabet?''

``Let's look at the titles,'' says Harlan.

Sure enough, there is a book for every letter, except for `V'\ldots{}
and `D'.

``Dragons!'' says Galadriel abruptly. ``The stolen book must be about
dragons. An animal book that starts with a `D'? Come on!''

``Do we know anyone who might want to steal a book about dragons?'' says
Harlan.

``Yes,'' says Hanamir. ``Remember the tiefling,
\href{/characters/magick/}{Magick}? The tiefling whose village, home,
and family were burned to a crisp by a dragon?''

They each look at each other, stunned at how much sense this makes, and
how quickly it came together.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

The adventurers head back to town and stop by the market, which is
crowded despite the foul weather. One drow has set up a stand selling
enchanted umbrellas that repel water and envelop the user in a toasty
warm glow. A family of half-elves is brewing hot chocolate, and the
scent wafts throughout the market square.

Hanamir fills in Harlan and Galadriel about the tracks he saw outside
Bryn's observatory.

``I was following some tracks north away from Bryn's when you sent that
bird to come and find me, Harlan,'' he explains. ``I came as soon as I
could, and we fought Guz and his goons, and we continued on to
Shinebright's tower. But I think those tracks might be our best lead if
we want to find Magick---or whoever it was that killed Bryn.''

``Yes, that sounds promising,'' says Harlan. ``Is there anything we need
to pick up here before we head that way?'' He takes a brief look at a
stall displaying some very cool hats. ``I don't think I need anything,
but I would like to exchange my copper for some silver\ldots{}''

He finds a money exchange stall and comes back with a small pouch of
silver coins.

``I feel at least 80 pounds lighter!'' he says, looking exhilarated.

``And you no longer jangle when you walk,'' says Galadriel.
``Congratulations!''

Galadriel stops at a stall featuring black cloaks and fishnet stockings
for humanoids of all heights, staffed by two very sad-looking drow
women. She purchases a stick of heavy black eyeliner and immediately
applies it, somewhat artlessly.

Hanamir finds a leatherworker and commissions a knife holster that can
be concealed under one's clothing.

``It'll be 20 gold, and you'll have to pick it up tomorrow,'' says the
craftsman.

``It's a deal, brother,'' says Hanamir.

``Shall we go find those tracks, then?'' says Harlan, once Hanamir has
worked out the particulars of his order.

``Let's,'' says Hanamir.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

Hanamir leads them back out of town, past Bryn's observatory, until he
finds the remnants of the tracks that led him north toward the
mountains. The rain has made them almost undetectable. They walk in
silence, Hanamir leading the way, until they come to a circle of stones
arranged around a rune etched in the ground.

``A teleportation circle,'' says Galadriel, touching the stones. ``This
location is linked to another one via this rune. Someone created a
portal here and passed through it. And\ldots it looks like they did it a
little sloppily, like they were in a hurry.''

``If only someone had been here to see them do it,'' says Harlan.

``Galadriel, could you use Speak With Animals, and see if a creature
nearby saw something?'' suggests Hanamir.

``Good idea!'' she says. She looks around the area and sees a groundhog
poking its head out of a little hole near the rune. A burst of magical
energy shoots from her hands and makes the groundhog glow for a moment.

``Hello, little one. Do you know what happened here?'' she asks the
groundhog.

``It messed up our hole!'' says the groundhog in an impossibly tiny
voice.

``Who did?'' says Galadriel.

``That\ldots{} demon looking thing!'' says the groundhog.

``Around what time was this?''

``The moon was up for a very long time!'' says the groundhog. ``I was
confused!''

``Oh, that's right. Sorry. What happened to the hole?'' says Galadriel.

``The demon put these rocks all over it! And we had to re-dig it!''

``I'm so sorry. Can you describe the demon you saw?''

``It looked like it was very scared! Very frightened!''

``And was she holding anything?''

``Carrying a bag! About as big as me!''

``Did she say anything?''

``No! Just fled in terror!''

``Did she look injured?''

``No! Just very scared!''

``Did she have any weapons?''

``Maybe a small dagger!''

Galadriel translates and looks at Harlan and Hanamir, as if to say,
\emph{A dagger, ehhhh?}

``And did you see anything through the portal she made?''

``It felt cold!''

``Thank you so much, little guy. Do you want some food?'' Galadriel
crumbles up a bit of a granola bar and puts it on the ground.

``Sure! But I'm watching my groundhog weight!''

The groundhog picks up the granola and pops back in the hole with a
\emph{voooop} sound.

``Gotta go!''

``It felt cold, he says,'' says Harlan, chewing his lip. ``I bet the
city of the dead is pretty cold.''

``Or the mountains,'' says Hanamir.

``Guys? I have the strong sense that we're being watched,'' says
Galadriel. ``I think Magick might be able to see us from the other side
of the portal.''

``Should we try and leave a message for her?'' says Harlan.

``I think we can probably just talk to her,'' says Hanamir. He turns
toward the stone circle. ``Magick, we understand your motivations and
we're sympathetic. We, too, seek justice for the wrongfully murdered
tieflings of your village. We'd love to work with you, if you're
interested. Please show yourself.''

There seems to be no response, until Harlan points upward.

``Look!'' he says.

There are words appearing in the clouds, disrupting the steady patter of
the rain.

\emph{TOWN DEFENDED}

\ldots{}

\emph{WILLING TO MEET}

\ldots{}

\emph{ABERITH?}

``How about\ldots in seven days?'' Hanamir asks the sky.

\emph{SOUNDS GOOD}

``Where in Aberith, though?'' says Harlan.

No more words appear in the clouds.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

``We have seven days to pursue other topics of interest, then,'' says
Hanamir, leading the way back south. ``And for my money, I want to know
what happened to the stolen books from the orc encampment.''

``We never looked at the temple near the encampment,'' says Harlan.
``Would you want to head over there next?''

``Yes,'' says Hanamir decisively.

It's a long walk. The rain begins to clear as they pass by Eillin again,
going around it instead of through it to avoid the heavy security at the
border. By evening, they have reached the temple on the outskirts of the
abandoned orc encampment. The City of the Dead is visible in the
distance, surrounded by a stark obsidian wall.

Hanamir does a quick stealth-lap around the temple to check for any
obvious traps or guards. He finds no traps, and sees that there is only
one door, slightly ajar, underneath a red glass window in the shape of a
crescent moon. He sneaks inside. Galadriel and Harlan approach the
temple but don't enter, listening and waiting.

Two orcs are inside. They seem to be searching for something. Hanamir
notices that they're not dressed as Shargaas followers, and wonders if
they might be looters. He approaches them.

``How ya doin', brother?'' he asks one of them.

``Brother? Who are you?'' the orc asks, looking him up and down. The
other orc chuckles in a series of grunts.

``Oh, just a traveler passing through,'' says Hanamir. Galadriel and
Harlan grip their weapons.

``You happen to know what went down here, brother?'' says the orc.

``I know a lot of things,'' says Hanamir. He makes a quick signal behind
his back. ``Hell of a day, isn't it?''

The orcs aren't interested in chit-chat; they draw their swords. Harlan
and Galadriel storm in to back up Hanamir. Galadriel throws up her
iounstone and climbs up the wall, readying her crossbow and aiming it at
one of the orcs.

Hanamir makes a swift slice at one of the orcs and kills him instantly.

``You wanna reconsider, friend?'' he asks the other orc.

The orc says nothing and takes a swing at Harlan. He misses, and Harlan
crushes his skull with his hammer.

A third orc, dressed in some fancier armor, appears in the temple.

``Did you see what just happened to your two friends, brother?'' asks
Hanamir merrily, seemingly energized by the two one-hit kills. ``Maybe
you'll think twice, if they didn't.''

The third orc conjures a spectral hammer and uses it to try and knock
Galadriel off her perch on the wall. She loses her footing and takes
some damage, but quickly rights herself.

``Say, how's your mother, son? Haven't seen her in a couple months!''
says Hanamir at the final orc.

``OHHHH SNAP!'' says Galadriel, absolutely living for this
sassier-than-usual Hanamir.

The orc growls but says nothing. The mockery seems to have unsettled
him, though, and Galadriel lands an arrow and Harlan a hit with his
hammer. The orc swings and misses at Harlan.

``Something wrong with your arm, son?'' says Hanamir.

The orc growls again and launches another unsuccessful attack. Harlan
hits him again and he falls to the ground---not dead, but winded.

``If you let me go, I won't knock the drow off the ceiling,'' he says to
Hanamir, in Orcish.

``Drow?'' says Hanamir, then realizes Galadriel is rocking a drow-esque
look today, what with the eyeliner. ``Ah. You see, brother, part of the
idea of a deal is that it's a transaction. If you're offering something,
what's the deal?''

``I won't knock her off the ceiling\ldots{}'' wheezes the orc, spitting
up a little blood.

``In exchange for?'' says Hanamir.

``You not killing me,'' says the orc.

``Not killing you, like I killed your dad, you mean?'' says Hanamir,
prompting a \emph{DAAAAMN!} from Galadriel on the ceiling.

The orc glowers at him and makes a half-hearted swing.

``Haha, I'm just messing with you. How is your old man?'' says Hanamir.
He brings down his sword and kills the orc.

``That was pretty messed up,'' says Harlan, looking impressed but
concerned.

``I want my books back,'' says Hanamir darkly.

They search the temple. Galadriel decides to climb over to the
crescent-shaped window and punch out a pound of red glass, just in case
that ever comes in handy again. Harlan checks out the dead orc's fancy
armor, and concludes that while it's unusual, it's not something he's
interested in taking for himself.

Behind a secret compartment in the altar, they find a book. It's a title
that was also part of Bryn's collection: \emph{Anatomy of Bugbears,
Second Edition}. But inside this one is a sticker that makes Hanamir's
eyes brim with tears:

\emph{Property of Drephis State University}

And, to make it worse: the book has been desecrated. Completely hollowed
out. It's nothing but a rectangular cavity between two covers and a
spine.

``How dare they,'' he whispers. He has lost all of his earlier zest and
humor.

Hanamir quakes with rage and puts the book lovingly in his backpack.
It's not much of a lead, but it's the first he's seen of his missing
books in quite awhile---and he's determined to find the rest.


\chapter{The Thaumazoologist}
\chapdesc{A new friend, and the party must decide whether to brave the City of the Dead.}

The adventurers huddle in the center of the empty orc temple. After
\href{/characters/hanamir/}{Hanamir}'s discovery of the hollowed-out
copy of Anatomy of Bugbears, Second Edition, they need to discuss their
next move.

``We should see if we find anything else in the encampment nearby,''
says Hanamir. His face looks like the placid surface of the ocean above
a deep-sea kraken fight. His fists are clenched; he's almost daring the
orc encampment to contain more defaced library books.

``Agreed,'' says \href{/characters/harlan/}{Harlan} delicately. ``But
first, do we maybe want to search this place once more, in case we
missed anything?''

``Yes, let's just do it for peace of mind,'' says
\href{/characters/galadriel/}{Galadriel}. She smiles tentatively at
Hanamir, who gazes into the middle distance.

They scour the temple top to bottom, and find shockingly few items of
interest. There are zero religious texts devoted to Shargaas, no sacred
implements, nothing in the way of sacrificial plunder, even. They just
about call it a loss when, leaning on the altar, Harlan activates a
well-hidden switch. The altar begins to swing sideways, and Harlan
stands over a stone staircase leading down into a dark pit.

``Whoa,'' he says. A chilly air creeps up the staircase, making him
shiver.

``Let's check it out, I guess,'' says Galadriel. ``With my blindsight, I
can lead, if you want---''

``No need,'' says Hanamir, and he springs down the stairs in silence.
Harlan and Galadriel follow in their usual formation.

The stairs lead down to a small cellar. It's at least 15 degrees cooler
than the temple and smells damp. The square of light above them
illuminates two squalid, iron-barred cells: one is empty, and the other
contains an elf woman shielding her eyes.

``Ow,'' she says, sounding hoarse. ``I haven't seen sunlight in days.''

Galadriel's ears perk up at the familiar voice, though she can't quite
place it. The elf woman's soft blue hair is sectioned into disheveled
plaits around her face. She squints up at the adventurers from the dirt
floor, and Galadriel finally gets a good look at her.

``\href{/characters/hermione/}{Hermione}? Hermione Daydark?'' Galadriel
gasps. ``It can't be you! It's been so long!''

``Galadriel?'' says the elf woman slowly. ``Silmion and Luthien
Moonwater's grandkid, right?''

``Yes!'' squeals Galadriel. ``From music class! I'm a bard now!''

``No way!''

``Not to interrupt a reunion here, but who is this?'' says Harlan,
interrupting the reunion. ``And what is she doing in an orcish jail
cell?''

``I don't know,'' says Hermione, the elf woman. ``I woke up here, and
I'm so confused. I'm just glad to see other people who don't smell
like'' ---she catches herself, noticing Hanamir--- ``um, like feet.''

``Smells worse than feet! Smells like an orcish prison!'' chuckles
Galadriel. ``Because that's what it is!''

``Can you get me out of here? It's locked pretty heavily, and my mind
feels so fuzzy, I don't remember any of my spells,'' laments Hermione.
``I don't have any of my things\ldots{} not even my notebooks\ldots{}''

``Yes, of course,'' says Galadriel. She tugs on the bars, testing them.
``We probably don't even need to use magic.''

``Hold on, do we trust her?'' says Harlan, glancing furtively at
Galadriel.

``Oh, yes, one hundred percent,'' says Galadriel. ``I know her from
home. She's a Moon Elf, like me.''

``That doesn't necessarily mean\ldots{}'' starts Harlan, but Hanamir is
already attempting to pick the lock. In the semidarkness, though, it's
hard for him to see what he's doing. ``Oh, fine, stand back, I'll just
use the hammer.''

Harlan smashes the lock. Galadriel offers a hand to Hermione, who steps
out of the cell unsteadily.

``Wow,'' she says, still blinking. ``Thank you, all of you, so much. I'm
Hermione. It's very nice to meet you. What are your names?''

``I am Harlan, cleric of \href{/characters/kord/}{Kord},'' says Harlan,
bowing deeply.

``Hanamir,'' says Hanamir.

``I met them at \href{/characters/fleck/}{Fleck}'s Tavern in Eillin some
weeks ago,'' explains Galadriel. ``We have been traveling companions
ever since.''

``Wonderful,'' says Hermione. ``You know, of all our classmates, I
suppose it makes sense that I'd run into you out in the world, in such
diverse company.''

``Thanks, I think!'' says Galadriel. ``Hey, is that your stuff over
there? Looks like they just locked it in the other cell.'' She points at
a jumbled pile in the corner of the second cell. Harlan smashes the
second lock.

``Oh, thank goodness! My notebooks!'' Hermione cries. ``And the rest
must belong to that gnome fellow who was here\ldots{} a crossbow, some
silver, and a letter\ldots{}''

``A gnome?'' says Harlan.

``Yes, a nice little guy,'' says Hermione. ``We talked for hours, or
what seemed like hours, in the darkness. They removed him from his
cell\ldots{} I can't say how long ago.''

She opens the letter.

``It says it's from Syndra to Rompit---ah, yes, Rompit, that was his
name---and Syndra says, \emph{`Not to worrye; thinges are going fyne;
but it'll be a bit longer untylle I get home; Lookinge into a waye to
bring back Dad.'}''

``Does that mean anything to you?'' asks Harlan.

``Not really,'' says Hermione. ``We mostly talked about, you know, what
we'd regret most if we died in here.''

``Understandable,'' says Galadriel. ``But before we go, let's make sure
we're not missing anything in here. We almost left the temple upstairs
without finding you!''

Hermione shudders.

They search the cellar. Hanamir brushes some dust off one wall and
uncovers a small seam, betraying the door to a wretchedly narrow
crawlspace. None of them can see anything when they look inside; it
appears to slope downward and become increasingly tiny.

``It's in the direction of the sealed city,'' notes Hanamir.

``Could this be a way in?'' wonders Harlan.

``A way in?'' says Hermione, blanching. ``Why would you be looking for a
way in to the City of the Dead?''

``It's a long story,'' says Hanamir, seeming to regain some of his
earlier pep. ``And we don't have a reason to go in there yet, but we
should revisit this once we explore the orc encampment. Hermione, does
that interest you at all?''

``As long as it's away from here!'' She gives him a tight-lipped smile.

``Where were you headed, when you were captured by these orcs?'' says
Harlan.

``I was researching magical creatures,'' she says, her eyes brightening.
``It's for my book. I was in pursuit of a very rare variety of unicorn
sighted in this region when the orcs took me prisoner.''

``That sounds fascinating,'' says Harlan. ``I'd love to hear about your
studies while we walk.''

``Really? You'll really take me with you?'' says Hermione. She beams at
them.

``We wouldn't just leave you here!'' scoffs Galadriel. ``You're one of
my own! Come on.''

The three adventurers lead Hermione, still a bit wobbly, up the stairs
and back into the light of day.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

The abandoned orc encampment is not much to look at. There's a fire pit
in the middle, now just a heap of ashes and rubble. There are a few
small tents, each partially destroyed. There's one larger tent that
seems to have been intended for one person, presumably the leader. The
camp may have supported fifteen to twenty orcs, tops.

In the ashes of the fire pit, Hermione spots something glimmering. She
fishes it out. It's a small gemstone, inscribed in a language none of
them can understand.

``This looks ancient,'' she says. ``I think only a specialized scholar
would be able to decipher this.''

In the larger tent, Hanamir finds a singed scrap of paper that he
immediately recognizes as being part of a book on Slaads.

``Oh! This was a good one. The Reproductive Cycle of the Slaad,'' he
says. ``Horrifying stuff.''

He also finds a diagram pinned to one panel of the tent. It looks like a
rudimentary map of the wall that surrounds the City of the Dead. The
orcs had made a few markings around its persimeter.

``I wonder what these mean,'' he muses out loud. Resolving to figure it
out, he rolls up the map and tucks it in his backpack.

Harlan finds an amulet very nearly obscured in the dirt. It resembles
the Shargaas amulet the adventurers found early on in their journey, but
this one has the symbol of an eye etched on it, rather than a crescent
moon. He inspects it for a few moments before pocketing it.

``Trophies of false gods? That's a bit Lolthian of you,'' Galadriel
says, flashing an odd smile.

``Is that approval I'm hearing from you?'' says Harlan. He gives her
some serious side-eye and directs his attention at Hermione, who is
familiarizing herself with some spells from one of the books found in
her neighboring cell.

``All right,'' she concludes. ``They're not my usual fare, but I think I
can whip up Modify Memory, Cordon of Arrows, Skywrite, and Dispel Evil
and Good based on this book.''

``Good,'' says Harlan. ``We'll need all the magic we can get.''

``Yes\ldots{} team, I think there's nothing left for it,'' says Hanamir,
staring out toward the forbidding black wall in the distance. ``Let's
see what we can see of the sealed city.''

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

As they approach the wall, the stench of decay grows stronger and
stronger. There is no life in the shadow of the wall, nothing thriving,
only the stillness of death.

Harlan approaches the wall with caution.

``Guys?'' he says. ``This is weird.''

``What's weird?'' says Galadriel.

``The wall is translucent up close,'' he says. ``I can see the buildings
inside---all abandoned, but looking\ldots beautiful.''

Galadriel approaches next.

``Oh wow,'' she says. ``I can't see through it, so I have no idea what
you're talking about, but wow I want to get in there.''

``You can't see them?'' says Harlan.

``Nope. Can't see nothing. Okay, let's go in,'' says Galadriel.

``Hold up, wait, wait, hold on.'' Harlan grabs hold of her sleeve before
she makes a running jump for the wall, presumably planning on
spider-climbing it. ``Please describe your feelings about the city in
detail right now.''

``Oh my god, why can't I see it?'' she says. ``Is it cool?''

``Um, I guess,'' says Harlan. ``It looks ancient, but not in disrepair
or anything---very clean. No people. Just buildings made of marble. Very
still.''

``Sounds so good,'' says Galadriel. ``Sounds like the museums are going
to be sweet as hell.''

Hermione joins them near the wall.

``Hm,'' she says. ``I can't see through it, either.''

``Are you overwhelmed with the urge to go in?'' says Harlan.

``No,'' shrugs Hermione.

``Okay, we're going to step away from the wall for a bit, then,'' says
Harlan, and he drags Galadriel back in the direction of Hanamir in the
distance.

``You are the WORST, Harlan,'' she flails and struggles to break away
toward the wall. ``You don't UNDERSTAND me and you're always trying to
murder my PIG---''

Harlan rolls his eyes and continues dragging her.

``She wants to go in the city!'' he reports when they rejoin Hanamir.
``She's ensorcelled by something, as per usual!''

``I would like to enter the city as well,'' says Hanamir.

``What?!'' says Harlan.

``The trail of the books leads there,'' says Hanamir. ``My code compels
me to follow.''

``But---but---should we not be better prepared? Would we not be served
by a trip back to town first, before we enter the literal City of the
Dead?!''

``Oh, sure, we can go back to town first,'' says Hanamir.

``I just think we need a plan, at least, before we rush in,'' says
Harlan.

``Of course, that's reasonable,'' says Hanamir. ``Look, I'm just going
to approach the wall, okay? I won't do anything rash. I'd just like to
check it out.''

He walks closer and chucks a rock against the wall. (He's got a great
arm.) It bounces right off.

``Did you learn anything?'' says Harlan.

``Not really,'' says Hanamir. ``But I can't see through it either, and
you can.''

Harlan raises a hand to show the ring of the Been that
\href{/characters/frunk/}{Frunk} gave him before they left.

``I wonder what happens if I take this off.'' He passes it to Hanamir
and approaches the wall again. He returns, nodding. ``Yes. It's the
ring.''

The adventurers begin the trek back to Eillin. They get an
extra-thorough patdown at the border, prompting some outrage from
Hermione.

``Honestly, you're no better than the orcs!'' she tuts. ``This is
ridiculous.''

``Standard protocol, ma'am,'' says a guard. ``A prominent citizen was
murdered not long ago. You're lucky we don't make you surrender your
magical items.''

``You wouldn't dare,'' she sneers. The guards wave them through.

Back at the inn, the adventurers gather over pints of Fleck's ale and
some mediocre pub food. In hushed tones at their table, they discuss
entering the City of the Dead.

``These books are my responsibility,'' says Hanamir. ``If they are all
destroyed, I must seek justice. If they are not all destroyed, I must
recover them.''

``I understand,'' says Harlan. He casts Augury, and a perfect miniature
hurricane swirls from the center of the table under his hand. ``Kord, I
call on thee to answer me this: will a journey to the sealed city result
in weal, or in woe?''

The voice of Kord crackles from the eye of the storm in four bursts:

\emph{Weal.}

\emph{Woe.}

\emph{Woe.}

\emph{Woe.}

The hurricane dissipates, and the four adventurers are left staring at
their drinks.

``So,'' says Harlan. ``About\ldots{} that.''

``There was some weal in there, though, right?'' says Galadriel. She
raises her glass. Hermione clinks with her, just happy to have had a
shower and to be among friends in a well-lit tavern.

``Whether weal or woe awaits me,'' says Hanamir. ``A man must have a
code.''


\chapter{Ring Cycle}
\chapdesc{Acquiring jewelry to stave off apocalypse: a fantasy staple. But is this the real life, or is it just fantasy?}

The early morning sun streams through the windows of the inn above
\href{/characters/fleck/}{Fleck}'s Tavern. The adventurers have had a
long rest, and with it, plenty of time to consider the 75\% negative
opinion of \href{/characters/kord/}{Kord} on the topic of entering the
City of the Dead.

They gather in the room shared by
\href{/characters/hermione/}{Hermione},
\href{/characters/galadriel/}{Galadriel}, and
\href{/characters/buddy/}{Buddy}. \href{/characters/harlan/}{Harlan} has
ordered room service, which Fleck brings up on a heavy tray.

``Thank you, sir,'' says Hermione. ``I like your eyes.''

``Aw, shucks, ma'am,'' says Fleck, glittering. He bows and leaves the
room.

Everyone digs in except for \href{/characters/hanamir/}{Hanamir}, who
sips his tea and looks somehow even more contemplative than usual.

``It's so nice to be back in a town with some elven population!''
Hermione sighs. ``A freshly toasted elf bagel with elf butter and elf
jelly\ldots{} what a delight, after nothing but orc rations!''

``You poor thing,'' says Galadriel, loading some elf cream cheese on her
own elf bagel. ``The stuff they eat is bad enough, but I can't imagine
what they give to their prisoners.'' She takes a bite and continues
talking, muffled. ``You know, nothing beats the elf bagels from home,
but these are nice.''

``These are just regular bagels, guys,'' says Harlan. ``Hermione, is
your memory coming back to you at all?''

``Why, yes!'' she says. ``I remember being on the road, doing research
for my book, and being captured by the orcs. They wanted to use me for
something---my magic? They wanted\ldots{} my ears, I think?''

``What about your fellow prisoner?'' says Harlan.

``The gnome, Rompit! Yes, he seemed very paranoid. He never spoke to me
about anything in this letter, the one from Syndra. And I never saw him
leave the cell. I woke up one day and he was gone,'' says Hermione.

``Do you think he went into the City of the Dead?'' says Hanamir.

``I really don't know where he went,'' she says.

There is a long silence, punctuated by the sound of Buddy chowing down
on some elf muesli. Finally, Hanamir clears his throat.

``Friends, I have something to say,'' he begins. ``The Crypt City is
certainly perilous; more perilous than anything we have yet faced. Given
what we know, and the auguries of Kord, we must expect danger---we may
emerge victorious, or we may not emerge at all.''

Everyone stares at him with rapt attention. Hanamir normally doesn't
speak in paragraphs.

``We could indeed take a more cautious path---gather our strength in
greener pastures, hope that the forces of shadow and death in this place
remain contained, until we are ready. But I do not believe that the
cautious path, in this case, is the wise path. The Shargaasians gather
strength; their evil will not stop with the destruction of my books, and
neither Eillin, nor Aberith, may long withstand whatever darkness they
seek within those black walls. Time, I fear, is not an asset we can
freely spend.''

Drephis State has produced quite the effective public speaker. They
listen on, transfixed.

``Harlan and Galadriel.'' He turns to them. ``We have faced together
many perils. I have no cause to doubt your courage or wisdom, but I know
that this quest is not yours. Hermione, you have recently escaped
captivity and it would be asking much to expect you to join me. This
path is mine, and I will walk it alone if I must---but I ask,
nonetheless, for your help.''

He takes a sip of his tea. No one is sure if he's finished and is
expecting a response, or\ldots{} nope, he continues.

``Come with me, and let us end this threat before it escapes its cage.
You saw the fear that the Lolthians had of the orcs. You know the
history of the town---the orcs and the undead have burned it before, and
they will burn it again.''

His voice reaches a crescendo, and he makes eye contact with each of
them in turn.

``I would choose a different way, if I thought I could. If I could
choose my time, it would be a time of peace. I would choose warm halls
and peaceful study. But this choice is not given to us.''

He looks down at the floor for a lengthy moment, then back at their
faces.

``This is a time of strife, my friends, and a time for heroes. This is a
time of dungeons\ldots{} and dragons.''

Galadriel blinks back the tears in her eyes and claps. Hermione joins
her. Harlan is quiet, and waits for the applause to die down before
responding.

``Well, I think there's no arguing with a speech like that,'' he says,
offering Hanamir a respectful nod. ``We must go to the City of the Dead.
In the interest of not immediately dying, though, I would suggest that
we stop by the marketplace to buy anything Hermione might need, and then
maybe have a quick chat with the town elders. We know now that the ring
of the Been has some type of supernatural power, and there may be more
we don't know about.''

``Agreed,'' says Hanamir.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

In the market, Hermione buys some basic magical supplies necessary for
her spells. She also picks up a longbow and a short sword. While she
rummages in her small bag of silver, Hanamir goes ahead and covers the
charges for all of these items.

``Whoa, thanks!'' she says. ``I'll totally protect the hell out of you
in the city.''

``Don't mention it,'' says Hanamir.

Meanwhile, Harlan approaches Galadriel while she is getting her
bellybutton pierced at a mildly sketchy tattoo stall.

``Can we talk?'' he says. ``I need you to think about what you're going
to do when we get back to the city and the urge to jump ahead into
danger comes upon you.''

``Yes,'' Galadriel sighs. ``I've been doing some reflecting on that. I
feel\ldots{} disturbed\ldots{} by my reaction to the city yesterday.''

``Was it the gauntlet, you think, that was the cause of your reaction?''
Harlan asks.

``I thought so immediately afterward, but now, I'm not so sure,'' she
says. ``I think it wasn't necessarily the gauntlet that was to blame.
But if I could take it off, I would, because I don't want that to be a
wildcard in our exploration of a dangerous place. I don't want to put
any of you in harm's way.''

``As a cleric, I know that Lolth doesn't have any particular alignment
to the undead, or to death. She's more about darkness---and spiders,
obviously,'' says Harlan. ``It may not be related to your gauntlet at
all. We should just be on guard when we next approach the city.''

``You could shackle me, just in case,'' says Galadriel. She pays the
piercer and admires her new jewelry, which is a cool spider charm. ``I
don't want to hurt any of you under the influence of Lolth.''

``Thank you for understanding,'' says Harlan. ``We will see if that's
necessary when we get close.''

They rejoin Hanamir and Hermione. With her new magic supplies, Hermione
performs a ritual to see what she can learn about the shimmering red gem
she found in the fire.

``It's not magical,'' she says, sounding surprised. ``But the
inscription is indeed ancient. It says \emph{Geril IV} in some language
I still can't identify.''

``Geril IV,'' says Harlan. ``Hmm. I'm not familiar with any Gerils, much
less four of them.''

Hermione puts the gemstone back in her bag, seeming unsatisfied.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

The adventurers head over to the residence of Mayor
\href{/characters/frunk/}{Frunk}, a stately-looking place on the corner
of Boogie Woogie Avenue and Market Street. Hanamir uses the heavy door
knocker just once, and Frunk appears.

``Greetings,'' he says. ``I'd been meaning to seek you all out now that
you're back in town.'' He waves them inside, and they have a seat in his
parlor. It was obviously once an elegant room, but looks like it has
been neglected of late. ``I thought you should know that King
\href{/characters/slee/}{Slee} is sending more of his guards. We're
putting Eillin on total lockdown in the next few hours.''

``So there hasn't been any progress?'' asks Hanamir.

``No, none. We fear that the suspect may strike again, and if he is
targeting members of the Been, we want to be extra cautious. There will
be a full garrison of the town by order of the king.''

``Nobody in, nobody out?'' says Harlan.

``So\ldots{} if we wanted to leave, we should do that now?'' says
Galadriel.

``You have about two hours, but yes,'' says Frunk.

``Frunk, what can you tell us about the City of the Dead?'' says Harlan.

``There were raids on Eillin long ago from the undead that dwell
there,'' says Frunk. It's as if a storm cloud has passed over his face
as he remembers this. ``We sealed up the city afterward using powerful
magic. The only way to enter or exit the city is with one of our blessed
rings.''

``I did notice that I could see through the wall while I was wearing
it,'' says Harlan. ``But we also found a tunnel underneath the nearby
orc temple that we believe might lead into the city as well.''

``Oh, no, that's quite impossible,'' says Frunk.

``Are you sure? It was in the wall of the orc dungeon,'' says Hermione,
speaking up for the first time.

``Oh yes---how rude of us---this is Hermione, our new partner in this
quest,'' says Harlan. ``She was captured by the Shargaasians, and has
agreed to help us stop them.''

``A pleasure to meet you, Hermione,'' says Frunk.

``The pleasure is mine, sir,'' says Hermione.

``We believe the orcs were trying to access the city,'' says Hanamir.
``Either through this tunnel, or by chipping away at the wall with
axes.''

``They'll never get in that way,'' says Frunk, and he seems confident
about this.

``What kind of magic is guarding the city?'' asks Hermione.

``I'm afraid that's a question for \href{/characters/bryn/}{Bryn}, who
can no longer answer it,'' says Frunk. ``Sealing the city was his
doing.'' He pauses, frowning. ``What interests you in the city?''

``I believe the orcs have succeeded in entering it, and that they are in
possession of some stolen library books,'' says Hanamir.

``Library books?'' says Frunk. This is clearly not the answer he'd been
expecting. ``Look, the orcs could not have passed through the wall by
any physical means---not underneath it, not through it, not over it.''

``But there is a way in, then? And it involves the rings?'' says Harlan.

``There is a passage through the wall from the Shadowfell, but they'd
need a powerful magic user to access it,'' says Frunk, sighing. ``And,
yes, the rings allow you to pass through the wall.''

``That sounds like a lot of ways the orcs could have entered the city,''
says Galadriel.

``Very unlikely ways,'' says Frunk. ``And if you all are even
entertaining the idea of going in yourselves, I must advise you in the
strongest terms not to do so. You would be putting the entire continent
in danger. If what dwells inside the city were to ever get out\ldots{}''

He trails off and doesn't feel the need to elaborate.

``Why did Bryn make so many rings, then, if even one of them ending up
inside has catastrophic consequences?'' says Galadriel.

``That's just how Bryn set it up,'' says Frunk. ``I assume he had his
reasons. He always did.''

``And what, pray tell, is inside the city that should never get out?''
says Harlan. ``Beyond the undead, which we know about.''

``I fear any more that I say will just encourage you to attempt this
foolish thing,'' says Frunk.

``We're going,'' says Galadriel. ``Anything you say can only protect us
on our journey. Any information you can give us is armor.''

Frunk is quiet for a long moment.

``Though we have never seen him, we believe what dwells in the city may
be a Lich,'' he says quietly.

``A what?'' says Galadriel.

``A Lich. A wizard who has occupied himself with the secrets of
immortality\ldots{} who has defied the gods of death themselves.
We\ldots{} don't know if there is a way to defeat a Lich. They have
surpassed death.''

``Frunk, say that we're right, and that the orcs have in fact found a
way into the city,'' says Hanamir. ``Would this not be a threat that
needs to be addressed?''

Frunk looks Hanamir in the eye, and for a moment, Hanamir can see that
he is very old.

``How sure are you?'' says Frunk.

``The orcs were gone. There were no tracks leading out of the
encampment. There was an underground tunnel toward the city,'' says
Hanamir. ``I don't know how else to interpret the data.''

``What would you have me do?'' says Frunk.

``We'll need a ring for each of us,'' says Harlan.

``I gave you Bryn's,'' says Frunk. ``And I'll give you mine now.'' He
takes off his ring and hands it to Hanamir.

``So you believe we're doing the right thing?'' asks Hermione.

``I don't believe I can stop you from doing it, right or wrong,'' says
Frunk. ``But if one of these rings falls into the Lich's hands, it's all
over.''

``Would you be able to convince H'Jun and Fleck to give us their rings
as well?'' says Galadriel.

``I cannot compel them to do so,'' says Frunk. ``You'll have to ask them
yourselves.''

``Thank you, Frunk,'' says Harlan. ``We promise we'll do all we can to
protect Eillin.''

``You've been lucky before,'' says Frunk as he walks them out. ``Let's
hope you can be lucky again.''

He doesn't say goodbye; he only gives them a long and unnerving stare.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

The adventurers return to the tavern under the inn to talk to Fleck.
It's still morning, so the bar is empty except for its most enthusiastic
patron, H'Jun, who is passed out at one end. Fleck sits on a cushioned
stool behind the bar with a magazine, running his fingers over the
pages.

``Hey, Fleck!'' says Galadriel. ``Whatcha reading?''

``Oh, hi again, guys,'' says Fleck. ``Just this old copy of Bartenders
Weekly. It's the only thing I can get in Braille.''

``I'm sure we can find something else for you,'' says Galadriel,
realizing that she and her companions have made this promise before and
not followed through. ``There's gotta be a spell.''

Fleck shrugs.

``So what brings you to the bar so early?'' he asks.

``We're on another quest to protect the city,'' says Galadriel.

``Sounds like you guys.'' Fleck smiles.

``And we need your help,'' adds Harlan. He lowers his voice. ``Our
newest focus is the City of the Dead. Frunk has been kind enough to tell
us what he knows, and to share with us his ring.''

Fleck's smile falls into a grave line, making his coin eyes look
sinister.

``You plan to enter?''

``We plan to defeat the evil that lies within,'' says Harlan. ``By
entering, yes.''

``Hi! You can't see me, but I'm here, too. I complimented your eyes this
morning,'' says Hermione. ``I'm Hermione. It's nice to meet you.''

``Aha, I thought I smelled someone else,'' says Fleck, bowing a little.
``You're too kind. Nice to meet you, miss Hermione.''

Hermione curtsies, but Fleck cannot see her.

``Listen, I care greatly for all of you. You gave me my beautiful copper
eyes, and you may not know this, but they're great for attracting
business. I do wonder why you would ask me to send you to your deaths by
helping you access the City of the Dead.''

``You believe we're not strong enough to defeat the evil that dwells
there?'' says Harlan.

``I do not!'' says Fleck, laughing. ``Do you?''

``We're not sure,'' says Galadriel. ``But we believe that a party of
orcs has entered the city already. We fear that they are trying to loose
the terrors within upon the world. And if no one confronts them, we will
surely all be dead soon.''

``These are strange times,'' says Fleck. He takes off the golden ring he
wears on his left index finger. ``I will give you my ring.''

He reaches out with it, and Galadriel's hand meets his. She takes the
ring and quickly puts it on.

``Thank you, Fleck, thank you,'' she says.

``Have you heard anything interesting lately at the bar?'' asks Hanamir.

``I have heard of the recent discord among the orcs. Some travelers
passing through have seen orcs battling each other---there's something
that has divided them up amongst themselves,'' says Fleck.

``Have you seen \href{/characters/the-savage/}{the Savage}?'' says
Galadriel.

``Not since the day of the Moon Festival,'' says Fleck. ``And only
briefly. He hasn't been back.''

A pathetic groaning can be heard at the end of the bar. H'Jun lifts his
head and stares at them as if they are a five-headed Wyrmling from the
Ethereal plane.

``Oh hey, bud!'' says Galadriel, adopting the tone of voice she reserves
for babies and small animals. ``You doin' okay?''

H'Jun groans again.

``What day is it?'' asks Galadriel.

``Today!'' grunts H'Jun.

``How many fingers am I holding up?'' Galadriel makes a peace sign.
H'Jun has to think about it.

``Nine?'' he guesses.

``Incorrect,'' says Galadriel, looking worried.

``I heard you were looking for a property manager,'' he slurs, somehow.

``Yes!'' says Harlan, thrilled. ``We can pay you a good wage if you take
care of the place and manage the tenant relationships. It's a truly
one-of-a-kind space.''

``Where is it?'' says H'Jun.

``You know \href{/characters/shinebright/}{Shinebright}'s place, north
of town?'' says Hanamir.

``He's not living there anymore?'' asks H'Jun.

There's a pause.

``Nope,'' says Galadriel.

``Did I tell you about the dragon?'' says H'Jun.

``Yes, you actually mentioned that at the Moon Festival,'' says Hanamir.

``Nobody believes me!''

``We believe you,'' says Hermione. ``I'm Hermione, by the way.''

``Oh, we've met,'' says H'Jun.

``Have we?'' Hermione is befuddled. ``I don't think so.''

``Yeah, I'm pretty sure we have.''

``Um, anyway, we were wondering if you might part with your ring,'' says
Harlan. ``We're trying to get into the City of the Dead, and we
know---''

``Oh, sure, you can have the ring,'' H'Jun says, slipping it off and
rolling it down the bar at them. Hermione catches it. ``If I could just
get a month's pay ahead of time\ldots{} I'm a little behind my bar tab,
and I just need a little extra\ldots{}''

``Yes, we can arrange that,'' says Hanamir. ``Will you look for a tenant
for the property?''

``Sure!'' says H'Jun.~He seems more lucid now. ``So you all are staying
with Shinebright, then?''

``Oh, um, no, unfortunately, he won't be back,'' says Harlan.

``Did the dragon kill him?!'' says H'Jun.

``We don't know that it didn't,'' says Hanamir.

``No one believes me! They all just say I was drunk!''

``Were you, though?'' asks Galadriel.

``I was eight!''

``But were you drunk, though?'' she repeats.

H'Jun sighs.

``Yes,'' he says.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

Back in the town square, the adventurers start making their plans to
leave Eillin before the lockdown begins. Galadriel admires the ring
Fleck gave her. It's large enough that she wears it awkwardly on her
thumb, but she finds it cool nonetheless.

``Let's all put our rings together and do a `go team' thing,'' she says.
She expects everyone to roll their eyes and refuse, but they don't!
Without mockery, the four of them lift up their hands and touch rings.
But before Galadriel can make a speech about togetherness and teamwork,
they each feel something like a mild electric shock as the gold bands
meet.

``I can feel the other rings!'' says Harlan.

``Me too,'' says Hanamir.

``One more here in town\ldots{} that must be
\href{/characters/feld/}{Feld},'' says Galadriel.

``One in Aberith, for the king,'' says Hermione.

``And one beyond the wall,'' says Hanamir.

Without discussing it further, they rush back to Frunk's house.

``Frunk,'' says Hanamir, when the mayor opens his door. ``What you
feared has already come to pass. There is a ring of the Been inside the
City of the Dead.''

``You have my blessing to go in,'' says Frunk. He looks resigned to the
apocalypse. ``If you are to have any chance at surviving, you'll want to
go back to Bryn's observatory. He had a book on Liches that might be
helpful. I don't believe it was among the books he bequeathed to others;
it'll be in his remaining collection---what was to become a public
library.''

``Is the person inside the sealed city\ldots{} is it the Savage?'' asks
Harlan. ``We believe he has two rings, not just one.''

``It may be him. And he may have two. I cannot say.''

``Thank you, again, for all your help,'' says Harlan.

And with that, the adventurers leave the town of Eillin, just as the
garrison is preparing to stop all traffic to and from the city. Bryn's
observatory rests upon the nearby hill like a student who has fallen
asleep sitting up in class. The adventurers jolt it awake with the sound
of their footsteps.

The book on Liches is not difficult to find: even in death, Bryn is
impeccably organized. Hermione dusts off its spine and reads aloud.

``Liches circumvent death by separating parts of their souls and storing
them in objects called phylacteries,'' says Hermione. ``Oh, so like,
horcruxes.''

``What?'' says Harlan.

``Don't worry about it, I read a lot,'' says Hermione. ``When a Lich is
killed, it lives on through the phylactery. It can then re-form a new
body. So it sounds like we're going to have to not only kill the Lich,
but destroy its phylactery, too, in order for it to be really gone.''

``How do we know what the phylactery is?'' asks Galadriel.

``Good question; we don't. It says the phylactery can be anything,''
says Hermione.

They all ponder this while Hanamir browses Bryn's book collection for
anything else that might be useful. Hermione puts the book on Liches in
her bag.

``Are we ready?'' says Galadriel.

``Ready as we'll ever be, I guess,'' says Harlan.

As they prepare to leave, Hermione steps on a squeaky floorboard. It
shifts noticeably.

``What's this?'' she cries, pushing it to the side with her foot. ``I
think there's another book in here!''

She kneels down and removes the floorboard. Inside is a heavy hand-bound
book covered with a sheen of dust. Each page is filled with Bryn's neat
but cramped handwriting.

``I think it's a journal,'' she marvels. She flips to the last page that
contains text.

``The last entry is dated just before the Moon Festival,'' says Hanamir,
looking over her shoulder. ``The night he died.''

``He writes that he noticed the orcs striking the walls of the sealed
city,'' Hermione reads. ``He says he knows they won't get in, but
wonders how long it'll take before they try another method. He says if
the undead hordes threaten Eillin again, he'll have to do some magic to
address it.''

``Mind if I keep this?'' asks Hanamir. He hasn't forgotten his pledge to
bring Bryn's killer to justice.

Hermione hands it to him. They leave the observatory and let it fall
back into its slumber.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

The adventurers decide to check out the tunnel in the underground jail
cell before approaching the wall. There's not much conversation between
them as they follow the now-familiar path southward.

The opening to the tunnel is just as they left it: dark, cramped, and
forbidding. Hanamir ties a rope around his waist and climbs inside, but
after about twenty feet, he's finding it difficult to move his arms at
all.

``Pull me back, please,'' comes his voice, sounding faint. Harlan heaves
on the rope until Hanamir is able to wiggle himself free. He emerges,
covered in peaty-looking soil.

``It gets very, very narrow,'' he reports. ``I don't think any of us
will have much luck in there.''

``I think I have an idea,'' says Hermione. She flips through one of her
books until she comes to the spell she's looking for: Find Familiar.

She begins to conjure a small creature out of a puff of magical energy,
spinning him into material existence with her hands like cotton candy.
It's the first time they've all seen her practice serious magic, and
they're all rather impressed with how elegant her process is. The
creature glows with what they would later recognize as Hermione's
magical signature: a soft blue light. It twitches its tiny nose at them
and practices digging in the cold earth floor of the jail cell.

``No no no,'' says Hermione. ``Sir Digs-a-Lot, we're going to put you in
here.'' She lifts him up to the mouth of the tunnel. ``Go in there and
tell me what you see.''

``What is that?'' asks Galadriel. ``A groundhog?''

``A prairie dog!'' says Hermione. ``They're not usually magical, but I
have a soft spot for them anyway. I've encountered a few in my
studies.''

Her eyes have taken on an eerie cast, the color of milk.

``He's about seventy feet in,'' she says. ``The tunnel slopes downward.
And then---wow, there's an enormous chasm. It's\ldots{} I think this
leads to the Underdark?''

They switch their focus from the mouth of the tunnel to Hermione's face,
and back again, as if waiting for some visual confirmation that this is
true.

``Glowing mushrooms\ldots{} creatures that look like squid, floating in
the air\ldots{} I can hear something that sounds like bats' wings. No
humanoids so far, but there is a rope at the edge of the chasm. Someone
was here and climbed down. I wonder if it was Rompit!'' She looks
suddenly worried. ``There's a giant snake at the bottom of the
chasm---and some huge red scorpion spiders---and I think if I let him go
any farther, I'll lose contact\ldots{}''

She calls the enchanted prairie dog back. It takes him a few minutes,
but soon the little creature appears again at the opening of the tunnel.
It hops down and sits at Hermione's feet.

``Good work, little guy!'' she says, picking him up and letting him sit
on her shoulder. ``I'm going to keep you with me while we approach the
sealed city. You might be able to do some scouting for us in there.''

The down side of this plan is that, while Sir Digs-a-Lot is active,
Hermione is blind. She can only see through the eyes of the prairie dog
that sits on her shoulder. For now, this is fine, but it does feel
awkward to make eye contact with the small furry creature during
conversation and not with the woman herself.

``You could send him into a pocket dimension temporarily, you know,''
says Hanamir. He's trying to be helpful, but Hermione reacts as if he's
just suggested she should drown a puppy.

As the adventurers approach the wall, the gravity of what they're about
to attempt starts to feel quite real and quite scary. Only Hanamir seems
unperturbed as ever. At first, the rest of the party attribute this to
his zeal for rescuing his stolen books, but it's not long until it takes
an uncanny turn. With about fifty meters to go, he breaks into a full
sprint toward the wall.

``Hanamir! Wait!'' shouts Galadriel, but Hanamir either can't hear her
or doesn't care to listen.

``You're not feeling the urge to run in, are you?'' Harlan checks with
her.

``No,'' she says, frowning. ``I think it got Hanamir this time.''

Hanamir has already disappeared through the wall. Harlan, Galadriel, and
Hermione start running after him. And thus, without ceremony, the
adventurers burst through the wall and enter the City of the Dead.

Luckily, Hanamir hasn't gone far. He's standing at an intersection ahead
of them, staring down a skeleton on the other side of the road who holds
a lute and wears a silly, old-fashioned hat. The city is pristine and
unruined, just as Harlan had described it. All the impressive marble
walls of the buildings look freshly powerwashed. There is no one around,
though, except for this skeleton and his jaunty hat.

Galadriel, Hermione, and Harlan catch up to where Hanamir stands,
enraptured at the sight of the skeleton. The three of them are a bit
embarrassingly winded. Galadriel clutches her knees and lets Buddy down
from her backpack to reduce the weight. Buddy snorts and sniffs at the
ground, looking agitated.

``Hanamir,'' she says. ``What's going on? Why didn't you wait for us?''

``Just felt like the right time to go in,'' he says cheerfully. ``What a
city, am I right?''

``I mean, yeah,'' says Galadriel. She catches her breath, to an extent,
and looks around. The tallest building, its domed ceiling gleaming in
the distance, seems to be in the center of town. She notices the
skeleton across the street is holding a lute. ``A dead musician,'' she
wheezes. ``That'll be me in about five seconds if I don't get some
water.''

Seeming to hear her, the skeleton strums a chord on his lute and beckons
them to follow him. He points at a nearby tavern. Its sign says ``The
Ball \& Socket.''

``Ha! Cute,'' says Galadriel.

``Careful,'' warns Harlan. ``Please, please do not try to befriend this
actual minion of the undead just because he has a lute, please\ldots{}''

``I like your style, bud!'' Galadriel calls to the skeleton. She takes
her lute out of its case and does a little riff on it, which the
skeleton mirrors. ``Wow, you're good!''

``Oh my god,'' says Harlan. He quickly thinks of a distraction. ``Hey,
why don't we see if we can pinpoint the location of the Been ring that's
inside the city, now that we're here?''

The adventurers press their rings together again, but they don't get a
clear picture of where the other ring might be. It's close, but they
don't know much more than that.

``You know, I think I like this guy,'' says Galadriel, after another
round of back-and-forth lute riffing with the skeleton.

``Kord save us,'' says Harlan. ``Hermione, would you let Sir Digs-a-Lot
roam around the area a bit and see what he sees?''

``Good call,'' says Hermione. Sir Digs-a-Lot jumps down from her
shoulder and scampers away down an immaculate stone alleyway.

``The city looks like\ldots{} a model city. Like it's not really real,
even. It's so clean and perfect. Okay, I'm sending him into the
tavern\ldots{} there are three other skeletons inside. They are sitting
down, having drinks, playing cards. They don't seem to notice Sir
Digs-a-Lot. And\ldots{} they're being friendly to each other. They don't
seem scary,'' she says, a little surprised. ``Decor in the tavern is
really nice, but way outdated, like, pre-Empire, you know? Okay, I'm
bringing him back.''

This time, she assents to Hanamir's suggestion to stow him in a pocket
dimension, if only for the practicality of getting her sight back. She
apologizes profusely to the prairie dog, who doesn't seem to care.

``Guys, I think it's safe to follow this skeleton. From what I
saw\ldots{} I don't think they know they're dead,'' she says.

The skeleton beckons again and points to the tavern. Galadriel makes the
first move, crossing the street toward the skeleton. He moves ahead to
hold the door to the tavern open for her.

``Thank you, sir!'' she says. The skeleton bows, and the other
adventurers follow her into the interior of the tavern. It is indeed a
cozy place, as Hermione described---if very old fashioned. All three
skeletons turn their heads at the arrival of newcomers, but nobody gets
up. The skeleton with the lute goes behind the bar and gestures for them
to have a drink. He writes something down on a piece of parchment and
hands it to Hanamir; his writing is archaic, but not unintelligible.

``My name is Bandi. We don't get visitors very often here! We're so
excited to have you,'' Hanamir reads. In his head, he estimates that the
style of writing might be at least a thousand years old.

``Hello, Bandi,'' says Hanamir. ``Can you tell us anything about this
city? We're travelers from far away, and aren't quite sure where we've
ended up.''

Bandi writes some more on the parchment.

``This is Teron, the capital of the continent of Ivrind,'' the paper
reads.

``I apologize for the silly question, but what year is it?'' says
Galadriel. ``We've been traveling for quite some time.''

Bandi writes some more. ``We're in the reign of Geril VIII, and of
course, it is a time of peace. We haven't had visitors in a long time.''

``A beautiful city like this, and no visitors?'' says Harlan.

``It's strange, yes! I think it's just a quiet time, not the tourist
season,'' writes Bandi.

``What's the ruling family like?'' asks Hanamir.

``King Geril has had his health problems, of course, but he rules the
city in peace. He's away right now. He left my brother in
charge---Andi!'' writes Bandi.

``Is he in the big dome-shaped building?'' asks Harlan.

``No no,'' scribbles Bandi furiously. ``No, don't go in there. That's
the royal crypt. Don't go to the royal crypt.'' He underlines that a few
times. ``My brother is in the other big building in town.''

``Who are your friends, here?'' asks Hermione.

``Oh! This is Handi, the handyman, and Mandi, she runs the inn, and
Vandi, who's an excellent cook,'' writes Bandi.

``And what do you do, Bandi?'' says Galadriel.

``I run the bar, and of course, I'm a musician, like you!'' writes
Bandi. He cocks his head to the side, and Galadriel imagines that if he
had eyelids, he might be winking. ``We'd be glad to have you all stay in
town. I think the inn isn't too full. Mandi would be happy to get you a
room.''

Bandi waves one of the three other skeletons over. The skeleton, assumed
to be Mandi, takes up the quill and parchment and writes them a message.

``Hello! I'm Mandi, the innkeeper. I'd be glad to put you all up for the
night. The inn is mostly vacant. It's one electrum a night to stay
here.''

``Question for you, Mandi,'' says Hermione. ``Have you, perchance, seen
a gnome around the city? By the name of Rompit?''

``A gnome in these parts?'' writes Mandi. ``I'm sorry, I've never seen a
gnome in my life!''

They are interrupted by a startling noise from outside the tavern. It
can only be described as horrific---as if the fabric of spacetime itself
is ripping, as if the concept of sound is undergoing a traumatic
experience. The skeletons are terrified; Handi and Vandi run to the back
room. Mandi starts bolting the window shutters closed. Bandi runs to the
door and pushes a table against it to barricade it shut.

``What's going on?!'' says Hermione. But none of the skeletons are
writing anything down; they're too busy prepping for what seems like an
imminent attack.

Hermione peers outside one window before Mandi shuts it.

``There's a giant bat,'' she says nervously. ``An orc is riding it. And
behind them\ldots{} there's this\ldots{} rift. And, oh god, twelve more
orcs are coming through the rift. They have something in a cage that
they're carrying. I think they found another way in.''


\chapter{The Merman Cometh}
\chapdesc{Like its titular returning hero, this chapter is both violent and short.}

\href{/characters/harlan/}{Harlan} joins
\href{/characters/hermione/}{Hermione} at the window.

``One of them is shouting orders,'' he whispers to
\href{/characters/hanamir/}{Hanamir} and
\href{/characters/galadriel/}{Galadriel}, who are drawing their weapons.
``Can't understand him, but it looks like he's telling them to fan out.
I don't think they know anyone's in here.''

``Care to take advantage of that?'' says Hanamir.

In response, Harlan casts Shatter on the band of orcs before they can
spread out too much. A blast of thunder hits the orcs head on, and the
entire city seems to quake. Two of the orcs are knocked backward, while
some of the others are stunned for a moment as the thunder ricochets off
the stone buildings and fades away.

There's a brief moment of silence before another reality-shredding noise
splits the air.

``Now what?'' sighs Harlan. The adventurers brace themselves for another
legion of orcs to materialize.

But this second rip in spacetime erupts with oceanwater and belches out
just one humanoid, too short to be an orc, wielding a golden trident. A
couple of small fish fall out of the portal with him and flap tepidly
against the ground.

``Guys\ldots{} I think it's \href{/characters/tannin/}{Tannin}! You
guys!!!'' Harlan tries to keep his voice at a whisper just in case the
orcs somehow weren't able to tell where the Shatter spell came from.

``WHAT?!'' yelps Galadriel, blowing any cover they might have had. She
leaps over to peer out the window. Sure enough, it's Tannin, but he's
got full-on \emph{Castaway} hair now, with a few barnacles stuck in
there for good measure. He stands on the street, shaking sand and pieces
of seaweed off of his legs. ``Why is he nautical-themed now?''

``He returns to us in a time of great need,'' says Hanamir.

Indeed, Tannin's sudden appearance has diverted the front line of orcs
away from the adventurers inside the tavern, for the time being.

``Take out the dwarf first!'' the orc leader commands. Hanamir
translates for the non-Orcish speakers.

``Not so fast,'' says Hermione, to no one in particular. ``I haven't had
a chance to introduce myself yet.'' She casts Ray of Sickness on one of
the orcs, and he immediately sinks to his knees, vomiting. Harlan takes
out another one with a second cast of Shatter.

The bat riders ascend to circle over the soggy barbarian and throw
spears down at him. Orc footsoldiers surround him, swords drawn.

``This seems about right,'' says Tannin, grimacing. Out of the corner of
his eye, he notices the faces of Harlan, Galadriel, and Hanamir crammed
into the narrow tavern window. He chuckles and gives them a goofy wave,
then goes back to staring down the approaching orcs with steely-eyed
intensity.

Three orcs swing at him at once. He takes a grisly cut to his side, but
doesn't seem perturbed. He launches into his trademark rage and swings
his trident in a reckless attack against the group of orcs---but then he
does something curious. He uncorks a flask and spills a puddle of water
on the ground at their feet. He looks over at the tavern window again,
checking to see if his friends are watching the cool thing he's about to
do, but they have been accosted by the other half of the orcs.

``Damn, I guess I'll wait,'' mutters Tannin. In the meantime, he dodges
another spear from a bat-rider and tosses a stray jellyfish at one of
the orcs, beaning him right in the mouth. Then he whirls around and
tridents another guy in the neck.

Inside the tavern, the skeletons' attempt at a barricade is reduced to
splinters by a blast of Thaumaturgy from a cloaked orc mage with bony
white hands. Another orc, so huge he could pass for part-troll, bursts
through the threshold and takes a slice out of Hanamir with his axe.
Galadriel, who has scaled a wall, jumps down onto the big guy and stabs
him in the back with her rapier. She rolls off of him just in time for
Harlan to bring down his maul directly on the giant orc's skull. There
is a surprisingly large splatter radius, and it is an egregious health
code violation. Harlan makes a mental note to apologize to Bandi.

Not missing a beat, Tannin takes the momentary pause in the tavern fight
to shout at his friends.

``Guys, check this out!''

He makes a swift beckoning motion at the puddle of water he spilled, and
it juts out into a solid spike of ice. He kicks an orc in the chest and
impales him on the icicle.

``See? It's the perfect crime!'' shouts Tannin, but the tavern battle
has already resumed.

The orc mage has cast Sphere of Silence around the tavern, rendering
impossible any vocalized spells by the adventurers inside. Hermione pops
outside the door to evade the Sphere. She observes Tannin and the orc
impaled on an icicle and gives him a nod and a thumbs-up before
summoning Sir Digs-a-Lot from his pocket dimension.

``Go, Sir Digs-a-Lot, go!'' she says. ``Distract one of them!'' The
fuzzy little creature grabs ahold of an orc foot and starts climbing up
an orc leg, interrupting an orc spell in progress. ``Good work!'' says
Hermione. She then casts Ray of Sickness on the orc mage, who clutches
his stomach and sways.

Galadriel smashes through a window to evade the Sphere of Silence as
well. Down the street, two orcs are still guarding what appears to be a
prisoner in a cage. Under her breath, she casts Minor Illusion, and the
appearance of a fire breaks out inside the cage. The guards start
hacking at the lock with their axes, and in short order, they have
released a very tiny wizard man from inside.

``Is that Rompit?'' Galadriel yells to Hermione.

``No!'' Hermione yells back. ``Too old! Much longer beard! Different
gnome!''

Harlan and Hanamir take down the last orc who was foolhardy enough to
charge into the tavern and join Galadriel, Hermione, and Tannin on the
street.

``Enough,'' says the leader of the orcs. He turns to Hanamir and speaks
in Orcish. ``What business do you have in the City of the Dead?''

``I could ask you the same thing,'' says Hanamir.

The orc leader gives him a once-over.

``Perhaps we're here for the same reason,'' he says.

``Tell me more, brother,'' says Hanamir.

``Were you the ones who killed \href{/characters/cazna/}{Cazna}?'' The
orc leader's lips stretch into what could be a smile or a grimace.

``I've done a lot of things,'' says Hanamir. The rest of the adventurers
listen on, understanding nothing, though Hermione nods along with the
conversation.

``I took a semester of Orcish in undergrad,'' whispers Hermione.

``If you're willing to truce with us, we'll let you go. We'll even let
your barbarian friend go. You can leave the way you came,'' says the orc
leader. ``We don't want any more trouble with you. Cazna's death was a
setback, but it was\ldots{} deserved.''

``You're tellin' me!'' Hanamir chuckles. Galadriel hears the name
`Cazna' and gives Harlan a worried look. ``Well, sounds like a deal,
brother. We'll take the gnome, we'll take the dwarf, and we'll be on our
way.''

``Hold up,'' says the orc leader. ``That's not the deal. The gnome is
our way out of here. We're not giving him up.''

Hanamir's face remains frozen in its friendly expression, only blinking.
He says nothing.

``You're the delivery boy, then, aren't you?'' the orc leader continues.
``With all those books?''

``You could say that. What books do you mean?'' says Hanamir.

The orc leader laughs shallowly.

``You don't even know what you were carrying, do you?''

Hanamir responds again with only his chipper blinking and unnerving
silence.

``Hey, we'll sweeten the deal, how about that? After all, you're the
only reason we got in here in the first place,'' says the orc leader. He
points at Hermione. ``Give us back our other prisoner, the blue-haired
elf, and you'll get five hundred gold for your trouble.''

``Wait, what?'' says Hermione.

``Deal,'' says Hanamir. He turns to Hermione and winks at her. In an
instant, he has cast Minor Illusion to camouflage the real Hermione and
conjure a spectral Hermione in her place. He nudges the apparition
toward the orcs. ``Go on, back you go, you\ldots{} silly elf, you.''

The remaining orcs congregate around the leader and prepare another set
of shackles. Harlan takes the opportunity to cast Thunderwave on the
group of them. Two fall over, dead.

``Wow! Heck of a storm today!'' quips Hanamir. ``Never mind that, here
comes your prisoner!'' His ghostly facsimile of Hermione starts to do a
slightly silly walk toward the group of orcs, and they finally catch on
to the scam.

``All right, clear `em out,'' growls the orc leader to his remaining
soldiers.

An all-out melee begins in the street outside the tavern. The bat riders
rain darts down on Tannin. Hanamir and Harlan each take swings at a tall
green orc with skin like extra-bubbly pizza crust. Galadriel shoots a
spray of arrows at the mage. Hermione conjures a web and ensnares the
two closest orcs. Tannin throws a javelin clean through one of them.

The other one, the green guy with the painful-looking boils, breaks
free. And then it happens---the next few moments unspooling faster and
faster like the last of a tightly coiled rope.

Hanamir throws a dart at the orc with the skin condition---it hits. A
massive pustule on the orc's back erupts, drenching Harlan, Galadriel,
and Sir Digs-a-Lot in a viscous layer of putrid goo---Sir Digs-a-Lot
disintegrates before their eyes---Hermione cries
``NOOOOOO!''---Galadriel's skin makes a sizzling sound, but she is
mostly spared, and she skitters away---and Harlan falls to his knees,
seeming to melt, \emph{Raiders of the Lost Ark}-style, in the
flesh-liquefying orc zit fluid.

Before his skin is fully the texture of gak, Harlan gropes around for
the satchel he keeps tied at his hip and finds the Bread of Eternal
Hunger. He plunges his left hand into the bag, hoping for a merciful end
to this torment, no matter the evil god who might grant it to him. But
instead, he lets out an agonized scream.

\emph{``AUGHGHGH!''}

Harlan pulls away his arm from the bag to reveal a jagged stump, a
handless wrist, spurting alarming quantities of blood. He collapses to
the ground in a semisolid heap.

The God of Hunger, at last, has eaten his fill.


\chapter{The Gospel According to Shargaas}
\chapdesc{An unlikely alliance, a religious revolt, and a redemptive flight.}

``Get the body!''

One of the bat riders lands and drags \href{/characters/harlan/}{Harlan}
by his feet toward the group of orcs. Blood trickles between the
cobblestones.

``Hands off!'' shrieks \href{/characters/hermione/}{Hermione}, and it's
unclear if the pun is intended. She sends three Magic Missiles straight
into the orc's neck. He doubles over, letting go of Harlan.

\href{/characters/hanamir/}{Hanamir} and
\href{/characters/tannin/}{Tannin} dart forward. They pull Harlan to the
threshold of the house into which
\href{/characters/galadriel/}{Galadriel} had fled. Hermione joins them,
and there is a moment of reprieve as she shuts the door behind her.

Galadriel has crept up to a dark ceiling corner. She sounds like she
might be hissing. With dawning disgust, Hermione realizes it's just the
continued noise of Galadriel's skin sputtering and popping. After a
minute or two, when the sound finally fades, Galadriel climbs down. The
left half of her body is raw and dripping, like the sunken remains of a
candle.

``Sorry, I'm disgusting,'' she says. ``But he needs this more than I
do.'' She kneels over Harlan and casts Healing Word on him.

As the soft magical light passes from Galadriel's hand to surround
Harlan, the most gruesome aspects of his injuries start to fade. His
wrist ends in an angry red scab, but he's no longer losing blood, and
the rest of his skin starts to bounce back from its drooping silly-putty
quality. He opens his eyes effortfully.

``Better,'' says Galadriel. ``But still not great.''

``You're one to talk,'' he croaks, pulling a face at her lopsided
visage. ``Thanks.'' He closes his eyes again.

``That was rough, guys,'' observes Tannin. ``Pretty lucky I showed up,
huh?'' He notices Hermione and points at her. ``Who's this?''

``Hermione Daydark.'' Hermione holds out her hand to Tannin, and he just
sort of grunts at her in acknowledgement. ``Elf wizard, leading scholar
of magical creatures, and award-winning author of \emph{Cursed Critters:
A Practical Guide to Magical Pest Removal}, among other things.'' She
waits another moment, then drops her hand. ``And you must be Tannin
McBitters, the dwarven barbarian I've heard so much about.''

``Guilty,'' smirks Tannin.

``We're grateful you came back when you did,'' says Hanamir. ``Where,
exactly---''

But they are interrupted by a voice from outside. They recognize it as
the gravelly contrabass of the orc leader.

``Let's try this one more time, shall we?''

Another Orcish voice begins reciting something that Hanamir guesses is a
prayer to Shargaas. A sudden magical darkness descends on the
adventurers inside the house; even with blindsight, Galadriel can't see
anything.

``Prisoner exchange. We'll give you this gnome you're so interested in
if you hand over our elf prisoner and leave the city right now.''

``Of course! That's the deal we've been \emph{trying} to make!'' Hanamir
replies. ``Here she comes! Send in the gnome!'' He makes some comically
bad Foley artist footstep sounds.

``Are you really sending her over this time, or is it another magic
trick?'' comes a different, impatient orc voice.

``No tricks! Just a blue-haired lady, exiting the house right now!''
Hanamir makes more dubious sound effects. ``Still waiting on that gnome,
though!''

``I'm losing patience,'' says the voice of the orc leader. ``What is it
that you all even want here?''

``Oh, we'd like to prevent the unspeakable horror in this city from
escaping and terrorizing the world,'' Hanamir explains.

``I think you're in over your head, half-orc,'' says the orc leader,
switching to Common. ``We have business with the king of this city. We
don't want or care to fight you, really. We thought what you did to
\href{/characters/cazna/}{Cazna} was hilarious.''

``Well, first of all, it \emph{was} hilarious, so thank you,'' Galadriel
interjects. ``But what kind of business do you all have with the king in
the City of the Dead?''

``We don't have time to explain this to you. And it's none of your
concern. Just get out of here.''

``Hey, you're the ones who have lost several soldiers in this fight and
failed to kill any of us, despite your advantage in numbers. We should
be the ones telling you to get out, and \emph{we'll} let you live,''
points out Hermione.

The orc leader takes a moment to respond to this, and when he does, it
sounds like Hermione struck a nerve.

``Here's the deal. You all stumbled into this situation because the
little half-orc delivery boy didn't even know what he was carrying, and
you wound up entangled with Cazna and the Lolth followers. But this is
bigger than all of you.'' He sounds like he's spitting. ``This is the
business of Shargaas. And it is no business of yours.''

``You say you're going to see the king, yes?'' says Hanamir. ``Why don't
we all go? Sort things out as a group, maybe?''

``You really won't just leave? What is it that you want?'' The orc
leader sounds incredulous.

``You know, I've been curious about Shargaas for a long time, I gotta
tell you,'' says Hanamir. ``I think there may be something in there for
me. A way to connect to my culture. I'd love to hear about it all.''

The orc leader unleashes a string of wildly offensive curse words in
Orcish.

``Fine. Come with us. But if any of you draws a weapon, you're dead. And
we're leaving the gnome back here, guarded, so no funny business. Got
it?''

``Great!'' says Hanamir.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

The adventurers walk alongside the orcs in an uneasy lockstep, neither
group willing to walk ahead of the other.

``So, brothers,'' Hanamir chirps. ``Tell me the good news about
Shargaas!''

``You really don't know?'' says the orc mage, peering at Hanamir with
some curiosity.

``I grew up around humans,'' explains Hanamir. ``At a university. Never
met any orcs until later in life.''

``That does explain a lot,'' says the mage. ``I've never seen a half-orc
before.''

``I have a lot of catching up to do,'' says Hanamir. ``Tell me
everything.''

``Well, you're in for a treat. Shargaas is cool. He won't even hold it
against you that you're only half,'' says the mage. ``Don't get me
wrong, he's completely evil, but he rewards anyone who makes offerings
of stolen tribute in his honor.''

``Fantastic,'' says Hanamir.

``And you know about Gruumsh, right?'' the mage continues. ``Top of the
pantheon, and been there a long time. And if you were to ask me, or any
one of us, for that matter, it's time for him to go. I follow Utris
myself, but I'm allied with these Shargaasians in a common purpose.''

``You mean to overthrow Gruumsh, then?''

``Yes.'' The mage says something salty and profane about Gruumsh in
Orcish, prompting raucous cheers from the rest of the orcs. The rest of
the walk through the sparkling, empty city devolves into chanting and
roaring.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

After some haphazard wandering, the unlikely companions arrive at an
ornate building near the center of the city. A skeleton in a fancy robe,
carrying a staff, greets them on the front steps.

``Welcome to the palace,'' says the skeleton. The adventurers are
surprised that this one can speak after their experience with the
skeletons in the tavern. Its jaw doesn't move, making the voice that
emanates from the skull that much creepier. ``What brings you here?''

``We are here for an audience with the king,'' says the orc leader. ``I
am \href{/characters/khargol/}{Khargol}.''

``Hello, Khargol,'' says the skeleton. ``I am the king. I request kindly
that you leave this city. We do not allow visitors.''

Khargol seems taken aback for a moment, but pushes ahead.

``I must insist,'' says Khargol. ``I have lost countless men in pursuit
of a private audience with the king. It will be worth your while.''

``Very well,'' says the skeleton. ``Come with me to the throne room.
Your companions can wait in the anteroom.''

They all follow the skeleton into the palace. The anteroom is
high-ceilinged and made of the same pale, glossy marble as the exterior
of the building. Khargol looks back at his men and nods once at them
before continuing into the next room with the skeleton.

Once he's out of earshot, Hanamir turns to the mage.

``Say, just like how Gruumsh has been in charge for too long, it seems
like maybe Khargol has been in charge for too long,'' he says. ``You're
the brains of the operation. Now's your chance to really be the leader.
What do you say?''

The mage stares blankly at Hanamir.

``I knew you weren't really one of us,'' he says. He motions to the war
chief. ``You should probably put this one in chains.''

``Anyone else have something to say?'' says the war chief as he tightens
a pair shackles around Hanamir's wrists.

``There's no way we're just gonna let them shackle him, right?'' Tannin
mutters to Galadriel.

``It's better than everyone dying,'' Harlan says, speaking up for the
first time in a long while. His voice sounds far away, like he still
hasn't caught up to them, and he's back outside the tavern looking for
his missing hand.

``I didn't plane shift all the way back here to be rational,'' says
Tannin. He leaps forward and shoves the mage with his trident, knocking
him to the ground. Following right behind him, Galadriel stabs him with
her rapier.

Hanamir then rests a foot on the fallen mage's chest. The mage sputters.

``I can't believe this,'' he wheezes. ``I thought we were really
connecting, and then you double cross me.''

``What would Shargaas do, brother?'' Hanamir rests more of his weight on
the mage.

``F-fair---point---'' gasps the mage.

Tannin takes another swing with his trident, and the mage is toast.
No---with the trident sticking out of his stomach like a fork, the mage
is more like a well-done tray of brownies.

Hanamir, wrists still shackled, turns to the war chief next.

``You know, you're the muscle of this operation. I think it's time you
were in charge. What do you say?''

The war chief looks like he's not in the mood to be murdered today.

``You know what? No,'' says the war chief. ``I'm out. Bye.'' And he runs
straight out the front door of the palace and doesn't stop.

Meanwhile, one of the bat riders, who has been circling above them and
looping around the buttresses, drops a few darts on Harlan.

``He has been through enough today!'' Hermione scolds the bat rider. She
shoots Magic Missiles back at him. ``Can't you follow your friend's
example and get out of here? Fly away!''

As if expressly to contradict her, the bat rider lands on the marble
floor across from Hermione and starts to dismount. What he doesn't see
is the one-handed cleric approaching him from the side. He is taken by
surprise when that cleric uses his one remaining hand to grab the back
of his shirt and swing himself onto the bat, motorcycle passenger style.
The bat flaps its wings in distress and, haltingly, Harlan and the bat
rider lift off into the air, nearly scraping the ceiling of the
anteroom. Harlan is clinging to the bat rider like a sailor to a mast on
stormy seas.

Hermione watches them take off in total awe.

``Yes!!! Steal his bat!'' she cheers.

Galadriel climbs up a wall to get closer to the bat rider. She shoots an
arrow at him and sinks it, secretly impressed with herself for not
accidentally hitting Harlan.

Hanamir rushes outside to see if the war chief is really gone---he is.
He spots the second bat rider patrolling the airspace above the palace
and shouts up at him.

``Hey! You're the flyingest of all these guys! Maybe you should be in
charge!''

The bat rider ignores him.

Back inside the anteroom, the first bat rider is struggling to rid
himself of Harlan.

``You're going down,'' Hermione says to herself. She casts Magic Missile
one last time, and her aim is true. The bat rider is knocked off his
steed, falling at least thirty feet to the cold marble floor. He's
alive, but he lands on his neck in such a way that Hermione has the
immediate sense that he will never walk again.

Harlan steadies himself on the bat's back and gains control, flying in
wide circles around the room. He is grinning.

``YAAAAS HARLAN!'' cries Galadriel from the ceiling, surprised and
delighted.

At that moment, Khargol emerges from the throne room. He takes in the
chaos of the scene in the anteroom for a moment, then shakes his head as
if dismissing it.

``We're getting out of here,'' he shouts.

He starts to run toward the door, and the adventurers notice that he is
limping heavily. A smeared trail of blood follows his uneven footsteps
on the glowing white marble. He shouts at the bat rider with the broken
neck as he passes.

``It was a trap! I said let's go!''


\chapter{Fear and Loathing in Teron}
\chapdesc{A Savage journey to the heart of the Ivrindian dream.}

``So\ldots{} how'd your meeting go?'' asks
\href{/characters/tannin/}{Tannin}. He blocks
\href{/characters/khargol/}{Khargol}'s blood-spattered path through the
anteroom.

``I said let's go!'' shouts Khargol, and his voice sounds tense and
panicky.

``Sorry, not so fast,'' says \href{/characters/hermione/}{Hermione}. She
conjures a web that binds him to his position in the center of the
anteroom.

``No!'' says Khargol. ``You have to cut me out of here. We need to go
now if we want to survive!''

``Survive what?'' says Tannin. ``You gotta give us more than that.''

``There's a paladin who was waiting in there to kill me,'' says Khargol.
``It was a setup.''

``What about the king?'' asks \href{/characters/galadriel/}{Galadriel}.

``I didn't even get to meet the king. Please, let me out.''

``So who was that skeleton who greeted us, then?''
\href{/characters/harlan/}{Harlan} shouts down at them from his bat.

``Not the king!'' says Khargol, struggling against the web. ``I don't
know what it was. Seriously? Come on!''

``How many arms would you say this paladin had?''
\href{/characters/hanamir/}{Hanamir} asks without looking up as he
begins picking the lock on his shackles.

``He only had one arm,'' says Khargol. ``How did you know?''

``Ha!'' says Tannin, pleased that he knows who Hanamir is referring to.

Sure enough, the one-armed wonder himself emerges at the doorway of the
throne room. But the adventurers notice that he looks older---by what
looks like at least thirty years.

\href{/characters/the-savage/}{The Savage} stares ahead at Khargol,
brandishing his longsword (in one hand!!!), and looks dead set on
finishing what he started.

``Savage! It's us! We've secured Khargol!'' says Harlan. He lands his
bat and ties it to a column.

But the Savage doesn't take his eyes off of Khargol. He sprints forward
down the long anteroom.

``For the love of whatever you find holy, let me out!'' pleads Khargol,
flailing ineffectually against the web.

The Savage stops directly in front of Khargol and raises his sword,
about to deal a mortal blow.

``Savage! Come on! What's your hurry?'' says Galadriel. ``We got him.
Can we talk for just a second?''

The Savage looks confused for a moment.

``Don't you recognize us?'' asks Tannin. The Savage looks at him,
hesitating. He clearly has to think about it.

Hermione can sense an arcane aura around this paladin, whom she's never
met before, but who is definitely behaving oddly. She gives Galadriel a
sidelong glance as if to say \emph{You can tell too, right?} Galadriel
gives her a look back that says \emph{Yes, totes. WTF.}

``Hey, big guy,'' says Hanamir gently. He holds up his ring. ``Remember
the Been?''

The Savage blinks at him and then turns back to the orc in the web.
Then, without flinching, he thrusts his sword directly into Khargol's
chest. It is pretty gross to watch up close. Once he has done this,
however, he seems to relax, and looks at each of the adventurers in
turn.

``Welcome back,'' says Harlan. ``You feel better now?''

``How did you all get here?'' says the Savage slowly.

Galadriel wiggles her fingers at him, showing off her ring.

``I'm\ldots{} not sure I understand,'' says the Savage.

``You know what this is, right?'' Galadriel asks.

``Of course,'' he says, raising his own hand. ``The Ring of Been.
But---''

``Hold up, we should ask him a question only he knows,'' hisses Tannin.

``Before that, I hoped I could apologize, Savage,'' says Hanamir. ``We
didn't really get the chance before. I just wanted to say that we're
really sorry that dragon took your arm off back in the Lolth tower. Are
we good?''

Tannin looks like he's about to correct him---it wasn't the Wyrmling
that took the Savage's arm, it was the Death Slaad!---but then he
catches himself. He grins and nods at Hanamir, tapping the side of his
head.

``Oh, yeah, of course,'' says the Savage, seeming to notice his own arm
stump for the first time. ``A simple regeneration spell will take care
of this. No big deal.''

``Ooh,'' says Harlan. ``If you happen to have any referrals for
regeneration specialists, do let me know.'' He waves his own stump.

``I might know a guy,'' says the Savage.

``Lucky it snagged just one limb! That sure was an angry dragon, wasn't
it?'' Hanamir doubles down. ``And I'll never forget those fearsome
scales! The color of\ldots{}''

He trails off, as if he's struggling to find the most poetic descriptor.
The adventurers stare at the Savage expectantly.

``Oh. Um. Yeah\ldots{} that's a fuzzy time for me. I had a lot of things
going on,'' says the Savage.

``You don't remember the dragon that ripped your arm off?'' blurts
Hermione. ``I mean, I wasn't there, but I think I'd remember that.''

``Look, I'm an experienced adventurer,'' says the Savage. Now he sounds
more like the egotist they remember. ``I've gone head-to-head with a lot
of dragons.''

At this point, Hanamir succeeds in picking the lock on his own shackles.
He tries to silently slip them off his wrists and sneak away to the
throne room to investigate, but he drops the shackles on the floor. The
Savage turns around and glares at him.

``A lot of dragons, huh?'' says Galadriel, trying to divert his
attention away from Hanamir. ``Wow. I didn't know that!''

She did know that.

``Yeah, I slew my first at fourteen,'' he says. He puffs up a little,
then remembers it's no big deal. ``There was a dragon threatening my
hometown, and I did what I had to do.''

``Fourteen? That is really impressive,'' says Galadriel. Silently,
Hanamir tiptoes into the throne room. ``So after we fought the last one
together, where did you go? I really---'' She blushes a little. ``I
mean, \emph{we} really missed seeing you at the Moon Festival.''

Harlan's mouth is clenched shut in a frown, as if willing himself not to
vomit.

``I take my oath very seriously,'' says the Savage. ``I can't just hang
around attending festivals when there are threats to the safety of
Eillin.''

Behind them, Hanamir creeps around the throne room and sees the skeleton
with the robe and staff. It stands next to the throne, unmoving. There
is no one else there. The throne, white and polished like everything
else, sits on a dais in the center of the room. There is a considerable
amount of Khargol's blood on the floor, as expected. The only curious
thing, Hanamir notices, is that the skeleton is now holding a book
tucked under his arm.

Hanamir takes the book from under the skeleton's arm. The skeleton
doesn't react. He flips through it---it's completely blank.

``Well, I'm a bard, after all. I guess I wouldn't understand,'' says
Galadriel. ``But I feel like if you can't have a little fun sometimes,
what's the point of all the adventuring and fighting? You know?''

``No, I don't,'' the Savage retorts. ``If I were to let my guard down
just once, my enemies would take the opportunity to destroy everything
I've---''

The Savage looks stunned. His body has gone still, as if frozen in fear.
Galadriel snaps her fingers in front of his face, but he appears utterly
lost to the world.

Hanamir thumbs through the book again, checking for enchantments, but it
seems to be an ordinary spellcaster's book with nothing written in it.
The skeleton's staff is similarly mundane. He tucks the book back under
the skeleton's arm and sneaks out of the throne room.

``Hey! Look alive!'' Harlan claps his hands (sounding, faintly, like
thunder), knocking the Savage back to reality. He looks irritated, but
continues his train of thought.

``---they would destroy everything I've worked my entire life to
protect. It's too important to risk for the sake of\ldots{}
\emph{merriment}.''

``Cool, cool,'' says Galadriel, dropping her pretenses. ``So, just
wondering, what happened to your face?''

``My face?'' The Savage looks nonplussed.

``Yeah, you look about a million years old,'' says Galadriel.

``Oh, I guess I've seen better days,'' he says, sounding a bit distant
again. ``It's been a long time since I've been able to rest. Once the
orc threat is defeated, I'll finally get some sleep.''

``But haven't you defeated the orc threat? Just now, when you killed
Khargol?'' prompts Harlan.

At that moment, Khargol sputters and sits up, coughing blood, and makes
some kind of gesture, before collapsing again.

Harlan and Hermione look at each other in bewilderment.

``Should've
\href{http://tvtropes.org/pmwiki/pmwiki.php/Main/DoubleTap}{double
tapped},'' notes Tannin.

Hanamir rejoins them back in the anteroom, having just caught a glimpse
of Khargol's strange outburst from the brink of death.

``Guys, this feels bad,'' says Hermione. ``I think we should get out of
here.''

From outside, they hear footsteps and the sound of metal knocking
against metal. A skeleton holding a spear appears in the doorway. He
waves at no one in particular.

``Why, because of that skeleton? He's not a threat,'' scoffs the Savage.

``What about the other one, the one wearing a robe and holding a
staff?'' asks Harlan. ``Were you working with him to trap Khargol?''

``Oh, yeah, I just asked him to send\ldots{}'' the Savage cuts himself
off and starts to look nervous.

``Matter of fact, he's still in the throne room. Awful quiet now,'' says
Hanamir. ``And holding a book.''

``A book?'' Hermione perks up a bit.

``Throne room\ldots{}'' says Tannin longingly.

``Yeah, why don't we go check out the throne room together?'' says
Galadriel. ``And maybe you can explain how you knew to wait for Khargol
there.''

Tannin is already through the door. The other adventurers walk to match
the Savage's somewhat hesitant pace.

``So\ldots{} you knew about Khargol's meeting with the king, then?''
asks Harlan, after the Savage fails to voluntarily begin explaining.

``The king?'' says the Savage. ``The king of Teron has been dead for
hundreds of years.''

``Interesting. Were you surprised that Khargol believed he'd be meeting
him?'' asks Harlan.

``The orcs had bad information,'' says the Savage.

``Uh,'' says Galadriel, ``that is some really bad information.''

They come to stand in the throne room around the pool of blood at the
foot of the dais. Tannin is aggressively inspecting the skeleton. He
kicks its ankles a little bit as if kicking the wheels of a cart.
Hanamir slips the book out from under the skeleton's arm and passes it
to Hermione, who double checks it for magic. She shakes her head.

``It's completely unremarkable,'' she says. ``Parchment bound in
leather.''

Galadriel prods the Savage again, unsatisfied.

``So the king is dead-dead, and not undead, then? Meaning he cannot be
met with?'' she asks.

``Hey, I can take you down to the king's grave, if that would convince
you he's dead,'' says the Savage.

``It would convince me that a king died at some point,'' she says. ``But
not that Khargol would make an appointment with someone he obviously
could not talk to.''

``Psh! I don't think he had an appointment,'' the Savage laughs.

``But weren't you lying in wait?'' says Harlan.

``I knew that he was on his way here, so I waited for him,'' says the
Savage.

``Right, so\ldots{}'' begins Harlan, but he is interrupted by the
entirety of the skeleton's bones falling to the floor in a dusty heap.
Tannin holds the skeleton's staff.

``I had to see what would happen,'' he says, looking defiant.

Meanwhile, Hanamir slinks up onto the dais and circles the throne,
brushing a hand along one arm of the chair.

``What are you doing?'' snaps the Savage.

``Just admiring this throne here,'' says Hanamir. ``And wondering what
it'd be like to sit down in it!''

``Please do not disrespect the city of Teron that way,'' the Savage says
sternly. ``It is long fallen, and there are many beautiful artifacts.
But we don't touch them. They are sacred.''

``Fair enough,'' says Hanamir. ``Give me your ring, and I won't sit on
it.''

``The ring again!'' says the Savage, his voice rising. ``What is it with
the rings? Why do you want them?''

``Oh, I just like them,'' says Hanamir. ``Hell of a ring. Harlan's got
one, Galadriel's got one, Hermione's got one. Tannin doesn't have one. I
think we'd like the matching set.''

``Fine,'' says the Savage, and he reaches into his bag and produces a
second gold ring inscribed with a `B.' He hands it to Tannin. ``Now we
all have one.''

``Thank you, Savage,'' says Harlan, sounding a little surprised. ``This
is a sign of great trust, and we appreciate that.''

``So can we leave now?'' asks the Savage. He is just barely keeping his
cool.

``First, let's put our rings together!'' says Galadriel. Sighing, the
Savage obliges, and the six of them hold up their rings so that they are
touching. But instead of the mild electric feeling they experienced when
they did this before, there is nothing. Galadriel is visibly
disappointed.

``Huh,'' she says. ``But hey, if we're going to be on our way, I might
as well let \href{/characters/buddy/}{Buddy} out for the walk back. I'm
sure he'd like to stretch his legs. Or maybe see the view from that
throne! How about it, sweetie?''

Buddy's round pink snout is already poking out of the top of her
backpack, sniffing at the air. She lowers the bag to the ground and
gently places Buddy on the sleek marble floor. He oinks a bit, but stays
close to Galadriel's legs.

``What is the meaning of this?'' says the Savage, his voice deadly
quiet.

``Oh, I forget if you met him before,'' says Galadriel. ``This is Buddy!
They'd all say he's my pet pig, but I'd say he's more like my best
friend.'' She beams down at him. ``He travels with us on our adventures,
usually in my backpack, but I do let him wander around when it seems
like we're not at risk of attack or anything. He's my special little
guy.''

``Please don't desecrate the throne room with your filthy pig,'' says
the Savage.

``Oh! Hahaha, he has excellent hygiene, I promise!'' Galadriel tries to
lighten the moment, but the Savage is livid.

Then, in an odd instant, Galadriel turns off as if by a switch. She
hears a voice.

HEY. IT'S ME.

She looks for signs of comprehension on the faces of her companions and
finds none. Only she can hear it. And---without understanding how, or
why---she knows in her bones that it's Buddy.

WE NEED TO GET OUT OF HERE. THERE'S A LICH IN THE CITY. DON'T LET ANYONE
SIT ON THE THRONE.

The adventurers watch as all the blood seems to drain from Galadriel's
face.

IT WOULD OFFEND THE LICH.

Galadriel stares down at Buddy, who blinks up at her. She tries thinking
back at him. \emph{How do you know this, Buddy?}

NOW'S NOT THE TIME. WE'RE IN DANGER.

\emph{Where should we go?}

ANYWHERE BUT HERE.

Galadriel takes a deep breath and tries to collect herself. She kneels
down and guides Buddy into the backpack again and slides her arms into
the straps. A bit unsteady, she stands and addresses the Savage.

``You---you're right. I'm sorry, that was thoughtless of me,'' she says.
``Bringing my pet out in this place was disrespectful. Please forgive
me.''

``All right, let's go,'' says Harlan, looking deeply worried. He makes
eye contact with Galadriel, and they silently agree to talk about it
later.

``Yes, I think we're done here,'' says Hanamir.

``Let's go back and see if we can trade what's left of Khargol for the
gnome,'' says Hermione.

Again, Khargol sits up, gasping for breath.

``How is this possible?'' murmurs Harlan. He begins to take out his
medical tools to try and stabilize the orc leader with the gushing,
catastrophic, 110\% fatal trunk wound, but the Savage takes out a knife
and rests it on Khargol's throat.

``What are you doing? Don't save him,'' says the Savage.

``It's more likely that we'll get the gnome in return if we offer him up
still alive,'' reasons Harlan.

``Make the trade if you must,'' says the Savage. ``But I will not let
him survive.''

Hanamir carries Khargol on his back while they make their way toward the
site of their earlier battle outside of Mandi's inn. The two guards are
still there, looking bored, each holding a chain attached to one of the
gnome's shackles.

``Prisoner exchange,'' announces Tannin. ``But for real this time.''

The guards notice Khargol on Hanamir's back (and the new rider on top of
one of their giant bats, landing it like a pro).

``What happened to the others?'' one of them asks.

``They tasted our fury!'' says Hermione. She makes sparks fly out of her
index fingers and gives them some sassy finger guns.

The orcs break into riotous laughter.

``You want some, then?'' says Harlan. At that, Hanamir drops Khargol's
totally wrecked body on the ground in front of them. They quiet down.

``All right, all right,'' one of them says. ``Just let us leave through
the portal and you can have the gnome.''

``Deal,'' says Hanamir. ``Send him to us now, please.''

The two orcs let go of the chains and shove the gnome forward, then
disappear into the mind-warping abyss behind them. There is a flash of
blinding light, and before anyone knows what happened, the gnome is
nowhere to be seen.

``Fools!'' Khargol splutters through a mouthful of blood. ``Now we'll
all die here! That was the only way out!''

Fulfilling that prophecy at least for one of them, the Savage again
brings his sword down on Khargol, splitting him nearly in half. There
can be no doubt that, this time, he is really and truly deceased.

``Jeez,'' Galadriel grumbles, still looking pale from earlier. ``Can you
chill out for like, even one second?''

``No!'' says the Savage, heaving his longsword back out of the corpse
and wiping the blood and guts onto the leg of his pants.

``Listen, it's been an exhausting day,'' understates Harlan, who lost an
appendage a few hours ago. ``What do you say we find ourselves some
rooms at Mandi's inn?'' He considers. ``If she'll have us, after what
went down in her tavern.''

``Yes,'' says Hermione. ``That'll give our friend the Savage here some
time to rest and maybe, uh, get back to himself a little, before we
leave the city.''

They notice that Hanamir is walking at a bit of a distance behind them
as they approach the tavern. His backpack is looking overstuffed in way
that is uncharacteristic of his minimalist lifestyle. They silently
decide to let him do his sneaky Hanamir thing, hoping against hope that
it has something to do with the disappearing gnome.

To their surprise, the tavern is in pretty good shape when they file in.
Handi and Vandi are busy repairing the door, and someone clearly spent a
long time ridding the floor and walls of the various fluids that were
caked there just this morning.

``Welcome back!'' writes Mandi on a sheet of parchment. ``If you'd like
to stay here tonight, we'd be glad to have you. There are four rooms
available at the inn tonight, with two beds each.''

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

The adventurers plus the Savage trudge up the narrow staircase to the
second floor, which consists of a cramped hallway and two doors to each
side. Harlan and Tannin take the first room, Galadriel and Hermione take
the second, and the Savage takes the third by himself.

``You need all the rest you can get,'' explains Harlan. ``Tannin and
Galadriel are both snorers, so you'll be glad to have a room to
yourself.''

``Sure,'' says the Savage. He shuts the door behind him without saying
more.

Bringing up the rear, Hanamir and his overlarge backpack take the fourth
room.

Once the Savage has been quietly inside his room for a good few minutes,
Galadriel and Hermione sneak over to discuss plans with Tannin and
Harlan.

``So, we're keeping watch tonight, right?'' says Tannin. ``We do not
leave this guy unattended.''

``Yes, of course,'' says Hermione. ``One of us should be watching his
door at all times.''

``He does seem more like himself now, though,'' says Galadriel. ``We
should ask him about the dragon again in the morning.''

``Oh, yeah, that's right, do we trust that you're allied with us and not
with him?'' snickers Harlan. He does his best Galadriel impression.
\emph{``Ooh, the Savage, I missed you at the Moon Festival! Ooh, the
Savage, you're so good at fighting dragons!''}

``It's called flattery, you dolt,'' she snorts. ``He loves to hear how
impressive he is. And besides that, have you seen him lately? He looks
old enough to be my father.'' And then she frowns at a sudden terrible
thought. ``Oh man. I hope he isn't.''

Tannin, paying zero attention, has retrieved an enormous bear trap from
his backpack.

``I'm gonna put this outside the Savage's door,'' he announces. ``And
that way if he comes out\ldots{} there's a bear trap.''

``Good idea,'' says Harlan.

``Okay, good night,'' says Hermione, and she and Galadriel tiptoe back
to their room. The inn is quiet. There is no noise from the tavern
downstairs. There is no noise from the city outside.

Tannin and his bear trap take first watch.


\chapter{Zombie! Zombie! Zombie!-ie!-ie!}
\chapdesc{What's in your head? Mind games abound in the City of the Dead.}

During the night, \href{/characters/harlan/}{Harlan} has a dream.

He is in the cave he once protected. He relishes the scents of the
mineral stream and the petrichor in the air filling his lungs for the
first time in so long. But it's not just the comfort of being home;
there's something else he's feeling\ldots{} a new confidence, an
expansiveness of self that feels exhilarating. A storm roils outside the
cave. The percussive sound, the electrifying light---he can feel it all,
and it's coming from within him.

As another crash of thunder reverberates through him, \emph{from} him,
Harlan understands: he is the most powerful being on the planet. He
rules over the material plane. He is the slayer of
\href{/characters/kord/}{Kord}.

He wakes up, heart pounding, to the eerie silence of the inn. He
struggles to shake off the feeling the dream left him with and go back
to sleep, but finds it impossible. He decides to get out of bed and
volunteer for the next shift. At least then
\href{/characters/tannin/}{Tannin} can get some rest.

``Thanks, man,'' whispers Tannin as they trade places. ``He hasn't come
out yet.'' Tannin glances down at the bear trap a little ruefully.

Across the hall, \href{/characters/hanamir/}{Hanamir} sleeps on his
back, straight as a board, tightly tucked into his blankets. His face is
perfectly neutral. You might not be able to tell by looking at him that
he's deep in a dream about his favorite place in the world, Drephis
State.

He is finally home! And he has restored the missing library books---and
then some. The library is now the pride of the school, and it's all
thanks to Hanamir's dedication and diligence. The student body names a
school holiday for him. After a long day of receiving thanks and praise
from his colleagues, Hanamir retires to the library for his usual
pre-bedtime book inventory check. Nothing brings him more satisfaction
than seeing all his books in their proper place, neatly organized and
cared for. But out of the corner of his eye, he spots a terrifying
figure in blood red robes. It clutches a black book bearing a demonic
seal. Upon detection, the creature makes eye contact with Hanamir for a
split second. He wakes up, bolting upright out of bed.

Unnerved, Hanamir paces quietly around the room, careful not to wake the
small, sleeping figure in the other bed. He figures now's as good a time
as any to go take his turn on watch.

Meanwhile, \href{/characters/hermione/}{Hermione} has finally managed to
tune out \href{/characters/galadriel/}{Galadriel}'s aggressive snoring
and fall asleep. She, too, has a dream.

She is out in the wilderness, having just discovered some fascinating
material for her book on magical creatures. She is certain that it's
shaping up to be another bestseller, perhaps her finest work yet. There
are only a few more rare beasts that elude her, but if she can be
patient and follow her instincts, the creatures she's waiting for might
just come to her\ldots.

``There are secrets that even the gods do not know,'' comes a voice from
behind her. She whips around, spooked, and sees a strange figure with
long stone spikes on its back and a single bright eye. It is a
Nothic---not one of the creatures she'd been planning to write about,
but uncommon and intriguing nonetheless. Nothics were once wizards,
transformed and corrupted by the pursuit of magical secrets.

Before she can respond, the Nothic makes a strange motion (a nonverbal
spell, perhaps) and disappears into what Hermione can only assume is the
Shadowfell.

She wakes up, feeling a mixture of fear and curiosity\ldots{} and with
that curiosity, some shame. She decides to take the next watch.

As Hermione leaves the room, she sees Galadriel sleeping sprawled on her
stomach with her face contorted in what looks like unspeakable pain.
\href{/characters/buddy/}{Buddy} is nestled in the warmth of her armpit.
She whimpers in between snores.

Galadriel dreams that she has found \href{/characters/magick/}{Magick},
and by accident, too. She stumbled across a hidden cellar door while
searching for a bathroom and discovered the elusive tiefling inside.
Magick has her back turned and is leaning over a table. Flashes of
light, accompanied by agonized screaming, periodically illuminate the
cellar.

She can't see what's on the table, but her stomach drops to the floor
with a horrible feeling that it's someone she loves.

``Please, no!'' she cries. ``Stop! Don't hurt him!''

An invisible force field holds her in place. She wants to run forward
and tackle Magick, or shoot an arrow at her back, but she can't move.
All she can do is speak.

``Magick, please,'' she sobs as another round of screaming begins.
``He's good. I know he's good.''

A thought worms its way into her mind, its origin unclear. If she says a
single word, she can put an end to this. She can kill Magick to save
this person she loves. And she knows she has to do it.

She speaks the word. Magick turns around and stares at her, then
freezes---and falls to the floor, dead. An overwhelming relief floods
through Galadriel's body. She rushes to the table to comfort the
creature, still weeping, but knowing at last that it is safe. Everyone
she loves is safe.

Galadriel wakes, shivering and sweaty. Buddy licks her face a little,
and she smiles.

``What a scary dream,'' she murmurs to him. ``Stay cozy. I'm gonna go
take my turn keeping watch. Love you, Buddy boy.''

Back in Harlan and Tannin's room, Harlan is having a hard time getting
back to sleep. Tannin is dreaming, uh, loudly: mumbling, thrashing, and
punching the air in his sleep.

Tannin stands on a desolate battlefield. A sulphurous wind stings his
eyes and tangles his hair and beard. An army of giants---fire giants,
frost giants, hill giants, cloud giants---is closing in on him, and he's
never felt more alive. He grips his trident and swivels, pointing it at
each of them in turn. He wants them all to get a good look at the
magnificent weapon that will be ending their lives in short order.

``Ha-HAAAAAA!'' he bellows, and this prompts the first giant to charge
at him. Tannin strikes him down easily, and quickly flies into a
rage-filled frenzy, toppling giants one after the other.

Soon the only one left is the leader, the largest giant of them all, a
storm giant. In a language Tannin can't understand, it begs for its
life.

``Sorry, big guy,'' says Tannin. ``You messed with the wrong dwarf.''
And he throws down his trident and clobbers him to death with his bare
hands.

He wakes up with a smile and a sigh, wishing the dream could have lasted
longer. He can hear Harlan mutter, ``Oh thank Kord,'' and assumes he
must have been making a lot of noise. \emph{Worth it}, thinks Tannin,
rolling over. He stays in bed, replaying the dream in his head.

At this point, the night has given way to a dim pre-dawn haze. Hermione
still struggles to get back to sleep, her mind racing and her bed
feeling uncomfortable in every respect. She finally gives up and goes
out into the hallway to sit with Galadriel.

``Can't sleep,'' she whispers.

``Ugh,'' Galadriel whispers back. ``I slept for awhile, but had the
worst dream.''

``Really? I had a creepy dream, too,'' Hermione says. ``I wonder if it's
something about this place.''

``Wouldn't be surprised,'' says Galadriel. They sit together in silence,
staring at the bear trap, then \href{/characters/the-savage/}{the
Savage}'s door, then the ceiling, wishing the sun would hurry up and
rise already.

``Want to go see if the boys are awake, too?'' says Hermione.

``Sure,'' says Galadriel. They approach Harlan and Tannin's door and tap
on it lightly, quiet enough not to wake them if they're asleep, but loud
enough to alert them if they're already up.

Harlan answers the door, looking mildly cranky.

``Can't sleep? Weird dreams?'' he asks.

``Yes,'' says Hermione.

``My dream wasn't weird,'' says Tannin.

``Let's check on Hanamir,'' says Galadriel. ``I want to know what was up
with his backpack.''

They follow the same knocking protocol at Hanamir's door. He opens it a
crack, sees it's them, and lets them in. They all immediately notice the
tiny, withered old man who is tucked neatly into the second bed,
blinking up at them.

``This,'' says Hanamir, ``is \href{/characters/redyl/}{Redyl}.''

``How do you do,'' says the elderly gnome. He looks like a white-bearded
baby in a bed far too large for him.

``Pleasure to meet you, Redyl,'' says Harlan, bowing. ``Hanamir, what
happened? The orcs pushed him forward as they went through the portal,
and there was this flash of light, and then you were both gone\ldots{}''

``Yes, I spirited him away for just a moment,'' says Hanamir. ``Wanted
to have a word with him outside the earshot of our friend the Savage,
whom I believe to be magically compromised.'' He pauses a moment.
``Redyl, do you mind if I tell them what you shared with me?''

``Please,'' says Redyl.

``He told me he'd been held by the orcs for a long time, and that they'd
forced him to bring them through the Shadowfell to the City of the Dead.
The orcs had been collecting various tuning forks, and once they had the
ones they needed for the spell, they coerced Redyl into doing their
bidding. They told him they had his children captive,'' says Hanamir.

``Oh, how terrible,'' says Hermione. ``I'm so sorry, Redyl.''

Redyl bows his head.

``Redyl believes that the orcs ultimately wish to slay the gods,''
continues Hanamir. ``We've heard inklings of this from the Shargaasians,
who want to take down Gruumsh in particular. But this sounds like it is
a much broader effort than just that.''

Harlan remembers his dream and how good he felt being the slayer of
Kord. He feels the hairs on the back of his neck stand up.

``Anyway, I told him what I suspect about the Savage, and asked him to
get in my backpack so that I could transport him with us in secrecy. He
agreed, and was an excellent sport about it,'' says Hanamir.

``Oh, it was plenty roomy for me,'' says Redyl with a tiny chuckle.
``And I was very glad to be out of the company of
\href{/characters/khargol/}{Khargol} and his men.''

``I also told him that whatever is going on with his kids, whether that
threat was real or not, we will do what we can to help him,'' says
Hanamir.

``Of course,'' says Galadriel. ``I can't imagine how terrifying this has
been for you, Redyl.''

``Hey,'' says Hermione, pulling a letter from her pocket. ``I was
imprisoned with the Shargaasians myself for awhile, and my cellmate was
a gnome named Rompit, and he left this letter---''

``Rompit?!'' cries Redyl, almost forgetting to keep his voice down.
``Rompit is my son!''

``Really?'' Hermione beams.

``Yes. It is almost a comfort to know that they really did have my son.
At least I was truly protecting him when I submitted to their evil
will,'' Redyl sighs.

``The letter was from someone named Syndra---''

``That's my daughter!'' Redyl is overcome with emotion. Galadriel offers
him her handkerchief.

``They were looking for you,'' says Hermione. She skims the letter,
which she almost knows by heart. ``Syndra wrote to Rompit saying that
everything was going fine, but that it would take her a bit longer to
get home. She said she was looking for a way to bring back Dad.''

Redyl cries into the handkerchief, which is the size of his entire body,
while Galadriel rubs his back.

``Sorry,'' he hiccups, and calms himself down. ``Here's what I know: the
orcs have been collecting some very rare artifacts that are necessary
for planar travel. Some of them were the tuning forks Hanamir mentioned;
some of them were---I think---smuggled out of a university. They had
people trying to make new ones. Eventually, they found what they needed
to get here. They came here to enlist someone's help, but I don't know
whose. I assume it's all a part of this plot to slay the gods.''

``Thank you, Redyl,'' says Hanamir. ``Harlan, how has your connection to
Kord been feeling since we entered the city? Among the group of us, you
have the closest relationship to a god who might be threatened by
this.''

Harlan considers this. He feels guilty, somehow, even though he knows he
hasn't actually done anything to betray his deity.

``I feel\ldots{} strangely disconnected from Kord here,'' says Harlan.
``There's just this emptiness. I'm still able to cast my spells. But it
feels odd, and---wrong. Everything is just \emph{off} here.'' He's quiet
for a minute. ``And that reminds me. Galadriel, I meant to ask you about
what was going on in the throne room, when you let Buddy out and then
looked like you were about to faint.''

``Oh yeah!'' says Tannin. ``I was sure whatever had gotten the Savage
had gotten you too.''

``It wasn't that,'' says Galadriel. ``Okay, this is going to sound
insane, and I haven't been sure how to phrase it,'' she says. ``But
Buddy talked to me. In my head.''

``Like, telepathically?'' says Hermione. ``Your pig is telepathic?''

``I don't know,'' sighs Galadriel. ``I guess so.''

They wait for her to elaborate, but she doesn't.

``So what'd he say?'' says Tannin,
\href{https://youtu.be/uV8TcpRQJCM?t=44s}{weirded out}.

``He warned me not to let anyone sit on the throne,'' she says. ``He
said there's a Lich in the city, and that we weren't safe.''

``And you waited until \emph{now} to let us in on that little tidbit?!''
whispers Harlan through gritted teeth.

``Hanamir waited until now to tell us he had the gnome!'' says
Galadriel. ``I wanted to talk to you all together, and not in front of
the Savage. Besides, it only confirms what we already suspected.''

``Can we talk to him now?'' says Hermione.

``We can try,'' says Galadriel. ``I don't know how it works.''

She crosses the hallway and retrieves the little pink pig. She returns,
stifling giggles as he sniffs her neck and nibbles softly on her
earlobe.

``Should we entice him with something? Some, I don't know, slop?''
Hermione wonders.

``Ew, no,'' says Galadriel. ``He eats what I eat.''

``Okay, so think something at him,'' says Tannin. Galadriel does so.

\emph{Hi, Buddy. My friends are wondering if you'd be willing to talk to
us.}

The same sourceless, soundless voice enters her mind.

HI GALADRIEL. YES, I COULD TALK. BUT I WORRY IT'S NOT THE BEST IDEA.

\emph{Why not?}

I THINK THE MORE I REVEAL OF MYSELF, THE MORE LIKELY IT IS THAT THE LICH
WILL CATCH ON THAT I'M NOT WHAT I APPEAR TO BE.

\emph{Is he watching us right now?}

HE IS EVERYWHERE IN THIS CITY.

Galadriel takes a moment to relay this information to her friends.

``Oh, great,'' says Harlan. Galadriel turns back to Buddy.

\emph{So what would happen if he found out what you really are?}

IT WOULD BE BAD. FOR ME AND FOR ALL OF US. OUR PEACEFUL PASSAGE THROUGH
THE CITY MIGHT END ABRUPTLY.

\emph{Do you know how to defeat him?}

NO. BUT I CAN FEEL HIS PRESENCE, AND I AM AFRAID.

\emph{Okay. Thank you, Buddy. You don't have to talk anymore.}

She gives him a cuddle and summarizes his concerns back to the
adventurers. They are silent for a good long while as they turn this
information over in their heads.

``So,'' says Hanamir. ``It sounds like we should get out of the city.''

``And we have to either take the Savage's ring, or get him into a state
where we can safely bring him out with us without also bringing along
the Lich, or some sort of interplanar demon, or whatever is possessing
him,'' says Harlan.

``You can use Dispel Magick, right?'' asks Hanamir. Harlan nods. ``We
should try casting it on the Savage before he leaves his room, and then
going to talk to him to see if it worked.''

``Before we do that,'' says Galadriel, ``I want to take the chance,
while we're all sharing stuff, to ask Tannin where the hell he's been.''

``Oh yeah!'' says Tannin. ``Ha, I forgot I hadn't already explained
this. Well, that potion I drank was supposed to be a plane-shifting
potion, but we know Magick is kind of terrible at potions, right? So I
figured maybe it'd heal me or something, because I was cut up pretty bad
in that Lolth tower,'' he reminisces. ``Anyway, it didn't, and it didn't
take me back to her hut like she said, either.''

``Did it take you to the ocean?'' Hermione makes an educated guess.

``It wasn't just the ocean,'' says Tannin. ``It was an entire plane of
water. There was no surface. I thought for sure I was going to die,
like, right away.'' He laughs. ``But then this strange creature saved
me, and took me in, and taught me in his mysterious foreign ways. He
taught me how to breathe underwater, and it was lucky that he could do
that in under a minute. Otherwise, you know.'' He mimes clutching at his
throat and drowning. ``And not only that, he also had information about
what happened to my clan. The darkness that seeped in and took
everything I knew.''

``Wait, what?'' says Galadriel. ``You've never mentioned that before.''

``I'm a very private person,'' says Tannin.

``More a man of action than of words, it's true,'' Hanamir says.

``Yeah, exactly. So I stayed there in his temple for what seemed like
years. I can speak Aquan now. And they taught me some great tricks. You
saw what I did with the icicle back there, but that's just the
beginning.''

``How did you leave? And how did you find us?'' asks Harlan.

``That was all you, dude,'' says Tannin. ``The Genasi---the underwater
people---told me that Kord was summoning me to come back to this plane
in your time of need.''

``Whoa, nice going, Kord!'' says Galadriel.

``Praise Kord, indeed,'' says Harlan. He smiles. It feels good knowing
that even if he's disconnected from Kord at the moment, the god himself
is still looking out for him.

``Wanna see me breathe underwater?'' says Tannin.

``Duh,'' says Galadriel.

Tannin takes his water flask and empties it into his mouth while
pinching his nose. He then spends the next five minutes striking poses
with his trident and gesturing at how not-drowned he is.

``Was it hard to swim with that?'' says Hermione.

``Nah, I learned to move around all right. And it definitely came in
handy when this weird monster made of mouths appeared and I had to kill
it.''

Harlan, Galadriel, and Hanamir look at each other and wordlessly decide
it's not worth explaining that right now.

``Well, it's good to have you back,'' says Hanamir. ``Redyl, it might be
time for you to hop back in my backpack. Sorry about that. But we'll be
leaving soon, I think.''

``No trouble at all, Mr.~Hanamir,'' says Redyl. He's surprisingly spry
for an old man, and leaps into the backpack without hesitation.

``So that leaves us with the problem of the Savage,'' says Hermione.
``We should pool our resources to boost Harlan's Dispel Magic as much as
we can.''

``Agreed,'' says Galadriel. She grants him Bardic Inspiration. Harlan
gives himself the Guidance of Kord and then casts the spell. Harlan
doesn't mention this, but he suspects it is his knowledge that Kord
cares enough to have brought Tannin back that makes the spell so
successful. Through the wall of Hanamir's room, they can hear something
like rushing wind.

They go out into the hallway and see that all of the doors have been
blown open by the force of the enchantment leaving the Savage. The smell
of fresh air after a storm is strong, though none of the windows are
open. Tannin deactivates the bear trap and nudges it back into his room.
Hanamir knocks on the Savage's door, now ajar.

``Come in,'' says the Savage. The five adventurers file into the room a
little apprehensively. The Savage is sitting up in his bed, looking
disoriented. ``What's happening?''

``Good morning, Savage,'' says Harlan. ``How much do you remember of
yesterday? Or of the recent past, more generally?''

The Savage rubs his eyes and thinks for a second.

``I remember meeting you all, but that was ages ago, and somewhere else,
right? That's about it,'' he confesses.

``You were acting strangely yesterday, and we determined that you were
in fact enchanted,'' Harlan explains. ``We just dispelled the
enchantment.''

``Do you know who might have done this to you?'' says Galadriel.

The Savage seems to understand, suddenly, where he is.

``We need to leave,'' he says. ``Now.''

``Before we do, would you mind checking if you're wearing or carrying
anything you don't recognize?'' asks Hanamir.

The Savage checks his pockets, and then rifles through his bag.

``No,'' he says, sounding worried. ``But I'm missing something very
important.''

``Your arm?'' says Tannin.

The Savage stares at him murderously.

``Not that,'' he says.

``Do you remember what took your arm, though?'' asks Hanamir.

``That Slaad, of course,'' he says, getting it right this time. The
adventurers share a look of relief. ``And it was also kind of your
fault. All of you.''

``Sure, sure, sure,'' says Galadriel. ``So what else are you missing?''

``Is it, perhaps, a ring?'' asks Harlan.

``Yes!'' says the Savage.

``Oh, you gave that to me yesterday,'' says Tannin, giving him a
ring-to-ring fistbump, which the Savage returns unenthusiastically.

``Well, good,'' says the Savage. ``That was the only thing. Why did I
give it to you?'' He looks at the mer-dwarf up and down, struggling to
understand his own ensorcelled judgment.

``\href{/characters/frunk/}{Frunk} told us the significance of the rings
back in Eillin,'' says Hermione, showing off her own. ``We probably
shouldn't talk about it here.''

``That is correct,'' says the Savage. ``We can assume anything we say or
do here is being observed by the Lich. You're a smart one. Who are
you?''

``Hermione Daydark,'' says Hermione.

``The author?'' says the Savage.

``Yes! You've read my books?'' Hermione is beside herself.

``I don't read much,'' says the Savage. ``But my niece is a big fan.''

``So did Frunk send you to the City of the Dead?'' asks Harlan.

``No one did. I protect Eillin, and I thought it was important to the
town that I come here to try and dissuade the Lich from dealing with the
orcs,'' says the Savage.

``Well, it seemed to us like things went poorly for Khargol,'' says
Harlan. ``You---and we assume you were under the influence of the
Lich---murdered him pretty decisively back there.''

``This only worries me more,'' says the Savage. ``No one can die within
these walls. If Khargol is `dead', it may mean that the Lich accepted
his offer and used me to carry out his plan. Khargol is undead now,
along with any of his men who perished here.''

Nobody is sure what to say to that. In the silence, the Savage
continues.

``They're closer than ever to overturning the entire orc pantheon.''

``Well,'' says Hanamir. ``The orc pantheon is not, you know,
\emph{great}.''

``It would have unforeseen ripple effects that could destabilize
hierarchies we don't even know about,'' says the Savage. ``Order is
important.''

``On that, we agree,'' says Hanamir.

``So should we start making our way to the wall, then?'' says Harlan.

The Savage looks at them in confusion.

``Are any of you practiced in the kind of advanced magics that could get
us out of here, and do you have the tools to do so?'' he asks.

The adventurers stare back at him quizzically, but don't want to spell
out what the rings do, now that they know the Lich is listening in.

``Uh, just trust us,'' says Harlan. ``You'll see.''

``Oh, sure,'' says the Savage, gathering up his things. ``When has that
ever gone badly for me?''

They check out of the inn and bid Mandi and Bandi farewell. Harlan
retrieves his giant bat steed from the stables and, to his surprise, the
bat allows him to climb onto its back again without issue. They fly in a
few loop-de-loops before leading the way in the direction of the wall.

After a few minutes, the adventurers notice that they're being followed
at a distance by a few skeletons. It's clear the skeletons are trying to
be sneaky, but their efforts at stealth are not very effective.

``Stay alert,'' says Hanamir. ``It's likely they'll try to impede our
exit in some way.'' Then he swivels ninety degrees and starts walking in
a completely different direction.

``Hanamir?'' says Harlan.

``C'mon, guys,'' says Hanamir. ``That's the wrong direction. We need to
go this way.''

``But that way leads further into the city,'' says Hermione.

``Oh, no it doesn't,'' says Hanamir. ``This is the way we want to go.''

Tannin goes up to Hanamir, looking into his eyes and tapping on the side
of his own head.

``Think about it, man,'' says Tannin. Hanamir finds this unpersuasive.

Hermione casts Protection from Evil and Good on Hanamir, which doesn't
seem to do anything to change the situation.

``Hanamir,'' Galadriel starts, ``you know we're in the City of the Dead,
and you're acting like you're possessed right now, right?''

``Oh, I understand your concern,'' says Hanamir, starting to walk
backwards. ``But really, enough. Let's go.''

At this, Tannin tackles him, and it's enough to give Hanamir another
chance to throw off the enchantment.

``Whoa,'' he says. He pushes Tannin off of him before he can fly into a
barbarian rage out of habit. ``Thanks, guys. The Lich possessed me there
for a minute. He wanted me to take us to the tombs.''

``Okay, I have had it with this place,'' says Hermione. ``Let's get out
of here \emph{right now}.''

``Or,'' says Tannin, still lying on the ground, ``we should go to the
tombs, because he'd never expect it.''

``No thanks!'' says Hermione, and she marches ahead of them toward the
wall. It's visible in the distance beyond some buildings.

But as the adventurers were dealing with the Hanamir situation, they
didn't notice a group of about fifteen skeletons gathering ahead of them
to block their path forward. One of them addresses the group.

``Why leave now?'' it says through ever-grinning teeth.


\chapter{Walk the Swine}
\chapdesc{A man-at-arms disarmed, a gnome far from home, and a hog dialogue.}

The adventurers hesitate. The speaking skeleton walks closer.

``There's no need to depart so hastily,'' it continues. ``Why not stay a
little longer?''

\href{/characters/tannin/}{Tannin} and
\href{/characters/hanamir/}{Hanamir} glance at each other and ready
their weapons. But as they prepare to charge, a bolt of lightning
connects with the ground beneath the group of skeletons, illuminating
their bones for a fraction of a second, then exploding them. When the
dust clears, only four skeletons remain standing.

``\href{/characters/kord/}{Kord} be praised!'' comes
\href{/characters/harlan/}{Harlan}'s voice from above, on the back of
the giant bat. His lone hand, still crackling with electricity, is
raised in blessing. (\href{/characters/galadriel/}{Galadriel} makes a
mental note that this tableau should be the cover art for the metal
album she will one day compose about this very adventure.)

``I was merely inviting you to stay,'' says the skeleton coolly. He and
his compatriots step aside to let the adventurers pass.

They approach the forbidding black wall at the edge of the city. The
four skeletons watch on without showing aggression, but also without
retreating.

``You guys can leave us alone now,'' Tannin suggests. Their empty eye
sockets stare back at him.

``Let's just go,'' says \href{/characters/hermione/}{Hermione}. ``Now,
quickly, before they try to pull any more tricks.''

``So we're all right with them seeing how we leave?'' says Hanamir.
``And that we're leaving with\ldots{}'' He points behind himself to his
backpack, where \href{/characters/redyl/}{Redyl} is stowed away.

``I think we've given the Lich enough contextual clues at this point for
him to be aware that the rings are special,'' says Galadriel. ``And if
he sees everything in the city, he'll already have seen us talking to
Redyl at the inn.''

Hanamir nods and sets his backpack down to let Redyl out.

``Who's this?'' \href{/characters/the-savage/}{the Savage} grunts.

``We'll explain later,'' says Hermione, dancing back and forth on her
feet. ``Please, let's go. Who's in the first group?''

``I'll give my ring to Redyl and stay behind while he crosses,'' says
Hanamir. He slips off his Ring of Been and hands it to the gnome.

``And I will stay and tackle you again, if you need me to,'' says Tannin
with an air of noble sacrifice.

``I'll pass through and then come back to give you Redyl's ring,'' says
Galadriel.

``I can't really hear you guys, but I'm just gonna fly through the wall
now,'' Harlan calls down from the air.

And with that, Harlan, Hermione, Redyl, Galadriel, and the Savage pass
through the wall. It takes a few seconds---they're not running, this
time---and the sensation of being inside the illusion of a solid
structure is extraordinary. Galadriel feels as though her internal
organs have expanded to fill the volume of the wall. She breathes deeply
when she reaches the other side, not really looking forward to crossing
through it twice more.

Redyl hands her the extra ring.

``Go bring back Mr.~Hanamir,'' he urges her. ``I won't feel like I've
truly escaped until he's out, too.''

Galadriel passes back into the City of the Dead, expecting to see
something horrible: Hanamir and Tannin being eviscerated by an army of
undead, or the Lich holding them hostage, or no sign of them at all. But
the pair of them are standing right where she left them not half a
minute ago.

``All good?'' she asks. She tosses the ring back to Hanamir. He puts it
on.

``I guess,'' says Tannin. He looks askance at the four skeletons, who
still watch them from a distance.

``All right, then, team,'' says Hanamir. ``Let's go.''

The three of them walk through the wall and emerge on the other side.
They're greeted by cheers from Harlan, Hermione, and Redyl. The Savage,
aloof as ever, is busy taking a swig from his water flask.

``I can't believe how well that went!'' says Hermione.

``Me neither, frankly,'' says Harlan, who has landed his bat. ``What's
the catch?''

``If there is one, I'm sure we'll find out soon enough,'' says Hanamir.
He looks soberly toward the Savage.

``Are you not certain that the Lich has been banished from my mind?''
says the Savage.

``I believe you are no longer under his influence, but I do not think we
yet know the consequences of all that transpired in the city,'' says
Hanamir.

The Savage gives him a curt nod.

``Until then,'' says Hermione. ``Where should we go next?''

``Eillin? To check in with \href{/characters/frunk/}{Frunk}?'' Tannin
floats.

``Remember, we have a meeting with \href{/characters/magick/}{Magick} in
Aberith in four days,'' says Harlan.

``Eillin is on the way,'' says Galadriel, ``and Frunk needs to know what
we've learned.''

``I, too, would like to speak to Frunk,'' says the Savage.

``Eillin it is, then,'' says Harlan.

The adventurers set off. The simple act of putting distance between
themselves and the City of the Dead has a noticeable effect on their
moods. Even Hanamir's attitude seems markedly more jovial once the wall
is out of sight; he carries Redyl on his shoulders like a toddler.
Hermione has ceased her nervous fidgeting. Tannin levitates the dew from
the grass ahead of them and makes it shimmy in the air to the rhythm of
Galadriel's lute strumming. Harlan, soaring ahead of them on his bat,
looks downright joyful.

``So, what I still don't understand,'' Hanamir says to the Savage, ``is
how you got into the city.''

``I'll be honest with you,'' says the Savage. ``I had no idea the Rings
of Been allowed you to pass through the wall. I did not know what a
danger it was that I had two of them on my person.''

``Frunk never told you?'' says Galadriel.

``No,'' says the Savage. ``It must have been information reserved for
higher-order members. And\ldots{} you all, I guess.'' He stares ahead
sourly.

``That seems wildly irresponsible,'' says Hermione. ``I mean, given that
the possession of one of those rings would allow the Lich to escape, I
can't understand why Frunk did not make every owner of every ring aware
of its power.''

The Savage bristles at her.

``I trust he had his reasons,'' he says.

``So how did you get in, then?'' Hanamir repeats.

``That's all a bit fuzzy to me,'' says the Savage. ``I don't remember.
On my way to the city, something happened to me, and I\ldots{} found
myself inside.''

``That's really bad,'' says Galadriel. ``It means that taking the rings
outside the city doesn't make you safe. Someone with a ring can be
compelled to go back in.''

``When we talk to Frunk, we should tell him the rings need to be locked
away somewhere for good,'' says Hermione.

``Or turned into toe rings, so that nobody will ever wear them,'' says
Tannin. ``Not even the Lich.''

``Or destroyed entirely,'' says Galadriel.

``I would like to be part of this conversation!'' Harlan yells down at
them.

``We'll be at Eillin soon, and then we'll all get a chance to talk,''
says Hanamir.

``What?!'' shouts Harlan.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

At the edge of Eillin, they reach a heavily-guarded checkpoint.

``No one enters and no one leaves the town,'' says a guard. ``Please be
on your way elsewhere.''

``I'm certain Mayor Frunk will make an exception for us,'' says
Galadriel. ``Don't you recognize us?'' She assesses the guards, trying
to determine how big of a charm bomb she will have to detonate on them
in order to get her way.

``The mayor does not have the authority to make an exception,'' says the
guard, stony-faced.

``Then who does?'' says Tannin. He's not really listening for an answer.
He turns around and waggles his eyebrows at the party, just itching to
let loose on these goons.

``None but the king of Aberith,'' says the guard.

``Well, could the mayor come up to the border and speak to us here?''
says Hanamir.

The guard looks annoyed.

``No one enters \emph{or} leaves,'' he repeats.

``Right, but if he just comes right up to the edge, he won't be leaving
and we won't be---'' starts Hermione, but she's interrupted by Harlan.
His voice booms over the airspace above Eillin, reverberating off walls
and buildings.

``HEY FRUNK,'' he alerts the entire town, ``WE'RE BACK.'' He then adds,
``IT'S HARLAN.''

The guard throws up his hands and resumes his post, cursing. In a few
minutes, the adventurers see a familiar dwarf hurrying down the path
toward the checkpoint. He argues with the guards for a moment---they
want to supervise the meeting---but Frunk uses his ace in the hole.

``The king will hear about this,'' he says.

At that, the guards back down. Frunk beckons the party to come forward
and greets them with a weary enthusiasm.

``Glad to see you all made it out of there in one piece,'' he says.
``Plus a few more, I see.'' He nods at Tannin, and gives Redyl a
respectful but confused handshake. His eyes widen at the sight of Harlan
landing his bat. When his gaze reaches the Savage, he throws his arms
wide and embraces him.

``We missed you! We thought we'd be seeing you at the Moon Festival!''
he says.

``I had to investigate the orc threat,'' says the Savage, who is clearly
uncomfortable being hugged. ``I found myself imprisoned by the Lich.
Then these people here stumbled in without much strategy, or
grace\ldots{}''

He sneers this last part. Galadriel makes a huffy, insulted noise.

``Anyway, I'm in a weakened state, and I need somewhere to rest. Can I
stay with you?'' says the Savage.

``I'm afraid they're very serious about no one entering or leaving the
town,'' says Frunk.

``In that case, I suppose I'll head to Aberith,'' says the Savage.

``You know, you could be a bit more appreciative!'' Galadriel snaps. He
ignores her.

``We have a lead on who might be responsible for
\href{/characters/bryn/}{Bryn}'s murder,'' Harlan says to the Savage.
``Would you be interested in helping us track her down in Aberith?''

``To neutralize the threat to Eillin, yes, I would,'' says the Savage,
making it clear that he would not be interested in doing it just to
continue hanging out with them. ``It is my duty.''

``Good,'' says Harlan. He turns back to Frunk. ``Has anything else
suspicious or noteworthy happened since we last saw you?''

``No, no,'' sighs Frunk. ``Everyone's on edge because of the lockdown,
but nothing much has gone on other than some outrage at the cancellation
of an upcoming concert, since the band can't enter town limits.'' He
rolls his eyes. ``My house has been egged repeatedly. I didn't even make
this rule.''

``Yikes,'' says Galadriel. ``What band, though?''

``The Backstreet Bards,'' says Frunk.

``What?!'' cries Galadriel. ``You deserve worse than eggs!''

``Sorry, sorry,'' says Harlan, pulling Galadriel aside. ``We wanted to
let you know that the Savage here was the Lich's prisoner because he'd
been compelled to enter the city---we don't know how this was possible
outside of the wall---and was possessed by the Lich when we encountered
him inside.''

``It is lucky that I did not know of the rings' power while the Lich was
in my head,'' says the Savage, with a hint of resentment in his voice.
``But I entered the city, not knowing that the two rings I possessed
were two opportunities for the Lich to unleash total destruction upon
the continent. This was a great danger.'' He stares at Frunk, awaiting
an explanation.

``Bryn created the rings,'' says Frunk. ``I did not have any part in
that.''

``Yes, but you \emph{knew}, and didn't tell him,'' says Hermione
sharply. ``Is there any reason why we should not destroy them?''

``Bryn is the only one who truly understood them,'' says Frunk, eyes
downcast. ``And he and Uncle were the ones who sealed the city. But it
seems like you may have a point.'' He pauses. ``I had hoped\ldots{}
foolishly, it now seems\ldots{} that it was just a terrible rumor. That
there was not really a Lich in the City of the Dead.''

``Well, there definitely is!'' says Tannin blithely.

A long silence follows. Each of them searches for something to say, but
finds nothing---minds empty as the hands of firefly chasers. Finally,
the quietest one speaks.

``I am dissatisfied,'' says Hanamir. ``But I think traveling onward to
Aberith is the right move.''

``I do hope your theories about this suspect bear fruit,'' says Frunk.
``It would be a great relief to put this murder behind us and find
justice for Bryn.''

They say their goodbyes and watch as Frunk returns up the pathway toward
town. When he is out of sight, they take their first steps toward the
great city of Aberith.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

The sun shines high over the gently sloping meadows north of Eillin.

``And there's where we fought Guz and his polymorphed goons.'' Galadriel
points to a nondescript hillock near a small thicket of trees. ``And
Harlan talked to a bird to tell it to go get Hanamir.''

Redyl nods and makes all the requisite noises to indicate interest, but
seems distracted.

``You all right up there, Redyl?'' asks Hanamir. He has the gnome
sitting on his shoulders again in order to spare him the strain of
keeping up on foot with the rest of the longer-legged party.

``Oh, yes, I'm just fine; thank you for asking,'' says Redyl. ``I admit
I'm preoccupied with worries about my children. And without my magical
supplies, I do feel\ldots{} vulnerable.''

Harlan has opted to walk, at least for this portion of the journey,
while his bat stays close in the sky. He gives Hanamir a nudge.

``Hey, you think \href{/characters/shinebright/}{Shinebright} had
anything Redyl might find useful, until he can get new supplies?'' he
says.

``We could stop by our rental property, just in case, and take a look,''
says Hanamir. ``Check in with H'Jun, too.''

``Hold up, what?'' says Tannin. ``You guys have a rental property now?''

``So, uh, yeah,'' says Galadriel, chewing on her lip. ``Remember that
monster you mentioned? Fleshy horror, lots of mouths? That used to be
the owner of this tower up ahead.'' She squints and points at the
emerging shape of Shinebright's tower in the distance.

``Did you do that to him?'' says Tannin, with a mixture of disgust and
respect.

``Yeah, and you're the one who technically killed him, so you're in on
this grift, too.'' She grins at him slyly, then shrugs. ``Anyway, he
literally begged us to do it, so.''

``It's a comfort to know I'm not the only victim of this group's
haphazard attempts at adventuring,'' mutters the Savage, who has been
quiet since their departure from Eillin.

``I'm gonna go ahead and pretend I did not hear any of this,'' says
Hermione.

They approach the tower in good spirits, with Galadriel and Harlan
reminiscing about the talking sheep, the nail-biter of a battle with
Noke and the bed dragon, and the final, unenviable fate of both Noke and
Shinebright. When they arrive at the gate surrounding the property, they
can see H'Jun hunched over in the herb garden that Harlan planted.

``Would you look at that! He's taking care of my plants,'' says Harlan.
``I knew this responsibility would help him turn things around.''

They come closer, and Harlan's face falls. H'Jun is vomiting all over
the spring peas.

``Oh, hi guys,'' mumbles H'Jun, wiping his mouth on his sleeve.
``Rain'll clean that off. What\ldots{} why you\ldots{} I mean, what
brings you all here?''

``You okay?'' says Galadriel.

``Totally, totally,'' says H'Jun.~``And you know what, I'm almost out of
all the ale I brought with me, so that's good, right? Then I won't have
any more.''

``Sure,'' says Harlan. ``So what have you been up to?''

``Uhhhhh,'' says H'Jun.~``Well, I have my tools, and I was thinking of
doing some repairs on the outhouse, you know, for the\ldots{} for the
tenants\ldots{}''

``Found one of those yet, big guy?'' asks Hanamir.

``Not yet\ldots{} a few leads, though\ldots{} don't worry,'' says
H'Jun.~``My word is--- \emph{hic} ---my bond.''

``Well, mind if we go inside for a bit?'' says Harlan. ``Our friend here
is a wizard who's been robbed of his implements, and we'd like to see if
Shinebright left anything he could use.''

``By all means, please.'' H'Jun gives them a wave toward the door with
an elaborate bow and tips over into the chives.

The magical supplies remaining in the tower, such as they are, are of
very little interest to Redyl.

``This was a transmutation wizard, you say?'' he says, inspecting a
cloudy set of crystals.

``Yes,'' says Harlan. ``But not a very good one.''

``I could take some of the more quotidian supplies,'' says Redyl. ``Can
always use a bag of ash or some shards of bone. But I'm afraid there's
not much else for me here.''

``Sorry, Redyl,'' says Hermione. ``We'll be in Aberith soon enough, and
you can get higher-quality things there.''

``We'll spot you the gold,'' says Hanamir.

Redyl bows.

``My gratitude to you all is unending,'' he says.

After a short rest in the tower, they decide it would be best to get a
move on. They will need to travel at a quick pace in order to reach
Aberith in time to meet up with Magick. The Savage trails several yards
behind them all, brooding. Back atop Hanamir's shoulders, Redyl is
reassuring them that he didn't have high hopes for another wizard's
supplies, anyway.

``I'd need my arcane focus,'' he explains. ``It was an amulet. It
allowed me to channel my magical energy, and that's how most of my magic
was done.'' He nods at Hermione. ``You're a wizard, you understand.''

``Of course,'' she says. ``I know it's a long shot, but would you happen
to have any use for this?'' Hermione reaches up and hands him the amulet
she found in the fire at the abandoned orc camp.

``How did you\ldots?'' says Redyl. His eyes widen. ``This is the amulet
of an ancient king!''

``We thought it might be something important. But we didn't recognize
the name inscribed there,'' says Hermione.

``This is---ancient isn't even the right word. Legendary is more apt,''
explains Redyl. ``Geril IV was a king of Teron.''

``Teron, like\ldots{} the City of the Dead?'' says Harlan. ``The
skeletons there were all calling it that.''

``I don't know if that's true,'' says Redyl. ``It could be. No one knows
for sure where Teron was. It was the capital city of an empire that fell
long ago.''

``How do you know all this?'' says Tannin, brow furrowed skeptically,
staring up at the gnome.

``About Teron? I learned it in school,'' says Redyl. ``Everyone I know
did. But I'm from a gnome community, of course, in the forest at the
northern edge of the continent.''

``What else do you know about Teron?'' asks Hermione, as Redyl hands the
amulet back to her.

``Well, let's see,'' he says. ``It was ruled by an unbroken line of
seven and a half kings. That part is easy to remember.'' Redyl chuckles
at their confused faces. ``They possessed a great power that was passed
down from king to king, and it allowed them to prolong their lives. Most
of them lived a century, or a century and a half at most, and then
handed it down to their child. But Geril VI, the sixth king\ldots{} he
decided to live for a thousand years. And when he eventually died, he
gave the power to his son, and that's when things started to go badly.''

``What happened?'' Hermione looks fascinated but also a bit miffed that
this story was left out of her history courses.

``Geril VII had a difficult time as a ruler. Within thirty years of his
succession, the city was completely bankrupt. And Teron, remember, had
been the most powerful city in the empire. It fell into ruin---burned
down, in the end, I believe,'' says Redyl, scratching his head. ``This
was all thousands of years ago, mind you. These stories could be as much
myth as history. But primary sources do suggest it was a real place.''

Hermione turns the amulet over in her hands, thinking.

``We should show this to King \href{/characters/slee/}{Slee}, and see
what he makes of it,'' she says.

``I think it's bad news,'' murmurs Hanamir. ``If Teron is indeed the
City of the Dead\ldots{}''

``Why wait?'' says Tannin. ``We could just smash it now.''

Redyl laughs and looks down at Tannin.

``You remind me of my son,'' he says. ``Headstrong. Rash. Thinks he's
invincible.'' The anxious creases return to his face. ``I worry about
him, especially what he'd do to try and rescue me. Rompit's never been
one to shy away from danger. But he's smart, and he's well-trained, so
he gets away with a lot.'' Redyl sighs. ``Syndra's got a good head on
her shoulders, and I hope she'd keep him in line. I have faith in both
of them, of course, but\ldots{} the magical dispatches I sent
out\ldots{} there's been no response.''

``They sound like great kids, Redyl,'' says Hanamir. ``And one of us saw
your son quite recently. There's reason to hope.''

``Yes, he seemed in pretty good shape when I met him,'' says Hermione.
``The prison was awful and dark, but we were both glad not to be alone.
He didn't tell me anything of his plans, though. I think he was keeping
his secrets close to the chest.''

``Did you see any other prisoners?'' asks Redyl.

``No, just Rompit. Did you?''

``Yes, yes. Prisoners, co-conspirators, all kinds of strange folk. I was
being kept above ground, though,'' says Redyl.

``What were the people like?'' asks Harlan.

``The first thing that struck me was how strange it was that they were
meeting with drow,'' says Redyl. ``Orcs and drow---you don't see them
together much. But the drow were part of their scheme to kill Gruumsh, I
think.''

``That sounds right,'' says Hanamir. ``We defeated a faction of drow who
were attempting to kill another god,
\href{/characters/eilistraee/}{Eilistraee}, and they were in league with
orcs.''

``Yes, I don't think Gruumsh was the only target. It seemed much bigger
than that. I saw creatures coming and going that I couldn't even
identify---tentacles on their faces and whatnot.''

``And the other prisoners?'' says Hermione.

``There were many. Spellcasters, all of them. The orcs burned through
them quickly. I'd see them form expeditions and attempt the
plane-shifting spell, trying to get to where they were trying to go, and
they were all failures. A lot of people died. I was there three months,
watching all of this. When it was my turn, I got lucky.''

He pauses to take a breath, smiling wryly.

``Not sure if it was truly lucky, or unlucky, actually. But my spell
worked, and we went through the Shadowfell to the City of the Dead.
\href{/characters/khargol/}{Khargol} then came through the portal after
us. I don't know what became of the other orcs who didn't come with us,
or of the remaining tuning forks they had with them.''

The party walks in silence for awhile, turning this information over.
The afternoon bleeds into evening, and the setting sun makes them all a
little sluggish. Harlan whistles for his bat to carry him awhile. Under
the pink sky, the terrain is flatter now, with no forests or rivers in
sight, though a faint marshy smell is in the air.

Galadriel walks side-by-side with \href{/characters/buddy/}{Buddy}. She
has noticed that since his admission that he's not really a pig, he's
been more open about his preference to trot alongside her rather than
peek out from the top of her backpack. Sometimes he still gets tired,
what with his little legs, and he'll go back in---but it makes Galadriel
happy to see him in this new light.

\emph{He's growing up so fast,} she can't help but think. \emph{Sorry. I
know you're not a baby, if you're listening.}

HAHA. THAT'S OKAY.

Galadriel shivers, but not because she's frightened. It's just that
having one's train of thought interrupted by someone else's is not an
experience that she thinks she'll ever get used to.

GALADRIEL, HOW MUCH DO YOU TRUST THE PEOPLE WE'RE TRAVELING WITH?

\emph{With my life!}

EVEN THE NEW ONES?

\emph{Oh, well, we really just met the gnome, but he seems sincere. I
don't have solid proof, but I think he's trustworthy.}

YOU KNOW I'VE COME TO TRUST YOU. AND\ldots{} ONLY YOU.

Galadriel is unable to suppress her joy. She smiles at Buddy, eyes
twinkling.

\emph{Aw, Buddy. That means a lot. I trust you too.}

I WANT YOU TO KNOW THAT I THINK SOMEONE WITH US HAS AN ULTERIOR MOTIVE.

\emph{Wait. You don't mean Hermione, Tannin, Hanamir, or Harlan, right?}

NO.

\emph{So\ldots{} you're worried about the Savage, then?}

MAYBE. SOMETHING FEELS DIFFERENT NOW THAT THE NEWCOMERS ARE HERE.

\emph{We've fought next to him before, and he's always been on our side,
even if he's not a great guy personally. Is it that you think the
influence of the Lich isn't fully gone?}

I DON'T KNOW. I WISH I DID. BUT UNTIL I FIGURE OUT WHAT'S GOING ON, I
JUST WANTED TO EXPLAIN TO YOU THAT THIS IS WHY I INTEND TO REMAIN A PIG
FOR THE TIME BEING.

\emph{Oh, I understand. You don't need to explain yourself to me.
Whenever you're ready to stop being a pig, that's up to you.}

HAHA. I'VE BEEN READY FOR AWHILE.

Galadriel's heart does a somersault.

\emph{Oh?}

YES. THIS PRANK HAS GONE ON FAR TOO LONG.

\emph{\ldots Prank?}

SORRY. I'LL BACK UP. I TURNED MYSELF INTO A PIG AS A PRANK.

Galadriel's mind is actually blank. All of her theories on why Buddy did
this, or why this was done to him, have fallen through a trap door at
the base of her skull, promptly devoured by sharks in the pit below. It
never, ever occurred to her that Buddy might be a pig because\ldots{}
\emph{comedy.}

I CAN FEEL THAT YOU'RE CONFUSED. I KNOW. THE PRANK GOT OUT OF HAND. I
KEPT THINKING `MAYBE NOW WOULD BE THE FUNNIEST TIME TO REVEAL MY TRUE
FORM.' BUT THEN EVEN FUNNIER OPPORTUNITIES WOULD BE JUST DOWN THE LINE,
AND I'D HOLD OFF. AND I JUST KEPT HOLDING OFF.

\emph{Totally.}

REMEMBER WHEN WE WERE ON TOP OF THAT TOWER? I WAS SO CLOSE TO DOING IT
THEN. BUT THEN WHAT YOU DID WAS REALLY FUNNY TOO, SO\ldots{}

\emph{It would have stolen your prank thunder. I get it.}

YES. SO I'VE BEEN WAITING AWHILE.

Galadriel gathers up some of her composure.

\emph{I bet when you finally do it, it'll be worth it. Best prank of all
time?}

I HOPE SO. BUT NOW I DON'T THINK I SHOULD DO IT AROUND THE NEWCOMERS AT
ALL. AND---I KNOW HE'S NOT A NEWCOMER, BUT---DID YOU NOTICE THAT YOUR
DWARF FRIEND CAME BACK AND HE'S A FISH MAN NOW?

\emph{Yes! Isn't that the coolest?}

I'M IN YOUR BACKPACK, JUST EATING YOUR PROVISIONS AND STUFF, AND I POP
MY HEAD OUT AND HE'S A FISH MAN NOW?

\emph{Are you jealous? It's a pretty good twist. Almost a prank, if it'd
been intentional.}

HA.

\emph{But really, Tannin's a great guy, don't worry about him. I'm sure
he'd admire your commitment to landing a joke.}

I GUESS WE'LL FIND OUT AT SOME POINT, RIGHT?

\emph{I guess so.}

WELL, YOU SEEM LIKE YOU'RE DOING ALL RIGHT. BUT IF YOU EVER NEED MY
HELP, LET ME KNOW.

\emph{If you happen to know anything more about the Lich, that would be
a huge help.}

AH, NOPE. I'M TOO YOUNG TO KNOW MUCH. I'M JUST ABOUT SIX HUNDRED.

\emph{Six hundred?!}

YEAH. WHAT ARE YOU GUYS? A THOUSAND?

\emph{No! I'm only fifty, and the rest of the group\ldots{} well, I'm
not sure, but no one's as old as you.}

BUT YOU'RE SO BIG! HOW ARE YOU ONLY FIFTY?

\emph{I'm a pretty average-sized adult, for what I am. Do you know what
I am? I'm half-elf, half-human. How big do you think I should be?}

NOT TOO FAMILIAR WITH ELVES AS A SPECIES, I'LL ADMIT. BUT FIFTY? YOU'RE
AN INFANT. YOU SHOULD LOOK LIKE A BABY ELF.

\emph{Sorry, that is incorrect.}

Galadriel is giggling aloud, and the others in the group turn and give
her some quizzical looks. She waves them off.

``Just thinking about funny stuff from the other day,'' she says. ``You
know. Nothing. Whatever.''

NICE COVER STORY, YOU BABY!

\emph{Yeah, yeah, yeah. Okay, now that we're getting into personal
details, do you mind telling me why you were in that spider cave inside
the well, where I found you?}

THEY DUG THAT STUPID THING INTO MY HOME LIKE TWO HUNDRED YEARS AGO.

\emph{Who did? Why were the spiders there?}

I DON'T KNOW.

\emph{And what was with that gauntlet that I made you throw up? Why did
you swallow that?}

OH, THAT? THAT WAS ON SOME DROW I ATE.

If Galadriel's heart did a somersault before, it now does a quad salchow
with a messy landing.

\emph{Oh, um\ldots{} oh!}

IT WAS A LITTLE BUMPY IN THERE WHEN I SHRANK DOWN INTO MY PIG SIZE. IT
FIT A LOT BETTER IN MY REGULAR STOMACH.

Her pulse is pounding. Buddy is large enough to eat a drow? Buddy ate a
drow? How big is Buddy's regular stomach?

\emph{Well\ldots{} it's attached to my arm forever, now.}

YEAH, HOW'S THAT GOING?

\emph{It's been weird, but there are perks. I mean, you've seen,
obviously. I can climb on walls and ceilings and stuff.}

SOMETIMES I LOOK OUT OF THE BACKPACK AND I'M LIKE `WHOA, WE'RE UPSIDE
DOWN, THAT'S COOL, BETTER HANG ON.' THERE WERE TIMES WHEN I WORRIED YOU
FORGOT ABOUT ME IN THERE.

\emph{No, no, no! I'd never forget about you. It's just that in combat,
I want to make sure you're safe, and it's safest when no one even knows
to target you. And as long as you're strapped in there, you won't fall,
I promise.}

GALADRIEL, YOU REALLY DON'T NEED TO WORRY ABOUT ME. BUT I APPRECIATE IT.
YOU JUST LET ME KNOW WHEN YOU NEED ME, OR WHEN YOU THINK OF A REALLY
FUNNY TIME FOR ME TO REVEAL MY TRUE FORM.

\emph{Okay, Buddy. Good to know. I'll try not to worry about you.}

Without warning, Galadriel feels her eyes start to well with tears.

\emph{Love you.}

In place of a goodbye, Buddy sends a different kind of thought into
Galadriel's mind. It is infinitesimally brief. It's a vision, and it
makes her stop in her tracks as the rest of the party continues walking.

She sees a dragon, enormous, decked in glittering scales, unfurling its
massive wings and shaking its horned head. It glows with a warm light.
She is unable to draw breath. A feeling she might have called fear is
washing over her, but it calls itself awe.

When the vision disappears---and it does, so quickly that she then
wonders if she imagined it---she continues walking, giving her legs
explicit instructions to move forward. Left, then right, then left. By
her side, the little pig oinks contentedly, scuffling through the
night-cooled grass.

``We should set up camp,'' says Hanamir. ``We have another long day of
walking tomorrow.''

Hermione groans. Harlan brings the bat down, treating them all to a
soothing breeze from its wings as it lands. The Savage finally catches
up to them, but then starts setting up his bedroll a noticeable distance
away.

``What's with you, Moonwater?'' says Tannin. He spreads out his own
bedroll on a horrible patch of bumpy ground, then dives into it.
``You're never this quiet. You're usually loud and annoying. Bards, am I
right?!'' He reaches out to give Harlan a high five, and is ignored.

``What? Nothing,'' says Galadriel.

She tucks herself in next to Buddy, as she always does, but sleep feels
laughably impossible. She stares wide-eyed into the dark.

\emph{I am, at this moment in time, spooning with a DRAGON. There is a
DRAGON in my sleeping bag. A six hundred year old DRAGON is my pet pig.}

She listens to the sound of crickets and the chorus of the other
adventurers breathing.

\emph{This unfathomably deadly creature is my favorite person in the
world.}

The gods of sleep must have been waiting for her to acknowledge this. To
her surprise, they let her sink into dreams without much ado.


\chapter{Rockabout}
\chapdesc{Crikey! A petrifying foe, and two new mates from down Underdark who want no rulesjust rights.}

As a young elf, \href{/characters/hermione/}{Hermione} suffered
frequently from nightmares. It's not that she was afraid of the
\emph{dark}, she would always explain. She was afraid of what might be
\emph{hiding} in the dark. It's part of how she became interested in
thaumazoology, in fact.

``To study a creature is to tame it in your mind,'' she would sometimes
say when introducing herself at cocktail parties. ``If you know its
needs, its weaknesses, its habitual behavior\ldots{} you can outsmart
it. You can protect yourself with knowledge.''

Tonight, during the group's long rest on the road to Aberith, Hermione
suffers from nightmares for the first time in years. But they're nothing
like the nightmares she used to have.

It's the same dream over and over: her friend---it's not clear which
friend---has a child, a young boy no older than four. He is dying, and
there's nothing anyone can do. The most talented healers in the world
have all failed to cure his illness. Hermione is overwhelmed with grief,
and would do anything to save him, but all she can do is watch on
helplessly as he dies.

The boy dies this way countless times in Hermione's head before she
wakes up. The darkness around her is still deep. There are hours to go
until sunrise, but she can't just lie there with that dream rattling
around in her head. She packs her things quietly, leaves a short note,
and walks onward alone.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

The other adventurers awaken abruptly to the sound of
\href{/characters/tannin/}{Tannin}'s voice reading in a loud monotone.

``My dear friends,'' he announces. ``Due to some distressing dreams I
have decided to travel ahead on my own worry not though I will meet you
at the gates of Aberith much love---'' He squints.
``Herm---Hermy\ldots{} nine. Ohhh, is that the blue-haired chick?'' He
counts the other members of the party, who are grumbling incoherently.
``Yeah, must be.''

``We did introduce you,'' says \href{/characters/harlan/}{Harlan}.
``Days ago.''

``Forgot,'' shrugs Tannin. He drops the note on the ground. ``Come on,
guys, the sun's almost done rising. Let's go.''

\href{/characters/hanamir/}{Hanamir}, \href{/characters/redyl/}{Redyl},
and \href{/characters/the-savage/}{the Savage} find this call-to-action
persuasive. Harlan seems to be considering it.
\href{/characters/galadriel/}{Galadriel} dissents.

After a few minutes, though, even she cannot remain asleep amidst the
high-pitched shrieking noises produced by Harlan's bat.

``Whoa, whoa, whoa,'' Harlan says, holding out his single hand for the
bat to sniff. ``It's me, remember?''

The bat considers this, sniffing, and then shrieks again.

``Have you thought about giving it a name?'' asks Hanamir.

``It's a him, I think,'' says Harlan. ``And yes. I was thinking
Camazotz, for the god of bats. Zotz for short. That all right with you,
Zotz?''

Zotz emits another noise, still piercing, still horrible, but somehow
reminiscent of a purr.

``I'll take it,'' says Harlan.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

As the morning lengthens, the scent of marshland grows stronger in the
air. There's still low tree coverage along their path, and a thick
underbrush that seems alive with unseen fauna.

``Don't react,'' Hanamir murmurs to the party, ``but I think there are
two large creatures off to our right that may be stalking us.'' He makes
eye contact with each of them, then nods to the Savage. ``Take the gnome
and stay clear, will you?''

``Fine,'' says the Savage. He scoops Redyl up by his armpits and places
him on his own shoulders. It's very cute, and the Savage scowls, knowing
it.

Hanamir tiptoes into the dense thicket to the right of the path. In a
matter of seconds, the adventurers hear the bass-clef version of an
angry owl's hoot. Hanamir reappears among the party like a snake
retreating to its den after a successful bite.

``Owlbears,'' he reports. ``Two of them. One smaller, one larger. I
stabbed the smaller. Ah, here they are.''

As described, the two giant feathery beasts burst from the brush with
talons curled. The smaller of the two is bleeding. Galadriel casts
Thunderclap on them both, knocking them back before their claws can find
a target.

Harlan squeezes his heels into Zotz's side and the bat takes flight over
the impending battle. From the air, he casts Sacred Flame on the smaller
owl. It hits the ground again, and this time struggles to get back up.
Galadriel shoots a well-timed arrow, and it collapses for good.

As if retaliating, the larger owlbear lashes out at Hanamir and carves
into him with its hooked beak. Hanamir stabs back at it, but it's hard
to tell if any of the blood on the owlbear's feathers is its own or if
it has all spurted directly from a half-orc artery.

Tannin flies into a barbarian rage and punctures the creature's back
with his trident. As he pulls out the weapon, the owlbear turns to
stone.

``HA!'' he cries triumphantly. ``Another new power!''

While Hanamir is struggling to stanch the flow of blood from his beak
wound, he also waves an arm in warning.

``Look away!'' he hisses. ``No, Tannin, don't look in my direction. I
believe a basilisk may be behind me. Tannin, seriously, don't look
around the owlbear statue. The basilisk turned it to stone.''

Before shutting her eyes, Galadriel casts Healing Word on Hanamir and
Stinking Cloud in the direction of the petrified owlbear. Hanamir and
Tannin, as well as whatever is behind Hanamir, are enveloped in a thick
and noxious fog.

From above, Harlan casts Call Lightning. A thick bolt of lightning
splits the cloud for a moment.

``Did I hit it?'' shouts Harlan.

``Maybe,'' Tannin shouts back. ``You didn't hit me, at least. Hanamir?''

``I'm good,'' says Hanamir. ``I think I'm close to it. I'm going to try
to get a hit---''

The party can hear Hanamir's sword connect with something scaly.

``I don't need eyes to kill this thing!'' roars Tannin. Harlan and
Galadriel can see the faint glimmer of his trident spinning in all
directions until he, too, hits something solid. ``Ha! Found it!''

The trident acts a bit like a fan and blows some of the stink cloud
away.

``Don't look!'' Hanamir warns again. ``Eyes closed, everyone!''

Galadriel casts Mage Hand. A small, golden-glowing facsimile of her own
hand appears before her. She directs it to undo the buckles holding her
bedroll in place atop her backpack, and then slowly carry the blanket in
the air to the place where she can just about glimpse the prongs of
Tannin's trident above the cloud. The floating hand drops the blanket,
dispersing more of the cloud, and leaving a reptilian-shaped lump under
the bedding.

``Ah, well done,'' says Hanamir. He stabs the lump through the blanket a
few times, to be thorough. ``Got him.''

``Bad news about your bedroll, though, Galadriel,'' says Tannin.

Harlan directs Zotz back to the ground.

``We should probably be careful handling this,'' he says. ``Keep it
wrapped in the blanket, maybe, until we're sure it's safe to look at.''

``I know these critters sell well in some circles, but don't know what
for,'' muses Hanamir. ``Alas, Hermione might know.''

``Something about the organs, I'm pretty sure,'' says Harlan.

``We can take it with us, and ask her when we meet up outside Aberith,''
says Galadriel.

Tannin volunteers to carry the basilisk corpse. He slings it over his
shoulder in the bedroll like a sack of potatoes, then pulls out a small
pad of parchment and adds a line to what must be his (very short)
inventory.

``One (1) basilisk corpse,'' he intones in time with the scratching of
his quill.

``Now, as for owlbears,'' says Hanamir, ``I hear these grill up nicely
in steak form.'' He makes quick work of butchering the smaller owlbear.

The other one is still frozen in place, a permanent stone statue of an
enraged owlbear in the center of the clearing.

``Too bad about this one,'' says Tannin. ``I guess we could carve our
initials into it, though?''

The adventurers sit down for a short rest in the statue's shadow, and
one by one, they take up Hanamir's chisel and make their marks on the
base of the stone. During this idle time, the Savage rejoins them. He
has attempted to diminish the cuteness of toting a gnome on his
shoulders by fashioning a makeshift gnome-sized baby bjorn. Obviously,
this backfires, and the effect is cuter than ever.

Now bereft of a bedroll, Galadriel and \href{/characters/buddy/}{Buddy}
lounge on some cushy moss.

\emph{Hey Buddy}, thinks Galadriel.

YEAH?

\emph{You know anything about basilisks?}

NEVER RUN INTO ONE MYSELF. BEFORE NOW, THAT IS. QUITE A FIND.

\emph{Really?}

WELL, I'M SURPRISED TO SEE ONE AROUND HERE. BUT THAT'S ABOUT ALL I KNOW.
SORRY I CAN'T BE MORE HELPFUL.

\emph{That's okay! Thanks anyway.}

She closes her eyes and strums her lute, but quickly falls asleep.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

The ground becomes swampier as they approach the coastal region of
Aberith that afternoon. From his scouting position a few paces ahead,
Hanamir falls back.

``Voices ahead on the path,'' he says. ``Sounds like Undercommon, but I
could be wrong. Anyone speak it?''

Tannin raises his hand. The voices are growing slightly louder, and he
can pick up some of what they're saying.

``Something about\ldots{} `the twelve supreme entities gather around a
table and laugh at us\ldots{} dividing the world into dark and light.'
Something like that,'' Tannin translates.

``Resentment of the gods?'' says Harlan. ``Seems like someone we may
want to check out, what with all this god-killing going on.''

``All right, want me to say hi?'' says Tannin.

``Yes, but I will elect to stay hidden.'' Hanamir disappears behind a
tree.

``G'day,'' shouts Tannin, as two drow appear around the bend. They are
dressed in simple drow attire, not displaying any particular religious
or military affiliation.

``G'day,'' the drow nod their heads at Tannin. ``You all speak Common,
mate?''

``Yes,'' responds Tannin in Common. ``Thanks.''

The drow continue in heavily Undercommon-accented Common.

``Don't see too minny trevelers out here,'' says the older one. ``Where
you all hidded?''

``To Aberith,'' says Galadriel. ``A first visit for us all.''

``Ah, yis! Ebberith. We just came from thet way. Now hidded off on a bit
of a walkabout, up to the mountains. Oi'm Nim, by the way. And this is
my son, Nizana.''

``Wonderful to meet you both,'' says Harlan. ``You know, we couldn't
help but overhear that your son might have gotten up to a bit of trouble
with the gods\ldots?''

``Oh? Wott'you mean by thet, then, mate?''

``Sorry,'' Galadriel interrupts. ``It's a sensitive topic, I know. I was
recently ensnared in an evil spider cult myself, and I know how easy it
is to run afoul of the gods. I just wanted to offer my support, that's
all.''

Nim glances at her gauntlet.

``D'you follow Lolth, then?'' he asks.

``Yes, but\ldots{}'' Galadriel hedges. ``Maybe not so much by choice.''

``See!'' Nim gives Nizana a soft punch in the arm. ``This is what I was
troying to till you! The gods, they eckt like we're their playthings.
They've enslaved us. She isn't even a drow, and they've got her mixed up
with Ol' Cobwebs!''

``Might I ask what happened?'' asks Harlan.

``Wot?''

``We mean, what made you feel this way about the gods?'' asks Galadriel.

``I hed my eyes opened, thet's all, mate. There's this priest in the
kepital who's got it all figured, roight? Now I'm just troying to do the
same for my son. He's been indoctrinated from choildhood to worship
these toyrants.''

``We'd certainly be interested in hearing this priest's teachings,''
says Harlan. ``He's in Aberith? What's his name?''

``They call him the Missinger, and he'll sit you straight all roight,
mate,'' says Nim. He nudges Nizana again. ``Think---wot if when he was a
baby, I gave him a loaded crossbow and walked away? Oi'd be a tirrible
parent. That's wot the gods've done! Gave us all this meggic, then left
us to kill each other with it!''

``The Messenger, all right, thank you,'' says Galadriel. ``We'll look
out for him when we get to the city.''

``If you esk around, you'll foind him,'' says Nim. ``Safe trevels,
then!''

``Oi,'' says Tannin, as they walk away. ``Want any owlbear steaks? For
the barbie? We got tons.''

``Nah, no thenks, mate, `preciate it!''

When the drow are out of sight, Hanamir reappears. The adventurers
discuss what they just heard as they set up camp for another night.

``How much you wanna bet the Messenger is somehow related to the Lich?''
says Tannin. ``Trying to get people on his side, trying to make people
want to kill off all the gods\ldots{}''

``Could be,'' says Hanamir. ``Or just your standard demagogue. Hard to
say until we see him for ourselves.''

``Nim really did not like my amulet of \href{/characters/kord/}{Kord},''
yawns Harlan. ``He kept glaring at it.''

``He was not a fan of my gauntlet, either,'' says Galadriel. ``But I
think he saw us more as poor suckers than as agents of evil.''

``Stop talking,'' commands the Savage from his sleeping bag a few yards
away.

``Lots to think about, that's for sure,'' whispers Harlan. He holds his
amulet, turning it over and over.

As he sinks into sleep, he wonders if he'll dream about being the slayer
of Kord again.


\chapter{Neophytes, Big City}
\chapdesc{What's a mob to a king? What's a king to a god? What's a god to a non-believer?}

The next day, the road to Aberith becomes gritty with sand. The
adventurers can hear the sound of seagulls in the distance, but the
ocean is still out of sight. They have reached the edge of a coastal
farming town in the grassy lowlands. A few hulking, horned creatures can
be seen grazing to the side of their path.

``I can't tell if that barn up ahead is oversized, or if I'm just
feeling insignificant,'' says \href{/characters/harlan/}{Harlan},
squinting.

``Oversized, I think,'' says \href{/characters/hanamir/}{Hanamir}. ``For
scale, I spy a certain blue-haired elf.''

He's right: emerging beside the barn,
\href{/characters/hermione/}{Hermione} is pacing in a circle, scribbling
notes in her logbook with characteristic intensity. When they are close
enough to her to get her attention, she looks up and smiles.

``I thought you all might catch up to me here,'' she says. ``I couldn't
help but stop and observe the aurochs.''

\href{/characters/tannin/}{Tannin} drops the tattered bedroll at her
feet.

``Observe this!'' he says proudly.

``Uh,'' says Hermione. ``What?''

``We killed a basilisk,'' says Harlan.

``What?!'' Hermione yelps, kneeling down and starting to unwrap the
reptilian corpse from the bedding. ``I missed a basilisk?!''

The other adventurers cringe and shield their eyes.

``Oh, you can look,'' says Hermione. ``Once it's dead, it can't hurt
you. Unless you know how to prepare potions from its organs.''

``Do you?'' asks Hanamir.

``Sadly, no,'' says Hermione. ``But I'm sure someone in the city does.''
She strokes the basilisk's spiny face and sighs. ``I've always wanted to
encounter one of these in the wild.''

Tannin re-packages the basilisk into the bedroll and tosses it over his
shoulder again.

``So, while you were observing the aurochs,'' says Harlan, ``did you
find out why the buildings around here are so big?''

``Large, blue humanoids live here,'' says Hermione. ``Eight to ten feet
tall, pointy ears. I don't know what they're called, and thought it
might be rude to ask.''

``Probably a good instinct,'' says Hanamir.

They continue on through the community and see the blue people attending
to their morning farm chores. As they walk, a foreign thought appears in
\href{/characters/galadriel/}{Galadriel}'s mind.

GALADRIEL, HEY.

Even though it's no longer new or surprising, Galadriel still feels her
heartbeat accelerate.

\emph{\href{/characters/buddy/}{Buddy}! What's up?}

I DON'T THINK I SHOULD GO TO ABERITH.

Galadriel tries to hide her disappointment. She'd been afraid of
this---the moment when Buddy would decide he'd had enough of her, and
would leave, and go off to do far more interesting things, and would
forget about her within a year or two of his next century of
life\ldots{}

DON'T WORRY. IT'S NOT THAT.

She flushes.

I'M CONCERNED THAT THERE MAY BE PEOPLE IN THE CITY WHO ARE ABLE TO TELL
WHAT I AM.

\emph{Okay}, thinks Galadriel. \emph{So do you want to stay here in town
while we go to Aberith?}

YES. MAYBE YOU COULD FIND A FARMER WITH SOME EXTRA SPACE IN HIS STABLE
FOR ME AND THE GIANT BAT?

\emph{Oh man\ldots{} farmers and pigs, though? I don't know. What if
someone tries to eat you?}

HAHAHAHAHAHAHAHAHAHAHAHAHA. HAHAHAHAHAHAHAHAHA. THEY COULD TRY!
HAHAHAHAHAHAHA.

\emph{All right. I know I promised not to worry about you.}

YOU DID. I'LL BE FINE. LOOK AT ME.

Galadriel glances down and sees Buddy give her an exaggerated wink. She
can't help but smile.

``Harlan,'' says Galadriel. ``What do you think of asking that farmer up
ahead if he'd care for Zotz and Buddy while we're in the city?''

``Good idea,'' says Harlan. ``I doubt it's practical to fly a giant bat
through the streets of Aberith. But\ldots{} Buddy? You're not bringing
him with you?''

``No,'' she says, without elaborating.

``Hmm,'' says Harlan. He gives her some side-eye. ``Okay.''

They approach a tall, pointy-eared, blue-skinned individual wearing a
straw hat. He is brushing the coat of an auroch and patting its head.

``Good morning, sir,'' Harlan addresses him.

``Oh, hey there,'' says the blue man in a charming drawl. ``Name's
Elris. Nice to meet y'all. Never seen a bat that big before.''

``Yes, this is Camazotz,'' says Harlan. ``I won him through conquest and
now he's my trusty steed of the air.''

``Mighty fine bat there, indeed.'' Elris nods appreciatively.

``We were wondering if you might have any room in your stable to look
after my bat, as well as this little pig, for a few days while we visit
Aberith,'' says Harlan.

``Certainly, certainly, I'd be happy to take care of your critters,''
Elris says. ``Only problem is that the city right now---well, they're
not really letting people in.''

``Is that so?'' asks Hermione.

``Yes, ma'am. I'm afraid only people with official business are going in
right now. There's been a rash of crime going on in the city. All y'all
might be stayin' out here for a spell.''

``Well, we do have business with the king\ldots{}'' starts Harlan.

``Business with the king?!'' The farmer is shocked, but still speaks at
a leisurely pace. ``Who might y'all be, if you don't mind my asking?''

``Adventurers,'' says Harlan. ``I'm Harlan Stormborne, cleric of
\href{/characters/kord/}{Kord}, and these are my companions. We have an
important message for King \href{/characters/slee/}{Slee} from the mayor
of Eillin.''

``Well, you shouldn't have an issue if you're acquainted with such
folk,'' says Elris. ``I can take care of the bat and the pig for five
silver a day.''

``Thank you,'' says Harlan. ``I'll add another five silver on top of
that just to make sure they get the best possible care.''

``Why, thanks, that's very generous.'' Elris tips his hat.

``Just to be clear,'' says Galadriel, a little more sharply than she
intended, ``this pig is like my son.''

``That's mighty strange, miss,'' says Elris with a chuckle. ``We do tend
to eat these kinds of critters normally, but don't you worry, this one
will be off limits.''

``Thank you,'' says Galadriel.

``And if it doesn't work out for y'all at the border, and you find
yourselves in need of a place to stay, we do run an inn here,'' says
Elris.

``We appreciate the offer,'' says Hermione. She pauses. ``Before we go,
do you have any details about the crime wave you mentioned? We want to
keep ourselves safe in the city.''

``Oh, yes,'' Elris sighs. ``It's very troubling. What we hear is that
there's been a tremendous number of people disappearing.''

``That is worrisome,'' says Harlan.

``I always just tell everyone to stay out of the Kiln, but we hear folks
are disappearing from all over the city, not just there.''

``The Kiln?'' says Hermione.

``It's a rough neighborhood in Aberith,'' says Elris. ``Here, I've got a
map on me. Y'all can take it with you, now.'' He produces a wrinkled but
functional street map of Aberith from a pocket in his overalls.

``Thank you, once again, sir,'' says Galadriel.

``Is there a pattern to the people who have gone missing?'' asks
Hermione.

``I'm afraid I don't know, miss. You could ask the guards.''

``Well, thanks again for everything,'' says Harlan, extending a hand.
``We'll see you in a few days, and thank you for taking care of our
animal friends.''

Elris shakes his hand and tips his hat again.

``All right, Harlan Stormborne and company,'' he says. ``Travel safe,
now.''

Zotz gives Harlan a farewell shriek. Galadriel stifles her sorrow at
leaving Buddy behind and reminds herself it's for his own safety. Buddy
gives her a gentle headbutt in the shins and follows Elris to his
stables.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

The adventurers follow the road out of the farming village and reach the
edge of the city. Beyond the wall, there are three tall towers that
dominate the skyline, and the ocean glitters like a field of sapphires
in the distance.

The gate ahead is guarded by several human men in shiny armor. They look
overheated, bored, and surly. One of them speaks as the party
approaches.

``What business do you have in Aberith?''

``We're here to see King Slee,'' Galadriel announces.

``Oh?'' says the guard. He and his compatriots laugh. ``Are you a close
personal friend of the king, little lady?''

``We have an important message for him from the mayor of Eillin,'' she
says. ``The mayor is unable to deliver it himself, since that town is
also on lockdown, as you know.''

``And what is the nature of your message?'' says the guard. His friends
have quieted down. He peers at Galadriel's face with some surprise, as
he registers that she's serious.

``There is a grave threat from the City of the Dead,'' says Harlan.

The guard turns his attention to Harlan, looking unimpressed.

``All right, well\ldots{}'' He glances at the other guards and shrugs.
``We're just supposed to make sure no one unsavory comes in. You guys
seem fine. But if you want to see the king, you'll have to get through
another checkpoint in the north of the city, and I can't help you
there.''

``While we have you,'' says Harlan, ``can you tell us what's going on in
the city? With the disappearances, that is?''

``People have been going missing.'' The guard shrugs again.

``Yes, but what people?'' Harlan presses.

``Frankly, I don't know why we care. Just riff raff. The council had us
put these restrictions in place anyway, though.''

``Do you know who might have more details on this?'' asks Hermione.
``I'm a little nervous.''

``Well, if you're going to see the king, he'd be able to tell you all
the specifics,'' says the guard. ``Or any of the other ministers on the
council. But from what I heard, it's mostly just like\ldots{} goblin
kids going missing.''

``Is there a large goblin population in Aberith?'' asks Galadriel.

``Larger than I'd like,'' says the guard snidely. The other guards
guffaw behind him.

``And where do they live?'' asks Harlan.

``They're not welcome in the north of the city, that's for sure.'' The
guard pauses. ``There have been some humans who've gone missing, too,
though. So be careful, I guess.''

He opens the gate and waves them through.

They walk through a neighborhood marked on Elris's map as Smalltree.
Just as the farming village was oversized to accommodate its residents,
this community is built on a much smaller scale. Halflings going about
their daily errands pay little attention to the adventurers as they pass
through. Tannin looks thrilled to be a head taller than almost everyone.

But given its miniature scale, Smalltree does not occupy much area, and
it soon gives way to a sprawling slum labeled on the map as the Kiln.
The halflings are replaced by a population of goblins, half-orcs,
strung-out humans, and some cloaked figures that may be hiding the tails
and horns of tieflings.

\href{/characters/the-savage/}{The Savage}, still holding
\href{/characters/redyl/}{Redyl} in the baby bjorn on his chest, flares
his nostrils with disgust as he passes a street vendor selling a variety
of eyeballs. Mercifully, little old Redyl has fallen asleep with his
gnome hat over much of his face.

A few of the half-orcs nod at Hanamir as he passes.

Hanamir addresses each one in Thieves' Cant, which sounds oddly poetic
(but nonsensical) to the ears of the other adventurers.

``I've a pair of eyes to switch a gallows-green chunk of brandy,'' he
murmurs to a half-orc with a jagged scar on his cheek. He slips him a
piece of gold. ``Point me to a piece man?''

``A pigeon-plucker you'll find at the beggar-maker's door,'' says the
other half-orc, pocketing the gold. ``Soon. At six dirty fingers.''

``Thanks,'' says Hanamir.

The adventurers stare at him, awaiting explanation. Hanamir smiles
softly.

``Just asking about a potential buyer for our special cargo,'' he says.
He nods at Tannin's bedroll-wrapped burden.

``Ohhh,'' says Tannin. ``Nice.''

Hanamir leads them to what must be ``the beggar-maker's door,'' or an
alleyway next to a disgusting tavern. In a few minutes, an individual of
orcish and goblin heritage emerges from the dark recesses of the alley.

``How can I help you fine folks today,'' he croaks, looking at each of
them in a way that could be interpreted as threatening. Hermione looks
intensely uncomfortable.

``We have come into possession of a certain item,'' says Hanamir. ``I
understand you're interested in items.''

``At times I have been known to purchase items, living and dead,'' says
the man.

``I see,'' says Hanamir. He gestures to Tannin, who hands over the
bedroll. ``Check this out.''

The man takes a brief look under the blanket and inhales deeply.

``Mm. Fresh. I'm willing to buy this one for sixty gold, and any future
ones for eighty.''

Hanamir turns to Hermione, who has been trying unsuccessfully to hide
behind him.

``Does that sound reasonable to you?'' he asks.

``Seems low,'' she says, without making eye contact.

``How about a trade?'' says Hanamir, turning back to the orc-goblin.

``What are you looking for? Body parts? I got all kinds of body parts.''
He takes another whiff of the basilisk corpse. ``Listen, you know it's
dangerous to ask around about what you've got here, with the AMLs and
all. You should take the deal.''

``AMLs?'' asks Galadriel.

``The Anti-Magic League,'' says the man. ``You not from around here or
something?''

``Just passing through,'' she says.

``Well, the Minister of Trade caved to the AMLs, and it's illegal to buy
or sell magical items right now. You all ought to be careful.''

``Instead of selling you the item itself, could we pay you for your
knowledge of how to use it?'' asks Hanamir.

``Not my area of expertise, as it were,'' says the man. ``If knowledge
is what you're after, you might stop by this tavern here, the Upstanding
Gentleman, after nightfall, and find someone who can tell you what you
need to know.'' He licks his lips. ``Do we have a deal on the item here
or not?''

Harlan turns and looks at them all.

``No, right?'' he says. ``We can do better.''

``All right, all right, you're too smart,'' says the orc-goblin. ``Two
hundred and fifty gold, if you're gonna play hardball.''

Hanamir looks tempted, but Galadriel shakes her head.

``I want more information on what exactly we can do with it first,'' she
says.

``Tell you what,'' says Hanamir to the man in the shadows. ``I'll come
and find you tomorrow.''

``Fine,'' says the man. ``Good luck out there.''

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

Harlan inspects Elris's map.

``If we want to try and see the king, we need to head north,'' he says.

He leads them through several more cramped streets lined with
illicit-seeming storefronts until they turn a corner and reach a more
mainstream thoroughfare. They pass through a touristy area of souvenir
shops and cafs, and then an upscale residential neighborhood labeled on
the map as Rivergate.

Past the stately riverfront properties, they come to a bridge heavily
patrolled by guards in the same gleaming armor as the ones outside the
city. The guards are questioning a handful of well-dressed people who
are attempting to cross to the northern part of the city.

``We may not be able to get across here with the, uh, item,'' mutters
Hermione.

``I can stay behind. You know. With the\ldots{} \emph{asilisk-bay
orpse-cay},'' says Tannin, grinning conspiratorially.

``Yeah, we know,'' says Hermione. ``As long as you don't draw any
attention to yourself.''

``I'll stay behind, too!'' pipes up Redyl, sounding groggy. ``I don't
want any more trouble. I'm old and tired. Let me stay with Mr.~Tannin.''

``Fine by me,'' says the Savage. He sets Redyl down on the cobblestone
street and then takes out his dagger, shredding the makeshift baby bjorn
as if ridding himself of a parasitic growth.

``All right, so the rest of us will try and cross the bridge,'' says
Harlan. ``What's our story here? Galadriel, do you want to take the
lead?''

``Sure,'' she says. ``I'll be a fancy diplomat of some kind, and you all
just pretend to be my entourage of bodyguards or something.''

Harlan looks skeptical, but lets Galadriel walk ahead of him to the
bridge checkpoint. She throws her shoulders back and gives her hair a
good, regal-looking toss.

``Hello, good sir,'' she smiles at the nearest guard. ``I have arrived
for my appointment with King Slee.''

``Good afternoon, madam,'' says the guard, flipping through a pad of
parchment. ``You have an appointment with the king?''

``Yes, a standing appointment.''

The guard rummages again through his papers, then looks up at Galadriel.

``What does this appointment pertain to, madam?''

Galadriel stares at him. The guard gets the sense, somehow, that
\emph{she} is trying to figure out what \emph{he} is up to.

``It's above your paygrade,'' she says, smirking. She can hear Harlan
sighing and muttering something about tact behind her.

``And who are all these people accompanying you?'' says the guard.

``These are my bodyguards. I feel very vulnerable in the city right now,
what with all the disappearances,'' she explains. ``I'm sure you
understand. It would be dangerous for a public figure such as myself to
travel alone.''

The guard's eyes widen with confusion.

``I'm not\ldots{} I mean\ldots{} we would have heard if we were supposed
to let you through today, madam\ldots{}''

``You don't recognize me?'' says Galadriel, sounding amused. Behind her,
Hanamir gives the guard a toothy grin.

A bead of sweat drips down the side of the guard's face.

``Okay, look, I guess I can let you through, but we'll have to have some
guards escort you to the king,'' he says.

``Oh, that's fine,'' says Galadriel, as if taking the high road. ``I'm
sure this is a misunderstanding. The king is expecting me.''

With spears pointed in Hanamir's direction, a group of guards in
different, amber-colored robes leads them across the bridge and into a
wide, marble square with a beautiful plein-air market. It looks like a
place that would usually be bustling with activity, but is now sparsely
populated due to the lockdown.

They pass by two of the tall towers visible from outside the city---the
Temple of Light and the Temple of Winds, which Harlan recognizes as a
temple to Kord.

``Look at that!'' he marvels, craning his neck upward. ``I've never seen
a more magnificent monument to the Lord of Storms. Praise be to Kord.''

Finally, they reach the steps of the castle. One of the guards runs up
to alert the king to his visitors. In just a few minutes, he returns,
and the rest of the guards lead them up the stairs and down some
impressive entry halls to the king's reception chamber.

``Friends from Eillin!'' says King Slee, waving them in and dismissing
the guards. ``I thought it might be you.''

The adventurers bow, and the guards depart.

``I don't think I'm acquainted with all of you, though\ldots?'' Slee
looks at Hermione.

``Yes, our adventuring party has grown, your majesty,'' says Galadriel.
``This is Hermione, a very learned scholar of magical creatures. And
another of our friends, Tannin, awaits us outside. You will surely meet
him someday.''

``Pleasure to meet you, Hermione,'' says the king. ``Do come inside.''

He leads them from the reception chamber to a smaller room, a parlor,
where a sharply-dressed man sits on an embroidered chaise, smoking a
pipe.

``I hope you all will excuse me,'' says Slee, as if he somehow should
have known they'd drop by unannounced. ``One of my ministers is here,
meeting with me. I feel anything you might need to share with me can be
shared with him as well.''

``Hello,'' says the man with the pipe. ``I am Ultas
\href{/characters/kandir/}{Kandir}, the Minister of Trade.''

The adventurers are suddenly tongue-tied.

``Your highness,'' says Hermione delicately, ``would it be appropriate
to discuss matters of garbanzos, kidneys, and limas?''

The king looks amused, and the Minister of Trade chuckles.

``I'm well aware of the Order of the Been, if that's what you mean,''
says Kandir.

``Well, we just came from Eillin,'' says Harlan. ``Rather, the Eillin
border, where we were able to speak briefly with Mayor Thunderstruck. We
told him, and now must tell you, that the Lich is amassing power within
the City of the Dead, and is allied with
\href{/characters/khargol/}{Khargol} and his orcs with the goal of
killing one or more gods, and of loosing his undead upon the
continent.''

Slee furrows his brow, but the trade minister speaks up first.

``And how, pray tell, would the Lich escape? He's been sealed in for
centuries,'' says Kandir. ``If that's all you came to say, I would ask
you to please allow me to continue my meeting with the king.''

``If you were really familiar with the Order of the Been, you'd know
it's very possible for him to escape,'' says Hermione. ``And it's
disconcerting if you do know that and you're not willing to listen.''

``Speaking of being familiar with the Order,'' says the Savage. ``I
wonder if the only two actual members of this \emph{secret order}
present might be allowed some time to chat alone. About \emph{secret
order} business.''

``Of course, old friend,'' Slee says warmly. ``It's been far too long,
Savage. I had hoped I'd see you at---''

``Yes, the Moon Festival,'' sighs the Savage. ``As I have explained to
these tryhards, I was away on important business to protect Eillin, and
couldn't make it to the party.''

``Sorry, but no, you weren't,'' snaps Galadriel. ``You were possessed by
the Lich and were under his control until we showed up and freed you. So
you'll include us in your secrets from now on.''

``Possessed by the Lich?'' says Slee, suddenly pale. ``Savage, is this
true?''

``It's impossible,'' Kandir butts in. ``And if this is all about
Eillin---an uncultured backwater town with no real government to speak
of---I implore you, your majesty, to waste no more of your time with
these people and to return to more important city matters with me.''

``Aberith has pledged itself to protect Eillin,'' says Slee. ``Kandir, I
beg your patience. I must hear them out.''

``The Lich possessed the Savage outside the City of the Dead,'' says
Harlan. ``His direct influence can extend beyond its walls.'' The Savage
looks down at the floor, which Slee, horrified, takes for confirmation.
``Further, we know that he was trying to recruit Khargol's army of orcs
to do his bidding. If he's recruiting minions to do his ill works, that
is a concern to the entire kingdom, not just Eillin.''

``We beg for your assistance, with knowledge or other resources, in
addressing this threat,'' says Galadriel.

``I don't have much knowledge,'' says King Slee.
``\href{/characters/bryn/}{Bryn} and Uncle sealed the city. For that, we
are all grateful. There haven't been any undead sightings since then. If
what you say is true, I would expect to have heard of \emph{something},
rumors, at least, of their reappearance\ldots{}''

``The undead have not ventured outside the city yet, as far as we
know,'' says Hermione. ``But we have seen the orcs inside, entering via
coercion of magic users who can plane-shift them through the
Shadowfell.''

``This is very troubling,'' says Slee.

``We're going after the Lich,'' says Hanamir. ``Our goal is to defeat
him. Any knowledge about how best to fight him would be a gift not only
to us, but to all of your people.''

``I understand, and I will support you however I can,'' says the king.
``I will write you passes to the royal library, which you may browse at
your leisure\ldots{}''

Hermione and Hanamir look at each other, ecstatic.

``\ldots And I will also grant you passes to move freely through the
city checkpoints.''

``Thank you, your highness,'' says Harlan, sinking into a deep bow.

``The laws will still apply to you. I expect you not to cause any
trouble in the city, or I'll have to revoke your privileges. That
includes the ban on buying and selling magical items.''

``Understood,'' says Harlan.

``May we ask the cause of the ban, your majesty?'' asks Hanamir.

``Oh, well,'' the king says, sounding tired. ``Pressure from the AML,
mostly. Since all the disappearances, they've been much more active.
They keep spreading false reports of ridiculous sightings---ten dragons
rampaging through the city, you get the picture---and we had to do
something to calm everyone down. The ban seems to satisfy them for
now.''

Trade Minister Kandir is slumped on the chaise, looking bored out of his
mind. He drums his fingers on his knee.

``Are you done---'' he starts, but the Savage interrupts.

``Slee,'' he says. ``I really do need to speak to you alone.''

``No,'' says Galadriel. ``No more of that from you. You cannot hold out
on us now. We've proven ourselves to be working toward the same goal as
you.''

``Sir,'' says the Savage.

``You still have gaps in your memory!'' cries Galadriel. ``And you still
look old, for reasons you can't explain---''

``Old?'' says the king.

The adventurers all exchange confused looks.

``Unless\ldots{} your youth was the disguise,'' murmurs Hanamir.

The Savage is apoplectic.

``Very well,'' he spits. ``Slee, I request command of a portion of your
troops. We need to drive out the orcs. All of them, across the entire
continent.''

The king looks at him in silence.

``This is the way for me to uphold my oath. They need to be gone.
Whatever this rift is between factions of orcs---the Shargaasians and
the Gruumsh loyalists---we can exploit it. I have already killed
Khargol; his men are leaderless. The time is now.''

``Savage,'' says the king, sounding wearier than ever, ``the time cannot
be now. Not in the middle of everything else that's going on. We cannot
raise another army and start a war.'' He takes a moment to think. ``I
will grant you an audience with the council in a few days' time, but
until then, I ask that you stand down. We must table the issue.''

The energy in the room has dwindled, and the king looks finally ready to
resume his prior meeting. The adventurers thank him for his time and are
escorted out by the same group of guards as before. Galadriel makes eye
contact with the one who doubted her.

``Thank you, dear,'' she says, with a benevolent smile. ``Lead the way,
now, if you would.''


\chapter{Are You There, Kord? It's Me, Harlan}
\chapdesc{Sometimes even the toughest heroes need a hand.}

The adventurers make their way back over the bridge to meet up with
\href{/characters/tannin/}{Tannin} and \href{/characters/redyl/}{Redyl}.
The two are sitting on a bench and look to be deep in an animated
conversation.

``\ldots and that's how I learned to ride dolphins into battle. It's all
in the knees!'' Tannin says. He and Redyl both laugh. ``Oh, hi guys.''

``How did your meeting go?'' asks Redyl.

``Great!'' says \href{/characters/hermione/}{Hermione}. She shows off
the library passes and checkpoint passes that King
\href{/characters/slee/}{Slee} signed for them all. ``We can research
how to defeat the Lich in the royal library, and we can pass through the
city without having to pretend to be diplomats.''

\href{/characters/the-savage/}{The Savage} stares off into the distance.

``I'm going to go talk to some people about forming a militia,'' he
says.

``Didn't the king tell you to wait until you could speak to the
council?'' says Hermione.

``Yeah,'' says the Savage. There is a silence.

``So\ldots{} if we need to get in touch with you, how should we do
that?'' asks \href{/characters/harlan/}{Harlan}.

``I don't care,'' says the Savage.

``We can sense your Ring of Been using the ones we have,'' says
\href{/characters/hanamir/}{Hanamir}. ``And then Hermione can Skywrite
to you, if that's necessary.''

``I guess,'' says the Savage. He walks off without saying goodbye.

``Well,'' says Redyl, after a moment, ``I'm afraid I'll be taking my
leave of you all now, too. I have cousins here, in the Gillyheart
neighborhood, whom I'd like to see. I---I can't thank you enough for all
you've done for me.'' He chokes up a little.

``Aw, Redyl,'' says \href{/characters/galadriel/}{Galadriel}. ``Enjoy
your family time! I'm sure we'll meet again. We'll be on the lookout for
Rompit.''

Redyl bows deeply and gives them a tiny wave before disappearing into
the crowded street.

``That guy is cool. I hope he finds his baby,'' says Tannin. Nobody
corrects him. He gives the bundled basilisk a shake. ``Where to now?
Back to the Kiln to sell this?''

``I would like to stop by the Temple of Wind, just to see if there's
anything my fellow \href{/characters/kord/}{Kord} followers can do about
appendage loss,'' says Harlan.

``Plan,'' says Hanamir.

They head back to one of the impressive towers they saw during their
walk to the palace. It looks like a service is just ending; several
worshippers in simple attire are leaving through the front gate. Harlan
makes sure his holy symbol is centered on the chain around his neck and
leads them in. A few people are still milling about, and one of them is
dressed as a cleric. Harlan approaches her and bows while making the
Sign of Lightning.

``Under the Eye of the Storm,'' he says.

``May we behold His Fury,'' she says, bowing back. ``I'm sorry to say
you've just missed today's service, but I am always happy to welcome a
devotee of the Storm. Are you from out of town? I haven't seen you here
before.''

``Yes, my friends and I have just traveled up from Eillin,'' says
Harlan. ``I'm glad to see that reverence for Kord is alive and well in
the city.''

``We are blessed, indeed,'' says the woman. ``Lovely to meet you. I'm
\href{/characters/deru/}{Deru} \href{/characters/nyanceth/}{Nyanceth},
priestess of this temple.''

``Harlan Stormborne. I came to pay my respects and admire this monument
to He Whose Fists Are Thunder, which---by the way---is gorgeous,'' says
Harlan. ``It has clearly flourished under your care. But I also have a
request. Thanks be to Kord, we were recently able to defeat a tremendous
foe, but in that process, I found myself\ldots{} shorthanded.''

He holds up his wrist stump.

``I was wondering if you could put me in touch with someone skilled in
the arts of regeneration, so that I may more effectively enact Kord's
will.''

``Ah, yes, of course,'' says Deru. ``Regeneration is indeed a service we
offer here at the temple. Many of our followers work in the shipyards,
so such injuries are not uncommon. This spell does require one hundred
gold pieces' worth of diamond dust, which we can provide for you if you
do not have it. The casting service itself is five hundred gold. So, all
told, it would cost six hundred gold to regrow your hand.''

``Dang!'' crows Tannin. ``Now we really gotta sell the basilisk, huh?''

``Basilisk?'' says Deru, with some alarm.

``Oh, yeah, uh, `sell the basilisk' is just a\ldots{} Dwarvish turn of
phrase,'' says Harlan. ``He means we need to find a way to make some
gold, that's all.''

``Okay,'' Deru says.

``Anyway, that sounds very reasonable. As soon as I can come up with it,
I'll be back,'' says Harlan. ``In the meantime, would you happen to have
a recommendation for a good place to stay in the city?''

``Sure. In Silver Hill, the Prismatic Inn is the place to go, though
it'll run you five gold a night,'' she says. ``A more affordable but
still pleasant option is the Half-Full Flagon. It's an inn above a
tavern of the same name, down in Southgate.''

``Thank you,'' says Harlan. ``We'll check that out.''

``Be careful, though! Don't take a wrong turn and end up in the Kiln,''
says Deru.

``Oh yes, we'd been meaning to ask about that, too,'' says Harlan.
``We've heard that people have been going missing from that area,
right?''

``Well, from the Kiln, that's nothing new,'' she says. ``But the recent
disappearances have been from all over the city. One of our patrons has
a daughter who went missing just two weeks ago.''

``May I ask---does the daughter have any magical powers?'' asks
Hermione.

``Not that I know of,'' says Deru. ``And her father is a simple
shipbuilder, so there's no chance of a high ransom, or anything like
that.''

``Perhaps we might speak to this patron tomorrow,'' says Hanamir.

``Ern Sailbright is his name, if you'd like to do that,'' says Deru.
``He works down in the shipyards, as I said. You'd find him there.''

``Would you say it's mostly young people who have gone missing?'' asks
Galadriel.

``I think it's primarily people who are vulnerable, and that often
includes the young,'' sighs Deru. ``It's been people who go off on their
own and don't come back.''

``One last question, if you'll indulge us out-of-towners,'' says Harlan.
``We heard a rumor on our way into the city about a demagogue who is
turning people against the gods. He's called the Messenger. Do you know
of him?''

At this, Deru looks yet more dismayed.

``Yes, I have heard whisperings of this Messenger,'' she says. ``We've
seen a slight drop in attendance, too. With all the difficult news
lately, some people feel that the gods have turned against them. My
father is a member of the king's ministry, and I've asked to see if he
can do anything to address this growing sentiment. But, to be blunt,
he's probably the least influential member of the ministry right now.''

``What's his area of expertise?'' asks Galadriel.

``He's the Minister of the Sea. His name is Haelon Nyanceth.''

``So do you think anything will come of it?'' says Galadriel.

``I'm not sure. My dad may not have\ldots{}'' Deru pauses. ``Um, it's
tough to talk about my dad.''

``I'm sorry,'' says Galadriel. ``I understand if you'd rather not.''

``I'm just not sure he's himself anymore. He used to be the Minister of
War, and now he's switched to the Ministry of the Sea, and ever since
then, he hasn't been the same.''

``Pressures of the job, or something else?'' asks Harlan.

``He's getting old. It might just be that,'' says Deru. Her eyes flicker
to the ground and back up, then widen as she notices Galadriel's
gauntlet. ``Hey. What's that there, on your arm?''

``Oh!'' Galadriel holds up her arm. ``This? Just a protective gauntlet I
found during our travels. I'm an archer, you see.''

``Okay,'' says Deru. ``As long as it keeps you safe, I guess.''

``It does! Prevents so many wrist wounds while nocking arrows, you
wouldn't believe it!''

``All right, all right, that's enough now,'' says Harlan. He turns
Galadriel around by the shoulders and starts guiding her toward the
exit. ``Great to meet you, Deru. Thank you for all your help.''

The sun is starting to set as they leave the temple. They decide to
start toward the neighborhood of Southgate to see if the Half-Full
Flagon can accommodate them for the night. It isn't difficult to find:
once they're in the area, they can hear the sounds of music and
carousing from a well-lit establishment right at a central street
corner.

``Five silver a night for a bed,'' the innkeeper informs them when they
arrive.

``Tell you what, I'll part with two and a half,'' says Tannin, ``because
I'm half size.''

The innkeeper laughs.

``A bed is a bed,'' he says. ``If you want to pay less, there are other
places to stay.''

``No, no, he'll pay five,'' says Hermione.

They check into their rooms. Tannin and Hanamir take fifteen minutes to
stuff the basilisk corpse in the magical mini-fridge. Some rope is
required to tie the thing shut, but they succeed. Now sweating from the
effort, they go downstairs to the tavern to join the others.

Unsurprisingly, Galadriel is already lying down on the bar having shots
poured into her mouth by a beleaguered-looking bartender. Harlan and
Hermione are sitting nearby, sipping their drinks and pretending they
don't know her. Hanamir and Tannin pull up chairs to their table.

``I think we should take this opportunity to ask around about the
Messenger,'' says Harlan. ``Hanamir, can you try using Thieves' Cant?
And Tannin, can you use Undercommon?''

Hanamir obliges and disappears into the crowded room. Tannin, on the
other hand, is glancing longingly at the table of other dwarves doing
drinking challenges in the corner.

``Fine,'' he says. He shuffles around the room saying, ``G'day,
mate\ldots{} g'day mate\ldots{}'' but it's clear his heart isn't in it.

Hanamir returns in a short while, shaking his head.

``Not a lot of thieves in this establishment,'' he says. ``At least none
who wanted to speak with me.''

Tannin does not return, and instead can be seen at the table of dwarves
showing off his trident. His voice carries.

``Yeah, axes are cool, but this thing takes people by surprise, you
know? Sure, you can hold it.''

They then observe him making a bet with a drunk dwarf that he can hold
his breath the longest with beer in his mouth. He pockets ten copper
pieces this way as he challenges everyone at the table, winning easily.

Galadriel now stands up on the bar and leads the tavern in an energizing
rendition of a popular drinking song before leaping off and crowd
surfing while still shredding on her lute.

``I hope she's still able to function tomorrow,'' says Harlan. ``I did
see some kind of hangover curing potion in the market earlier, but it
looked expensive. We don't have the money to waste.''

``Speaking of money,'' says Hermione. ``How are we going to raise the
money for your hand? Will the basilisk even cover it?''

``The man from the Kiln offered two-fifty, but I'd still need another
three-fifty on top of that,'' says Harlan, sounding resigned.

``Well, you can have all my silver,'' says Hermione. She pushes him the
small pouch of coins that she found in the cell next to hers in orc
prison. ``It's not much, but\ldots{}''

``Aw,'' Harlan smiles. ``Thank you. I appreciate it.''

Hanamir goes up to the bar and returns with a massive sandwich.

``Just a nightcap,'' he says. ``That was the last thing I wanted to buy,
at least for now. I have four hundred gold, Harlan, and you can have
it.''

``What?! Are you serious?''

``Of course, man.'' Hanamir smiles and looks down at the table, as if
he'll be embarrassed if Harlan makes a big deal out of it.

``I don't know what to say. Thank you so much, Hanamir. I'll find a way
to pay you back---installments, or---''

``Sure, sure,'' Hanamir waves a hand. ``We need two-handed Harlan back
if we're going to defeat the Lich.'' He takes a bite out of his sandwich
and chews it thoughtfully. ``Smoked auroch, apparently. It's good, but
nothing compares to that mystery meat from the Lolth tower.''

The tavern slowly empties out as the night lengthens. The adventurers
are some of the last to retire, in part because Galadriel insists on
improvising a sonnet for the bartender for facilitating her excellent
evening. But eventually, they all make it upstairs to their rooms and
pass a restful night without incident or interruption.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

The morning is not kind to Galadriel.

``Come on, time to get up,'' says Harlan. ``Have some water.''

``Nooooooooooo,'' she groans, but gulps down the proffered water before
burrowing back into her pillows.

After a considerable amount of wheedling, Galadriel is persuaded to face
the day, but she looks as if she's been hit by a battering ram.

``All right,'' says Hermione. ``Who wants to come to the library with
me? We'll figure out what the basilisk corpse could be used for, and if
it'd be more valuable to sell it as-is or in pieces\ldots{} and then,
I'd like to do some reading about tieflings before our meeting with
\href{/characters/magick/}{Magick}.''

Hanamir raises his hand. Galadriel grunts.

``Great. I'm going to go to the market to see if I can find a good deal
on that diamond dust, and maybe save some gold that way,'' says Harlan.

``I'll go with you,'' says Tannin eagerly, seeming to jump at any
alternative to library time.

``Meet back up at the library steps in two hours?'' says Hermione.

Harlan nods, and the two groups part ways.

At the royal library, the librarian accepts their passes from King Slee
with some surprise.

``Three new scholars in a day! Most unusual,'' says the librarian,
ushering them inside. ``How can I help?''

Hanamir and Hermione seem to have departed the mortal plane, struck dumb
by the sight of the library. Spiral staircases and arched bridges
connect the many levels of bookshelves that look down on the wide floor.

``My friend here is a renowned scholar of magical creatures,'' says
Galadriel, indicating Hermione. ``She's writing a book about basilisks,
and we were hoping that a city with a library of this caliber might have
some research materials for her work.''

``Of course. One moment please; I'll fetch you some selections on
basilisks,'' says the librarian. He bounds up one of the spiral
staircases with the confidence of a goat scaling a salt cliff. The
adventurers sit down at one of the long wooden tables on the ground
floor. The librarian returns moments later with \emph{Staring at
Basilisks: An Eyeless Man's Perspective} and \emph{Stone Cold, Hot
Commodity: The Untold Story of the Underground Basilisk Trade}.

``These should be a great start, but let me know if you need more
material,'' says the librarian.

``Thank you,'' says Hermione. She wastes no time cracking open
\emph{Stone Cold, Hot Commodity}. ``All right, it says here that the
most valuable part of a basilisk is this gland that produces the
material that petrifies things. Also the eyes, but more as
trophies\ldots. The gland can be processed in a number of ways to create
petrification potions or antivenoms to protect against petrification, or
to cure petrification after the fact. It is most commonly consumed as a
potion.''

``So would it be more valuable to just sell the whole thing, or to try
and make a potion out of that gland and sell it?'' asks Galadriel.

``I'm not sure\ldots{} that Kiln guy did say he'd pay more for any
future basilisks we might find, but I don't know how likely it is that
we'll come across another one,'' says Hermione.

Hanamir has been perusing \emph{Staring at Basilisks} during this time,
and speaks up.

``It says here that basilisks are most commonly found in the far western
woods. It's actually quite unusual that we ran into one where we did,''
he says.

``Their eggs are also valuable,'' says Hermione. ``Apparently, some
people try to raise them from birth, and train them not to look at you.
Huh! And\ldots{} they eat stone. So when they petrify things, they
usually eat them afterward, and that gland helps them digest it.''

``Any detail on how exactly the gland can be turned into an antivenom,
or\ldots?'' says Galadriel.

``Not so far,'' says Hermione.

``My gut tells me we're better off selling the whole thing than
attempting advanced potion-making without guidance,'' says Hanamir.

While they continue to read, Galadriel tiptoes over to the librarian.

``Do you have any books on dragons?'' she whispers.

``Many,'' says the librarian. ``Chromatic, metallic, what kind are you
interested in?''

``Um,'' says Galadriel. ``Are the metallic ones\ldots{} shiny? Like
metal?''

``Uh, yeah,'' says the librarian.

``Then\ldots{} those,'' she says. ``Please. Thanks!''

The librarian returns with a tome entitled \emph{Bahomet's Children}.
Galadriel tries to bring it back to the table and sit down without
drawing attention to herself, but Hermione looks up at the hefty volume
with curiosity.

``What's that?'' she asks.

``Oh, just, um\ldots{}'' But in a rare moment, Galadriel is at a loss
for words. ``It's about dragons.''

``Huh? Why?''

``Well, we know Magick stole a book about dragons from
\href{/characters/bryn/}{Bryn},'' says Galadriel, thinking quickly. ``A
dragon destroyed her home. Maybe I can learn something relevant to that
before our meeting.''

Hanamir raises his eyebrows but continues reading.

``Hmmmm,'' says Hermione. ``Well, I'm going to ask for a book about
tiefling society, so that I'm culturally sensitive when I meet her.''

Galadriel scans through \emph{Bahomet's Children}. The good news, she
learns right away, is that most metallic dragons are good; the evil ones
tend to be chromatic. But what kind of metallic dragon is
\href{/characters/buddy/}{Buddy}? He seemed to glow with a warm,
yellowish light, but that might have been gold, or bronze, or
copper\ldots{}

She flips to the section about copper dragons.

\emph{They enjoy constructing cave lairs with mazes designed to cause
confusion\ldots{} fond of puzzles, jokes, and elaborate pranks\ldots{}}

\emph{Welp}, she thinks. \emph{That is definitely Buddy. Case closed.}

She reads on.

\emph{Razor-sharp talons and teeth\ldots{} gargantuan wingspan\ldots{}
cone of poisonous gas\ldots{} breath of acid\ldots{}}

Her stomach does a swan dive to the floor. Is it possible that Buddy
could have been the one to destroy Magick's home and kill all her
people?

Yes, certainly, that is possible.

She shuts the book.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

Harlan and Tannin wander the bustling market near the royal library.

``All right, we're looking for a jeweler who might have some diamond
dust,'' says Harlan. ``And, hopefully, someone who's willing to cut me a
deal due to my unfortunate circumstances.''

Tannin stops in his tracks to ogle a knife seller's booth.

``Look at these,'' he murmurs, gazing at his reflection in a fanned
display of wicked-looking blades.

``Five hundred gold for the set,'' says the seller. ``A rare bargain for
this level of quality.''

``Oooooh,'' says Tannin. ``Should I?''

``What? You can't afford that,'' says Harlan.

``Ha. Don't be so sure.'' Tannin tosses him his pouch of gold. ``Count
it!''

``Uh,'' says Harlan. ``There are\ldots{} maybe thirty gold pieces in
here, Tannin.''

``Oh,'' says Tannin. He shrugs. ``Well, you can have it, then. For the
diamonds.''

They walk on until they come across a jeweler's tent with many rows of
glittering gems. Harlan addresses the posh, bespectacled man behind the
counter.

``Do you sell diamond dust?'' he asks.

``We sell diamonds,'' says the jeweler.

``Of course, of course. Hey, just wondering, do you know how large a
diamond I'd need to grind in order to make up a hundred gold pieces'
worth of dust?''

``What? We don't do that here.''

``Right, but what about when you're cutting the diamonds? Do you have
any diamond dust from that?''

``Our diamonds start at four hundred gold apiece,'' says the jeweler,
sliding his glasses up the bridge of his nose. ``You might not be in the
right place, sir.''

``Aha. I see.''

Harlan does an about-face, looking a little flustered, and he and Tannin
continue walking amongst the stalls.

``This is for a spell, right?'' says Tannin. ``Maybe there's a magic
supply store.''

``Yes, it's for a spell!'' sighs Harlan, waving his stump. ``I'm trying
to get my hand back, remember?''

``You could try there,'' Tannin says, pointing at a storefront labeled
\emph{Zoinks! Arcane Goods}. Compared to the rest of the market, it
looks a little shabby.

``Might as well,'' says Harlan.

The two of them enter the shop. It smells of mildew and neglect. A gnome
with an unkempt beard swivels on his stool behind the counter to peer at
them as they walk in.

``Hi there,'' says Harlan. ``Do you, by any chance, happen to sell
diamond dust?''

``I do indeed, sir,'' says the gnome. He hops down from the stool and
disappears into a back room, returning a moment later with a large
canister and a set of scales. ``How much you need?''

``Well,'' says Harlan, ``how much would usually cost a hundred gold
pieces? I'm afraid that's all I have to go on.''

The gnome uses a scoop to transfer some shimmering dust onto one side of
the scales and places a few perfectly rounded pebbles on the other side.

``About this much,'' says the gnome. ``That'll be a hundred gold,
please.''

``Is there any chance you could give me a discount?'' asks Harlan. ``I
lost my hand\ldots{} I'm on a noble mission to save the world,
and\ldots the temple, they said they could heal me\ldots{}'' His voice
falters.

``Now, see here,'' says the gnome. ``If you don't buy this dust, I know
someone at the temple will.''

``That's a good point,'' says Harlan, exhaling loudly, in apparent
defeat.

``So why should I make a deal with you, huh?''

``You know what? Never mind. I'll just go,'' says Harlan. ``Come on,
Tannin.''

As if to teach the gnome some obscure lesson about not granting
discounts arbitrarily to strangers, Tannin punches a display of small
pouches of sand on his way out.

``I guess I'm better off just paying the temple extra for the diamond
dust,'' says Harlan.

``Yeah, probably,'' says Tannin. ``Oh, wait. Would you mind staying out
here for a second? I'm going to go back in. I need to see if he has
something. It's personal.''

``You just punched a display---'' starts Harlan, but the tiny bell on
the door is already announcing Tannin's re-entrance.

``Hey,'' says Tannin to the gnome, who is putting the sand pouch display
back together forcefully.

``What do you want?'' asks the gnome.

Tannin leans against a glass case full of carved wooden statuettes.

``I'm looking for a health potion,'' he says, eyebrows raised, arching
his fingers.

``We got those,'' says the gnome tersely. ``Potion of healing, potion of
greater healing.''

``What's greater healing?''

``Healing, but twice as effective.''

``Okay, how much?''

``A hundred gold for the regular, two hundred for the greater,'' says
the gnome. He dusts himself off and returns to his stool behind the
counter.

``Oh,'' says Tannin. ``I just learned I can't afford that. But\ldots{}
do you have anything that would protect against infernal creatures?
Creatures of demonic origin? From down deep below? And is it cheaper
than the healing potions?''

``Oh yeah, absolutely,'' says the gnome, arching an eyebrow. He looks
suddenly eager to make a deal. ``Protection from infernals, you said? I
could sell you an amulet. You looking for an amulet? Magical amulet?''

At this point, Harlan barges in, and the bell over the door is knocked
off its post and clangs to the floor.

``Sorry, sorry, I believe my companion misspoke,'' he says. ``We were
just looking for a place to find more information about infernal
creatures, not a magical object of any kind. Perhaps a book? A
library?''

``There is a giant library across the street,'' says the gnome, deadpan.

``Ohhhh of course! How silly of us,'' says Harlan. He grabs Tannin's
wrist and drags him toward the door. ``Come on, Tannin, let's go find
that information you wanted.''

Once they're outside, Tannin wriggles free.

``What the hell, man?'' he says, glaring. ``That guy was about to sell
me a magical amulet that I, like, really need!''

``He was trying to entrap you! It's against the law to buy and sell
magical items in the city right now! Come on!''

``Wait, what?'' says Tannin.

``Yes! It's completely illegal. We didn't tell you?''

``No!'' says Tannin.

``Well,'' says Harlan, ``I'm sorry, then.''

``And---and \emph{by the way}, it's not cool that you were listening to
me even after I said it was personal,'' says Tannin, a little red in the
face. ``I'm a very private person! I've said so before!''

``You have,'' says Harlan. ``I'm sorry. I was just trying to look out
for you.'' He takes a deep breath. ``Well, this was a complete bust.
Come on, let's go join up with the others at the library.''

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

When Tannin and Harlan enter the library, they see Hermione, Galadriel,
and Hanamir hunched in a close circle at one of the study tables,
whispering fervently. They fall silent as the other two adventurers
approach.

``Hey guys,'' says Harlan, searching their faces for clues. ``Everything
all right?''

``Uhhhhhhh,'' Hermione starts, with a wide-eyed glance at Galadriel.
``I'll let her tell you. How'd your market trip go?''

``Not great,'' says Harlan heavily. ``Galadriel? What's going on?''

Galadriel bites her lip.

``I couldn't keep it from you all any longer,'' she says. ``I\ldots{} I
told them the truth about Buddy. What he is.''

``And?!'' Harlan exclaims, prompting a loud ``shhhhh!'' from the
librarian in the opposite corner.

``He's a dragon,'' whispers Galadriel. ``A copper dragon, I think.''

``Oh, \emph{Kord}.''

``I hope he'll forgive me for telling you. It was something he revealed
to me in confidence,'' says Galadriel. She looks down at the book in
front of her. ``But if I'm right, and he's a copper dragon, then he's
not a danger to us\ldots{} I mean, I already knew that he wasn't, but if
it makes you feel better, his type of dragon is generally good.''

``Oh, sure, Galadriel, that makes me feel sooOOOooo much better!'' says
Harlan. The librarian shushes him again. ``How are you so sure we
haven't been wandering around with a mature chromatic dragon? He saw us
kill the Wyrmling! Is he okay with that? He could be biding his time,
waiting for the perfect moment to roast us in vengeance---''

``No, no, I saw him. He's definitely metallic, not chromatic,'' says
Galadriel. ``I'm just worried that he may have been, um, the dragon who
destroyed Magick's village.''

``You saw him? How big was he?'' asks Hanamir.

``Big. He said he's around six hundred years old,'' says Galadriel.

``What?!'' Harlan yelps, and the librarian comes over to the table.

``Sir, I am going to have to ask you to leave,'' says the librarian.
``This is a place for quiet study.''

``Oh, we're on our way out,'' says Harlan. ``Don't worry.''

``But hey, Galadriel, copper dragons don't do fire, right?'' says
Hermione. ``The dragon who did all the tiefling murders---that was a
fire-breathing dragon, if we're to go by the evidence of the burning
forest.''

``I wish I could be sure,'' says Galadriel.

``No, that's a valid point,'' says Hanamir. ``Copper dragons have acid
breath.''

``He might be gold!'' says Galadriel. ``I don't know, I only saw him for
a second\ldots{}''

``Nah, I'm not worried,'' says Hanamir. He reluctantly stacks the books
on the table and gives the librarian a nod. ``Thank you, friend. We're
sorry for the noise.''

``Hmph,'' says the librarian. He takes the pile of books and stalks off
to re-shelve them.

Outside, the sun is almost directly overhead. The sound of bells can be
heard in the distance.

``Harlan, I think it's time,'' says Hanamir cheerfully. ``Shall we go to
the Kord temple and grow you a new hand?''

``Yes, please,'' says Harlan. ``I need \emph{something} to go right
today, Kord willing.''

At the Temple of Wind, they find Deru Nyanceth tending to a flourishing
rose garden in the inner courtyard.

``Under the Eye of the Storm!'' she calls to them with a wave.

``May we behold His Fury,'' says Harlan. The other adventurers see his
worried face relax into a smile.

``Are you here to regenerate your hand?'' asks Deru. She puts down her
garden shears and wipes her brow.

``I am,'' says Harlan. With a grateful look at Hanamir, he brings the
requisite gold to Deru and hands it to her.

``How very exciting,'' says Deru. ``We are happy to serve you, Harlan
Stormborne, and to heal you by the power of Kord. Please come with me to
the temple.''

She leads them into the nave and instructs Hermione, Tannin, Galadriel,
and Hanamir to find a seat. She gestures for Harlan to follow her to the
altar.

``This ritual will take about an hour to complete,'' she says. ``I will
have one of my monks fetch me the diamond dust, unless you brought some
of your own.''

``I didn't,'' says Harlan. Deru nods at a monk behind the altar, who
disappears to a store room.

``Very well. And, to confirm, you would like your new hand to grow out
of your left wrist here?'' asks Deru.

``Uh,'' says Harlan. ``Yes please.''

``Just checking,'' she smiles. ``We like to account for all kinds.
Sometimes we get folks with unfamiliar anatomy here, and it never hurts
to ask.''

``That's very considerate,'' says Harlan.

The monk returns with a small bowl of glittering powder.

``Are you ready?'' asks Deru.

``Yes,'' says Harlan.

``Good,'' says Deru.

She reaches into the bowl of diamond dust and throws a handful onto the
altar. A blast of thunder rips through the temple, shaking its
foundations and causing the many wind chimes that hang from the ceiling
to erupt with eerie, reverberating noise. Deru begins to chant:

\emph{Lord of Thunder, God of Storms,}

\emph{King of Tempests in all forms,}

\emph{We call thee now, we seek thy aid,}

\emph{To make whole that which was unmade!}

\emph{Blizzard frozen, Cyclone screaming,}

\emph{Whirlwind, Cloudburst, Downpour streaming,}

\emph{Hear our cry, our sole demand:}

\emph{Restore to Harlan his left hand!}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

An hour later, the adventurers stand at the gate of the temple.

``Now, let's see you wave that hand goodbye!'' Deru laughs, walking them
out.

Harlan stretches his new fingers and gives her an energetic wave.

``It's so \emph{soft},'' he marvels. ``And\ldots{} pink!''

``Yes, that'll fade soon enough,'' says Deru. ``But you'll have to build
up those calluses again from scratch, I'm afraid.''

``My trusty maul will make quick work of that,'' says Harlan. He cannot
stop beaming. ``I have two hands! What a day!''

``Come back again soon, all right?'' says Deru as the adventurers step
back into the city streets. Harlan waves again, just for the novelty of
it.

``Well, I have to say, that was pretty cool,'' says Tannin. ``I have
been to religious services before, and they are not usually that wild.''

As the adventures turn a corner, they hear the sounds of screaming
followed by the roar of an angry mob.

``Aw, man,'' says Harlan. ``And my day was just turning around.''


\chapter{The Tell-Tale Tiefling}
\chapdesc{What's a little murder between friends?}

The adventurers run toward the rising chorus of shrieks and bellows. At
the center of the chaos is a tiefling, who seems to be growing---a pair
of horns now seven feet, eight feet, nine feet in the air, and a pair of
shoulders ripping through a too-small cloak.

Some guards from the nearby bridge checkpoint descend on the scene,
spears pointed at the giant figure. They struggle to manage the crowd of
frightened onlookers. Rocks, fruit, and other small projectiles hurtle
toward the tiefling from all sides.

The adventurers get close enough to catch a glimpse of the tiefling's
face, which is contorted in panic.

``It's \href{/characters/magick/}{Magick},'' says
\href{/characters/harlan/}{Harlan}. ``That's definitely her.''

``She looks afraid,'' says \href{/characters/hermione/}{Hermione}.

``I don't think she planned this,'' says
\href{/characters/hanamir/}{Hanamir}. ``She was trying to stay
incognito.''

They reach the back of the crowd. Harlan casts Thaumaturgy.

``YOU!'' he says, pointing at Magick. The mob ahead of him parts,
physically jumping out of the way of his voice. ``WE HAVE BUSINESS WITH
YOU.''

Magick turns toward Harlan and sees the group of adventurers. A flash of
recognition and relief lights up her face. Harlan and
\href{/characters/tannin/}{Tannin} march up through the divide in the
crowd and make a big show of grabbing hold of her arms. The guards do
not make any moves to intervene.

``THIS TIEFLING IS WANTED FOR QUESTIONING, POTENTIALLY IN CONNECTION
WITH A MURDER,'' announces Harlan, mostly for the benefit of the guards,
who squint at him from a few yards away. Turning off the Thaumaturgy, he
whispers, ``We'd been hoping to cross paths with you, Magick. We're
going to take you someplace where we can speak privately.''

``Oh, good,'' says Magick. ``I wasn't sure how to find you all. I was
trying to cast Skywrite, and then\ldots{}'' She gestures at her
still-expanding frame. Half of a lemon, mostly juiced, hits her in the
eye. ``Ow!''

\href{/characters/galadriel/}{Galadriel} glances at the guards. They
seem willing to cede the problem to Harlan, but the crowd is still
screaming obscenities and hurling objects at Magick. She furtively casts
Warding Wind, and a sudden gale begins whipping around her, with Magick
and the adventurers in the relatively calm center. The wind is loud
enough to drown out the sound of the mob, and it pushes them back far
enough to clear a space to move. She waves the adventurers to follow
her, and they proceed down the street in the direction of an
empty-looking shipyard.

Hermione looks behind them and sees that the group of guards is
following along, but at a distance. She points to a shabby old warehouse
near the docks. They approach it, and it looks as though the guards are
willing to wait outside and let them have a private conversation.

Galadriel's windstorm begins to die down. As if soothed by the slowing
breeze, Magick starts to shrink down to her regular height. They enter
the warehouse through a heavy, creaking door. Its inside is all rusted
metal, an empty cavern of stale and dusty air.

``So, bad news, Magick!'' says Tannin, clapping his hands together,
stirring up a cloud of floating grime. ``That potion you gave us? It
does \emph{not} take you back to your hut in the forest.''

``Oh, interesting,'' says Magick. ``It only ever took me there. I was so
curious how it'd react with individuals of other species. Where'd it
take you?''

``The Elemental Plane of Water,'' says Tannin. He spins his trident like
a deadly baton.

``Neat,'' says Magick. She begins a sort of scattered, dreamy monologue.
``Well, I did have limited resources while I was making those\ldots{}
and I did my best\ldots{} and as you can see, I managed to get back on
my feet after you all freed me from the forest\ldots{} and now things
are going great! I'm glad you all came\ldots{} I was hoping to talk to
you about something very important.''

She looks with uncertainty at Hermione, who is sneezing multiple times
in succession.

``Sorry,'' Hermione says between outbursts. ``Hi Magick. I've heard a
lot about you. I'm Hermione, and I too am a pur-pursuer of---''
\emph{Sneeze.} ``---magical knowledge.''

``Hi,'' says Magick.

``Listen, Magick, as glad as we are to see you, we weren't kidding
around about the whole murder thing,'' says Harlan. ``We need you to
convince us you had nothing to do with the murder of our friend,
\href{/characters/bryn/}{Bryn} Starloft.''

``Oh, I don't know anything about that,'' says Magick, instantly and
obviously uncomfortable. ``I wanted to talk to you about something else.
You all were kind when I met you, and I was hoping I could recruit you
to help me on my quest.'' Her eyes widen, taking on a slightly manic
quality. ``I have a mission now that's so much more important than
anything else. When you all freed me from my misery in those woods, I
found my purpose. And because it was you, there must be some connection
between us. It's---it's \emph{fated} that you help me on my quest. We
were brought together for a reason.''

``Wait, Magick, hold on just a second,'' says Galadriel. ``Before we get
into your quest, can I just ask\ldots{} did you steal a book?''

``A book? Yes. I---I did take a book. I needed it for my quest. It's the
most definitive resource on dragonkind available in the world, so.''

``So you were at Bryn's observatory, and you stole a book for your
quest\ldots{}'' says Galadriel, trying to prompt Magick to finish the
sentence.

``But I didn't kill him,'' says Magick with a strange laugh.

``Did he see you stealing the book?'' prods Hanamir.

Magick doesn't answer. She looks around the room, giggling.

``We like you, Magick. And we were so glad to let you out of the forest
you were trapped in. But you need to be honest with---'' starts Harlan,
but he is interrupted.

``Why was I the only one spared? There had to be a reason. And now I
know it!'' she says.

``And what is that reason?'' asks Hermione.

``To save the world! From everything---everything evil,'' says Magick.
She grins, and the adventurers allow a long moment of silence to pass.

``You know,'' says Galadriel, ``I'm no fan of evil myself. So I get why
you took the book. But when Bryn saw you taking the book, did you
feel\ldots{} panicked at all?''

``He didn't want me to have the book,'' murmurs Magick. She sounds
almost like a child.

``Did he try and stop you?'' says Galadriel.

``He asked me not to take it.'' Magick's voice has dwindled to a
near-whisper.

``And what did you do then?'' says Galadriel.

``I took it.''

``And then?''

``I don't remember.'' Magick is staring intently down at her own feet.

``Huh,'' concludes Galadriel. She purses her lips and gives the rest of
the group a grim look. Harlan takes the opportunity provided by Magick's
distraction to cast Detect Magic on her, hoping to find an arcane
explanation for her unusual behavior.

``Whoa,'' says Harlan. ``I can feel\ldots{} an \emph{overwhelming}
amount of magic flowing through her. But there's no particular spell
being cast\ldots{} no particular school of magic\ldots{} it's just magic
itself, the source of all magic that weaves through all of
creation\ldots{}''

Magick does not react to this statement. She continues looking at the
ground, her lips mouthing inaudible words.

``Hey, out of curiosity,'' says Hermione gently, ``what types of magic
have you been doing lately, if you don't mind my asking?''

``Oh, I'm trying to keep a low profile here, so not\ldots{} not
much\ldots{}'' says Magick.

``You just enlarged yourself in the street,'' Hermione reminds her.

``That was an accident. Sometimes I make mistakes.'' Magick shrugs.

``Wow, you don't say!'' snorts Tannin.

At this point, Hanamir slips away from the group. He doesn't have much
to say to Magick that the others won't cover. He figures it'd be wise to
get a read on their situation, especially as far as the guards outside
are concerned.

Hanamir tiptoes to the door and places an ear to it. He can hear the
guards chatting with one another, but they are far enough away that he
can't understand their conversation. \emph{Good}, he thinks. He uses a
piece of scrap metal to bar the door. He then walks the interior
perimeter of the warehouse and discovers another door on the opposite
side of the building. \emph{Good}, he thinks again.

He returns to the center of the warehouse, where it seems Harlan,
Galadriel, and Hermione are still cajoling Magick to talk about Bryn's
murder. Tannin has become distracted by an oily puddle of water next to
them and is staging battles between iridescent water-dwarves and
water-giants.

``We really do want to hear more about your quest, but we can't until we
figure out what happened to Bryn,'' says Harlan. ``He was our friend.''

``And I'll be real with you, Magick. It sounds like you killed him,''
says Galadriel.

``No! I would never hurt anyone! I've simply been learning\ldots{} just
trying to gather information! I needed that book,'' says Magick. Then
she falls limply into an eerie, full-body shudder.

As she does, a burst of magical energy erupts from her hands. While
Harlan and Galadriel look on in consternation, Tannin transforms into a
hideous ooze, Hanamir a winged demon, and Hermione a large, fiery wolf.

Magick yelps and starts running for the door. Hanamir, in demon form,
chases her down and grabs her by the hem of her cloak, bringing her down
to an undignified face-plant on the floor.

``I'm sorry! I'm sorry for running!'' she cries.

Harlan catches up and attaches the dimensional shackles to Magick's
legs. He then turns to the demon next to him.

``Just checking, you're all still in there, right? And aren't really
terrible monsters?'' he asks.

``Yep, still me,'' says Hanamir from the demon's mouth.

``Me too,'' says the wolf with Hermione's voice.

A small, walking mechanical cube appears in the room. It swivels around
slowly, as if getting its bearings. It is quite cute.

``Tannin, is that you?'' says Harlan.

``Nah, over here,'' comes Tannin's voice from the horrible ooze.

``Magick, did you cause these illusions?'' asks Galadriel. ``What's
going on? And who's the little guy?''

``Look, sometimes accidents happen! I told you!'' says Magick,
struggling with her shackled legs. ``I was trying to get away,
and---and---sometimes things just happen.''

``Now would be the time to tell us why you're infused with so much
magic,'' says Harlan.

``I've been studying!'' Magick flails. ``I've been reading!''

The cube creature approaches Hermione's wolf form.

``Hello,'' she says. She repeats this in multiple languages, just in
case.

``Well, gr-r-r-reetings!'' says the cube. It speaks Common, with a bit
of a robotic clicking in its voice. It swivels again, observing them
all.

``Whatcha doing here, little friend?!'' asks Galadriel, with the
fanatical look on her face that Harlan interprets to mean they will soon
be adopting yet another wayward creature.

``I d-d-d-don't know,'' says the cube. ``I think your friend
accidentally b-b-b-b-brought me here.''

The cube tilts its body toward Magick.

``Don't worry,'' says Galadriel. ``We'll do what we can to get you back
home. Where are you from?''

``I am from the Plane of Mechanus,'' says the cube.

``What's your name?'' asks Hermione.

``I do not have a name. I am just one of the d-d-d-d-duodrones.''

``What's that?'' Hermione tries to reach for her notebook, but realizes
she is still a wolf and cannot write.

``I was once a monodrone. Now I am a duodrone,'' says the cube.

``Oh, congratulations,'' says Hanamir.

``Well, a duodrone had to d-d-d-d-die. There can only ever be the same
number of us. Such is the order of things.''

``Oh, my condolences,'' says Hanamir.

``Yes, yes,'' says the cube.

``How can we help you get back home?'' asks Harlan.

``I will try to cont-t-t-tact Primus,'' says the cube. It starts making
a whirring noise and walking in a perfect square.

``Hey, until you find a way back home, do you want to hang out with
us?'' says Galadriel.

``Not you,'' says the cube. It continues whirring, but sounds
displeased. Galadriel's mouth falls open in shock.

``What about me, big guy?'' says Hanamir.

``You're okay,'' says the cube. It walks in another perfect square and
sits down, an antenna emerging with a click from its top surface.

``Fine,'' says Galadriel, blinking back angry tears. Harlan stifles a
laugh.

``You're crying because this cube we just met doesn't like you?'' he
says.

``I'm not crying!'' She crosses her arms and turns back to Magick. ``So,
tell us about your quest, then.''

``So you'll help me?!'' says Magick.

``Just tell us about it,'' says Galadriel.

``We have to get a weapon. There's this weapon---and I learned about
it---it'll end evil. It can slay anything with a thought. And it can
only be used once, and I know how to use it,'' rambles Magick.

``What's it called?'' asks Harlan.

``Que---quet---quiz---I don't know how to say it,'' says Magick. ``But I
was hoping you all would help me find it. I know it exists. And with it,
I could expel an entire evil population from the planet.''

``What evil population did you have in mind?'' asks Hermione.

``The ones that terrorize us! I will have my vengeance!'' Magick says
with a surge of righteous anger. ``At first, I wanted just to slay
Grizzleby\ldots{} he killed everyone I ever knew\ldots{}''

``Grizzleby, the, uh, \emph{red} dragon?'' interjects Harlan, with a
glance at Galadriel.

``Yes! Of course!'' says Magick, exasperated. ``Keep up! But then I
thought, Grizzleby isn't the cause. He's merely a symptom---of the evil
of all dragons. I must eliminate dragonkind!'' She looks at them all in
turn, heaving big triumphant breaths at having finally reached her
thesis statement. ``And all we need to do is go and get this weapon and
bring it back here.''

Magick digs in her pockets and holds up some hand-scrawled notes and
pages torn from books. One of them contains a map. She points at one
area in particular, an ancient ruin.

``This is the last place the artifact was seen,'' she says. ``And if I
find it, I can rid the world of this evil---and all will be
well\ldots{}''

``That sounds like a noble cause,'' says Galadriel delicately. ``Where
did you find all these papers?''

``I have been searching\ldots{} traveling around. I found some of the
most important books. I can feel them, the books that have the
information I need! It's fate\ldots{} I found the book from your friend
that way, and several others\ldots{}'' she trails off, realizing she's
led the conversation back to the death of Bryn.

``Were any of the owners of the other books unhappy about you taking
their things?'' Hermione says.

``Most weren't home,'' Magick sidesteps.

``Most,'' says Tannin, whose ooze appears to be spreading to nearby
surfaces.

``Listen,'' says Harlan, starting to sound exasperated, ``we would like
nothing more than to help you however we can, but if you lie about
killing our friend---''

Suddenly, a clap of thunder knocks all of them back about ten feet. The
cube creature disappears. Those who had been transformed into monsters
are returned to their original bodies, just in time to bruise themselves
on the warehouse floor.

``Stop!'' cries Galadriel. ``You can't keep doing this and expecting us
to help you!''

``I didn't mean to! I promise!'' says Magick. ``I'm sorry!''

``What were you trying to do that time?'' asks Hermione.

``Nothing!'' says Magick.

Galadriel dusts herself off and walks back to where Magick sits,
shackled and trembling. She casts Suggestion.

``Magick, we are your friends. But we can't help you if you won't be
honest with us. You need to tell us the full truth of what happened with
Bryn,'' she says, in the most feather-soft voice she can summon.

Magick holds her hands over her lips, eyes wide. She looks to be deep in
an internal struggle. She tries stuffing her own fist in her mouth,
without success, before screaming,

``I KILLED HIM! I DID IT! I DIDN'T MEAN TO, BUT I KILLED HIM! \ldots{} I
DON'T KNOW WHY I'M SHOUTING!''

If the guards weren't already curious about the sound of the blast, this
enthusiastic confession is enough to summon them to the warehouse door.
They shove against it and realize it has been barred; then they pound
forcefully on its heavy metal exterior.

``Open up!'' shouts one of the men. ``By order of the Amber Guard!''

The adventurers look at each other, hoping one of them will have a clear
idea on how to proceed.

``Do we entrust her to the justice system of Aberith now?'' whispers
Harlan.

``Maybe we try to take her to \href{/characters/frunk/}{Frunk}
instead?'' says Hanamir.

``She's mentally unstable,'' says Galadriel. ``They'll probably spend
five minutes with her and then execute her.'' She glances around the
warehouse. Nothing but old, unidentifiable debris to work with. ``Damn.
I'll just---we need to buy some more time.'' She tries out a new spell,
this one known in her songbook as Leomund's Tiny Hut.

In an instant, a structure of four walls and a distinctive hat-shaped
rooftop surrounds the party. The walls are translucent from the inside
but opaque from the outside. The entire edifice swirls with all the
colors of the rainbow, shifting and shimmering like light on a beetle's
wing.

``It's even cooler than I thought it would be,'' murmurs Galadriel. She
sniffs the air. ``\href{https://www.youtube.com/watch?v=7HpCJov3Uj0}{And
does it smell like tomatoes to anyone else? And\ldots{} cheese?}''

The adventurers look at each other, nodding.

``I'm going to go hide and back you up if things go south,'' says
Hanamir, darting out of the hut and disappearing somewhere in the
shadows of the warehouse.

``All right, then,'' says Harlan, clearing his throat and nodding to
Galadriel. ``You want to go initiate negotiations with the guards, or
should I?''

``I'll go,'' says Galadriel.

``And I'll jump in with the muscle once you've got them distracted!''
says Tannin.

``I'm hoping that won't be necessary, but I appreciate it,'' says
Galadriel. ``Let's play it by ear.''

She squares her shoulders and walks out of the hut to approach the
barred warehouse door.

``Officers,'' she begins, ``we know you heard some alarming things just
now. We have secured a confession from the tiefling to the murder of
Bryn Starloft, a renowned scholar and friend of King
\href{/characters/slee/}{Slee}.''

``We know who Starloft was,'' says the voice of a guard. ``We're here to
take the tiefling.''

``You should know that she's suffering from severe magical instability
right now,'' says Galadriel. ``If I open this door, I need your word
that she'll be placed in the care of a skilled magician rather than
summarily executed. At least not until her condition is examined by an
expert and she's had a fair trial.''

``Uh,'' says a different guard. ``Okay. Open the door.''

Galadriel removes the bar from the door and opens it a crack.

``So I have your word, then, that---''

The guards in their amber robes shove the door all the way open and
barge into the warehouse, nearly flattening Galadriel. They stare at the
rainbow-colored, pizza-smelling hut.

``What in the Nine Hells?'' says the tallest guard. ``Is the tiefling in
there? And the rest of your friends from the street?''

``Yes,'' says Galadriel. ``It's a small magical force field---a tiny
hut, if you will---and if those inside it choose to leave, they may do
so. But you will be unable to enter.''

``End it,'' says the shortest guard. ``End the spell now, or you will be
considered an accessory.''

Galadriel stares him down, arms crossed.

``I will not end it unless you promise she'll get help,'' she says.

``That's enough out of you,'' says the middlest guard. He casts Hold
Person on Galadriel, and she freezes in her defiant pose. Her eyes blink
rapidly. If the guard were paying attention, he'd see that she was
calling him many unkind names in Morse code.

``Now's my moment! AAAAAAAAAAAAAAGHHH!'' Tannin barrels out of the tiny
hut. He lands a spectacular headbutt right to the middlest guard's gut,
knocking him to the floor.

The shortest guard casts Hold Person on Tannin, who is suspended in a
triumphant post-headbutt stance.

``All right, anyone else in the hut, time to go,'' says the tallest
guard.

Hermione and Harlan exit the tiny hut with their hands up.

``Where is the tiefling?'' asks the middlest guard. He has mostly
recovered from the indignity of Tannin's headbutt, but still looks a
little pink behind the ears.

``Still inside. We shackled her ankles, as a precaution, so she has a
hard time walking,'' explains Harlan.

``I said everyone out,'' says the tallest guard. ``Go back and bring the
creature out now. Carry it if you must.''

``Look,'' says Hermione, ``we are on your side. We don't want this to
end in bloodshed. Can we just talk to the king before you do anything?''

``No,'' says the shortest guard. ``This is a matter for the Amber Guard
to handle according to our protocols. There will be no special treatment
for you or for this tiefling.''

``But we've been entrusted by the Mayor of Eillin, and by King Slee
himself, to bring their friend's killer to justice,'' says Hermione.
``We must be part of that process. You can't take her without us.''

``We can and we will,'' says the tallest guard. ``You---the
human---what's your name?''

``Harlan Stormborne, sir, Cleric of K---''

``Great. Go back in the hut and bring out the tiefling.''

Harlan sighs. Without addressing anyone in particular, he announces, ``I
think we need to comply. We can't fight this with two of us frozen.''

Galadriel blinks something furiously.

Harlan disappears into the hut for a minute or two, then re-emerges with
Magick. He has removed the shackles from her ankles and attached one of
them to his own newly-intact left wrist and the other to Magick's right
wrist.

``All right, here she is,'' he says. ``But these are dimensional
shackles. You won't be able to remove me from her. So whatever you do to
her, you do to me too.''

``This is ridiculous,'' mutters the shortest guard. ``Why do you even
care? She just confessed to killing someone!''

``But you don't know all the information!'' says Hermione. ``You are
missing some key details about this situation and you don't seem to want
to listen!''

``We'll figure out all the details when we take her in,'' says the
middlest guard.

``But---'' starts Hermione.

``Are you trying to say you have relevant information to this murder
case? That makes you a witness, honey.''

``I didn't witness it! We just have \emph{important contextual
information} about this person that you \emph{must} take into account
before you---''

``Enough. Enough. You're all coming in,'' says the tallest guard. He
conjures some thick, ropelike vines from the floor and binds Hermione's
hands.

``Explain yourselves! This is unacceptable!'' Hermione squawks. ``Let me
speak to your boss \emph{right now}!''

``You'll get your chance,'' says the shortest guard. ``Don't worry.''

Tannin and Galadriel are unfrozen and immediately shackled together.
Harlan and Magick follow them. Hermione refuses to stop kicking, and
thus ends up with both arms and legs shackled, hoisted over the tallest
guard's shoulder. To the outside observer, their procession toward the
Barracks looks like the punchline to some kind of complicated joke.

Meanwhile, Hanamir hangs back. When the guards are at least thirty feet
away, he slips out of the warehouse and follows along.

``Hey,'' Harlan whispers to Magick as they trudge side by side. ``Don't
panic. We'll get through this together.''

Magick glances down at him, looking very much like a frightened child.

``Please don't leave me,'' she says.

At the Barracks, the guards lead them to a row of jail cells. Hermione
flails with a renewed vigor at the prospect of her reimprisonment.

``We're on the same side!'' she cries. ``I don't understand why you're
putting me in here!''

``Because right now you're under arrest,'' says the middlest guard.

``No I'm not!'' says Hermione.

``I'm afraid that's not up to you, ma'am,'' says the tallest guard.

``One cell per person,'' barks the shortest guard in the direction of
Harlan and Magick. ``You can stay together for a minute or two, but
you'll have to separate once we get the containment chamber set up for
her.''

``You can't put me in containment with her?'' says Harlan. ``Her mental
state right now is very fragile. I think having a friend nearby might
help keep her stable.''

``Look, man. You've been the easiest to deal with,'' says the tallest
guard, ``though that's not saying much. But believe me, you don't want
to be put where she's going.''

``Can I at least keep watch over her?'' he asks.

``Fine, I suppose. For now. Unshackle yourself.''

Harlan complies. The guards escort him and Magick to an interrogation
room and call in someone who looks like the boss---a man wearing flowing
amber robes with a few important-looking pins by his shoulder. He begins
conjuring a colorful orb that expands to surround Magick, layering it
with coats of radiant energy until she is seven layers deep in a magical
containment bubble like a gobstopper. It would be beautiful, Harlan
thinks, if it weren't for the expression of terror on Magick's face.

The Amber Guard boss does not speak to Harlan, but sits down across from
him. After a few minutes, the lesser guards bring in another person of
seemingly high rank. She is a short, stout woman in dark military garb.

``I am General \href{/characters/pouru/}{Pouru},'' she states,
addressing Harlan. ``I am Aberith's Minister of War. I understand you
have information regarding the disappearances that have been plaguing
the city.''

``Oh, actually, no,'' says Harlan. He is more nervous in front of these
officials than he thought he would be. ``Um, this is about a murder---a
scholar named Bryn Starloft was killed in Eillin not long ago, and this
tiefling here, by the name of Magick, has confessed that she is
responsible. But I don't have any information on the disappearances.''

``We believe the information you have will help resolve both issues,''
says the general.

``I would caution against jumping to conclusions,'' Harlan says. ``I
know of no reason to believe she's involved in the disappearances. And,
as far as the murder is concerned, my companions and I believe that she
is not in control of her faculties right now. She might not understand
what she has done. You, sir---'' Harlan nods at the Amber Guard boss who
conjured the containment bubble. ``---I'm sure you can sense the
overwhelming amount of magic that is coursing through her right now.''

``We appreciate your input, but a threat to the city is a threat to the
city, and we will deal with it how we see fit,'' says General Pouru.

The Amber Guard boss remains silent, but looks at the general and nods
his head in the direction of the hallway.

``Excuse us for a moment,'' says General Pouru. She and the Amber Guard
boss leave the interrogation room and shut the door. Harlan can hear the
faint, muffled back-and-forth of an argument, but can't make out any
words. It sounds heated.

After awhile, the general returns, but the Amber Guard boss does not.

``So. Describe to me what you've seen this tiefling do, in terms of the
uncontrolled magic you mentioned,'' she says.

Harlan recounts the unintended growth spurt, the monstrous
transfigurations, the summoning of a duodrone from the Plane of
Mechanus, and the blast of thunder.

``And that's all just stuff that happened \emph{today},'' he says.

``I see,'' says General Pouru. ``And nothing about that behavior
suggests to you that this creature could have, intentionally or not,
caused the disappearances?''

``I suppose it's possible,'' says Harlan. ``But I would just ask that
you not rush to judgment, and take the appropriate steps to ensure that
justice---''

``There's a reason why we're not doing this through the regular
channels,'' says the general.

``There is?''

``I am the Minister of War. We're at war. My job is to win the war,''
she says.

``Pardon my ignorance, but with whom is Aberith at war?'' asks Harlan.

The general sidesteps the question.

``Whoever is causing citizens to disappear is an enemy of Aberith. We
will keep you and your friends here until we decide what to do,'' she
says.

``How long?''

``As long as it takes,'' says the general. ``You will join your friends
in the cellblock. The tiefling will be held separately.''

``Are you absolutely certain that I can't accompany her?'' pleads
Harlan. He glances at Magick, who looks shrunken into herself. She has
her arms wrapped around her legs and rocks back and forth at the bottom
of the multilayered bubble. ``She's in a very vulnerable place, and I
just---''

``No,'' says the general.

She opens the door for an amber-robed mage, who dispels the bubble. At
that moment, both the general and the mage find that their feet are
stuck to the floor, as if their legs are pillars of stone.

``Hey!'' shouts the general. She struggles to move. ``Amber Guard!''

A dozen more robed guards flock to the interrogation room. One of them
pulls Harlan from his seat and escorts him back to the cellblock, where
Tannin, Galadriel, and Hermione sit dejectedly in their cells.

``How'd it go?'' asks Tannin.

Angry voices leak from the direction of the interrogation room. More
guards rush to help unstick the general. Harlan's guard shoves him into
a cell and locks the door.

``Not great, Tannin,'' says Harlan. ``Not great.''


\chapter{Amber Is the Color of Your Enemy}
\chapdesc{A jailbreak, a scuffle, and two appeals to authority.}

\href{/characters/hanamir/}{Hanamir} has always been quiet, and that
fact never fails to surprise people. At first glance, all anyone sees is
``half-orc''---and the reality of mixed orc parentage is typically met
with either disgust or pity. Regardless, before he says a word, he's
assumed to be violent. Troubled. Aggressive.

He learned long ago that the best defense against this assumption is to
be the very quietest one; he must carry himself with the lightest step
and the gentlest demeanor. It helps set people at ease. Even the
students and faculty at Drephis State, who are proud of their
worldliness, need to be reassured that the half-orc librarian won't rip
their throats out if they return a book past its due date. And
sometimes, Hanamir thinks, it's easiest if they just don't notice he's
there at all.

In the past, he would make a game of re-shelving books without drawing
the attention of a nearby student. How close could he get? How silently
could he wedge an eight-pound copy of \emph{The Encyclopedia of Medical
Magic, 5th Edition} between two other books? Could a broad, tall,
prominently-fanged individual such as Hanamir stand in such stillness
that he could blend into a wall?

And ever since he began adventuring with this crew, that practice has
served him well.

Today, Hanamir walks unnoticed into a heavily-armed compound patrolled
day and night by trained guards, and it's as easy as breathing. He
sneaks past the cellblock where his friends are locked up, and none of
them see him. \emph{Good}, he thinks. He passes the store room, where he
spots \href{/characters/harlan/}{Harlan}'s maul and
\href{/characters/tannin/}{Tannin}'s trident, among other weapons, piled
in a corner. There are racks of uniforms hanging on the back wall.
\emph{Good}, he thinks.

Down another corridor, he hears voices. They're discussing politics.

``All I'm saying is that it's a shame about
\href{/characters/nyanceth/}{Nyanceth}. He served the city admirably,
and it stings to see him pushed aside.'' There are murmurs of agreement
and scoffs of disdain. ``Aberith's military was his life's work. He'll
always be one of us. And I just don't feel that way about
\href{/characters/pouru/}{Pouru} yet.''

``Hey, speaking of Pouru,'' says another voice. ``I just got orders that
we're supposed to transfer the prisoners to a ship.''

``What?''

``Yeah, see for yourself. Supposed to bring them to the docks
immediately.''

``Wait, but\ldots{} we've never---''

``I'm not gonna be the one to say no to the general,'' says the voice
who received the order. ``If that's what you want to do, be my guest.''

Hanamir tiptoes away, silent as a cloud. Prisoners transferred to a
ship? \emph{Not good at all}, he thinks. There's nothing for it: it's
time for him to spring them out of jail. He slips back to the store room
and snags four uniforms in measurements he hopes will be roughly
appropriate for his variously-sized friends. They're the plain variety,
not the amber robes of the special force that appears to handle
magic-related issues. But he'll take what he can get.

He materializes at the cellblock, and holds a finger to his lips before
Tannin can voice his excitement to see him. He begins picking the locks,
making quick work of them all. He tosses a uniform to each of them.
\href{/characters/galadriel/}{Galadriel}, Tannin,
\href{/characters/hermione/}{Hermione}, and Harlan quickly don the robes
and exit their cells, mimicking Hanamir's stealth as closely as they
can.

Once they are out of the cellblock, they creep down the hallway to the
room where the guards are still discussing the order to move the
prisoners.

``I have an idea,'' Galadriel whispers.

The other adventurers watch as she casts a spell on herself. It's
another new one, and it's immediately clear to them that it was not
quite successful. She does shrink down several inches and bulk up
considerably, but the edges of her resulting form look slightly blurred.
Her guard's robes morph into a discount Halloween facsimile of an
Aberith general's uniform. Her hair fades to iron gray and ties itself
up into a tight bun---but whenever she moves, they can see a flicker of
her actual face behind the uncanny mask-like one she has conjured.

Nevertheless, she marches into the room where the guards are
congregated.

``Change of plans,'' she says gruffly. ``I need you to release the
tiefling immediately.''

A few of the guards jump at the sight of her.

``General\ldots{} Pouru?'' one of them asks, squinting.

``Yes,'' says Galadriel. ``It's me, the general.'' She clears her throat
in a way she hopes sounds authoritative. ``There's no time to explain.
We're letting the tiefling go.''

One guard gets up close to her and peers directly into her eyes.

``How'd this prisoner get out of her cell?'' he asks. He grabs her by
the wrist.

``How dare you!'' Galadriel wriggles but can't pull away. ``I am the
general! Unhand me!''

The guard seizes her other wrist and swiftly pulls both arms behind her
back.

``Enough,'' he says. ``We know you're the half-elf prisoner. But if you
don't like the cellblock, we can always take you to solitary.''

He leads her out of the room and back into the corridor, which he now
finds filled with a heavy black smoke.

``Whoa!''

Hanamir's fist appears out of the haze and connects with the guard's
jaw. The guard momentarily loses his grip on Galadriel. She takes her
chance to flee into the dark hallway.

Another guard pops out into the hallway to back up his friend and is
immediately hit in the face with a splash of water from Tannin's flask.
As he sputters and spits, Tannin freezes the water on his face. His
eyelids are frozen shut and his nose and mouth are covered in icicles.

``It's \emph{ice} to meet you!'' says Tannin. He chuckles at his own pun
while the ice-faced guard punches himself in the mouth to break a hole
in the ice that is large enough to breathe through.

Hermione doesn't wait for another guard to leave the room. She shoots
Magic Missiles directly inside, not entirely able to aim at anyone in
particular through the smoke. She hears the sound of at least one
missile hitting someone. And then another guard---maybe the one who had
originally detained Galadriel, but maybe someone entirely new---gets a
punch in the gut from Harlan.

``All right!'' one of them bellows. ``Look, we're just the night shift.
This isn't worth it. Just\ldots{} go.''

Hanamir re-corks his smoke bottle and the black fog begins to dissipate.

``Where were you ordered to take the prisoners?'' he asks. ``On what
ship?''

``I don't even know. Just take the order.'' The guard hands him a piece
of parchment with the general's seal and signature.

The adventurers waste no time running back toward the store room. They
grab their weapons from the pile in the corner.

``Is that really all they've confiscated?'' wonders Harlan. ``I'd expect
more than just our things and that bag in the middle of the floor.''

``That's not just a bag!'' says Hermione, kneeling down beside it. ``I
think this is a Bag of Holding!''

``Wow,'' says Tannin. ``I've always wanted one of these. Bag of Holding,
I request all the gold you have inside!''

From the opening of the bag, five gold pieces spring out like jumping
beans. Tannin dives down to the floor for each of them.

``Awesome,'' he concludes.

Galadriel slings the Bag of Holding over one shoulder and looks
anxiously back at the corridor.

``We should go. We can check out what else is in here later.''

Hanamir casts Pass Without Trace on the party, and suddenly, they all
feel much quieter and quicker than usual. When they have escaped the
Barracks and walked far enough that they feel safe speaking, they
huddle.

``We should go talk to \href{/characters/slee/}{Slee}, right?'' whispers
Galadriel. ``He needs to know about this secret order to ship us off.''

``I don't know how all five of us are going to make it to the king's
chambers at this time of night,'' says Harlan. ``Maybe we should split
up.''

``I'll go with Galadriel to see the king,'' says Hanamir. ``Where will
you go?''

Harlan turns to Hermione and Tannin.

``Maybe to the Minister of the Sea---remember, he's the father of the
priestess who gave me my hand back. That's a connection I can use to get
us access,'' says Harlan.

``What was their name again? Niacin?'' asks Hermione.

``Nyanceth,'' says Hanamir. ``And that reminds me. I heard some guards
talking about him earlier. They were saying he'd been pushed aside from
his post as Minister of War, and one of them wasn't happy about it.''

``\href{/characters/deru/}{Deru} did say her father wasn't what he used
to be,'' recalls Harlan. ``Just old age, or something more sinister, I
wonder?''

``Time to find out,'' Tannin says. ``Meet back at the library tomorrow
morning?''

``Plan,'' says Hanamir.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

Halon Nyanceth lives in a stately house not far from his daughter's
temple. A garden, lush but overgrown, leads to a wide, lantern-lit porch
with two uniformed guards on either side of the front door.

``Halt,'' says one of the guards as Harlan, Tannin, and Hermione make
their approach. ``What is your business at the Minister's home at such
an hour?''

``I know this is unorthodox,'' Harlan begins. He adjusts his
\href{/characters/kord/}{Kord} medallion so that the guards can see he's
a respectable man of faith. ``We have just witnessed something truly
disturbing that requires the Minister's immediate attention.''

``Something\ldots{} related to the sea? To Aberith's coast?'' asks the
other guard.

``Not quite, but it involves infighting amongst the council,'' says
Harlan.

``Ha!'' says the first guard. ``The council? Infighting? You bring no
news at all.''

``We wouldn't be here if we had any other options,'' says Harlan in the
most solemn and foreboding tone of voice he has in him.

``If you must,'' says the second guard. He checks a timepiece on his
wrist. ``The Minister is still awake, but not for long.''

Harlan leads Hermione and Tannin into the mansion as the guards hold
open the doors. The interior is elegant, though in need of a thorough
dusting. They see an old man with a tuft of white hair sipping a cup of
tea, sitting in an armchair by the embers of a fire. He wears a fluffy
red bathrobe and a pair of well-worn slippers.

``Oh! Hello,'' he says. He places his teacup down on a saucer and looks
at them searchingly.

``Minister Nyanceth,'' says Harlan, bowing. ``Thank you for seeing us at
such a late hour. Allow us to introduce ourselves---I am Harlan
Stormborne, cleric of Kord. Your daughter Deru healed me of a missing
hand by the grace of the Lord of Storms.''

``Ah, yes! Deru is a good girl,'' says the Minister.

``This is Tannin McBitters, a valorous warrior with a connection to the
sea,'' says Harlan. Tannin takes an elaborate bow and makes the
Minister's tea levitate in a spiral formation before settling back into
the cup, unspilled. He waits for a reaction, but the Minister does not
notice.

``And this is Hermione Daydark, an esteemed scholar of magical
creatures,'' says Harlan. Hermione curtsies. Her nose twitches at the
dust in the air, but she catches herself before she can succumb to the
kind of chain reaction of sneezes she experienced in the warehouse.

``Of course, of course, I remember you, Harlan,'' says Nyanceth. ``How
have things been?''

``Troubling, Minister,'' says Harlan. ``Between the disappearances in
Aberith and our own quest for justice, there is much worry clouding our
minds at this time.''

``Ah, clouds, clouds, yes\ldots{} very cloudy\ldots{} Kord be praised,''
says the Minister. Harlan nods at him, but glances nervously at Hermione
and Tannin.

``Yes, you see, we recently arrived in the city with the goal of
apprehending a suspect in a murder.''

Nyanceth's eyes go wide. His heavily-wrinkled face grows somehow even
craggier.

``The victim was King Slee's friend, and he trusted us with this task,''
Harlan continues.

``King Slee\ldots{} yes, good king\ldots{}'' murmurs Nyanceth.

``We were able to meet with him briefly, but his Minister of Trade
shooed us out the door before long.''

``Oh yes, of course, Ultas is a dear friend,'' says Nyanceth, returning
to a tone of mellow confusion. ``Should I call for him? He helps me
often.''

``No, no, that won't be necessary,'' says Harlan. He assesses the old
man, who looks close to falling asleep in his chair. ``Are you feeling
all right, sir?''

``Nothing to worry about, my boy,'' says Nyanceth. ``I am not the
warrior I once was, but I feel just fine. Now---you mentioned a
murderer?''

``Yes,'' says Harlan. ``Someone murdered a dear friend of ours, and a
friend of the king. His name was \href{/characters/bryn/}{Bryn}
Starloft. We are dedicated to finding out what happened.''

``Bryn\ldots{}'' Nyanceth's eyes glaze over. ``Was he in the Royal
Guard?'' Harlan shakes his head, but Nyanceth is not paying much
attention. ``We ought to take this to Ultas. He'd know what to do.
Unless your friend is in the sea!''

Harlan and Hermione exchange frowns. Tannin has completely zoned out,
staring at the last cracklings of the fireplace.

``Just a little morbid humor, my boy.'' Nyanceth lets out a rattling
chuckle. ``My apologies.''

``Sir,'' Harlan clears his throat and changes the subject. ``Didn't you
once head a different Ministry?''

``Of course, yes, yes, but war is a young man's game,'' says Nyanceth
airily. ``Now that woman, I forget her name sometimes, she's younger
than I was, but she's in charge of it now. And she fights, and I admire
that, even as it frustrates Ultas!'' He laughs that same rattling laugh.
``And of course, he is my friend and I take his side, but I do like her
spirit.''

Hermione gives Harlan a significant look. They both notice it: he's more
lucid when reminded of his old work.

``Unfortunately, sir, we believe she is usurping the authority of the
king,'' says Harlan. ``And this is why we have come seeking your aid.''

``Terrible, terrible,'' says Nyanceth, snapping back to his previous
distance. ``Just what Ultas always rails against\ldots{} the king loses
too much power to the council.''

``Do you truly believe in Minister \href{/characters/kandir/}{Kandir}?
He seemed not to take our concerns seriously when we met him.''

``He is a busy man,'' says Nyanceth. ``When he's not working at his
office, he's working on those books of his, and perhaps he misunderstood
you.'' He scratches his head and yawns. ``He trusts and respects me, and
that's why he's helped me stay on the council this long.'' He yawns
again, even longer this time, looking just about ready to call it a
night. ``Nobody hates Pouru more than he does. And he's right, he must
be right, of course.''

A sharp knock at the door jolts them all out of their reverie. A
messenger of the King's Guard peeks his head inside.

``A message from the king for you, Minister,'' says the messenger. He
holds out a written note, but Nyanceth makes no moves to retrieve it.
Hermione accepts it instead. ``He has summoned the council to the
chambers first thing in the morning. He noted that he'd like you to
bring your guests.'' He glances at the three strangers, bows, and
leaves. The door shuts with a soft click.

``My guests?'' repeats Nyanceth, mystified. ``Oh! It seems our wise and
noble king was already aware you would be here.''

``Our friends may have let him know,'' says Harlan. ``And sir, I hate to
be any further bother, but could we crash here tonight? On a couch,
or---anywhere, really? Our inn is across the city, and we'd hate to be
late to this meeting in the morning.''

``My dear boy, this house is much too large for me now that I'm here all
alone,'' says Nyanceth. He laughs, but the adventurers feel sad. ``There
is plenty of room for all of you. Please make yourselves at home.''

The old man shuffles off to his bedroom, sniffing and sipping his cup of
tea.

The adventurers hear his door close with a decisive thud. Tannin
exhales.

``Wow, I hated that,'' he notes.

Harlan and Hermione tiptoe around the parlor, studying Nyanceth's
possessions. Harlan notices several Kordic artifacts, along with a few
Pelor relics, perhaps gifts from his daughter or other religious figures
around the city. Hermione stares up at an oil painting of a much younger
Nyanceth, sitting alongside a prim and noble woman who must have been
his wife, and an adolescent version of his daughter Deru, the priestess.

``I still can't tell,'' whispers Hermione. ``Do you think he's
ensorcelled, or just old?''

``It's time to check for sure,'' says Harlan. He silently casts Detect
Magic, but the musty old sitting room reveals no enchantments; none are
in the hallway leading to the Minister's room, either.

``Just old, then,'' says Tannin. He beckons them to follow him down the
corridor. He gasps theatrically at each open doorway. ``Guys. These
rooms are cluuuuuuuutch.''

Hermione peeks into a bedroom decked in old-fashioned but undeniably
luxurious furnishings. ``Wow,'' she says. She puts down her bags and
gives the bed a test bounce. Softer than a hay-stuffed pallet in a
tavern, and softer still than a bedroll on rocky ground. She smiles.

``Dibs on this one!'' says Tannin, diving into a four-poster bed in a
room at the end of the hall. It is large enough to accommodate a
bugbear. His satchel lands in the corner of the room and his trident
clatters to the floor. Still swaddled in his guard disguise, he falls
into a swift and fervent sleep.

Harlan opens the door to a room that his heart tells him once belonged
to Deru. The curtains are silver and multilayered, like a sky heavy with
stormclouds. His new left hand brushes against the bedspread, softer
than a snowdrift. Somehow, the texture feels familiar. He falls into an
uneasy sleep.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

Galadriel and Hanamir sneak through patches of darkness on the streets
between the Barracks and the palace. It's much too late for them to try
for an audience with the king the old-fashioned way, so without
discussion, they agree to rely on their combined powers of stealth and
deception.

It is, in fact, criminally easy to get in. Galadriel spider-climbs the
wall outside the palace and lowers a rope for Hanamir to climb. Upon
arriving at the other side, she decides to try out her Disguise Self
spell again to adopt the form of one of the palace servants. She checks
her reflection in a puddle. A convincingly weathered human woman's face
stares back.

``Oi, gov'na!'' she whispers, testing out her voice. ``Blimey, innit?''

``Disappearing now, but following you,'' says Hanamir. Galadriel looks
around, but he has already vanished.

She sees an abandoned bucket with a rag by a drain. Seems like a good
prop. She hoists it in the crook of one arm and knocks authoritatively
on the closest door. A scrawny young man opens it a crack.

``Lemme in, then,'' whispers Galadriel. ``I'm on chamber pot duty
tonight.''

``Doesn't that usually happen in the morning?'' says the boy.

``Course it does!'' says Galadriel. ``But `is `ighness's tummy's not
been feeling so well today, so some extra rounds've been deemed
necessary, if you know what I m---''

``All right, all right,'' he says. He ushers her inside. ``Please do not
tell me any more.''

She tries out a saucy grin on her new face and hoists the bucket so that
it rests on her hip.

``Come on, then, lad! Off with you, and don't tell no one you saw me out
there, neither, or I'll `ave you signed up for `is Majesty's next round
of irritable bowel syndrome!''

The boy grimaces and runs away. Galadriel struts, very satisfied with
herself, down the gilded corridor toward the king's chambers. Upon
hearing the bedpan story, the guards outside his suite let her pass
without challenge.

King Slee sits at his desk, poring over a pile of documents. He startles
at Galadriel's entrance, but his expression softens when she abandons
her disguise. She lowers her head and all but kneels before him.

``Your Highness,'' she says. ``I am terribly sorry to interrupt you in
your private quarters like this. But there is grave news concerning your
Minister of War that you must hear.''

King Slee glances back at the papers on his desk and clucks his tongue.

``What has the general gotten herself into now?'' he sighs.

Galadriel stands and passes him the order to transport the prisoners to
the shipyard.

``We found Bryn's murderer. It was the individual we suspected, a
tiefling named \href{/characters/magick/}{Magick},'' she says. ``We
secured a confession from her, but we were arrested by the Amber Guard
when we tried explaining her circumstances. She's under the influence of
some very powerful magic and is not in her right mind. The general then
separated us from her and gave this order to have us removed.''

She feels as if she has set down a great burden when all of this is
said. King Slee is frozen in shock.

``Bryn's murderer, caught here? And I wasn't informed immediately by the
guard?''

``Indeed, sir. It seemed the general was interested in keeping this
information from you.''

``And this order\ldots{}'' He inspects the parchment Galadriel handed
him. ``To transport you all out of the city before I would learn of
it?!''

She bows her head. The king takes a few moments to collect his thoughts
before continuing.

``The general is headstrong. She is younger than most who have held the
post, and she's had her fair share of scraps. But I've never had reason
to doubt her loyalty,'' he says. ``This is incredibly distressing
news.'' He closes his eyes. ``This tiefling, Bryn's murderer? They still
have her in custody?''

At this moment, Hanamir emerges from a shadow by the door.

``As of an hour ago, yes, sir,'' he says.

Slee jumps in his chair.

``I didn't see you there,'' he says, a bit sharply.

``Sorry about that, sir,'' says Hanamir, smiling slightly. ``Light on my
feet, as you know.''

King Slee shakes it off and clears his throat.

``I wish to see that tiefling brought to justice, and not rushed out of
town. The Minister of Justice should be involved here, although her ways
are a bit soft for my liking.''

``We're glad you agree,'' says Galadriel. ``What can we do to help?''

``I will demand that the tiefling be brought before the full council
tomorrow,'' says Slee. ``And I'll arrange for you to stay in guest
quarters here. First thing tomorrow we'll discuss this with the full
council present. I don't think Pouru is so bold as to move the prisoner
after this order goes out. She may backpedal her attempted treachery,
but we'll ensure she answers for that just the same.''

``Thank you, your highness,'' says Galadriel, bowing again. ``We are so
relieved to hear this, both for Magick's sake and our own.''

``Kandir was right,'' sighs the king, almost inaudibly. ``The bickering
on the council has gone too far.''

``Kandir, sir? That's the Minister of Trade we met, right?''

``Indeed,'' says Slee. ``He has suggested that the reforms that created
the council perhaps went too far to dilute my power. A noble man, Ultas
Kandir, who would give up his own power for the betterment of the
country.''

``He may have a point,'' says Galadriel, with a glance at Hanamir, who
nods, sagely. ``Well, we cannot thank you enough for your intervention
in this matter. We will gladly go now to wherever you'd like us to stay
until we can reconvene on this tomorrow. One last request---could you
make sure that the Minister of the Sea brings our friends with him to
the council meeting? When we parted, they were headed to speak with
him.''

``Yes, all of you who were witnesses to the tiefling's confession would
be welcome. I will send word to Nyanceth to include them.''

The king jots down a note, marking it with his seal. He opens his door
and hands it to the guards outside, and then instructs them to escort
Galadriel and Hanamir to the guest chambers.

The guest chambers at Aberith's royal palace are, it turns out, sick as
hell. In fact, they're more like a separate resort compound within the
palace. There are multiple bedrooms, sitting rooms, dining rooms, and
balconies. As soon as the guards leave, the two adventurers high five
each other (``To diplomacy!'') and gravitate toward the selection of
beautifully-packaged snacks in the main parlor.

``Owlbear jerky, candied giant scorpion bites, and BBQ fire beetles,''
says Hanamir. ``Want any?''

Galadriel grabs a packet of the BBQ fire beetles and starts funnelling
them into her mouth. Hanamir goes to town on some owlbear jerky.

``You know,'' he says between effortful chews, ``my backup plan was to
smash the window, grab you and throw you onto the exterior wall, while I
plummet three stories, relying on Slow Fall to avoid death. But your way
was better.''

``Ha!'' says Galadriel, spewing some BBQ fire beetle onto the carpet.
``Well, I'm not convinced we can trust Pouru to stay on the up-and-up
regarding Magick tonight. If she's gone in the morning, I'll have a hard
time forgiving myself.'' She peers around a corner into what turns out
to be a decked-out spa room. ``But these accommodations are something
special.''

Hanamir smiles, then gnaws off another piece of jerky.

``Well, goodnight,'' he says, and wanders off to seek a meditation spot.
As if out of habit, he disappears.


\chapter{Law and Order: Special Dictums Unit}
\chapdesc{In the High Council of Aberith, betrayals are considered especially heinous.}

\href{/characters/tannin/}{Tannin},
\href{/characters/hermione/}{Hermione}, and
\href{/characters/harlan/}{Harlan} sit in the empty council chamber.
Even whispering, their voices echo off the glossy marble.

``Where'd the guy go?'' asks Tannin. ``The old guy?''

``\href{/characters/nyanceth/}{Nyanceth}?'' says Hermione. ``He went to
see \href{/characters/kandir/}{Kandir}. Said he'd meet us here.''

``Does that strike the rest of you as odd?'' Harlan barely voices the
words. ``He seems to rely on Kandir for, well, everything.''

A goateed man holding a tall silver staff appears in the doorway.

``Guests of the king, you may take your seats,'' he says grandly, and
bows with a flourish. From behind him,
\href{/characters/hanamir/}{Hanamir} and
\href{/characters/galadriel/}{Galadriel} appear, looking well-rested and
eager to catch up. They slide into the row just behind Tannin, Hermione,
and Harlan.

``How did it go with the Minister of the Sea?'' whispers Hanamir.

``Interestingly,'' says Hermione. ``Like \href{/characters/deru/}{Deru}
said, he's very---''

But she is interrupted by another announcement from the man with the
staff.

``The Minister of War, General Nai \href{/characters/pouru/}{Pouru},''
he proclaims. The stern-faced woman enters the chamber without looking
at the adventurers. She sits at the far left side of the raised,
semicircular table at the front of the room.

``The Minister of Trade, Ultas Kandir, and the Minister of the Sea,
Haelon Nyanceth.''

Kandir and Nyanceth walk slowly to their seats together, not stopping
their whispered chat. Kandir has a steadying hand on Nyanceth's stooped
back.

``The Minister of Justice, Kir \href{/characters/mirama/}{Mirama}.''

An elegant woman appears in the doorway and gives a small smile to the
room. Tannin thinks to himself, somewhat awestruck, that her cheekbones
must be sharp enough to pierce heavy plate armor, or at least scale
mail. She carries herself with the confidence unique to individuals of
undeniable beauty.

``All rise for His Majesty King \href{/characters/slee/}{Slee} III of
Aberith!''

The ministers and the adventurers stand up as King Slee enters the
courtroom and takes his seat at the center of the semicircular table.

``Thank you. Please, be seated,'' he says.

The chamber is filled with the reverberating squawks of chairs against
the marble floor as everyone settles again. The tension in the air is
like a lute string stretched too tight.

``We are here today because our city is beset by conflict and
confusion,'' says Slee. ``In our chambers with us we have five guests of
the crown, who were tasked with investigating the murder of a mutual
friend. In pursuing a suspect, they were apprehended. We will hear about
the circumstances of that incident today, and the complications that
ensued. I now invite General Pouru to explain the order she issued to
send these individuals away as prisoners.''

Pouru clears her throat.

``Thank you, Your Majesty,'' she says. Her voice is even and strong.
``Given the disappearances that have been plaguing our city, and the
confession that was overheard by the Amber Guard, it was my
responsibility to detain the suspect. These five individuals attempted
to obstruct the Guard's efforts to bring the suspect in for questioning.
Therefore, we found it necessary to arrest them as well.''

``And what of the order to transfer them to a ship, without notifying
your fellow ministers or your head of state?'' prompts Slee.

``That\ldots{} that was a mistake,'' says Pouru. She seems to lose her
train of thought all of a sudden. ``I don't have a\ldots{} my authority
was\ldots{} it was an error in judgment.''

``This is highly irregular,'' says Mirama, the Minister of Justice. She
gives Pouru a sharp look. ``It is not just a breach of protocol---it's a
betrayal.''

Pouru wrestles with her words.

``I made a mistake,'' she repeats. Her face is slack with confusion.

Overlapping voices from the rest of the council grow louder and louder.
Hanamir stares at General Pouru, whose downcast eyes and knit brow
indicate that her bewilderment is genuine.

``Enough!'' says Slee. ``I invite our guests to provide their
perspective.''

The adventurers share a glance. Galadriel stands.

``I would like to clarify the circumstances of our arrest,'' she begins.
``The general heard reports that we were trying to prevent the Amber
Guard from detaining the suspect. That is not entirely true. We spoke
with the Amber Guard, and we acknowledged that the suspect was certainly
responsible for the murder of \href{/characters/bryn/}{Bryn} Starloft.''

She pauses to look at General Pouru, who is staring intently at her own
clasped hands on the table.

``But we also told them that the suspect is under the influence of a
powerful and unstable magic that has interfered with her state of
mind---to such an extent that we think she is not in control of herself.
She is traumatized. She needs help. We feared she would be summarily
executed without trial, when in fact it would be of greater benefit to
Aberith if we were permitted to investigate the underlying cause of her
condition.''

The councilmembers take a few moments of silence to digest this. King
Slee tilts his head and raises his eyebrows at Galadriel.

``I admit, I'm surprised by this,'' he says. ``She has confessed to
murdering a mutual friend of ours.''

``Sounds open and shut to me,'' says Kandir, leaning toward Slee. ``If
this is a matter of volatile magic, is imprisonment even an option?
We've contained it for now, but how can we let this creature live?''

Galadriel ignores him and continues addressing the king.

``We cared for Bryn,'' she says. ``He was a trusted advisor to us during
our quest to save the Moon, and because of that, he helped save us all.
He was wise, and kind, and he did not deserve to die this way.'' She
gives that statement a moment to linger in the air, out of respect.
``Our position is not that his murder should go unaccounted for. But we
think it would be a miscarriage of justice if a helpless person were
killed for a crime she was not in full control of committing. And we
think it's important to note that our resident wizard here, Hermione
Daydark, believes that if we had access to the suspect alongside an
expert magical practitioner, we could track down the true source of her
enchantment. And that might lead to the person ultimately responsible
for Bryn's death.''

Slee purses his lips. He seems to be considering her words carefully.

``Please explain why you feel that the suspect is not in control of her
actions,'' he says.

Galadriel explains: the ever-burning forest fire, the tiefling
skeletons, the lone hut spared from the flames. The knowledge that
Grizzleby, the red dragon, had killed everyone
\href{/characters/magick/}{Magick} had ever known and loved. The erratic
bursts of magic that resulted whenever they'd tried confronting her
about stealing the dragon book from Bryn, and subsequently killing
him\ldots{}

``The trauma of the loss of her people, combined with whatever magical
force has possessed her now, leads us to believe that she may not be
entirely responsible for what happened to Bryn,'' concludes Galadriel.
``She may be the unwitting tool of some more sinister actor.''

Hermione rises from her chair, looking nervous but determined to speak
up.

``Our other mutual friend, \href{/characters/the-savage/}{the Savage},
was under the control of some dark and powerful magic recently,'' she
says, ``so we know that right-thinking individuals can be swayed to
perform acts of evil, through no fault of their own.''

This results in a surge of murmurs from the council, which echo and
distort themselves until the adventurers can't quite make out any of the
specific words being said. After a short while, Minister Mirama holds up
a hand for silence.

``What became of this captured creature?'' she asks. ``She was arrested,
but then what?''

Galadriel smirks.

``Your Minister of War can answer that,'' she says.

All eyes turn to Pouru.

``The Amber Guard has the tiefling in custody for questioning as we
speak,'' says Pouru.

``But why not question her in front of the council, as is customary?''
says Mirama. ``This suspect has the right to a fair trial like everyone
else in the city.''

Pouru has no response, so Mirama clicks her tongue and turns back to
Galadriel.

``What alternate fate do you see appropriate for the suspect?''

``I would hope, with the council's connections, that we could call in
some type of magical consultant who might recommend a course of
treatment,'' says Galadriel. ``She needs the care of an expert.''

``We'd be happy to do the primary diagnostics,'' says Harlan quickly.
``But yes, our conclusion is that a well-practiced magician would be
most helpful.''

Mirama leans back in her chair, looking contemplative, and far more
amenable to the idea than anyone else at the high table.

``This is ridiculous!'' says Kandir. He throws up his hands
theatrically. ``The appropriate sentence for the killer tiefling can be
negotiated later. The more pertinent issue here is the betrayal of Nai
Pouru against the crown. I demand we address this now!''

Slee looks taken aback.

``You're right,'' he says, with a few quick blinks of his eyes. ``There
has been potential treason without explanation. The hiding of the
arrests, and the order to remove the prisoners without alerting myself
of the rest of the council, is a grave matter indeed.'' He turns to
Pouru. ``Explain yourself, General.''

``They were to be kept safe on the chartered ship,'' says Pouru. ``No
destination, just outside of the city. Given the strong magic at play,
it seemed like the prudent choice for the protection of Aberith.''

``And the lack of appropriate communication was because\ldots?'' says
the king.

``That was an oversight,'' says Pouru, again looking distracted.

Kandir leans over to Nyanceth, who has dozed off in his chair, and
whispers something in the old man's ear. He jolts awake.

``I have evidence of the intended destination of the ship in question!''
Nyanceth sputters. He procures a document from his pocket and holds it
aloft in a shaking, liver-spotted hand. Pouru's face turns pale. ``The
prisoners\ldots{} were to be transported to the Northern Ruins!''

Nyanceth hands the piece of parchment over to Kandir, who passes it to
the king. The chamber is silent.

``And what else?'' Kandir gives Nyanceth a gentle nudge.

``Oh yes!'' says Nyanceth, with an enthusiasm that doesn't quite pass
for understanding. ``There have been quite a few trips made to this
destination in the recent past! Trips that began around the same time as
all the disapp---''

``I've heard enough,'' says King Slee. He is livid, his voice tight and
clipped. ``Amber Guard, please escort the general out of this
courtroom.''

No one speaks as two men in amber robes take Pouru by the wrists and
lead her from the high table out through the marble archway. The door
closes decisively behind them.

Kandir gives Nyanceth a satisfied nod. Nyanceth smiles back vacantly.

``It is clear,'' says Slee, breaking the silence, ``that there must be a
thorough investigation of the general's betrayals. During her absence
from the council, I would ask Minister Nyanceth to take on his previous
duties as Minister of War.''

It is unclear if Nyanceth understands this, but Kandir claps him on the
shoulder in congratulation.

``In the meantime,'' the king continues, ``there is still a prisoner who
has confessed to murdering a friend of the crown. Let us devote our
attention to that matter now. I pose the question to our five guests: do
you think it is wise for us to bring the tiefling into this courtroom?
Can the creature speak for itself?''

``Indeed, she should be given the chance to speak,'' says Galadriel.
``But we've had some unpredictable experiences with her uncontrolled
magic. If any precautions can be taken for everyone's safety, we would
encourage that.''

``Thank you. I will consult with the Amber Guard, and we will make
preparations to bring her in. For now, we will take a short recess,''
says King Slee.

He excuses himself and shuts the door loudly behind him. The remaining
ministers stand up from the table and follow in his footsteps, with
Kandir leading Nyanceth, and the adventurers are left alone in the
council chamber.

``Okay, does anyone know what the Northern Ruins are?'' whispers Harlan.

``As a matter of fact,'' says Hermione, ``I do.''

The group huddles closer. She lowers her voice to a near-silent
susurration.

``They're the remains of a forgotten civilization on an island to the
north. Thousands and thousands of years old, lost to memory,'' says
Hermione. ``All overgrown and wild now, of course. And I've heard
stories of the strangest creatures that are said to roam there,
but\ldots{}'' Her eyes widen. ``Expeditions that have gone there usually
don't come back. Pieces of their ships will wash ashore. So I've never
made any plans to visit, myself.''

``And that's where Pouru was planning to send us,'' says Hanamir,
stroking his chin. ``And---if we're to take Nyanceth at his word---it
seems likely that the missing people were sent there, too.''

They think about this in silence for a minute. Harlan shudders, then
turns to Tannin.

``Tannin? You've been awfully quiet,'' he says. ``Are you disappointed?
Sounds like there would have been lots of great monsters to fight in
those ruins.''

``Huh? No.~What?'' says Tannin. ``But---you guys---isn't the Minister of
Justice, Mirama, isn't she \emph{amazing}?''

``She's certainly beautiful, if that's what you mean,'' says Harlan.

``Not just that. She's \emph{amazing}!'' Tannin repeats, shaking his
head in apparent disbelief.

The chamber door swings open again, and the king and his ministers file
back to their seats at the high semicircular table. After them, several
amber-robed guards enter, forming a human blockade around a figure who
must be Magick. The guard at the back of the group is holding a glowing
sphere in the palm of one hand. They stop to deposit Magick in a chair
at the center of the room, then walk back to stand at attention against
the wall.

The sight of Magick nearly makes the adventurers gasp out loud. She
looks emaciated and weak. She can barely hold her head up. Galadriel
stands.

``I would like to make the king and council aware that her condition has
deteriorated rapidly within the last twenty-four hours,'' she says.
``She looked healthy and strong the last time we saw her.'' She glares
at the guards. ``What have you done to her? What is that thing he's
holding?''

``That is a precautionary item, an Orb of Antimagic,'' explains Slee.
``I assure you, it is not harmful. It only prevents the use of magic in
its vicinity.'' He looks down at Magick with some amount of pity.
``Please, identify yourself for the council.''

Magick mumbles something.

``You'll have to speak up, I'm afraid,'' says Slee.

``My name is Magick,'' Magick slurs.

``Thank you, Magick. Is it true that you have confessed to the murder of
Bryn Starloft?'' Minister Mirama asks.

``Yes,'' says Magick.

``Can you describe for us what happened on the night he was killed?''
Mirama asks.

Magick heaves her head up with effort.

``My only goal is to bring peace to the world\ldots{}'' she sighs. ``I
thought that I had found a way to do that, but now I think that there is
no longer a way.'' She swallows drily. ``If the death of your friend
means that I can no longer live, so be it.''

``May I ask her a question?'' says Galadriel.

``Please,'' says Mirama.

``Magick, what happened to you since we last saw you? What has made you
ill?''

Magick lolls her head in the direction of the adventurers, but speaks to
the floor.

``Once you let them get me\ldots{} it all fell apart,'' she says.

``We did all we could,'' says Harlan. ``Magick, I shackled myself to you
to try and get you the best treatment possible.''

Magick doesn't respond. She slumps further into her chair.

``Magick\ldots{} do you need magic to survive?'' asks Galadriel.

At this, the tiefling displays a flicker of her previous vitality.

``Do you need blood to survive?'' she retorts.

``Yes, I do,'' says Galadriel. She pauses. ``I'm not familiar with
tiefling biology. Is that standard?''

From beside her, Hermione shakes her head.

``I require magic to live,'' says Magick.

King Slee clears his throat.

``This way that you felt you could bring peace,'' he says. ``Why was it
necessary to murder Bryn to accomplish it?''

Magick takes a long inhale, as if summoning all of her energy.

``I did not mean to kill the scholar. I am sorry. His book helped me to
understand\ldots{} to rid this world of evil we must first rid this
world of those who commit evil\ldots{}'' She closes her eyes. ``There is
an item I seek. A powerful relic of the ancient world. With it I would
erase them, dragonkind, from existence.''

Kandir perks up noticeably. He peers closer at Magick as she continues.

``All the texts point me to the ancient island, the place it was last
seen\ldots{} and I sought these people, these friends to help me so that
we could bring peace together, but they were angry at me, and I\ldots{}
now I have no more faith in my destiny. Or in the possibility of
peace.''

``If this item truly exists,'' says Kandir. ``Perhaps the tiefling
should be allowed to help us find it. It sounds too powerful to be
claimed by anyone other than the King of Aberith. If someone with such
obvious mental imbalances were to find it, there's no telling the
catastrophe that might result.''

``So you propose a voyage to do\ldots{} the exact thing the suspect
wants to do?'' asks Slee.

``The suspect cannot be trusted with it, of course, but if she has
already done the necessary research, why not use it?'' says Kandir.

``I don't presume to speak for Magick, but I imagine if you would like
her help, you're going to have to commit to treating her a touch more
humanely,'' says Harlan.

``I think we can do that, if she is willing to cooperate,'' says Slee.

``Maybe you could send her with people that she already trusts!'' says
Tannin. The council seems startled, as if noticing his presence for the
first time all day.

``Are you volunteering?'' Slee asks.

``Yes!'' says Tannin, with a thump of his fist on the table. ``We're the
very crew to go and find this artifact.''

While Harlan gives Tannin his best ``OH REALLY?'' face, Hanamir whispers
to him in Dwarvish.

``Are you sure you want to go on this side quest and abandon the Lich?''

Tannin chuckles.

``Whoa! I didn't know you spoke Dwarvish, my man,'' he replies in his
native tongue. ``Anyway, I'm not planning on abandoning the Lich. I'm
thinking we go get this item and then kill the Lich with it!''

``Got it. Good idea, big guy,'' says Hanamir. He switches back to
Common. ``Indeed, we would be grateful for the opportunity.''

Hanamir gives Harlan a reassuring look.

``At the very least, Your Majesty, we can guarantee that Magick will be
out of your city and will never return,'' says Harlan. ``You can trust
us to accompany her on this quest, and she will cause you no more
trouble.''

``That is my concern at the idea of letting the tiefling go,'' says King
Slee. He fixes an intense stare on Harlan. ``But I trust this party.
Will you vow, in the name of your god, that you will keep this tiefling
out of the city of Aberith, and deliver the appropriate consequences
should she attempt to return?''

He enunciates \emph{appropriate consequences} with precision. His
meaning is clear.

``Yes,'' says Harlan. ``I vow it, in \href{/characters/kord/}{Kord}'s
name.''


\chapter{Summer in the City}
\chapdesc{It's a pity that the days can't be like the nights in the summer in the city.}

The Half-Full Flagon is quite empty during the day. Its only occupant is
a man with an unkempt beard who sits slumped behind the bar, snoring
softly. The bell on the door isn't enough to rouse him when the
adventurers come in, but this does not discourage
\href{/characters/tannin/}{Tannin}.

``What do you think, guys? A round of ales?'' He kicks the bar and its
attendant sputters awake.

``It's not even noon yet,'' says \href{/characters/harlan/}{Harlan}.

``So?'' Tannin scoffs. ``A pint of your finest, if you would.'' The
bartender yawns and acquiesces.

``I'll pass,'' says \href{/characters/hermione/}{Hermione}, pursing her
lips. ``I have some research I'd like to do regarding the Northern
Ruins, and I don't want to waste any time. I just want to get to our
rooms upstairs, grab a change of clothes, and then get back to the
library.''

``We do have a few weeks, according to the king,'' says
\href{/characters/galadriel/}{Galadriel}. ``You know, for a port city,
it takes them a long time to charter a ship.''

``Unless it's being done in the dead of night to make prisoners
disappear,'' notes \href{/characters/hanamir/}{Hanamir}.

``No takers? Really?'' says Tannin, as the bartender sets down his ale.
He then chugs the entire pint in one go. To an outside observer, this
might be impressive, but the adventurers watch him without comment.
``Fine. Do what you want. I have plans of my own.''

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

Galadriel has two items on her to-do list for her free time in Aberith:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\item
  Look up any records on her father, a human named Jeff ``Bubba''
  Torpleton
\item
  Find a short-term gig
\end{enumerate}

The first item is infinitely more important than the second, and it's
why she hasn't mentioned it to her friends even once. In the sweltering
heat of the early afternoon, she walks to the Hall of Public Records on
the southern waterfront. A clerk, wearing thick spectacles and an
unflattering dress made of something like burlap, handles her request.

``Torpleton, with a T?'' says the clerk. ``Follow me.'' Galadriel
follows her downstairs to a musty room of shelved scrolls, leather-bound
books, and loose parchment.

``Here you go,'' says the clerk, pulling a dank-smelling volume from a
shelf.

``Thank you,'' says Galadriel. She waits for the clerk to leave before
even glancing at the book's spine. \emph{Heroique Soldieres of
Aberythe's Past}. Promising!

\emph{TORPLETON, Greggorye. Knowne to friends as ``Old Gregg.'' Thys
valiante soldiere fought for the Crowne of Aberythe under Her Majestye
Resia II. During the Battle of Twelve Swordes, he led a party of humans
against undead hordes at the Hillock Graves \& vanquished the hideouse
foes \& lost but three of his owne soldieres. Afterward, the TORPLETONS
pursued a quiette life of farminge to the west of the Elven City
Ang'Svin.}

Galadriel feels her face fall. That's all? Nothing more current? She
flips through the book in vain. She doesn't have a good idea of when
Resia II's reign took place, but it must have been hundreds of years
ago, judging by the book alone. And he moved his family to
Ang'Svin\ldots{} well, she supposes, it's better than nothing. It'd
explain his great-great-great-great-grandson's comfort level with elves.

Still, she can't deny her disappointment. She wanders back in the
direction of the Half-Full Flagon, but doesn't feel like seeing friends
right now. Out of curiosity, she continues onward to the Kiln, past the
daytime dealers of potions and the shadowy figures with nothing good to
say. Without knowing why, she stops at a doorway marked by a painted
black unicorn. \emph{FOOD - DRINK - MUSIC}, the doorway proclaims.
\emph{NOW HIRING}, adds a hastily-scrawled piece of parchment.

Worth a shot for that second item on the list, she thinks.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

Hanamir and Hermione don't need to discuss other options before
immediately venturing uptown to the library. It's the obvious
destination. Where else would an intelligent person spend their free
time before a dangerous mission?

They walk together across the entire city, making cordial conversation
at an extra-polite distance. They attract a few stares from the general
public---an elf woman and a half-orc man are an unusual pairing
anywhere, but they feel particularly scrutinized in a majority-human
city like Aberith.

``So, you are planning on researching the Northern Ruins?'' asks
Hanamir.

``Yes,'' says Hermione. ``I have a baseline familiarity, but I am hoping
to learn enough to help us navigate the ruins in pursuit of
\href{/characters/magick/}{Magick}'s dragon-slaying relic.''

``Very good,'' says Hanamir. ``Do keep me apprised of what you learn. I
have a small chore to attend to first, but then I'd like to do some
research myself.''

The librarian greets them coldly---he recognizes them as part of the
group he had to eject the other day for excessive noise. But he warms up
after the first five minutes watching the two of them behave like model
citizens.

Hermione looks on as Hanamir takes a roll of parchment and a pen out of
his backpack. He writes in a cramped but meticulously neat hand.

\emph{To my colleagues at Drephis State University Library,}

\emph{I write to you from the Royal Library of Aberith after weeks in
pursuit of our missing shipment of Interlibrary Loan books, No.~404. I
regret to report that the majority of the books remain unaccounted for
at the time of this writing.}

\emph{During my travels, I have had three encounters that did help to
illuminate the search. I relate them to you here:}

\emph{1. During the famed Moon Festival held in the town of Eillin, an
intoxicated individual told of an orc encampment nearby that had been
hastily evacuated. Among the abandoned items described therein were some
books, which struck the individual as unusual, owing to orcs'
stereotyped aversion to literacy. Upon visiting this encampment myself,
I was only able to recover a single page of what I recognized
immediately as} The Reproductive Cycle of the Slaad. \emph{Though I lack
hard evidence, I do suspect this page came from DSU's copy of the book.}

\emph{2. In a nearby temple to the orc god Shargaas, my companions and I
found DSU's own marked copy of} Anatomy of Bugbears, Second Edition.
\emph{It had been desecrated, its pages entirely hollowed out. Forgive
me---I know this is painful to read about. It was quite devastating to
see in person.}

\emph{3. \href{/characters/khargol/}{Khargol}, a leader of
Shargaas-aligned orcs, delivered a few oblique taunts regarding my quest
to recover the Interlibrary Loan shipment. He called me a ``delivery
boy'' and mentioned that I ``didn't even know what I was carrying.''
This, and the hollowed-out copy of} AoB2E, \emph{suggests to me that the
books are being used for some unsavory purpose by the cult of Shargaas,
perhaps as vessels to transport the magical tuning forks they have been
using to plane-shift into the Sealed City.}

\emph{The trail has since gone cold, but I have not given up. These
books are my responsibility. Accounting for them and seeking justice for
their theft and/or destruction is my sacred duty.}

\emph{Yours professionally and in deep, unyielding sorrow,}

\emph{Hanamir}

Hermione watches as he then copies this same text over twice, separates
the three copies, and seals two of them with wax. The third he tucks
into his backpack.

``Be right back,'' he whispers, and slips away toward the stacks. He and
the librarian then have an animated but essentially silent conversation
resulting in Hanamir handing over the other two copies of his letter,
and the two of them shaking hands warmly.

Hermione turns back to her pile of books. \emph{Ixquichpehua: History
and Myth} is the one she's starting with. A quick glance at the table of
contents gives her the beginnings of a headache.

\emph{Part I: A Magical Empire}

\emph{The Worship of Animal Gods, p.~1}

\emph{Cursed Shrines, Enchanted Treasures, p.~56}

\emph{A Legacy of Eternal Torment, p.~94}

\emph{Part II: Modern Exploration}

\emph{A Short List of Failed Voyages, p.~125}

\emph{Known Traps, p.~151}

\emph{Vengeful Guardians, p.~233}

She wonders if any of the other books might be a little more encouraging
in their content. But their titles, if possible, sound worse:

\emph{Divine Electrocution: The Eel God of Ixquichpehua}

\emph{Buried Alive: Greed and the Search for Ixquichpehua's Forbidden
Treasures}

\emph{It's Just Not Worth It: The Case for Leaving the Northern Ruins
Alone}

She decides to save those for later.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

Harlan finds \href{/characters/deru/}{Deru}
\href{/characters/nyanceth/}{Nyanceth} in the temple garden filling a
basket with herbs. She notices him and smiles widely.

``Under the Eye of the Storm!'' she calls. ``How's that hand holding
up?''

``May we behold His Fury,'' says Harlan. He waves his left hand at her.
``No complaints so far.'' He glances around. ``Isn't there a service
soon? I didn't mean to interrupt. I was hoping to spend some time in
communion with \href{/characters/kord/}{Kord}, and with other devotees,
of course.''

``Oh, yes,'' says Deru, wiping her brow. ``I'm cutting it close, aren't
I? Today's service starts in a few minutes, so you're right on time.
I'll come in with you now.''

``Also\ldots{} I did want to tell you,'' says Harlan. He looks down at
the ground for a moment. ``I met your father. He seemed\ldots{}''

``Confused?'' sighs Deru. ``Doddering? Unfit to hold office?''

She leads him to a side door of the temple and starts preparing for
priestess duty: washing her hands, donning a gray cloak, affixing her
holy symbol to her chest.

``I don't know about that,'' says Harlan. ``But I tried Detecting Magic
on him, and---''

``I know. I've tried too. Nothing,'' says Deru. ``But\ldots{} it's not
natural. It can't be. It happened so fast, and he's not \emph{that} old,
and I just---'' She turns away, her voice breaking. ``I miss my dad.''

``I'm sorry,'' says Harlan. He stands there awkwardly while she collects
herself, wiping her eyes. ``I didn't mean to upset you. I just wanted to
ask about his relationship with Minister
\href{/characters/kandir/}{Kandir}. It seemed to me that Kandir might
have an undue influence over your father.''

Deru sighs again. ``Can we talk about this later?''

``Of course,'' says Harlan quickly. ``I'm sorry. I should have waited to
bring it up.''

After the service, Deru seems back in good spirits. She spends awhile
talking to parishioners in the courtyard while Harlan stands aside,
listening. She has a rapport with each of them---no affectations, just a
warm demeanor and a genuine desire to spread the good news of Kord. Only
one young man in the group seems to be trying to cause a stir.

``Open your eyes, sheeple,'' he mutters, to no one in particular. ``Kord
is a joke.''

``What makes you say that?'' says Deru, sounding honestly curious.
``Kord has shown great power, and great mercy, to me and to others in
our temple.''

``The twelve Supreme Entities gather around a table and laugh at how
they have divided the world up into dark and light,'' he says. It rings
a bell in Harlan's memory.

``Hey,'' he says to the young man. ``I've heard that line before. Are
you a follower of the Messenger, by any chance?''

The young man clams up, shoving his hands in his pockets and kicking
some gravel.

``I'm just wondering why you chose to attend a service at the Temple of
Winds if you feel this way about Kord,'' Harlan prods.

``Boccob tricks them all by withholding his true powers, and they allow
it,'' the boy continues. A lock of his dark hair falls over his face. He
takes a deep, shaky breath. ``Kord and Gruumsh are as close as lightning
and thunder.''

This prompts gasps and murmurs from the crowd in the courtyard.

``If you knew anything about the gods, you would not speak so
foolishly,'' says Harlan, sounding angrier than he intended. ``Gruumsh
aims to sow destruction and discord. Kord is virtuous and fair. There
are \emph{worlds} of difference between Kord and Gruumsh.''

``Why then do the `good' gods tolerate the evil ones? Why have they not
eradicated evil from our world?!'' says the boy. ``Only because they
enjoy watching us suffer!''

Before Harlan can respond, the young man turns on his heel and flees the
courtyard, disappearing down the street.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

Tannin hasn't told his friends the details, but he does already have
commitments for the next few weeks. It wasn't something he'd planned to
do---but after the trial, he had stayed back, waiting for the room to
clear. He'd just wanted to introduce himself to the Minister of Justice
and let her know what an impression she'd made on him.

``Minister \href{/characters/mirama/}{Mirama},'' he had said. ``The
name's Tannin McBitters. I'm a bit of a justice-seeker myself.''

``Very nice to meet you, Mr.~McBitters,'' said Mirama. Her gaze, when
turned toward him, was so powerful that Tannin felt affixed to the
floor. ``Tell me more about your quest for justice.''

``A great wrong was done to my clan,'' said Tannin, his expression
darkening. ``But there is no council that will hold the perpetrators
responsible. No one can balance the scales except me. And it is my duty
to avenge them.''

There was a silence during which Tannin feared he might have shared too
much, out of whatever starstruck impulse had taken hold of him.

``Sometimes there is no justice but action,'' Mirama replied. ``Always
seek a merciful justice, where you can, but do not wait for permission
to seek it.''

And Tannin had felt, in that moment, that she understood his pain better
than anyone had before. A sudden thought had occurred to him.

``Hey,'' he had said, ``if you need a strong arm, especially around the
water\ldots{} I don't know what else I'll be doing while your lads
rustle up a boat for us.''

The Minister had given him a smile. ``I may have just the thing for
someone as courageous and capable as yourself.''

And that is how Tannin agreed to be Kir Mirama's enforcer along the
Coast of Beory.

Alone in the dark ocean, he is reminded of the time he spent in the
Elemental Plane of Water. It feels like returning home. He swims out
until he can barely see the haze of the Aberith shipyards behind him.
``Look to the naval guard, the Legion of Seals,'' Mirama had said.
``They do not respond to my orders as they once did. I believe them to
be corrupted by the magic smugglers.''

The hulking shape of a barge looms ahead. Tannin dives deep and swims
toward it. They'll never see him coming.

``I'll do what I can to restore order, Minister,'' he had told her, with
a grin.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

``A full week of performances down, and the crowd's taken quite a shine
to you, Ms.~Moonwater,'' says Slurpt Gearix, the goblin owner and
proprietor of the Black Unicorn, as Galadriel exits stage right down the
rickety staircase to the dressing rooms. ``How's it feel?''

``Can't complain!'' Galadriel says with a shrug, wiping the sweat off
her forehead with her sleeve. It hasn't been her best work---she gets a
little lazy when she senses the audience is more interested in their
drinks than in her---but it's fun enough, and a week has already flown
by.

``Well,'' says the goblin, ``I'd like to offer you a chance to make your
time here even more profitable.''

Galadriel raises an eyebrow. He continues.

``You might have noticed that many of our patrons take issue with the
restrictions on the buying and selling of magical goods,'' Gearix says.
``I make no secret of the fact that I'm opposed to them myself. I was
wondering if you might be willing to help me unite interested buyers
with some items I happen to have on hand.'' He drums his fingers against
the wall. ``For commission, of course.''

In the days that follow, Galadriel arranges several sales: a Sphere of
Annihilation to a short wizard in heavy black robes; a set of Iron Bands
of Bilarro to a Kenku named Squawker, whom she recognizes as the
potential basilisk buyer; and, most concerningly, a Mirror of Life
Trapping to a sweaty, shifty-eyed member of the Amber Guard.

The regulars begin to greet her by name, and she wonders if she ought to
have used a pseudonym when she started here---it seems to be common
practice among the denizens of the Black Unicorn. She hears quite a bit
of chatter about the Messenger and his anti-establishment teachings, but
learns nothing more about where one might find him. She also learns
about ``Mr.~Odo,'' a name usually whispered with trepidation. It sounds
to Galadriel like he may be a mob boss, or some other figure of
authority in the criminal underground. Either way, he is purported to be
brutal when disappointed with his minions.

Galadriel pockets more gold during her first week of moving magical
contraband than she has made in whole months of other gigs.

``Not bad, huh, Ms.~Moonwater?'' asks Slurpt Gearix as he pushes a pile
of coins toward her across his desk. They have just sold a Decanter of
Endless Water to an elderly drow for far more than its value. Galadriel
knows this is how black markets operate, but she feels a twist of
regret.

``Not bad at all,'' she agrees, flashing a weak smile. She pushes the
coins into her bag and starts to stand, but Gearix motions for her to
remain seated.

``Now, I have a special item that's just come in,'' he says, lowering
his voice to a murmur. ``I'm talking serious magic, seriously deadly. A
potion. And I think I know someone who'd appreciate having it on hand.
You ever seen a drow woman in here with white eyeballs? Like, I mean,
the part where normally there's a color in it, but it's white?''

Galadriel nods. She's noticed the drow woman in question staring
intently at her gauntlet during performances---though she could be
wrong, because with totally white eyeballs, it's sort of hard to tell
where she's looking.

``Her name's Yasaria. She's got this sort of, uh, gang of dancers, and
they kill people, you know, for money and stuff.'' Gearix shrugs.

``Dancers?''

``Yeah. Some kind of fighting style she invented where it looks like
they're dancing with you but then\ldots{}'' He mimes some feminine dance
moves, clunkily. ``Then they kill you, and you don't know it `til you
hit the ground and they're off bouncing on their hands and climbing up
walls and all that.''

\emph{Climbing up walls?} thinks Galadriel. \emph{She's seen my act.
She's seen me do that.}

``Anyway, I thought the two of you might have some things in common,''
says Gearix. ``And I was hoping you'd be able to work in the topic of
some extremely rare Underdark Ambrosia that is available for purchase at
a price that can't be beat. But, you know, in a subtle way.''

``Sure,'' says Galadriel---though the tightness in her throat betrays
her trepidation.

After that night's performance, she spots the white-eyed drow woman
sipping an ornate goblet of steaming black liquid. When she approaches,
Yasaria looks up at her lazily, as if she'd been expecting the encounter
hours ago.

``Hi,'' says Galadriel. ``I'm Galadriel. You must be---''

``Yasaria,'' says Yasaria. She downs the remainder of her drink and sets
the goblet on the bar. ``I've been hoping to meet you. You have skills.
I know a Daughter of Spiders when I see one.''

Galadriel feels the blood drain out of her face. She nods, too quickly.

``Yep. Yup!'' Flustered, hating herself, she waves her gauntleted wrist.
``Guilty.''

``You will join me and my sisters for training,'' says Yasaria. It is
not a question.

``Uh, okay,'' says Galadriel. ``I was supposed to talk to you about a
potion? Um, it's called Underdark Ambrosia?''

``Yes, I will buy it,'' says Yasaria, waving an impatient hand. ``Tell
Slurpt he is a crook and a fool. Meet me in three hours in the drow
cemetery. Bring nothing. Tell no one.''

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

At first, the Royal Librarian doesn't even know what to do with the
half-orc volunteer. He's clearly a lover of books, but is he really
prepared to care for a collection like this, with volumes of
considerable age? Is it prudent to allow a stranger such unfettered
access to the continent's largest hub of knowledge?

It turns out the answer to both questions is a resounding ``yes.''
Hanamir begins by donating some real gems to the library---\emph{The
True History of Eillin} and a very nice copy of \emph{The Idiot's Guide
to the Planes}, among others---and continues by taking exquisite care of
every book that passes through his hands.

It's clear to Hermione, too, that Hanamir is radiantly happy to be back
among the stacks. He procures books for her, as many as her heart
desires, and the librarian is glad to let the two of them pursue their
research at will. Once Hermione has read the Ixquichpehua material
cover-to-cover, she moves on to biographical texts on the king, his
family, and the councilmembers.

``Hey,'' says Hermione, without removing her nose from a book on
Aberith's recent history, as Hanamir sits down next to her for a brief
break from re-shelving. ``Did you know it was
\href{/characters/slee/}{Slee}'s mother, Queen Gillia VII, who started
the council in the first place?''

``I did not,'' says Hanamir. ``That's more recent than I thought.''

``I know,'' says Hermione. ``She was a real reformer, it sounds like.
Had an advisor who was openly part of the Harpers. Like, the radical
transparency group. And it turns out Nyanceth was a general, like
\href{/characters/pouru/}{Pouru}, before he was the Minister of War.
And---and---he wanted Deru to follow in his military footsteps instead
of becoming a priestess. And there was never a Minister of the Sea
originally, but the position was created for him, and some say it was a
landing place for his retirement\ldots{}''

``Are there any more books you'd want to look at today?'' asks Hanamir.
``The librarian is initiating last call a little early. Wants to close
up quickly tonight.''

``Oh!'' Hermione frowns. ``Well, if there's anything about Aberith's
historical involvement in international affairs, that'd be great. It
might shed some light on the conflict between Kandir and Pouru. Pouru is
a bit of an isolationist, while Kandir feels that the empire should
expand via trade, or war if necessary---and he himself wasn't born in
Aberith, so his connections to the outside world are stronger. It's
really fascinating. Now that Pouru is in prison for alleged treason,
Kandir may have much more freedom to---''

``I'll go check,'' says Hanamir, smiling.

After the library closes, Hermione feels purposeless.

``Want to grab a drink with me?'' she asks Hanamir. ``We could head back
to the Half-Full Flagon. I met a very interesting fellow there last week
who breeds chwingas. Maybe he'll be back.''

``I'm afraid I have some personal business to attend to,'' says Hanamir.
Hermione notices, then, that Hanamir has a bandage around the knuckles
of his right hand.

``Should I even ask?''

``I'd prefer that you didn't,'' he says, giving her a cheerful wave.
``See you tomorrow!''

He strides off in the direction of the Kiln.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

Some nights, Tannin wonders if he might be too good at this ``extralegal
bounty hunter'' thing. He does prefer a bit more of a challenge than
these small-time pirates can offer him. Still, he can't deny it's an ego
boost to hear that he's known around the Bay of Beory as the Murderous
Mer-Dwarf, even if it's not quite reflective of the truth. At Mirama's
request, he hasn't actually killed anyone yet.

That's the other thing that keeps him going: there's something addictive
about earning her approval.

``Intercepted a shipment of enchanted objects tonight, boss,'' he
reports, standing in her office at sunrise. She sips a cup of fragrant
tea while sifting through the scrolls that sit piled on her desk.
``Nothing dangerous or even very rare. Just your garden-variety tokens
for healing, clairvoyance, strength\ldots{} but there was a whole barge
full of the stuff.''

``Very good,'' she says to her teacup, then looks up at him. ``Any
casualties?''

``No, ma'am,'' says Tannin. ``As little bloodshed as possible, as
always. I promise.''

She stares him down, and his lips can't help but twist into a smile. He
may have knocked some heads a little harder than necessary last night,
but she doesn't need to know that. No deaths!

``My guards paint a very different picture of the Murderous Mer-Dwarf of
Beory,'' she says, lowering her gaze and taking another sip of tea. ``Be
careful not to get carried away in your zeal for restoring law and
order, Mr.~McBitters.''

\emph{Restoring law and order?} He knows she says that just to tease
him. As if he could ever be zealous about the law! He's zealous for
justice, the law be damned! He's zealous for\ldots{} well, for her! He
chews on his lip for a moment, sensing that it's a test of his
deference. After another half a minute of silence, she smiles warmly.

``I do appreciate your work, you know,'' she says. And instead of
sending him on his way, per their usual routine, she rummages in a desk
drawer for a hefty satchel with multiple complicated locks on its front.
``So much so, in fact, that I dread the hour of your departure for the
Ruins. I want to offer you this as an extra token of my gratitude, in
the hopes that you will have a greater chance of returning to Aberith
through its use.''

She heaves it up onto the surface of the desk and motions for him to
collect it.

``What is it?'' Tannin asks.

``A thousand gold pieces,'' she says, with no change in her expression.

``Whoa!'' says Tannin. That could almost buy two more hands for Harlan,
if he wanted to have four hands. Or two of that fancy knife set from the
marketplace. Or\ldots{} probably something more useful. He'd ask
Hanamir. ``Thank you, Minister Mirama. I don't know what to say.''

``Use it well,'' says Mirama. ``I'll see you tomorrow.''

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

Harlan meets Galadriel outside the Black Unicorn around noon on a
Tuesday. She squints her eyes at the daylight as she cracks open the
side door and emerges from the subterranean staircase, her clothes
reeking of pipe smoke and pungent goblin cuisine.

``Nice makeup,'' says Harlan. ``You look like a raccoon.''

``It's the style in there,'' she scowls at him. ``Try being even a
little bit cool for once.''

``No,'' says Harlan. ``All right, shall we head out? Do you have your
travel pass from King Slee?''

Galadriel waves the wax-sealed parchment at him and sighs theatrically.

``Merciful Kord, your breath. Thankfully, we're headed for open country
air.''

They reach Elris's farm by mid-afternoon. Galadriel clings to Harlan's
arm as the giant blue rancher goes to retrieve their respective animal
companions.

``I hope he's all right,'' she murmurs. ``I hope he hasn't been too
lonely out here. I've missed him so much.''

``I'm sure he's fine,'' says Harlan. ``He's had Zotz to keep him
company. And I trust Elris has taken good care of him.''

When \href{/characters/buddy/}{Buddy} appears in her line of sight,
Galadriel dissolves into joyful tears, her heavy eyeliner streaking down
her cheeks. She spends the next twenty minutes covering the little pig's
fuzzy head with kisses. Camazotz, on the other hand, is less willing to
accept affection from Harlan.

``He's a mighty fine bat, as I said,'' drawls Elris. ``But a wild one.
I've had a bit of luck using some giant moths as rewards for him when he
behaves.''

Harlan holds out a hand to his erstwhile steed, but Zotz only screeches
and snaps.

``Now, if you like, I could put him through some more serious training,
but you'd have to leave him here a few more weeks,'' says Elris.

``I'd be interested in that,'' says Harlan. ``How much would it cost
me?''

``A hundred and fifty gold, I reckon,'' says Elris.

``And you'd trust me to pay when I come back?'' asks Harlan. ``I don't
have the gold on me up front.''

``Well, by my thinking, if you don't come back, I'm down a few weeks in
effort, but I'm up one trained, giant bat,'' says Elris, with a chuckle.
``Deal?''

``Deal,'' says Harlan, shaking his hand.

Under the shade of a nearby apple tree, Galadriel and Buddy have resumed
full cuddle mode.

\emph{Please tell me you haven't been miserable out here,} Galadriel
thinks. \emph{You must be so bored.}

NAH, I'VE BEEN GOOD. ELRIS REALLY IS A NICE GUY. ZOTZ AND I DON'T HAVE A
LOT IN COMMON, BUT I'VE KEPT MYSELF BUSY MAKING PUZZLES FOR HIM.

\emph{Puzzles?}

YEAH. ELRIS GIVES HIM THESE GIANT DEAD BUGS AS TREATS. SOMETIMES I STEAL
A FEW FROM HIS SHED AND HIDE THEM AROUND THE FARM, AND THEN GIVE HIM
CLUES SO HE CAN FIND THEM. HE'S SMART.

Galadriel laughs.

\emph{And no one has figured out what you really are, right? You're
safe?}

SAFE AS CAN BE.

She kisses the top of his head. He oinks contentedly.

\emph{Good. Now, I have something to tell you, or\ldots{} ask you,
really.}

IS IT ABOUT\ldots{} THE NORTHERN RUINS?

\emph{Yes! How did you---?}

I CAN READ YOUR THOUGHTS EVEN WHEN THEY AREN'T DIRECTED AT ME.

\emph{Hey!}

I'M SORRY. IT'S HOW I KNEW I COULD TRUST YOU IN THE FIRST PLACE.

\emph{So you know about the legendary thing, the\ldots{} quiznos? And
about Magick wanting to use it to wipe out dragonkind?}

I PICKED UP THE GIST OF IT. AND YOU WANT TO KNOW IF I'LL COME WITH YOU?

\emph{Yes. I know it's a lot to ask, considering what you'd be risking
if she found out about you\ldots{}}

SURE, I'LL COME.

\emph{Really?!}

YEAH. AFTER ALL WE'VE BEEN THROUGH? C'MON, GIVE ME A LITTLE CREDIT. I'M
WITH YOU, GALADRIEL.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

Hanamir darts between punches like a mosquito avoiding a baby's swats.

``You can be quicker than that,'' he chides his student. ``Channel your
anger!''

The young half-orc roars and wallops the air where Hanamir's face was a
split second ago. Hanamir grabs his wrist and twists it behind his back,
swiftly disabling him.

``Remember to stay present,'' says Hanamir, releasing him. ``The Way of
the Open Hand teaches us that there is no past, no future. Only now.
There is only the energy that animates all things, and there is power in
directing its flow through you.''

The group of teenaged half-orcs stare at him, unified in rapture.
They've never met anyone like Hanamir. A half-orc who carries a book
under his arm? Who moves like a shadow? Who speaks as softly as a
songbird at midnight, and fights as doggedly as the winter's chill?

``Join me in meditation, friends,'' says Hanamir, settling into a
modified White Crane pose. ``Match your breathing with the movements of
your arms. Feel your own gentle spirit rise and fall, and your strength
ebb and flow.''

When it is time for the youths to leave this unfinished basement in one
of the Kiln's most dangerous slums, several linger by the stairs.

``Mr.~Hanamir?'' one of them asks. ``Last week, you said you're just
visiting Aberith\ldots{} how long did you mean?''

``Only a short while longer, I'm afraid,'' says Hanamir. ``My friends
and I must depart in another week or two.''

The stragglers are visibly crushed. Hanamir feels his heart ache for
them.

``I hope you will continue your practice in my absence,'' he continues.
``The Way of the Open Hand teaches discipline, and can give you great
peace in return. And with that peace, you might find that you can do
much more in this world than you thought you could.''

He leads them up the stairs and back out into the night.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

The night before their ship to the Northern Ruins is scheduled to set
sail, the adventurers gather for a pint at the Half-Full Flagon.

``To the unknown!'' says Harlan, raising his glass. ``And to a dangerous
and potentially misguided quest!''

The other four clink their glasses against his.

``To the awesome stuff we bought from
\href{/characters/sanford/}{Sanford} and Son today,'' adds Tannin,
spinning his new Ring of Protection on his middle finger. ``And to Kir
Mirama for bankrolling it!''

``I still can't believe you all went shopping without me,'' mutters
Galadriel.

``Somebody was too busy dance-fighting with the other spider girls,''
says Harlan. ``Priorities are priorities.''

``I could \emph{tickle} you and you would \emph{die}.''

``Now, now, you two,'' says Hermione. ``We should talk about our plan
for when we reach the ruins. Should one of us be on Magick duty? We
don't want her to run around unattended, right?''

``We'll use the Dimensional Shackles,'' says Hanamir. No one mentions
his bruised and busted lip, out of politeness (but he'd probably explain
that a teenage half-orc monk trainee got a lucky hit, if asked).

``Yes, but I'd like her to have a bit more supervision, you know, moment
to moment,'' says Hermione. The group is silent and avoids eye contact.
``Really?! Come on.''

``Sounds like you're saying you want to supervise Magick,'' says Tannin.

``Fine!'' says Hermione. ``If I have to be the adult here, I'll do it.
But don't make the mistake of thinking you don't owe me one.''

The others mumble excuses incoherently or take swigs from their drinks.
After a nebulous silence, Tannin speaks up.

``Do you think it's real? The thing?'' he asks, looking around the
table. ``The\ldots{} quiznos?''

``That's not what it's called,'' says Hermione. ``It's the
quitzananon---the quetzanyananaya---the quinceeara---''

``We're calling it the quiznos,'' says Harlan, with a wave of his hands.
``And\ldots{} yes. I do think it's real.''

``To the quiznos!'' says Hanamir. ``May we find it. And may it find us
in good health.''

They clink glasses again and drink deeply.


\chapter{Codex Quiznoza}
\chapdesc{Grab the Old Bayit's a dungeon-ous crab.}

The sky is marbled with clouds the color of smoke. Above the ship, a
lone seagull grows tired of circling the mast. It lands on the deck near
Magic and \href{/characters/hermione/}{Hermione}.

``Look at that!'' says Magic. ``What is that thing?!''

``It's a seagull,'' says Hermione. The bird blinks at them, then lets
out a short burst of mournful cries. ``Seagulls live by the water and
like to steal your food.''

``Steal my food?'' Her cloak balloons with ocean air as she bends down
to look at the bird. ``Maybe I'll erase them from existence, too!
Hahahahaha! Dragons and seagulls! Hahaha!''

Hermione gives her a strained smile.

\href{/characters/galadriel/}{Galadriel} and
\href{/characters/buddy/}{Buddy}, sitting nearby, catch this last
exchange over the roar of the ocean.

\emph{You know I had to tell them, right? Not just because I'm terrible
with secrets, I mean. After all their suspicions, I owed them the
truth.}

OH, YEAH, I KNOW, says Buddy. HEY, DON'T STRESS. I KIND OF APPRECIATE
THAT EVERYONE KNOWS NOW. I CAN BEHAVE A LITTLE MORE LIKE MYSELF. WALK ON
MY OWN FOUR LEGS, AND ALL THAT.

\emph{But we still have to keep it a secret from Magic, or she'll try to
kill you on the spot.}

HONESTLY? I AM NOT THAT WORRIED ABOUT HER.

They glance over at the tiefling, who is now flattened against the
ship's railing, cowering in terror at the seagull taking confident steps
in her direction.

\emph{Fair enough}, thinks Galadriel. \emph{Just be careful. She can be
unpredictable.}

They watch as the expression on Magic's face changes abruptly from fear
to ecstatic joy.

``I see it!'' she says, grabbing Hermione by the arm. ``I can see the
towers!''

\href{/characters/harlan/}{Harlan}, \href{/characters/tannin/}{Tannin},
and \href{/characters/hanamir/}{Hanamir} look up from their contentious
game of Drephis Hold'em. The horizon ahead is indeed marked by several
tall smudges, which they suppose must be the aforementioned towers.
It'll be awhile before it starts to look exciting, they realize, and
turn back to their game.

But Magic's excitement soon turns from cute to creepy. The Amber
Guardsmen who are crewing the ship watch her nervously.

``I've been waiting so long,'' she croons, leaning over the bow of the
ship. ``I need it, I need it, it's fate, it's mine\ldots{}''

The card game fizzles out when Hanamir wins everything in the (strictly
theoretical) pot, including Tannin's trident and Harlan's giant bat.

``Aha!'' says Hanamir placidly. ``And that's how they do it back at
Drephis State, my friends.''

``Well played,'' concedes Harlan. ``Should we get ready to go?''

Hanamir raises his eyebrows at the group of four Amber Guardsmen who
have gathered around the mainsail to whisper conspiratorially.

``Yes,'' he says. ``Looks like they can't wait to be rid of us.''

The adventurers pile into a rowboat. The Amber Guardsmen lower them down
into the iron-dark sea, and almost immediately adjust the ship's sails
to turn back.

``Wait! When are you coming back for us?'' Harlan shouts.

``Four days!'' calls one of the Amber Guard, just as the ship fades from
earshot.

The beach is noisy with both crashing waves and jungle sounds: birds,
insects, and the occasional unidentifiable growl. The air is heavy and
humid. The sand leads directly to the base of a large stepped pyramid
with lots of thick green overgrowth and walls in various stages of
crumbling.

Hermione lingers to the back of the group with Magic, much to Magic's
chagrin.

``I don't want her darting ahead and pushing some button that will
trigger a trap and kill us all,'' Hermione explains.

``Right. We have Tannin for that,'' quips Harlan.

Sure enough, Tannin is already standing at the base of the pyramid,
ankle-deep in a viscous, swampy puddle.

``Guys?'' he says. ``This puddle is really, uh, aggressive.''

``Aggressive how?'' asks Hanamir.

``Like, I think it's sort of\ldots{} sucking me into it\ldots{}''

``Like quicksand?'' says Harlan.

``Yes! Yes, exactly like that,'' says Tannin. ``Good thing your boy can
handle a little soggy sand.''

He casts Shape Water and directs the liquid of the quicksand away from
himself, enabling his escape. But as he scrambles back to stable ground,
the movement of the water tips something out of balance, and the nearest
wall begins to collapse. The adventurers find that none of the ground
they stand on is particularly solid after all.

In a disorienting rush, they have all fallen down into a long, narrow
vault. There's a light yellow haze in the air. They can see more rubble,
perhaps from a previous collapse, but most of the room is intact. There
is a diorama of a hunting party in the center of the room, and several
alcoves in the walls showing scenes from tribal life: fishing, weaving,
worshipping at a temple. The figurines inside are free-standing,
brightly-painted clay.

Harlan looks closer at the temple scene.There's a figure representing a
god standing there wearing a feathered garment, and he is surrounded by
people offering up bowls. There is a large snail that is painted to look
afraid.

``Looks like a sacrifice,'' he says. ``Maybe the poor snail is the
offering.''

He casts Detect Magic. The figurines all emit the telltale golden glow
of transmutation magic.

``These things are all transmuted, so be careful,'' he says. ``Except
for their weapons, actually. Their weapons seem to be just little dolls'
accessories.'' Harlan looks closer at a clay figure holding a shepherd's
crook. It is painted distinctively, but it does not glow.

``Transmuted, huh?'' says Tannin, picking up a warrior from the center
of the room and tossing it in his hand. ``Transmuted from what?''

He misses catching it on the next flip, and the clay warrior shatters on
the floor.

``Whoops,'' he says. A full-size human warrior materializes, holding a
spear and wearing an animal skull headdress. He moves his mouth as if
he's speaking, but no one can hear a sound.

The warrior stabs the air with his spear, making Tannin jump out of the
way.

``Sorry all,'' says Tannin. ``I'll fix this!'' He tosses his net over
the warrior. The warrior thrashes.

With a heavy sigh, Harlan swings his hammer at the warrior. He bursts
into dusty clay shards that settle noisily on the ground.

``Okay, no more touching the dioramas!'' says Harlan.

At that, Tannin pulls the shepherd's crook free from its figurine's
hand.

``What did I just say?!'' sighs Harlan. But this time, nothing happens.
Tannin smirks.

Meanwhile, Hanamir inspects the rubble.

``I don't think there's much likelihood of us getting out of here the
way we came,'' he concludes. ``If we move any of this, it's likely to
set off another collapse. The only way out now is through.''

Magic sulks.

``I could help you, you know,'' she whines. ``If you would only take off
my shackles\ldots{}''

``Not a chance, sweetie, I'm sorry,'' says Hermione. ``All right, shall
we check out the door, then? Is it locked?''

The door at the end of the room is made of smooth white stone. There is
no visible lock mechanism, but when Hanamir leans on it, it doesn't
budge. There is, however, a little notch above the door that could
potentially be a keyhole.

``I'll check it out,'' says Galadriel. She gingerly tests whether the
wall will accommodate her weight without collapsing again, and then
climbs to inspect the notch. ``Toss me that shepherd's crook thing,''
she says. Tannin does so.

Sure enough, the shepherd's crook fits inside the notch and the white
stone doors spring open to a long, dark hallway whose walls are carved
to look like bamboo.

``First room down,'' says Hanamir. ``All right, team. Let's get in
formation.''

The adventurers follow him. The hallway gets darker and darker until
everyone is using their darkvision except Harlan, who doesn't have that.
Instead, he lights up his \href{/characters/kord/}{Kord} medallion,
casting an eerie glow on the bamboo-carved walls.

Hanamir taps along the floors with a ten-foot pole. But the force of the
pole isn't enough to trigger a trap that only clicks into place when he,
Tannin, and Galadriel have all stepped onto the same piece of flag
stone. At that moment, two logs swing out from within the bamboo walls,
knocking Hanamir to his stomach on the cold, slightly damp floor.

It's a rare moment of discombobulation for the usually nimble monk, but
he quickly rights himself and approaches the set of tall bronze doors
carved with a seaweed texture that stand ahead of him. Pressing his ear
to the door, he can hear a faint tapping from the other side.

``Something is in there,'' he whispers. ``Something alive.''

He tests the door handle. It's not locked. He silently pushes it open.
The floor is wet and muddy. Galadriel holds out a hand to the
walls---they are similarly slimy.

The adventurers can see a massive boulder in the center of the room.
Next to it rests a long bamboo staff. Nearby, and the apparent source of
the tapping, a large crayfish scuttles in the mud.

``I'm going in,'' whispers Galadriel. She slides a little as she vaults
up the wall, but is able to hang on despite the slime.

The adventurers watch as she spider-crawls up to the center of the
ceiling, directly overhead of the boulder and the staff. Once there, she
casts Mage Hand and a faintly glimmering copy of her own hand descends
slowly until it reaches the staff. It grabs hold.

With a twitch and a shudder, the staff springs to life. It's not a
staff---it is, in fact, the leg of a giant hermit crab. The boulder
turns, revealing a spiral-patterned shell.

``Dang!'' says Tannin. He and the other adventurers jump backward into
the bamboo hallway and slam the seaweed door shut.

``What about Galadriel?'' hisses Hermione.

``She's on the ceiling, she's fine,'' whispers Hanamir. ``For now,'' he
amends.

``So what's our plan?'' says Harlan. ``Do we try to communicate, or go
straight to force?''

``Unshackle me!'' says Magic, breathlessly, unaware that she's being
ignored. ``Let me in there! I'll destroy them instantly and save the
music girl!''

``I can cast Speak with Animals,'' says Tannin. ``But it's a
ritual\ldots{} and it'll take ten minutes.''

``Get started, then!'' says Harlan.

Tannin procures a tightly bundled bunch of herbs and a flint stick from
his backpack. He attempts to light a flame.

``Whoops,'' he says, getting some smoke. ``Just a sec.''

``I think it's speaking in a human voice,'' says Hanamir, his ear to the
door again. ``Will Speak with Animals still work?''

``It should,'' says Hermione. ``It must be speaking Olmen! That's the
ancient tongue of the Ixquichpehua---I read all about it---and that
crab, that must be one of the gods they worshipped---''

``Like, that right there is the actual god, or---?'' says Tannin,
looking up from his materials.

``Do the ritual!'' says Harlan. He opens the door a crack and tries
miming the phrase ``wait just a few minutes, please'' at the giant angry
crab, to no avail.

When the ritual is finally complete after a brutally slow ten minutes,
the adventurers open the door again to see Galadriel crouched in the far
corner of the ceiling, very much like an actual spider, using her
still-glowing Mage Hand to slap the crab's claw cheekily each time it
makes a futile grasp at the air beneath her.

``Have you eaten my friend yet?'' says Tannin, his voice ringing out
confidently in a language no one else understands. The crab stops
pinching at the air and turns its stalked eyeballs toward him.

``Who is this?'' the crab's voice booms back at him. ``Who dares enter
the Temple of the Guardian? Be off with you! Before I lose my temper!''

``Cool, cool,'' says Tannin, mostly to himself. ``Uh, we'd love to get
out of here, sir. Can you direct us to the exit?''

``Begone whence you came!''

``We tried that, but there's a cave in,'' says Tannin. He raises his
eyebrows and gives a tentative thumbs up to the other adventurers. ``Any
other ways out?''

The crab snaps its claws inscrutably at its crayfish companion. They
confer for a moment.

``If I let you pass, you must touch nothing in my Temple,'' says the
crab.

``Deal!''

The crab lowers its claws, and calls off the crayfish from its frenzied
tapping against the wall beneath Galadriel.

``Hey Tannin!'' Galadriel shouts down. ``Can you tell the crab I'm sorry
I grabbed his leg? I thought it was a stick. Totally my bad!''

Tannin translates this to Olmen. The crab, surprisingly, looks like he's
going to be cool about it.

``Tell her if she comes down now, all is forgiven,'' he says.

``He says it's chill!'' Tannin yells back. Galadriel creeps down from
the ceiling slowly, rejoining the other adventurers by the door.

``Tell him thanks,'' she says, appearing to really mean it. Her face is
paler than usual.

``May I lay a claw on you?'' the crab asks Tannin, its eye stalks
looming in close.

``Uhhhhhhh,'' says Tannin, panicking. ``No\ldots{}'' He looks around for
help from his companions, but then remembers no one else can understand
the crab. ``\ldots No.''

``I understand.'' The crab draws its eyes back, turning its body away
slightly.

``Wait,'' says Tannin. ``Why?''

``I thought I might try to help,'' says the crab. The hostility is gone
from its voice.

``Okay, sure,'' says Tannin. His face has a hint of the mischievousness
that his companions recognize from the moments in battle immediately
preceding a Barbarian Rage. They each hold their breath. ``Sure, go
ahead.''

The giant crab lowers a heavy claw onto Tannin's shoulder.

``Now you understand our language,'' he says, ``without the need for
your silly spell.''

``Whoa,'' says Tannin. It's true: the language feels clear in his ears
now, like natural speech, rather than like an echo through a seashell.
``Thanks!''

``Yes,'' says the crab. He lifts his claw from Tannin's shoulder and
points it toward a narrow corridor behind him. ``That is the way out.''

``Like, it goes up outside the pyramid?''

``The stairs lead down, but eventually\ldots{} up.''

``Okay,'' says Tannin. He motions for the others to follow him. ``We'll
go that way then. Thanks again.''

He gives the crab a quick wave, and then the crayfish a polite nod of
his head. He leads the adventurers across the muddy floor toward the
hallway. The large crustaceans watch them pass in silence.

But the hallway only gets muddier as it slopes gently downward. The door
at the end of the hallway is blocked by a good two feet of heavy, wet
silt.

``Hmm,'' says Tannin.

He splashes noisily back to the crab room. ``Hey, uh, sorry to bother
you again, but this door down here? It's pretty blocked.''

The crab clicks its claws wordlessly.

``So\ldots{}'' Tannin looks around. ``Is there another way out?''

``Yes, yes, try the other hallway. On your right.''

``Both of them lead out?''

``Elsewhere, first,'' says the crab. ``Then out.''

Tannin gulps audibly. He turns to go, then swivels back again.

``Sorry, just one last thing. Could you give my friend from the ceiling
the gift of Olmen speech too? Or instead of me, maybe? She's more of a
talker, and\ldots{}''

``You have what you need,'' says the crab. ``Be on your way, now.''

``Okay,'' says Tannin. ``Oh! And, if you see us again, it's just because
we got blocked and had to turn around, not because we're disrespecting
you or your very good temple in any way. Okay. Bye!''

He plods back down the corridor, where the other adventurers wait,
wide-eyed. Only Buddy seems to be enjoying the abundance of mud.

WOW. SIMPLE DELIGHTS, GALADRIEL. GOTTA MAKE TIME FOR THE LITTLE THINGS,
YOU KNOW?

He rolls onto his back and snorts a mud bubble at Magic, who frowns.

\emph{Careful}, thinks Galadriel.

WHAT? THIS IS WHAT PIGS DO.

``All right, folks,'' says Tannin. ``They say there's another hallway we
could use, but if this is the one they recommended first, I think we
should just do this one.''

Hanamir inspects the door's visible hinges.

``Could be done with enough force, perhaps,'' he says. ``But it may be
worth our while to check the other way.''

``Nah,'' says Tannin. ``I'm gonna just Shape Water again and get all
this crap out of the way.''

Without hesitation, he sends a wave of force through the silt. Solid
ground appears in the center of the hallway as the sludge parts, rising
in parallel waves along each wall. Quickly, Hanamir tests the door
handle. It budges. With a heave, he pulls the stubborn door open, and
they hurry through it as the mud collapses back to the floor behind
them.

``Nice work,'' says Harlan, shaking some silt off his boots. ``You're
really thriving in this leadership role, Tannin.''

``Ah, shut up,'' mumbles Tannin, blushing faintly.

They look around. They are now standing on a rocky beach next to a pool
of glowing water that laps gently against the dark sand. Green fronds
float on its surface. The room itself is cavernous, with walls of rough
stone. Directly across the pool is a set of doors carved with a sun
symbol.

``Any linguistic insight on that symbol? I assume it doesn't have a
literal Olmen meaning for anything besides the sun?'' Harlan asks.

``Just a picture of the sun, I think,'' says Tannin. ``Oh! But\ldots{} I
understand the name of the quiznos now.'' He looks at Magic, shiftily.
``It means\ldots{} `plane-splitter.'\,''

``Ah,'' says Harlan. ``Great.''

``About that door, though,'' says Hermione. ``How should we do this?''

``Want me to crawl along the wall and check it out?'' Galadriel asks.

``Just a second,'' says Hanamir. ``I don't trust this water.'' He
procures his ten-foot pole and dips it into the pool.

A shape flickers under the surface of the water, and with the sound of
an aquatic squeal, a young woman emerges from the center of the pool.
Her golden hair and youthful face radiate light from the surface of the
water, and she holds a dark blue shawl around herself. She begins
singing in a language that even Tannin does not understand. Still, he's
the only one with a real shot at communicating with her. Galadriel
nudges him forward.

``Ma'am?'' says Tannin. ``Uh, hi. Sorry to disturb your pond,
ma'am\ldots{} and your song, very nice singing, by the way\ldots{}''

The woman stops singing and fixes him with her gaze. The adventurers
notice that they can't see the half of her body that is still beneath
the pool's surface. She responds to Tannin in Olmen.

``My name is Dasani,'' says the woman. ``Who are you? Why are you
here?''

``We stumbled down into this dungeon, and, well, we're trying to find
our way out,'' Tannin starts.

``Dungeon?'' Dasani's eyes narrow.

``Temple! I mean temple,'' Tannin says quickly. ``Sorry. I'm not a
native speaker.''

``Oh,'' says Dasani. She lowers her eyes and points to a narrow ledge
along the wall. ``You are free to pass through my room.''

Hermione tugs on Tannin's sleeve.

``You have to translate, or else we can't help you here,'' she whispers.

``Oh, right,'' says Tannin. ``She says we can pass. She seems pretty
cool.''

``You wanna ask her anything about the rest of the pyramid?'' suggests
Harlan.

``Okay,'' says Tannin. To the woman in the water, he says, ``You know,
I'm a fan of water, too. Very nice pool you got here.''

``Thank you,'' says Dasani. ``You're welcome to join me for a swim, if
you like. Though my pet might bug you a little.''

``Ah, thanks, I just might. And don't worry. I'm \emph{very} comfortable
with all kinds of sea creatures,'' Tannin chuckles. ``Anyway, how'd you
end up in here yourself?''

``Me?'' she giggles, hugging her shawl tighter around her shoulders.
``I'm an agent of Zotzahal, god of bats.''

``Ahh, nice! Funny story---one of my friends is a giant bat named Zotz.
Probably not the same guy, though.'' Tannin looks around, running out of
things to say again. ``So\ldots{} how do you spend your time down
here?''

``I help protect the treasures of this temple, for it was built to honor
Zotzahal, among other holy creatures.''

``Sweet,'' says Tannin. ``Well, I guess we'll be passing through now,
along the ledge, like you said.'' He glances at a dark shape beneath the
surface, moving near the periphery of his vision. ``I mean,
actually\ldots{} first, I want to take you up on that swim!''

He drops his backpack and dives in. Dasani disappears beneath the
surface, her shape nowhere to be seen, though they can all still see
Tannin, as well as something else undulating in the depths.

Tannin points his trident at the dark shape and actually uses it for its
Fish Command purpose for the first time in ages.

``Ha!'' he exclaims in Aquan. The creature is under his command. He
beckons with his trident for it to come closer to the surface. A giant
eel emerges, emitting a faint buzz of electricity. The hair on Harlan's
arms stands on end. Tannin transfers his consciousness to the eel and
looks down at the bottom of the pool through its eyes. The floor is a
beautiful crystalline cave, littered with gold and other treasures.

But Dasani is still invisible in the water. Tannin can hear her giggling
again, and this time it sounds malevolent. Something in the water next
to him is bubbling unexpectedly---it's very hot---suddenly, a boiling
wave pushes him out of the pool and back onto the rocky sand.

``What gives?!'' cries Galadriel. Then she thinks, \emph{Buddy, any idea
what her deal is?}

SHE'S A NARID. BUT THIS ONE SEEMS A LITTLE\ldots{} OFF. NARIDS USUALLY
DON'T BOIL PEOPLE.

She casts Mage Hand once more and directs the spectral appendage to
plunge into the pool until it reaches the crystalline floor. It gropes
around blindly for a moment, and then reemerges with a small silver idol
in the shape of a bird. It drops the idol at Galadriel's feet.

Dasani's voice reverberates off the cavernous walls, and she reappears
in the center of the pool. Her face is a mask of rage.

``Who dares plunder my treasure?!''

The words are meaningless to Galadriel, but she gets the idea
nonetheless.

``You started it!'' she yells back. ``We were just going to pass through
peacefully, and then you boiled Tannin!''

But Dasani does not care who started it. She wrings out a section of her
deep blue shawl in Galadriel's direction, and out bursts a spray of
acid. Galadriel is hit and blinded immediately, her eyes dripping blood.

``Release me!'' murmurs Magic, jumping up and down on her toes. She
pleads with Hermione. ``Release me, and let me take care of this thing!
It'd be so easy!''

``Shhh,'' says Hermione, dragging her away from the gory aftermath of
the boiling wave and the acid.

Harlan casts Thunderwave, knocking Dasani out of the water and onto the
rocky ledge. The ceiling trembles at the thunder's force, and dust rains
down on them all.

``Careful with that,'' says Hanamir. He takes the destabilizing moment
to sprint along the ledge and land a piercing blow to Dasani's abdomen
with his sword.

Recovered enough from his scalding wounds, Tannin flies into a rage. He
races across the surface of the pool---his feet never sinking more than
an inch---and impales the narid in the stomach with all three spokes of
his trident. It is a mortal wound, but she lives yet.

``If you spare me,'' she croaks, ``I'll let you take all the treasure in
this room.''

From the beach, Harlan interjects.

``Well?'' he says. ``What do we think about this?''

``We don't!'' snarls Galadriel, her face a horror-movie mess.
``Obviously!''

``It's worth considering,'' says Harlan. ``Since then we wouldn't have
to deal with the eel, and we could just pass through\ldots{}''

``Ha! She said we could pass through originally, and look what
happened.'' Galadriel spits out some blood that has pooled in her mouth.
``All right, now point me in the direction of this idiot and let me
handle it.''

Bewildered, Harlan pivots Galadriel so that she is facing Dasani.

``Guys! Duck!'' she calls out. A cloud of daggers appears in the air
above her. Tannin and Hanamir jump out of the way just in time as it
descends with brutal force on Dasani, ripping her to shreds.

``Nice,'' says Tannin. He tosses Galadriel a piece of bread from the
Satchel of Eternal Hunger. ``Eat up.''

The bread bounces off her face and falls to the ground. Harlan picks it
up and hands it to her.

``Thanks,'' says Galadriel. She eats it ravenously and is healed before
their eyes. Her expression remains murderous.

``So, what now?'' says Hermione. She nods at the shape of the eel
beneath the surface of the pool. ``You think we can all get across
without that guy zapping us?''

``I'll take care of it,'' says Tannin with a shrug. He dives back into
the water and tridents the eel, dragging it with him back to the
surface. Galadriel nocks an arrow and sends it piercing through an eel
eyeball straight through an eel brain. For reasons she can't quite
place, it brings back a feeling of nostalgia.

``Good work, team,'' says Hanamir. He tiptoes back across the ledge to
the beach and puts an ear against the door to the hallway that connects
to the crab god room. ``Hmm. I don't think they liked that Thunderwave
too much. Lots of agitated clicking sounds back there.''

Harlan shrugs. ``How about that treasure, then?''

Still in the water, Tannin produces his net. ``Coming right up!''

He dives down to the floor of the pool and gathers everything into the
net. He hauls it back out and deposits it all on the rocky beach.

``Let's see here,'' says Harlan eagerly. He picks up a small golden
figure of a reptile. ``These six little guys look expensive! Same with
the gold mask. We should see if \href{/characters/sanford/}{Sanford} and
Son want them.'' His smile fades. ``If we make it out of here, anyway.''

Galadriel inspects a silver idol that matches the one she originally
stole with her Mage Hand. It is, in fact, a bottle, filled with a
pungent yellow liquid and a single, floating eyeball. Over her shoulder,
Hermione gasps.

``That's a Clairvoyance potion!'' she says. ``I've seen those before.
Great find.''

The only remaining item is an ordinary-looking pair of gloves. Hanamir
puts them on.

``Aha!'' he says. ``I have the overwhelming feeling that, if a small
projectile were to fly by me, I'd be able to snag it from the air
easily. These must be Gloves of Missile Snare.'' He turns to Harlan.
``These might be of use to you on your aerial steed, Harlan.''

``Indeed!'' says Harlan. Hanamir takes off the gloves and passes them to
Harlan, who pockets them. ``Appreciate it.''

``Onward, I guess?'' says Tannin. He looks toward the door with the sun
symbol carved into it.

``Yes,'' says Hanamir. ``Follow me.''

And the adventurers pass, single file, along the rocky wall by the pool,
past the dead narid, deeper into the dungeon.


\chapter{Mortui Quiznos Docent}
\chapdesc{The dead teach the living, but they'll never graduate.}

The corridor beyond the narid's pool room is flooded. The water that
sloshes against their legs and soaks into their boots is icy cold, and
far too deep for \href{/characters/buddy/}{Buddy} to walk through
comfortably, so he resumes his old post peeking out of
\href{/characters/galadriel/}{Galadriel}'s backpack.

The adventurers round a corner and the flooding abates somewhat. A short
set of stairs leads out of the damp and up to a set of bronze doors.
\href{/characters/hanamir/}{Hanamir} approaches first.

``Looks unlocked,'' he whispers. He presses an ear to the doors'
surface. ``Nothing moving on the other side that I can hear.''

The adventurers hesitate, then nod at him to proceed. Hanamir pushes the
door open gently. It opens into a long, empty room---about a hundred
feet of dusty stone floor lined by mosaic-laden walls. Galadriel puts
Buddy down again, and he trots off to sniff the seam between the floor
and the wall.

``These are incredible,'' says \href{/characters/harlan/}{Harlan},
scanning the mosaics. ``Such detail in the battle scene, and very little
damage despite the obvious antiquity\ldots{}''

At the end of the room, another set of bronze doors leads to a
crossroads of hallways. In the center of the crossroads are four
statues: a bear, a coyote, a bison, and an eagle. Something shiny glints
in the eagle's mouth. Hanamir takes the ten-foot pole and carefully
knocks it out. The statue's mouth snaps onto the end of the pole.

``Ah!'' says Hanamir. ``Ten-foot pole, what would I do without you?'' He
inspects the newly-ragged edge. ``You're an eight-foot pole now, but you
know what? You're my best friend.''

He bends down and collects the shiny thing that clattered to the ground.

``A bracelet!'' He puts it on. His eyes widen. ``I think\ldots{} I'm
immune to petrification. And I can cast flesh-to-stone.'' He smiles.
``Beautiful \emph{and} functional.''

``All right,'' says Harlan. ``Let's check these corridors out and decide
where to go next.''

The corridor to their right is narrow and dark except for a faint light
several yards down that bobs and flickers in midair. The hallway looks
shabby, as if forgotten by the temple's ancient custodian, or simply not
meant for people to see.

``Not my first choice,'' concludes Harlan.

The other corridor---much more civilized-looking---leads to an alcove
with a pedestal at the end, and a silver coffer resting on top of it.
Hanamir approaches it and, seeing that it is unlocked, pushes it open
with the eight-foot pole. A copper figurine rests inside. It is in the
shape of some kind of humanoid sea creature, almost like a narid.

\href{/characters/hermione/}{Hermione} picks it up and inspects it.

``It's hollow,'' she says. She gives it a shake, and they hear the sound
of small particles shifting inside. ``Filled with\ldots{} beads? Or
rocks? And it's definitely giving off a magical aura.''

She turns it upside down.

``Elvish! It's inscribed with a name---Ilnidra---though that doesn't
mean anything to me.'' She glances at Galadriel, who shakes her head.

``Can I hold it?'' Galadriel asks. Hermione passes the figurine over.
\href{/characters/magick/}{Magick} looks on with transparent envy. ``I
wonder what the beads inside are for. What happens if I take one out?''
She pops open a hinge at a seam in the bottom of the statue, and picks
out a bean-shaped bead the color of a hazy sunset.

At once, the statue leaps out of her hand, spilling the remaining beads
all over the floor. It zooms back and forth through the air, knocking
against walls until finding its way down the hallway toward the cramped
and dark corridor with the pulsating light.

``What was that?!'' says \href{/characters/tannin/}{Tannin}, gripping
his trident. He is tensed, like a puppy resisting the urge to chase a
tennis ball. ``Do we follow it?''

``I think we have to, now,'' says Hermione, with some exasperation.

``I didn't know that would happen!'' says Galadriel.

``Oh, nah, let's forget about it,'' says Hanamir, approaching the next
set of doors with pole in hand. ``Easy come, easy go, right?''

He's the only one who takes this cavalier attitude, however, and he is
quickly overruled.

Galadriel leads them back toward the narrow passageway with the glowing
light. It bobs ahead of them, with no sign of the floating figurine.

``Your light awaits,'' Hanamir says, in an unusual burst of sass. He
bows to Galadriel, shirking his usual leadership responsibilities.
Galadriel rolls her eyes.

``Honestly, one hallway is as just as good as another,'' she mutters.
``There'll be something deadly no matter where we go.''

``Those are some good last words, Gals,'' Hanamir chirps. Harlan and
Tannin snicker.

Galadriel walks ahead toward the light. It dances in the air, then moves
backward as she moves forward. It leads them down the hallway until it
disappears around a corner. There, the corridor widens, and the
adventurers see a pit in the floor. Beyond the pit is a wedge-shaped
block that lies in the way of the entire space, floor to ceiling, ahead.
The light bobs away and disappears behind the wedge.

``Skeletons in the pit,'' says Magick, unprompted. She is taller than
the rest of them, and is peering down into the empty space ahead. ``Two
skeletons. Humanoids. Ten feet down.''

``Great,'' sighs Hermione. ``I think maybe we stop here and turn back.''

``Unshackle me?'' says Magick. ``For helping?''

``No,'' says Hermione.

Hanamir takes a copper coin from his bag and chucks it down into the
pit. They hear it clink against the floor unremarkably.

``I'll climb in and see what I see,'' says Galadriel.

She spider climbs down the nearest wall of the pit and then approaches
the skeletons cautiously. They are long-dead, perhaps even ancient. One
of them is probably human, and one has the distinctive skeletal markers
of an elf. Galadriel has a distinct feeling that she's seen enough when
she gets a better look at the scratch marks on the surfaces surrounding
the skeletons. She climbs back out onto the other side of the pit.

``Exactly what it looks like,'' she says, dusting herself off. There is
enough space on either side of the pit for the other adventurers to
pass, but they remain on the opposite side. ``Are you guys coming or
what?''

``There's a giant block in the way,'' says Harlan. ``We could break
through it with a spell, but we don't want to risk the ceiling caving in
on us, right?''

Galadriel leans her weight on the block.

``I think it swivels, actually,'' she says, straining. ``I'm not very
strong, but I think two of us could do it.''

``All right, then,'' says Hanamir. Galadriel has proven to him that
she's willing to pursue the mysterious statue (and the floating light)
as far as it takes, so he might as well get on board. He tiptoes past
the pit in the floor and joins her in pushing the block so that it
shifts on its axis, far enough to create a gap between the wall that a
humanoid could fit through.

``Here goes,'' says Galadriel. She slips into the gap, followed by
Hanamir.

``You three stay back for now,'' says Harlan, holding up a hand. He and
Tannin cross to the other side of the room, leaving Hermione, Magick,
and Buddy huddled together by the corner turn. Hermione looks less than
pleased.

Beyond the wedge, Galadriel and Hanamir see the floating light. It no
longer keeps its distance, and it flickers as if laughing. It swoops
through Hanamir. He feels his indigestion clear up, but no other adverse
effects. Instead, he makes a quick hit with his short sword and feels it
connect with something corporeal, a thickness in the air for a second,
but then misses it with his unarmed attack. Galadriel's rapier slices
right through the air with no contact.

The wedge shifts again, and Harlan and Tannin appear. The light plunges
through Tannin's chest as he enters, and it looks like Tannin has been
shocked---his hair stands on end, crackling and emitting a smoky odor.
Hanamir swings at the light again with his sword and misses; Harlan does
the same with his hammer.

``I'm starting to think my first one was just a lucky hit,'' Hanamir
says.

``Time to switch gears,'' says Galadriel. She turns to the light,
squinting at the blaze in the dark. ``Hi. I'm Galadriel. Who am I
speaking with?''

A voice fills the corridor, speaking an antiquated, echoing Elvish.

``A guardian. I protect this area of the temple. I have done so since my
death here on an expedition many years ago. Begone!''

``Are you an elf?'' says Galadriel. ``Are you\ldots{} Ilnidra, from the
inscription?''

``My name is Will,'' says the voice.

``Oh. We're sorry to have disturbed you, Will,'' she says. ``Where are
you from?''

The light pulsates angrily, ignoring the question.

``What is your business here?''

``Just like you, my friends and I are on an expedition here,'' says
Galadriel. ``We mean no harm. We were pursuing you because we found a
statue that floated this way, and we wanted to learn its significance.
We didn't mean to intrude on your territory, and we're sorry.'' She
pauses. ``Did you see it go by?''

``That statue is one of many traps here,'' says the voice of Will. ``If
you're here to raid this place like I was, I must see that you meet the
same fate.''

``Interesting,'' says Galadriel. She casts Suggestion. ``What if you
decided instead to prevent the same tragedy that befell you from taking
any more lives? What if you let us pass, and ended the cycle of violence
here?''

The light wavers in the air, then emits a softer, warmer glow.

``Although I have trapped many in this corridor\ldots{} I suppose you
may pass. Be careful.''

``Thank you, Will,'' says Galadriel. ``And best of luck protecting your
area in the future. We wish you well.''

The light bobs as if bowing, and then zooms back through the wedge,
presumably to resume its original post.

The adventurers signal to Hermione that it's safe to proceed. She leads
Magick and Buddy past the pit and the wedge, and the group ventures
onward.

The next passageway has an abundance of traps, both hidden and
already-deployed. Hanamir triggers several of them with the eight-foot
pole, while Galadriel scours the walls for any hidden switches. There
are several more stone pressure plates in the ground, but the group is
better at noticing these now, and sidesteps them easily. There is a
dusty, sandy material trickling from significant cracks in the ceiling.
It sits in piles on the floor.

Hanamir continues throwing copper coins down the hallway ahead of them
in case of motion-sensing traps, but it seems like the worst of the
traps have already been deployed. They reach the next set of doors and
pass through without much ado.

The next room is filled with foul, bitter-smelling air and has a few
piles of rubble and bones around its perimeter. There are tiny lights
moving on the floor.

``Beetles,'' says Harlan, peering down. One of the glowing bugs crawls
over his boot. ``I bet that's their nest.'' He points at a cluster of
lights in the corner. There's something shiny beneath them, reflecting
their light.

``Do we want to see what's in the nest there?'' muses Hanamir. ``Or
continue through one of these doors?'' He waves at a door to the north
and a door to the south.

``Might as well get some treasure,'' says Tannin. He stomps on a beetle,
and it leaks glowing fluid onto the floor. ``They're just bugs.''

``Are we sure they're just bugs?'' says Galadriel. ``Hermione, can you
identify them?''

But Hermione is busy dealing with Magick, who has put a beetle in her
mouth and refuses to spit it out, and disregards the question.

Harlan borrows the eight-foot pole and pokes at the nest of beetles. A
few of them object to this and sink their pincers into his toe. But they
do seem to be simple bugs, and they're demolished within a few minutes
of the adventurers tap dancing around the room. A few stragglers
disappear into the cracks in the walls, and they are left alone to dig
through the rubble.

Tannin tosses some pieces of rotten wood and cloth out of the way.

``Some pretty rocks,'' he reports. He picks one up. ``Is this
turquoise?''

``Looks like it,'' says Harlan. ``Add it to the Bag of Holding.''

Tannin dumps it in.

``A dagger!'' he says next, holding up a prodigiously rusty piece of
weaponry. ``Feels like this does more damage than a regular dagger. Must
be enchanted.''

``Yeah, enchanted with tetanus,'' says Harlan. He shakes the Bag of
Holding. ``Into the bag, if you must.''

There's not much else of note other than a broken crystal and some
polished, less-valuable rocks. Hanamir is already distracted, checking
out their door options.

``This one's interesting,'' he says. He points to the doors with an
Olmen inscription above them. ``Tannin, can you read this?''

``Uhhh,'' says Tannin, walking over to the door and glancing up. ``Yeah.
It says, `Beware, the many-eyed god will bring down a fiery death.'\,''

``Hmm,'' says Hanamir. He prods at the door handles. ``Shall we?''

``Seriously?'' Galadriel laughs.

``One hallway's as good as another, right?'' he smirks. ``Something
deadly no matter where we go?''

Galadriel scowls.

They enter a stone chamber containing two above-ground tombs. Upon each
tomb lies a human figure, and between them is a stone table with a
crystal flask and two crystal goblets. The room is silent as the grave.

The figures appear to be made of living flesh, but are unconscious, and
have been for a very long time---they are covered in an inch or more of
white dust. Harlan goes to inspect the goblets on the table.

``There's some type of silver powder in here,'' he whispers. ``Like, a
powder that looks different from the dust, I mean. Glittery.''

Hanamir puts his face up close to one of the figures.

``Looks like they're wearing snakeskin under all this dust,'' he
murmurs. ``The female figure here has a bracelet made of platinum, I
believe, and is holding an ivory wand\ldots{} the male figure wears an
amulet with a large red stone of some kind. My guess is these two drank
out of those goblets, and then lay down here, and haven't gotten up
since.''

``Mage Hand?'' Tannin whispers to Galadriel. ``We could wait in the
beetle room and see if they react if we take anything\ldots{}''

Galadriel nods. They all tiptoe back to the foul-smelling room and watch
as the ghostly hand floats toward one of the sleeping figures. The
bracelet slips easily off the woman's wrist, but this does appear to be
enough of a disturbance to end a centuries-long nap.

The man rises in a cloud of dust. The woman sits up.

``I am Cipatkonau,'' says the man, speaking Olmen. ``This is Oxomoko.
You have broken our glorious slumber.''

``What's he saying?'' hisses Harlan. Tannin translates.

The man says one more thing, and Tannin looks at his friends shiftily.

``Um\ldots{} he wants to know how we plan to atone,'' he says.


\chapter{Quiznius, Altius, Fortius}
\chapdesc{Thinking faster, climbing higher, cheating at sports.}

\href{/characters/tannin/}{Tannin} walks over to the pillow on the end
of one of the raised tombs and gives it a little fluff.

``Go back to sleep now,'' he says. ``Sorry to wake you. We're just
passing through.''

The two figures are still coated in enough dust to lend a stony, ghostly
cast to their skin. They do not react to Tannin's reassurances, so he
continues.

``I could tell you a bedtime story, if you want,'' he says. ``Or my bard
friend here could play you a lullaby?''

The two figures confer with one another. Then the woman speaks.

``Perhaps for a gift, we'd be willing to let you pass.''

Tannin translates this to his friends.

``You know, some people say my songs are a gift,'' says
\href{/characters/galadriel/}{Galadriel}.

``I already offered that,'' says Tannin. ``I think they want actual
treasure.''

``Some people say my \emph{songs} are an actual treasure---''

``Let's see if they want that cask of wine in the Bag of Holding,'' says
\href{/characters/harlan/}{Harlan}. ``They already have goblets. They're
probably wine conoisseurs.''

``No! That's special,'' says Tannin quickly.
``\href{/characters/mirama/}{Mirama} gave that to me for good luck. She
told me to only open it when we're on our way back.''

``Fine,'' says Harlan. ``Maybe we give them the turquoise we just found,
then?''

Tannin summons the turquoise from the Bag of Holding and offers it to
the dusty figures. The woman accepts it and shows it to the man. They
seem satisfied. They walk to the stone table and pour some of the silver
dust from the flask into each goblet.

``Wait,'' says Tannin. ``Before you go to sleep again, can you tell us
anything about where we are? We're a little lost.''

``Where are you trying to go?'' says the man.

``Out\ldots{} generally\ldots{} I guess,'' says Tannin. He looks around,
thinking quickly. ``But also we're just like, pilgrims, looking to pay
tribute to historical relics. We've met the crab god, and that was
really cool. Respectfully. Anything else of interest nearby?''

``You are in the lower chambers,'' says the woman. ``This temple is a
three-tiered structure, and all paths lead upwards in the end. These
lower layers serve primarily as tombs for great warriors laid to rest.''
She gazes at Tannin, her eyelashes blinking dust. ``Have you met
Talakepapaklas?''

``Doesn't ring a bell,'' says Tannin.

``He was interred here,'' she says. ``You must heed the warning.
Anything that desecrates his temple\ldots{}''

``Oh, nope, that's not us at all,'' says Tannin, shaking his head. ``We
are not about desecration, not one bit.''

The two figures each sip from their goblets and lie back down on their
tombs.

``Why was he buried here?'' asks Tannin, but they are fading fast.

``He was a great king\ldots{}'' says the man.

Then they are silent and still, their chests not even rising to breathe.

``Well, team,'' says \href{/characters/hanamir/}{Hanamir}. ``That went a
lot better than I thought it would.''

The adventurers return to the chamber that they refer to as the Beetle
Room. There are three exits they have not yet tried. One of them is a
doorless hallway, long and L-shaped. It slopes upward, prompting a
stream of excited babbling from \href{/characters/magick/}{Magick}.

``It'll be up higher, I'm sure of it!'' she says. ``The higher we go,
the stronger it feels. I need you to unshackle me so that I can grab it
when I see it---I know I'll recognize it, not even by sight, but by the
feeling in my \emph{heart}---''

But soon the hallway is blocked by a massive boulder.

``Looks like sandstone,'' says Tannin, patting it. ``Doesn't match the
materials the rest of the tomb is built from.''

``Unshackle me,'' pleads Magick. ``And let me blast through it.
Please!''

``No matter how many times you ask, the answer is still going to be
no,'' says \href{/characters/hermione/}{Hermione}. ``I'm not sure how
else to communicate this to you.''

Tannin is now peeking around the boulder through a sliver of empty space
between its edge and the wall.

``I think this was pushed down here from higher up,'' he says. ``Looks
like rollers behind it, like someone brought it here expressly to block
others from coming up.''

``Does it swivel, like the wedge from before?'' asks Galadriel.

Tannin pushes a shoulder against it and heaves.

``Nope,'' he says.

``Let's check one of the other hallways,'' says Hanamir, ignoring loud
protests from Magick.

The next hallway is a terrifying scene. Standing on ledges lining both
walls are twelve withered corpses, unnaturally upright, six to a side.
They obscure some glyphs carved into the walls behind them.

``Uhhhhhh,'' says Hermione, hanging back and clutching Magick's arm.
``Do we even want to bother?''

``This does look like the other end of one of the hallways we saw
earlier,'' says Harlan. ``It might only lead us back to where we've
already been.''

``I'd like to see if Tannin can get a better look at the writing behind
these guys,'' says Hanamir. He prods one of the corpses with the pole.
It creaks to life, moaning, which then wakes its eleven comrades.

``Oh, twelve zombies, that's exactly what we need right now!'' Harlan
shakes his head.

``Hey dead guys! Think fast!'' Tannin shouts. He pops a bead off his
fireball necklace and tosses it in the center of the cluster of undead.
It explodes, reducing the zombies to dust and briefly setting Harlan's
eyebrows on fire. Tannin looks around at the group, beaming with pride.

``\href{/characters/kord/}{Kord} Almighty!'' Harlan yelps, slapping
himself in the face to snuff out the embers.

As he says this, the ceiling begins to shake again. A shower of rocks
and debris knocks into each of them---there's no dodging it. But the
walls stay up.

``All right, read the walls so we can get out of here,'' says Harlan.

``Oh,'' says Tannin. ``It's just another warning about the many-eyed
god\ldots{} fiery death and all that.'' ``Cool,'' says Harlan.

In grumpy silence, the adventurers turn around and approach the last of
their hallway options, which takes the form of a series of short
staircases. The stairs, incidentally, lead up.

``Yes!'' Magick breathes. ``Up we go.''

Hanamir leads the way, poking at each stair with the pole. But, as with
the very first trap they triggered in the hallway leading to the crab
god, they do not hear the click of the pressure plate deploying until
the combined weight of Hanamir and Harlan sets it off.

A massive stone sphere ejects from above them and crashes down the
stairs. With the pole, Hanamir vaults over it. but it rolls directly
onto Harlan and Galadriel, flattening them both. Tannin, Hermione,
Magick, and \href{/characters/buddy/}{Buddy} are close enough to the
bottom of the stairs to jump back into the Beetle Room and out of the
way, just in time.

``Oh dang,'' Tannin says, running back up the stairs to see Harlan and
Galadriel's unconscious and unsettlingly pancakey bodies. ``Who's got
healing potions?'' He pats his flask. ``Oh! I do.'' He pours a little
potion into both mouths, and some color returns to their faces. ``Want
some bread, my dude?'' Tannin asks Harlan as his eyes flicker open.

``As long as I don't have to get it from that bag,'' Harlan mumbles.

``No worries, man,'' says Tannin, passing him a piece. ``Here you go.''
He breaks off another piece for Galadriel. They sit on the stairs for
awhile, the bread gradually shuffling them back onto this mortal coil.

``Short rest?'' says Galadriel. ``If there are no more boulders coming
down the stairs, anyway.''

``I think we're in the clear,'' says Hanamir.

The adventurers sit on the stairs for another hour, recuperating.
Galadriel leans against the wall and pets Buddy, who sits on her lap.

FEELING BETTER? he asks.

\emph{Somewhat. Nervous to fight anything else, though, until we've had
a real rest.}

But within a few minutes, the adventurers gather their things and
continue up the stairs. The yellowish haze in the air gets thicker the
higher they climb. When the stairs give way to a broad landing, they
open out into a spacious, vaulted hall dotted with stone statues of
monkeys.

``Oh, ew,'' Hermione says, glancing at the floor. There are roughly a
dozen dead baboons strewn around beneath the statues in varying states
of decay, and the smell is not great. ``Looks like something has been
eating pieces of these creatures and leaving the rest. I wonder if these
were sacrifices.''

``Scorch marks on the walls, too,'' says Harlan. ``Maybe a baboon
barbecue?''

``Shh,'' says Hanamir, pointing to the end of the room. A spherical
shape is floating in the air above one of the baboon corpses. It has a
single eye and multiple tentacles, and it does not seem to have noticed
the adventurers yet.

``Is that a Behol---'' Tannin starts, but Harlan claps a hand over his
mouth.

``I'm casting Pass Without Trace on us,'' says Hanamir. He closes his
eyes and generates a tiny translucent sphere in his hand, which grows
until it envelops the adventurers. Inside the sphere, they creep
forward, and realize that the sounds of their footsteps have been muted.

They walk slowly across the room, avoiding stepping in baboon remains
along the way. And as they get closer to the floating sphere, they
realize that it is actually made of wood, not flesh.

``Wait,'' says Tannin. ``So it's not real\ldots{} but it's still
floating\ldots{} and taking giant bites out of the dead monkeys?''

They walk past it into the next hallway, staring in confusion. The
wooden Beholder continues chowing down on its prey without acknowledging
them, or indeed appearing to see them at all.

``Anybody itching to back there and figure that one out? No? Okay,
good,'' says Harlan.

The passageway before them is decorated with carvings of people playing
a ball game, each of them holding what looks like a woven basket on a
stick. There is an inscription above them, which Tannin translates
before anyone asks.

``\,`Dare not open the pit unless ye be willing to meet the
challenge,'\,'' he reads. ``Pit? What pit?''

Galadriel swats him on the arm.

``Don't say that unless you want a pit to open underneath us, fool!''
she says.

``The pit, I think, is down there,'' says Hanamir. He points toward the
end of the hall, where there is a round lid with a handle sticking out
of the floor. On the wall above it, there's an indentation that matches
up with the playing court depicted in the carvings.

``Are we willing to meet the challenge?'' Harlan asks. ``Personally, I'm
still not feeling my best after that boulder episode.''

``Agreed,'' says Galadriel and Hermione, in unintentional unison.

``Oh, I don't know, what's an ancient game going to do to us?'' Hanamir
chuckles, waltzing down the hallway. He's already halfway toward the
hatch. The others scramble after him.

``Come on, really?'' sighs Hermione. The prospect of keeping Magick calm
during a sporting event feels overwhelmingly unattractive.

``Really!'' says Hanamir. He pops open the hatch door and gazes down
into the pit. ``Some treasure down there, folks. Some dead people too.
But mostly treasure.'' He smiles a sassy open-mouthed smile at
Galadriel. ``Can I get some Mage Hand help here?''

``Fine,'' says Galadriel. She summons the glowing hand and starts
another round of the world's most dangerous claw-grabber game. With her
first attempt, she picks up a jade statuette.

``I think the ball that goes with the game is down there,'' says Tannin,
sounding more excited than the context calls for. ``Oh! And now it's
floating! Probably because you touched the treasure.''

A heavy black ball rises from the opening in the floor and then drops at
their feet.

``I guess we're doing this,'' says Harlan with resignation. He reaches
down and picks up the ball.

Immediately, the ball zooms through the air down to the other side of
the hallway, bounces off the wall, and rebounds back toward them. Magick
crouches down and covers her ears, making an anxious noise that
increases in volume with every second that passes.

``Missile snare! Harlan! The gloves! Put them on!'' Hanamir urges as the
ball smacks their side of the wall, close to the indentation. The
adventurers all have a sinking feeling about what might happen if the
ball is allowed to score a point. Harlan whips out the Gloves of Missile
Snare. The ball is already rebounding back toward them when he succeeds
in getting one onto his right hand. He holds it up, just as the ball
whistles past his head, and the glove snaps his fingers around the
projectile with unnatural speed.

``Got it! Got it!'' he cries in disbelief. The ball is wriggling in his
gloved hand with a surprising amount of force. ``What now?!''

Hanamir picks up the Bag of Holding and opens it, lifting it up so that
it rests behind Harlan's hand.

``Let go!'' says Hanamir.

The ball flies straight into the Bag of Holding. Hanamir shuts it and
pushes it to the ground, just in case the bag starts flying too. It
doesn't. A grin spreads over his face, and it's contagious. The
adventurers can't believe how clever that was.

``Amazing!'' cries Tannin, leaping up and down. He claps both Harlan and
Hanamir forcefully on the back.

``Is the ball still alive in there?'' Hermione wonders. They open the
Bag of Holding.

``Nope. Just a ball now,'' says Harlan.

``We should make up our own game with it!'' says Tannin. ``Let's grab
the rest of that treasure, though, huh?''

The pit contains several more jade statuettes as well as a spectacular
golden chalice decked with amethysts.

``Doesn't seem to be magical, but it sure is pretty,'' says Galadriel.
It's almost too heavy for her Mage Hand to lift. ``Let's drink that wine
from Mirama out of this thing if we make it out of here.''

``\emph{When} we make it out of here,'' Tannin corrects her.
``\emph{When} we make it.''


\chapter{Panthera Quizno}
\chapdesc{The lion sleeps, but not for long...}

The adrenaline rush of the ball game has the adventurers in a feisty
mood, the trauma of the rolling boulder all but forgotten. They relive
the moment in excited whispers as they tiptoe onward.

``The gloves and the bag? And how we used them both?''
\href{/characters/harlan/}{Harlan} marvels. ``Brilliant. And that was
all you, \href{/characters/hanamir/}{Hanamir}.''

``Ah, it was a team effort,'' Hanamir says diplomatically, through an
irrepressible smile. He scans the next room. ``All right, what do we
have here? Cat room? Looks like a cat room.''

He stands with his hands on his hips and takes in the surroundings as
his companions file in beside him. The room is oddly-shaped, an
irregular hexagon. The southeast wall is carved to resemble the face of
a snarling tiger with hollow eyes. Opposite, on the northwest wall, a
large circular stone calendar hangs above a slab table. There are two
more sets of closed double doors, and the remaining wall space is
decorated with the hanging pelts of jaguars, cheetahs, and lions.

``Definitely a cat room,'' Harlan concurs, walking a slow circle around
the room. He stops in front of a taxidermied wildcat in the center of
the room. It has some stuffing poking out of its head. ``Looks like
somebody tore a chunk out of this guy's ear.''

``Maybe he got in a fight with six-nippled shirtless dude over here,''
says \href{/characters/tannin/}{Tannin}, staring up at a statue of a man
holding a spear and wearing a panther's head as a mask. The statue has a
jagged scar running the length of his chest---which does, troublingly,
have six nipples. He frowns, unable to avert his gaze. ``You know, as a
habitually shirtless person myself, I get it. I do. But if it were me,
I'd keep that situation under wraps.''

More stuffed cats are scattered around the room, frozen in sitting,
pouncing, stalking, and begging poses.

``Before we do anything that might cause these creatures to wake up,
let's do a thorough trap check,'' says
\href{/characters/hermione/}{Hermione}.

\href{/characters/galadriel/}{Galadriel} climbs up the side of one
fur-decked wall and runs the perimeter along the ceiling.

``The tiger face wall might be something,'' she says. ``I can't tell how
to trigger it, though.'' She creeps around to the stone calendar in the
opposite wall. ``There's something behind here! Like a gate closure sort
of thing? Maybe if we stuck the pole between here and the wall\ldots{}''

Hanamir lifts up the eight-foot pole and passes it to her.

``Okay, careful,'' says Hermione. ``Let's back up somewhere in case
arrows shoot out of all the walls or something.'' She ushers
\href{/characters/magick/}{Magick} and \href{/characters/buddy/}{Buddy}
back behind the cover of the hallway they entered through.

Galadriel slides the pole behind the stone calendar and nudges a latch.
The circular stone swings open like the door of a safe, revealing a
narrow passageway behind it. Another table sits directly inside. On the
table's surface rests a small jade statue---of a cat, naturally---along
with a knife. She squints into the darkness. It's cramped, but they
could fit inside if they wanted to. There's another set of doors at the
end of the passageway.

``More glyphs on the walls in here!'' she reports. ``Tannin, come
look.''

Tannin drags his feet on his way over.

``\,`Caution\ldots{} turn back\ldots{} no tresspassing,'\,'' he
translates. ``There are some symbols of abjuration, too. The vibe is
definitely `keep out.'\,''

``This must be a table for sacrifices,'' says Harlan. ``That knife looks
ceremonial.''

``Do we take the jade cat?'' says Hanamir, eyebrows raised. ``Probably
worth another thirty gold.''

``Guess that's what we do,'' says Galadriel. She climbs down to the
floor of the passageway and picks up the jade cat. ``Now, my money's on
the cat man coming to life riiiiiiight---''

A roar rings out in the main room. Hanamir's short sword is already
lodged in the cat man's upper back. Harlan follows up with a savage
swing of his hammer, knocking the part-feline individual to the floor.

``We are getting better at this,'' Galadriel notes approvingly.

As he hits the ground, the cat man morphs into a full-on panther. The
fur on its front is patchy, corresponding with the scar that had been on
his chest.

Tannin takes a running leap at the panther and lands trident-first on
its back. Harlan gets another hit with his hammer.

``Oh man, this actually really sucks now,'' says Galadriel, loosing an
arrow at the cat with a grimace. ``I didn't come here to murder
endangered animals!''

The arrow hits close to the panther's scar. It roars again and digs its
teeth into Tannin's side.

``It's about to murder an endangered Tannin!'' Tannin retorts. He rights
himself and gets a good headlock grip around the panther's neck and
pulls backward. It snaps. He drops the panther's body to the floor and
stares at it a moment, waiting to see if it'll transform back into a
human hybrid. It does not.

``You know,'' says Harlan, ``in his cat form, he looks a lot like the
stuffed cat in the middle of the room.''

He inspects the stuffed cat more closely, especially the missing ear.
Experimentally, he picks the entire thing up.

``Oh! There's definitely something inside here,'' he says. He pulls some
stuffing out of the rip and digs a hand in. ``Ew, it's slimy. Wriggly.
Probably should have used your Mage Hand, Galadriel\ldots{}''

When his hand comes out, they all gasp. He's holding a bloody, throbbing
human heart. Everyone is silent for a moment, listening to its rapid
pulse.

``Okay, I'll say it,'' says Tannin. ``Should we eat this?''

``What? No!'' says Harlan. He holds the heart out as far away from
himself as he can. ``Why would we eat it?''

``To absorb its powers,'' says Tannin. ``Obviously.''

``No, no, no,'' says Harlan.

``It could be a sacrifice,'' says Hanamir. ``Does
\href{/characters/kord/}{Kord} accept sacrifices as payment for
divinations? Or general life advice?''

``Kord has no need for that kind of morbid exchange,'' Harlan shudders.

``Lolth might like it!'' says Galadriel. Harlan gives her a look. ``Just
kidding, of course,'' she says with a nervous laugh.

``Well, I do think we should stab it, even if we don't do so in honor of
a god,'' says Hanamir. ``My hunch is that it's the actual life force
behind our panther foe.''

``Pass it to me,'' says Galadriel. ``I'll use the ceremonial knife over
here. It's cool.''

Harlan walks over to where she sits on the middle of the wall next to
the open calendar stone and hands her the heart, shuddering.

Galadriel places the heart on the stone table inside the passageway. It
twitches rhythmically. She holds the knife over it, hesitating.

\emph{Hey, um, Lolth? If you're listening\ldots{} I wanted to say thanks
for all the gauntlet stuff.}

She brings the blade down, piercing the heart. Blood erupts over her
hands and onto the table and floor, pooling at her feet.

WHOA. YOU SURE ABOUT THAT ONE, GALADRIEL? Buddy's voice says in her
head.

\emph{Not really}, Galadriel admits. She can already feel Lolth's
approval. A warm, powerful energy is spreading from her gauntleted wrist
in tendrils that crawl up her arm and into her own heart. It
feels\ldots{} good? But kind of bad\ldots{} but mostly good! She shoots
Buddy a ``guess we'll see what happens'' look.

``Aha, I knew it,'' says Hanamir. The slain panther crumbles to dust at
Tannin's feet. ``This must have been the reason behind his scar.''

Meanwhile, Hermione is struggling to keep Magick from headbutting one of
the sets of double doors in her eagerness to move on.

``Release me release me release me release me---'' Magick repeats under
her breath in between thwarted lunges at the doors. ``Foolish elf! We
are so close---my mission nears its end---''

``Hope you all are having fun over there,'' Hermione says loudly,
glaring at the other adventurers.

``Thanks, we are!'' says Tannin. ``Let's check out the tiger face wall
now. I bet there's something cool behind it. So far this room only had
that one tiny piece of jade.''

``It's probably something about the eyes, right?'' says Hanamir.
``They're concave while the rest of the shapes on the wall are convex.''

``Okay, Professor \emph{Nerd},'' Tannin says. ``You gonna poke the eyes
with the pole or what?''

``Yes,'' says Hanamir. He prods the left eyehole with the eight-foot
pole and stands back. With a low rumble, the entire stone carving slides
into the adjacent wall, revealing a wide corridor with glowing magenta
walls.

``Ooh,'' says Galadriel. She hops out of the sacrifice passageway and
joins the rest of them. Magick even stops berating Hermione for a second
and they all peer down into the hallway with very cool lighting.

``Shall we?'' says Hanamir.

He leads them forward cautiously. After about fifteen feet, the floor
disappears into a wall-to-wall pit that spans another forty-five feet
ahead. There are a few planks across the pit, roughly every five feet.

``Pretty deep,'' Hanamir assesses. ``Looks like it goes about
twenty-five feet down. Some plants down there, too, and I don't trust
`em.''

The rest of the group joins him at the edge of the pit. The plants are
short black shrubs with thorny branches and large yellow blossoms.
Colored by the light from the hot pink walls, they look like an interior
decorating choice made by an insufferably cool new restaurant.

``I love it,'' says Galadriel.

``Time for a test,'' says Hanamir. He pops back into the Cat Room for a
second and retrieves the stuffed cat that had contained the human heart.
Then he drop kicks it into the pit.

Immediately, the black branches of the plants below shoot
serious-looking thorns at the cat, impaling it in several places.

``Motion sensing plants, that's new,'' says Harlan. ``Galadriel, you
want to risk the walls? Can you crawl fast enough?''

Galadriel places a hand on one wall.

``Actually,'' she says, annoyed, ``I don't think I can stick to these
walls, for some reason. They feel like\ldots{} how walls used to feel.''

``So do we turn around? I don't see how we're getting across,'' says
Hermione.

``No, no, they can't stop me that easily,'' mutters Galadriel. ``If I
can't climb the walls, I'll just do a continuous handspring from plank
to plank until I'm across.''

``Uh, what?'' says Harlan. ``Sorry, you'll do what?''

``You'll see,'' says Galadriel. She walks backward, sticking out her
tongue and giving her arms a stretch, preparing to take a running start
toward the pit.

``Wait,'' says Hanamir. ``Let's tie a rope around you so we can pull you
back if we need to.''

``Sounds good,'' says Galadriel. She lifts her arms and allows Hanamir
to fasten a rope around her waist with a complicated knot. ``You can't
hold it taut, though, not until I'm all the way across, or you'll mess
me up.''

``Got it,'' says Hanamir.

``Okay,'' says Galadriel, taking a deep breath. She ties her hair back.
She shakes out her left leg, then her right leg.

And then she hurls herself into a full sprint toward the edge of the
pit, jumping out over the edge as if diving into a pool, but landing on
the first plank with her hands and springing forward again, landing her
feet on the next plank---this one cracks a little but stays up---and
then onto her hands again---the shrubs below are launching thorns at
her, but they're not quick enough---feet, then hands, like a wind-up
toy, until she lands on the other side, whooping and cackling in
triumph.

``\href{https://youtu.be/hHFPuBywhEg?t=3s}{Daaaaaaaaaaaamn}!'' she
cries. ``Did you all see that?!''

The adventurers applaud politely, but Galadriel is unsatisfied.

``Are you kidding me? I just \emph{did} that!'' She punches the air.
``That was cool as hell!''

``Yes, good work, Gals,'' Hanamir calls to her across the pit. He tugs
at the other end of the rope. ``Untie yourself and attach this to
something, and then let us know what you can hear past those doors.''

Galadriel takes another few seconds to cool down, then ties her end of
the rope to one of the massive door handles ahead of her. She lays an
ear to its surface.

``It sounds like\ldots{}'' Her eyes widen. ``Guys, it sounds like the
outside world in there. I can hear birds!''

``That is excellent news!'' calls Harlan. ``Maybe there's ventilation,
and we can take a long rest without poisoning ourselves.''

``Yes, try going in,'' calls Hanamir. ``And if there's immediate danger,
just do another one of what you did to get over there and come back to
us.''

``Oh, sure, I'll just \emph{do another one}. It's only the most
difficult move I've ever done \emph{in my life}. Sure, Hanamir. \emph{No
biggie}.''

Galadriel pulls the doors open.

``What do you see?'' calls Harlan.

``Oh, wow,'' says Galadriel. ``There's been a massive collapse in here!
It's open to the sky.''

She ventures inside, taking a breath of fresh air for the first time
since that morning. She stands still and listens to the trilling of
tropical birds and other wildlife moving in the vegetation that has
encroached upon the room.

``It's a pretty big room\ldots{} L-shaped, and I'm at the corner\ldots{}
there's another door leading somewhere else on one side,'' she shouts
back to them. In the periphery of her vision, she sees a large ape
observing her from across the room. It doesn't look aggressive, but her
heartbeat accelerates a bit.

``Okay,'' comes Harlan's voice, faint when competing with the ambient
noise of the jungle. ``Stay put. We're going to find a way to neutralize
the plants and get across to you.''

Back on the other side of the pit, the adventurers huddle for a
brainstorm.

``If I had enough liquid, I could freeze the plants, one by one,'' says
Tannin. ``Everybody take out your flasks, and maybe I can---''

``That is not going to work,'' says Hermione.

``Unshackle me! I will vaporize the plants!'' suggests Magick.

``Also no,'' says Hermione.

``Call Lightning?'' says Harlan. ``I might have to do it a few times,
but it'd probably take out a good swath of them at once.''

``Aren't we worried about the structural integrity of the temple?'' says
Hanamir.

``Yeah, but it's \emph{lightning},'' says Harlan.

``My point exactly,'' says Hanamir.

``I mean it's not thunder!'' says Harlan.

``I suppose it isn't,'' says Hanamir. ``Am I the only one worried?''

Tannin shrugs. Buddy blinks up at him. Hermione is quieting another
Magick tantrum and cannot be reached for comment.

``I'm gonna do it,'' says Harlan. He raises a hand, electricity
crackling and sparking in his palm. With a gesture like a chef artfully
seasoning a dish, he sends a bolt of lightning down to the center of the
pit. Several of the spidery-branched shrubs burst into flames, spitting
their projectile thorns out uselessly into the walls.

Harlan smiles, and prepares another handful of lightning. But before he
can release it, the ceiling crashes down.


\chapter{Et in Horto Quiznis, Serpens Est}
\chapdesc{There's trouble in paradise as the party is rent asunder.}

\href{/characters/galadriel/}{Galadriel} hides her face in her sleeve.
Dust, heavy with airborne rocks, hits her like an ocean wave from the
doorway and knocks her backward to the floor. The birds above her go
silent.

``Oh, come on,'' she groans to herself. She spits and blinks and
sneezes, finding her way back to her feet. ``Was it Call Lightning? I
bet he cast Call Lightning.''

She peers back through the passageway, now a mess of fallen rock. There
are no magenta lights to be seen.

``I hope they got out of the way, at least,'' she says, with a sudden
pang of fear, followed by the creep of guilt for her flippant initial
reaction. An idea occurs to her.

\emph{\href{/characters/buddy/}{Buddy}? Can you still hear me? she
thinks.}

She waits for an answer, but there is no sound except the gradual return
of activity in the canopy above. She catches a glimpse of another ape in
the greenery to her right. It watches her without making a move.

\emph{Okay. It's possible that everyone I care about has just died. It's
possible that I'm alone now. For good.}

Her breath catches in her throat.

\emph{But in case that's not true\ldots{} what would they want me to
do?}

An answer comes to her, and she forces herself breathe deeply, as if to
prove to herself that she's remaining calm.

\emph{They know where I am. I'll conjure up a little hut, and I'll take
a nice nap.}

She hums a tune to herself as she casts Leomund's Tiny Hut. It's
something her mother used to sing, but she forgets the words. The
rainbow-colored walls and roof of the hut spring into existence around
her and block out the world.

``All right!'' she says aloud. ``Time to restore some feelings of
well-being and magical ability!!!!''

She unfurls the deluxe black silk bedroll she purchased back in Aberith
(to replace the one that was stabbed to shreds during the encounter with
the basilisk). Despite it being mid-afternoon, she's confident she could
jump inside it and sleep for nigh on fourteen hours. Her shifts at the
Black Unicorn combined with her training schedule with Yasaria's drow
assassin squad has left her chronically sleep-deprived for the past
several weeks.

And she isn't wrong. She drifts off to a swift but uneasy slumber.

In her dreams, she's somewhere she's been before. It's the temple, and
it's not, but it's just like this, and she's full of dread\ldots{}

Of course! It's the room where she walked in on
\href{/characters/magick/}{Magick}, in another dream, not long
ago\ldots{} when Magick was hurting someone, someone she loved\ldots{}

Heart pounding, she steps forward, and she can finally see the object of
the torture, and it's exactly what she feared. A copper
dragon---\emph{Buddy}!---is restrained by some malevolent spell, his
life slipping away---she pleads with Magick for mercy, but the tiefling
doesn't even glance in her direction, so focused on her brutal task---

\emph{This is a dream,} some part of her conscious mind interrupts.
\emph{You're dreaming.}

What happens next? In the original dream, she stepped forward and
uttered a word that stopped Magick and ended her life instantly\ldots{}
but what was the word? She scans her memories frantically. What was the
word that saved Buddy?

\emph{Only the Lich knows the word,} she realizes. \emph{The word was
his offer.}

She startles awake, clammy and terrified. It's still mid-afternoon,
judging by the light filtering through the lava-lamp walls of the hut.

\emph{Buddy?} she thinks. \emph{Are you there?}

She drifts back to sleep waiting for his answer.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

On the other side of the cave-in, the mood is not great.
\href{/characters/tannin/}{Tannin} is picking gravel out of his beard,
while \href{/characters/hanamir/}{Hanamir} pours a cup and a half of
fine-grained dust out of one of his boots.
\href{/characters/hermione/}{Hermione}, Magick, and Buddy were far
enough away that they are physically untouched, but Magick rocks back
and forth in a fetal position on the floor.
\href{/characters/harlan/}{Harlan} stares at the rubble in surprise and
a fair amount of horror.

``What?!'' he repeats, again and again. ``But---but it was
\emph{lightning}, not thunder!''

``Yes, Harlan,'' says Hanamir, a little snippy. ``Who could possibly
have seen this coming?''

``But I---'' starts Harlan, then stops, not knowing where that sentence
was going anyway.

Tannin pokes around the ruined passageway with his trident, an arm over
his mouth.

``It'll take us awhile to dig through here,'' he reports. ``Like, I'm
talking weeks, probably.''

``We're not going to go through it,'' says Hanamir. ``We're going to
turn back the way we came and find a different way around.''

``Sounds good to me,'' says Tannin. He punches Harlan in the shoulder,
laughing. ``You really screwed up big time, my man!''

``Yes I did,'' says Harlan, eyes downcast. ``I'm sorry everyone. I
really, really didn't mean for that to happen.''

They trudge back to the cat room.

``Two more options, team,'' says Hanamir. He nods at a set of bronze
doors inlaid with lighter stone patterns, and another set of iron doors
with heavy wooden slats running left-to-right. ``Door number one or door
number two?''

``Definitely the pretty door,'' Hermione pipes up from the back of the
group. ``The stone pattern one. The other one looks like it goes to a
dungeon.''

``I'm going to defer decision-making to others for the time being,''
says Harlan.

``Works for me,'' says Hanamir. He leads the way through the stone
patterned doors into an L-shaped hallway. They progress slowly behind
him, alert for pressure plates or tripwires, but it proves to be free of
traps.

The hallway culminates in a short staircase leading up to a spacious
room that reminds Hermione of an empty terrarium and Hanamir of a zen
garden after centuries of blight. In the center of the room is a pond of
what looks like oily water. A gnarled and withered tree stands in the
water.

``No wonder it's dead,'' whispers Hermione. ``No sunlight in here. Why
have an indoor garden if you can't maintain it?''

``I don't trust it,'' says Hanamir. ``You all stay back; I'm going to
see what happens if I move closer.''

He dashes along the left side of the room, clutching the eight-foot pole
defensively.

Sure enough, as he passes, the tree begins to move; its bark crackles
and groans as it opens a single eye in the middle of its trunk and
unfurls its twisted branches like a sea creature's tentacles. It makes a
blundering grab at Hanamir, but he's far too quick for it.

``Ha!'' cries Tannin, following Hanamir in a dash across the room. ``Too
slow!''

The tree grunts in frustration as its next swipe at Tannin is, again, a
few seconds too late.

``It is pretty slow,'' Hanamir calls to Harlan. ``I think all of us can
probably speed through here.''

``Are you sure?'' says Harlan. ``Even Magick? She's still freaking out
back there.''

``I think now is the time for speed,'' says Hanamir. ``If our goal is to
reunite with Galadriel as soon as we can. At least, that is my goal.''

``No, no, that's my goal too,'' says Harlan. A note of worry has crept
into his voice. ``I just\ldots{} what if this doesn't actually lead us
to where she is? And we need to come back through here and go another
way? I think we should make sure that our way back is free of murderous
tentacle trees in case we need to escape from something even
worse\ldots{}''

As he makes this argument, the tree turns toward him and bellows with a
sound like a paper shredder with a metal binder clip stuck in it. It is
gaining a little bit of speed as it wakes up from its probably ages-long
slumber.

``Damn,'' says Harlan. His path is blocked by six fanning tentacles.
``Okay, here goes.'' He casts Sacred Flame and hits the tree directly in
the face. It reels backward, then makes an indignant grab at Harlan with
a tentacle branch. It lifts him up into the air and shakes him like a
baby with a rattle.

Hanamir frowns deeply. If he were the type of person to sigh and exclaim
``AGAIN?'' he'd do so, but instead he centers his mind, focuses on his
breath, and launches a set of darts at the back of the tree. One of them
sticks, but the others ricochet off of its bark.

``Its hide is particularly tough, it seems,'' he announces to the room.
``Like petrified wood.''

The single dart is not enough to distract the tree from its prey. It
holds Harlan in front of its face like a corn on the cob and takes a big
bite.

``Oh, jeez,'' says Tannin. ``Eaten by a bag of bread and then eaten by a
tree? Not on my watch!''

He flies into a rage and throws his trident at the tree's trunk, but it,
too, bounces right off and clatters to the ground.

Harlan, whose bite wound rains blood onto the floor with every passing
second, flails in the grip of the tentacle and swings his hammer however
he can. In a bit of luck, it hits the tree in its single giant eye.

``Hold on, bud,'' says Hanamir, his crankiness forgotten. He leaps up
onto the tree's back and begins sawing furiously at the tentacle that
has hold of Harlan. The tree stomps back and forth in an attempt to
shake him off, but soon Hanamir has hacked completely through. The
branch falls off, and Harlan with it, to thud heavily against the floor.

The tree, now making a noise like a woodchipper being force-fed a fax
machine, directs all five of its remaining tentacles to pick Hanamir off
of its back. It grabs him and brings him around to its mouth to bite
him, but Hanamir lands a swift punch to its eyeball. It then holds him
as far away from its trunk as it can.

``Okay, trying again,'' says Tannin. He has retrieved his trident from
where it fell and now takes another, more forceful stab at the tree. It
hits. But the tree has decided to leave it all on the mat today, and it
plucks Tannin from the floor with a tentacle and takes a vicious bite
out of his midriff.

Now Harlan is the only combatant not held by the tentacle tree. He casts
another Sacred Flame, summoning the most powerful radiant energy he can.
Large cracks begin to appear in the tree's bark, widening to canyons.
It's deeply upsetting to the tree, and in the distraction, Tannin takes
a final stab at the tree's large single eye. He skewers it, and it must
be the tree's only vital organ, because the tree's branches go limp and
release the dwarf and the half-orc from its clutches. The two of them
take a moment to lie there on the floor and collect their strength.
Finally, Tannin sits up and addreses Harlan.

``Next time you see the barbarian running?'' he says. ``You run too!''

``I'm sorry,'' says Harlan. ``Again. I'm not having a good streak
here.'' He casts Healing Word on Tannin's tree bite wound by way of
apology.

Hanamir says nothing, but gives Harlan a nod that indicates all is
forgiven. Tannin is already distracted and rummaging through the shell
of the dead tree's trunk.

``It's a treasure piata!'' Tannin cries. He holds up several large
pieces of blue jasper. Hanamir joins him.

``Look at this,'' says Hanamir, turning a simple silver rod over in his
hands. ``I wonder what this does?''

``Aha!'' says Harlan. ``That, my friend, is a Wand of Lightning Bolts.''
He smiles fondly and waves a hand. ``But I've got all the lightning we
need right here.'' His smile falls. ``Though\ldots{} lightning hasn't
been a great tool for us lately, anyway.''

``You want it, Tannin?'' asks Hanamir. ``For later? As in, when we are
no longer in this very fragile ancient temple?''

``A dwarf with a wand?'' says Tannin. He's looking at it with a mixture
of curiosity and skepticism. ``What would my brethren say?''

``Let them say whatever they want,'' shrugs Hanamir, who has no problem
behaving unusually for a half-orc.

``If you don't want to be laughed out of dwarven society, you could
disguise it somehow---affix it to your trident, and then you'd have a
weapon that commands fish AND fries them on demand,'' suggests Harlan.

Tannin does seem intrigued by this idea. He takes the wand, ``just for
now.''

Harlan goes back to the hallway to tell Hermione, Magick, and Buddy that
it's safe for them to come through the room now.

``Any sign of Galadriel?'' asks Hermione.

Harlan shakes his head, his guilt turning into real concern. He searches
his pockets until he finds a simple silver whistle. ``I'll use this,
just in case we're close enough to Galadriel that she can hear us. And
at least then she'll know we're on our way.''

But this turns out to be unnecessary, as they find that the next set of
doors leads them to the very same jungle room containing their lost
half-elf friend. They can see Galadriel's hut across the room.

``Whew,'' he says.

Hanamir holds up a hand indicating silence and caution. He scans the
room for threats and notes the small group of apes who are sniffing at
the hut with curiosity. The adventurers pop back through the doors for a
second to talk.

``Want me to do Speak with Animals?'' says Tannin. ``Those apes don't
look hostile. I can probably convince them to back down. We'd just need
to wait ten minutes.''

``She's been waiting for us this long,'' says Hermione. ``Another ten
minutes can't hurt.''

Ten minutes pass, and Tannin tries out a few ape-like grunts. They
really suit him.

He strides confidently into the jungle room and waves to the apes, who
look surprised, but still not aggressive.

``Howdy,'' says Tannin. ``Just a heads up. My friends and I are here and
we don't mean you any harm. Want these?''

He holds out a few pieces of the blue jasper, then chucks them over to a
far corner of the room. The apes watch with interest.

``All yours!'' he motions toward them, and the apes lumber off to
collect the shiny rocks.

Tannin knocks on the side of hut. Then he looks back and waves the other
adventurers to come on in. Galadriel appears, banishing the hut and its
pizza-smelling walls into thin air. She looks groggy but ecstatic.

``I knew you were all right!'' she says, giving Tannin a bear hug.

Buddy nudges her shins and she leans down and kisses his head. She and
Harlan exchange a look of understanding. She hugs him too. ``Glad you're
okay,'' she says.

``We're low on energy and at least a few of us have pretty serious bite
wounds from a tree,'' says Hanamir. ``Want to spin up another hut and
get a long rest going?''

``Absolutely,'' says Galadriel. But before she does, a ten-foot python
makes an attack on Tannin.

``I just wanna go to bed!'' laments Tannin, and the rage he summons is
full of exhausted fury. He wrestles the snake and at least holds its
constriction at bay for a moment while Harlan gets a good hit with the
hammer on the snake's latter half, flattening it. Tannin succeeds in
escaping the snake during this distraction. Once he's out, Harlan
finishes off the snake with another swing to its head.

``I need a NAAAAAP!'' Tannin roars at the sky. A few birds flutter away.

``Say no more,'' says Galadriel. She summons another hut. The background
noise of the jungle animals fades to a murmur.

The adventurers each settle in for a long rest. The vibe is one of
exhaustion, disbelief, and gratitude that a stopping point has been
reached and that safety, at least for now, is something they can count
on.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

They sleep through the entire evening and into the night. Hermione, as a
full-blooded elf, is the only one with a reduced need for sleep, so she
awakens in the pitch blackness and uses her darkvision to read. The rest
of them remain unresponsive until sunlight begins creeping through the
translucent walls of the hut.

``Brand new day,'' sighs Tannin. He stretches his arms over his head.
``Man, I needed that.'' He smacks his lips and looks around. ``Let's see
what the bread bag's got for us today, huh?''

He retrieves the satchel from his pile of belongings at the foot of his
bedroll. Harlan shuts his eyes and grimaces.

``Ugh. I don't even want to watch,'' he mutters.

``All right. I'm feeling lucky. No whammies, no whammies,'' says Tannin.

He unties the drawstring and plunges a hand inside.


\chapter{Humeris Gigantum Quiznidentes}
\chapdesc{When standing on the shoulders of giants, be prepared for the fall.}

\href{/characters/harlan/}{Harlan} finishes wrapping
\href{/characters/tannin/}{Tannin}'s wrist stump with bandages.

``There,'' he says. ``It's really not so bad, I promise. And we already
know where to go to get it fixed this time around!''

Tannin stares at the ground and makes a pitiful noise.

``And hey, what about that wand?'' Harlan continues. ``The Wand of
Lightning Bolts? We could just attach it to your arm instead of to your
trident. That'd be cool, right?''

``I guess so,'' sniffs Tannin.

``Can we agree to get rid of the satchel of bread?'' says
\href{/characters/hermione/}{Hermione}, searching the group for
consensus. ``It's claimed two hands now, and---''

``No!'' says Tannin. He clutches the satchel to his chest with his one
remaining hand. ``No way! This bread is an awesome deal!'' His voice
rises in both volume and pitch. ``It only sometimes eats a hand! The
rest of the time it's amazing!''

``Well, I suppose it's up to you,'' says
\href{/characters/hanamir/}{Hanamir}. After a silence that reveals the
extent of the adventurers' lack of interest in arguing with Tannin, he
changes the subject. ``Shall we check out those dead bodies over there,
or what?''

The skeletons definitely belong to a set of explorers. One of their bony
hands still holds a detailed map of the temple, marked to indicate that
they had rappelled up the side of the pyramid into this very room, where
they were apparently crushed by falling debris.

``Looks like they had a few places they knew they wanted to check out,''
says Hermione. ``And a few places they were told to avoid. That room
with the cat guy has a skull and crossbones drawn over it.''

``And it looks like we're on the first of three above-ground tiers,''
says Hanamir. He cranes his neck and scans the room. ``That door over
there looks like it corresponds with this one on the map, with stairs
leading up to the second tier.''

``Stairs?!'' \href{/characters/magick/}{Magick} whispers, eyes wide.
``Yes, stairs! Let's go---go to the stairs now---up and up, higher and
higher---''

``Maybe let's just see what's behind this other door we haven't checked
before we move on,'' says \href{/characters/galadriel/}{Galadriel}.
``They didn't mark it in any way. Hanamir, can you take a peek?''

Hanamir approaches a heavy stone door in one corner of the jungle room.
Its face is overgrown with vines, and they might not have noticed it
without the map. He holds an ear to the crack for a moment, then pushes
it open as quietly as he can.

Inside, he sees a dark, windowless room. A woman, translucent but
contoured in glowing light, stands in a cloud of dust. She turns to him,
revealing a haunting, tear-streaked face.

Hanamir shuts the door.

``Nothing in there,'' he says, jogging back over to the group.

``Excellent,'' says Harlan. ``If no one objects, let's try going back to
the cat room and looking at the door we missed in there. These explorers
have it marked on their map, but it's unclear if they meant to seek it
out or avoid it.''

``I object!'' says Magick. ``We need to go up the stairs! And I feel
like my condition is much better now, and I could be very
valuable---very helpful to you all if you'd only unshackle me---''

``Sorry, but still no,'' says Hermione. ``Let's go.''

The adventurers retrace their steps through the room with the dead
tentacle tree, then back to the cat room. The remaining unexplored door
is decorated with yet more images of cats.

Hanamir leads the way. The air in the chamber beyond is warm and
somewhat damp; it smells fetid, almost like a bog. It glows with a
bluish haze.

``We still wanna do this?'' whispers Galadriel.

``Could be great treasure in here,'' says Hanamir.

Harlan points to the far wall and frowns. Some kind of oddly-shaped,
leathery material is mounted there.

``I am going to bet that those tapestries are made of people,'' he says.
``And I hope that I am wrong.''

``There's also a really intense-looking whip hanging up there,'' says
Galadriel, pointing. ``Everyone see the whip? Everyone still cool with
this?''

``Just let me look around a bit,'' says Hanamir.

The most prominent features of the room, other than the maybe-human
skins and the cat o' nine tails, are a blackened mirror on one wall and
an enormous statue of a giant, its gaping mouth wide enough to swallow a
horse. The statue stands on a basin over smoldering coals, which is the
likely source of the marshy air. A flicker of movement in the dark blue
haze reveals a panther prowling around the base of the statue. It does
not react to the adventurers' entrance. Beyond the statue, there is a
well emanating a watery light. And above the well is a small opening in
the ceiling, about five feet wide.

``Seen enough?'' Hermione whispers. ``That panther makes me nervous.
What's it doing? Can it not see us?''

Upon noticing the hole in the ceiling, Galadriel is newly interested in
the room. She scampers up the side of one wall and creeps along the
gently-sloped ceiling.

``I can't climb up into this,'' she says. ``Something is preventing me.
Like the walls of the pit---the magenta ones---before the
cave-in\ldots{}''

Harlan approaches the well and peers over its walled sides.

``Anything you notice about the well from above?'' he asks. ``There's a
liquid in here. Not sure what it is.''

``Nothing remarkable,'' says Galadriel. ``But let's see what happens if
I Mage Hand some of it.''

She summons her magical third hand and directs it to grab an empty flask
from her belt. It floats gently down into the well, reappearing with a
flask full of the fluid.

``All right,'' says Galadriel. ``So it's a real physical substance that
can be scooped and poured. That's\ldots{} something.''

Seemingly prompted by the disturbance of the well, a voice in a harsh,
guttural language reverberates throughout the room.

``Giant!'' hisses Hermione. ``The voice is speaking Giant! Ugh, I hope I
remember enough of the declensions to answer politely\ldots{} it's a
highly inflected language\ldots{} and I mean, I know I look great for my
age, but it's been awhile since thaumazoological grad school\ldots{}''

``A giant?'' says Tannin, perking up considerably. ``What's it saying?''

``It says, `I am Zipe; who are you and what have you come for?'\,'' she
translates. ``Okay, I'm just going to wing it. I think I remember how to
ask for directions properly.''

``Hello\ldots{} very much!'' says Hermione in Giant. ``So piquant to be
hearing from you. Would you\ldots{} can\ldots{} explain to us the way in
which we are out?''

The voice replies, sounding mournful.

``It says `I suggest you leave,'\,'' Hermione whispers. ``What should I
say back?''

But Tannin and Hanamir have left her side to explore other parts of the
room; Hanamir is circling the base of the statue, while Tannin tries to
get the panther's attention, to no avail. He waves his trident in its
face, and it just sits there licking itself.

``I wonder what happens if I pour some of this on the ground?''
Galadriel is calling down to Harlan, who stands beneath her with his
arms crossed. ``Careful, I don't want to get any on you.''

She pours a quick dollop of the liquid from the flask in the Mage Hand
down to the floor, where it pools unremarkably near Harlan's feet.

``Hmm,'' says Harlan. He bends down and dips a finger in the puddle.

``Dude!'' says Galadriel. ``We don't know what that is!''

Harlan watches his hand as the strange shimmering liquid begins
spreading over his skin, soon enveloping his index finger.

``Hmm,'' Harlan says again, his frown deepening. ``I guess I didn't
think that through. It was a Galadriel moment, one might say.''

``Excuse me?'' says Galadriel.

``You heard me,'' smirks Harlan. He casts Detect Magic. ``Well, it's
definitely magical. Same with the hole in the ceiling. And the
panther---something about its eyes. Nothing else.''

``Not even this statue?'' says Hanamir, squatting near its base.

``Nope, just a statue,'' says Harlan. The liquid has swallowed his
entire hand, but doesn't appear to be doing any damage. ``I am concerned
about this. I regret everything. Oh, \href{/characters/kord/}{Kord}. I
can't lose a hand again.''

``I thought losing a hand was no big deal?'' sneers Tannin.

``Of course it's a big deal!'' says Harlan, panicking. ``I was just
trying to make you feel better! Obviously!''

Hermione, realizing she will be receiving no guidance from her friends,
addresses the bodiless voice again in what she hopes is gramatically
correct Giant.

``Sorry, please. My family is lost. We do not hope that we are doing you
in an annoying way. What is this\ldots{} juicy business?'' She bites her
lip, knowing that wasn't right. ``The, uhh\ldots{} the watery business?
Moistness? From the round\ldots{} floor\ldots{} source?''

Another raspy, solemn series of sounds emanates from the hole in the
ceiling.

``It says we should take as much as we want from the well and get out,''
says Hermione in Common, sounding confused. ``So I guess the stuff isn't
dangerous, Harlan.''

``That could be a trick!'' Harlan cries, watching the shiny liquid climb
up his arm. ``It could be its poisonous urine! The well could be its
bathroom! If I die from touching monster pee because I was feeling
reckless for one second, I will be so mad, I swear to Kord!''

``Did you do the watery business?'' Hermione calls up to the giant. ``Is
it\ldots{} a terrible water? Or a pleasing water?''

To this, there is no reply, just a sound like something enormous rolling
over in the room above them.

``No response? Great. Just great,'' sighs Harlan, as his shoulder is
engulfed. ``It's been nice knowing all of you. Take care of Zotz for
me.''

Meanwhile, the panther has finally taken notice of one of the
adventurers, and it's not Tannin, in spite of his energetic
trident-twirling.

HEY, GALADRIEL? I THINK THE PANTHER SEES ME.

Galadriel looks down from the ceiling and sees the panther staring at
\href{/characters/buddy/}{Buddy} from across the room, where he sits
with Magick. The panther's muscles are tensed, its ears flattened.

\emph{Oh no}, she thinks. \emph{Do you think it knows what you are?}

NAH, IT DOESN'T KNOW. BUT I'VE SPENT LONG ENOUGH IN THIS FORM TO
RECOGNIZE WHEN SOMEONE IS CRAVING BACON.

\emph{Ha! Well, it can't see me. I'll drop down onto its back and---}

NO NEED FOR THAT. I JUST WANTED TO LET YOU KNOW WHAT'S UP. YOU HAVE A
GIANT TO FIGHT.

\emph{You think? This guy doesn't seem to want to come down, and I can't
climb up there.}

ASK HANAMIR TO GIVE YOU HIS GRAPPLING HOOK AND TRY USING THAT.

``Hey, Hanamir?'' says Galadriel. ``Toss me your grappling hook, would
you?''

``Sure thing,'' says Hanamir. He underhand pitches it up to the ceiling,
and she catches it. ``You going up?''

``Yeah,'' she says. She unravels the rope attached to the hook and lets
it fall to the floor, where it coils in a loose circle. ``Join me?''

Galadriel launches the grappling hook into the hole in the ceiling. It
scrapes against something before shifting and locking into place. She
gives it an experimental tug.

``Here goes,'' she announces, and does a show-offy aerial trick on the
rope before inching her way up.

As she does, the rope begins to ascend.

``Whoa!'' she yelps, disappearing through the hole.

Hanamir makes an elegant hop up to the middle of the rapidly-vanishing
rope. In what looks like another impulsive decision, Harlan grabs on to
the end of the rope before it slips out of reach. They pass through the
ceiling one by one, leaving Tannin and Hermione downstairs with Magick,
Buddy, and the panther.

The room upstairs is cavernous, and it somehow manages to smell even
worse than the chamber below. Piles of bones and more human skins litter
the floor. A huge shape emerges from the darkness. Its hands, the size
of carriage wheels, toss the grappling hook and rope down through the
hole in the floor.

``I think this is an oni,'' notes Hanamir. ``A giant with certain
polymorphic powers. You'll note his clothing is fashioned from human
skin, in accordance with oni tradition.''

``Fascinating, thank you,'' says Harlan.

At that, the oni roars something in Giant and blasts the three of them
with a cone of freezing cold air, nearly killing them all in one blow.

``He says he just wanted to be left alone!'' Hermione's voice calls from
downstairs. ``Or that he just wanted to go for a swim! Those verbs sound
really similar!'' When no one responds, she calls again. ``You guys okay
up there?''

``Oh dang,'' murmurs Tannin. He paces around the well beneath the
opening in the ceiling. ``That did not sound good. How do I get up
there?''

``Don't leave me alone down here!'' says Hermione. ``Not with the
weirdos!''

``Hey, not cool. Buddy's chill,'' says Tannin. ``But whatever, you want
to try your luck? Sounds like they need reinforcements.''

``Yes!'' she says.

She evokes a cloud of mist at her feet and vanishes, reappearing in the
upstairs chamber. She arrives not a moment too soon, as Hanamir, Harlan,
and Galadriel are blue and shivering with hypothermia. The oni steps
back, surprised by her sudden appearance.

``Desist, you mealy and flavorless dumpling!'' she screams at it in
Giant. She casts Ray of Sickness with an unprecedented burst of magical
energy. The oni crumples on the spot, retching and heaving.

This gives the others some time to recuperate. But the oni is enraged.
Rounding on Hermione, it slashes her with an invisible blade, and the
injury is critical. All four of the adventurers are on the ropes\ldots{}
which is what gives Hanamir the idea to lower another rope down for
Tannin, who is now their last hope at survival.

``Yes!'' cries Tannin, clambering up the rope. ``I can feel a rage
brewing! The kind that can only be sated by sending a stinking,
good-for-nothing tumbletower crashing to the ground!''

He pops through the hole and immediately lands some devastating blows to
the oni's vital organs with his trident.

``Heads up, Tannin,'' says Galadriel, through chattering teeth. ``I'm
going to do Dissonant Whispers, and if it succeeds, he's going to be
compelled to flee as far away from me as possible.''

``Roger that,'' says Tannin.

Galadriel summons as much power as she can muster and casts the spell.
Without warning, the oni disappears completely from view.

``What?'' Galadriel stutters. ``That's not part of the---''

The adventurers hear a splash from the room below. They circle around
the opening in the floor and look down. A medium-sized humanoid shape
has fallen into the well and is now mostly coated with the same shiny
liquid that creeps over more and more of Harlan's skin.

``How'd it get small like that?'' says Tannin.

``Polymorphic powers!'' chatters Hanamir. ``Just as I thought!''

``And invisibility, too, I guess,'' wheezes Harlan.

``Close one,'' says Hermione, pale from blood loss. ``Someone please go
down and finish this.''

``On it!'' says Tannin.

He jumps down through the hole without considering the practical option
of climbing back down the rope. The other adventurers hear some gruesome
flesh-tearing noises mixed with a steady stream of truly tasteless
anti-giant slurs.

``All done,'' Tannin calls up at them.

Slowly, the other four lower themselves down to join him. The dead oni
has returned to its original, massive dimensions, and is still
glistening with the substance from the well.

``All right, enough's enough,'' says Harlan, landing heavily on the
floor. ``I'm casting Dispel Magic on whatever this stuff is.''

He casts the spell, and the silvery liquid slides off his arm like water
into a puddle on the floor.

``I still just wish I knew what it was!'' he sighs. He stares, brow
furrowed, at the giant corpse.

Galadriel looks around.

``Guys? Where did Buddy go? And Magick?''

``And what about that panther?'' says Hermione.

``Over in that corner, by the corridor,'' says Hanamir. ``Magick, are
you all right?''

Magick's eyes are shut and she is muttering something under her breath.
She hits her head against the wall again and again. Next to her, Buddy
sits quietly.

\emph{What happened down here? Where's the panther?} Galadriel thinks.

IT\ldots{} I HAD TO TAKE CARE OF IT.

\emph{What?! Did she see you?}

YEAH.

\emph{Magick knows you're a dragon?!}

YEAH.


\chapter{The Lost Episodes: Part I}
\chapdesc{An intrepid researcher scores two helpful interviews.}

The following chapter contains the first half of what historians have
come to call ``The Lost Episodes.'' The original records of these events
were destroyed.

Please be advised that the content herein has been pieced together from
fragments of physical evidence combined with interviews from
eyewitnesses. Memory is notoriously fallible, and witness testimony is
therefore not always reliable. However, their recollections have been
foundational to the purpose of telling this portion of the Southside
Chillers' story.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\textbf{Can you tell us a little bit about yourself?}

Sure. The name's Huixtochihuatl, and I'm the ghost of a temple attendant
who was entombed in the second tier of the pyramid.

\textbf{As a ghost, what can you tell us about your day-to-day?}

It's a lot of the same things I used to do when I was alive: I guard the
shrine containing the relic of my personal deity, I warn intruders to
stay away or face the wrath of the many-eyed god, and the rest of the
time I think about all my regrets.

\textbf{Do you remember seeing the Southside Chillers pass through your
section of the temple?}

I don't know anyone by that name, but if you describe them\ldots{}

\textbf{You would have seen a human man holding an enchanted hammer, a
one-handed dwarf wielding a trident---}

Okay, I'll stop you right there. Yes, I remember the dwarf, and I
remember his companions. Obnoxious, completely obnoxious. Even for tomb
raiders. I first saw them when they were running up the stairs, laughing
at their destruction of this holy place. They had swine with them.
Swine! Stinking of\ldots{} of panther's blood and viscera. I could tell
that they had just come from desecrating the sacrificial flaying chamber
and slaughtering the oni's familiar, and perhaps the oni himself.
Outrageous.

\textbf{Did they see you?}

No.~I deemed them unworthy to behold my beauty, which, as you can see,
is unfathomable.

\textbf{Hard to fathom, indeed, ma'am. But did you interact with them in
any way?}

I am named for the Goddess of Salt, so in death, I am blessed with a
portion of Her power. When I saw these buffoons approaching the steam
dragon trap, I imbued it with salt water so that their scalding wounds
would sting like a hot ocean wave to the eyeballs.

\textbf{Where is the steam dragon trap?}

It's at the top of the stairs to the second tier, right near where I
haunt. And it was a later addition to the temple, so it hasn't had as
much of a chance to shine yet as some of the older traps. Which is a
shame! Because it's capable of steam-cooking a humanoid to death on the
spot, sort of like how they do with lobsters, but better, because they
can verbalize their agony.

\textbf{Is that what happened to the Southside Chillers?}

Sadly, no. They got out of the way before anyone was ready to be dipped
in butter sauce. Though I did get a good salty steam burn on the bard,
and she did complain about it a lot, so that's something, right?

\textbf{Absolutely. Anything else you'd like to add?}

Just that I also watched them nearly inhale a centuries-old colony of
mutated
\href{https://moldblogger.com/the-most-dangerous-molds/}{stachybotrys}
that had made a home out of an illusory pile of gold coins in my
hallway. It devoured the respiratory tracts of countless looters before
them, but they burned it up with a torch like it was nothing. That mold
was my friend.

\textbf{Thank you so much for your time, Huixtochihuatl.}

Foolish mortal! Leave this temple or face the wrath of the many-eyed
god!

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\textbf{FIG. 36-1:} \emph{Deceased individual in a poor state of tissue
preservation. Wearing leather armor and holding a mildly enchanted
dagger. Forensic evidence indicates inhalation of toxic spores as cause
of death, c.~500-600 years ago.}

\textbf{FIG. 36-2:} \emph{Shards of a mirror. Analysis of the break
pattern suggests that the mirror was mounted on a wall, and that it was
broken when spin-kicked by a humanoid of at least six feet in
height---an impressive feat requiring unusual agility in such a narrow
chamber. It was found near the entrance to the Shrine of the Couatl.}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\textbf{Mr.~Frampton-Trogdor, it's a pleasure to meet you.}

Please, please, just Frampton-Trogdor is fine. Nice to meet you too.

\textbf{Would you mind walking us through what happened the day of your
escape from the temple?}

Not at all. I'd been stuck in there for thousands of years, so getting
out was the most exciting thing that's ever happened to me, probably. I
was so bored. You would not even understand how boring it was in there.
I could try to describe it to you, but until you've been stuffed into a
crystal cylinder and kept there for eons, you just won't get it. You
think about every little dumb thing you ever did to end up where you
are, and you berate yourself, and eventually you start to wonder how
long it'll be until the sun explodes.

\textbf{So, the day you escaped. What's the first thing you remember?}

Oh, right. Yup. Well, I remember the sound of the mirror shattering
outside my door. I just thought, ``oh boy, the worshipers are feisty
today.'' Time had really lost all meaning to me at this point, so even
though there hadn't been any living devotees to my shrine in centuries,
it's not like I knew that. It could have been a week, for all it
mattered to my sense of temporality.

\textbf{When did you know that this wasn't a regular visit from your
acolytes?}

As soon as they walked in, I knew something was up. This was a weird,
weird group, okay? A half-orc, a human, a dwarf, a half-elf, an elf, a
tiefling, and a dragon disguised as a pig. That kind of variety doesn't
just happen, you know? Clearly, this is a group of individuals who've
come together for some common cause. And it seems like they've been
through some rough stuff, too, at this point, because the tiefling was
wigging out like I cannot describe to you. Like, she was really losing
it.

\textbf{Losing it how?}

Screaming about dragons. And as a couatl, I'm sensitive to that, because
people often lump us all together, like there's no nuance, just because
we speak Draconic too. It's just ignorance, but you have to learn to
deal with it. Anyway, the dragon in the group was playing it cool, but I
could tell she was starting to get to him. Also, she was refusing to
move, so the blue-haired elf had to drag her along.

\textbf{When did you come up with your plan to trick them into freeing
you?}

Right away. I knew I had to trick them into doing it, because they were
so on edge, they wouldn't have trusted me if I just came out and asked
for it up front. They would have tried to kill me, and then I would've
had to fight the dragon, and to be honest, I really didn't want to do
that. I'm trying to get out there and live life again, right? Not be
maimed or killed fighting a Draconic brother because of some nervous
oids.

\textbf{Pardon\ldots{} oids?}

Humanoids. Oids. Sorry. It's not rude, I promise, it's just how we refer
to you all in Draconic.

\textbf{Got it. So you decided to tell them they'd been poisoned, is
that right?}

Yeah. And I don't feel great about that. My goal isn't to scare people.
But I'd been trapped for so long that I didn't know when my next chance
to escape would come around. My sense was that these people had been
fighting their way through the temple and were expecting hostility, so
they'd be wary if I tried to introduce myself as someone sympathetic.
And I sensed that they would be motivated by taunting.

\textbf{How exactly did you taunt them?}

Let's see\ldots{} well, they actually bypassed some of the dangers in
the room. There were all sorts of pitfalls around the staircases
surrounding the crystal cylinder that could have gotten them, but the
half-orc went straight for the warrior statue. So I was all, ``You
better hope you can pass my tests or else you'll die of poison,'' and
pretty much implied that the warrior was a test of their strength, so
that only the worthy would be spared. And implied that they weren't
worthy.

\textbf{Were you at all nervous that the warrior would kill them all and
you'd remain trapped?}

You know, I really didn't think about that at all.

\textbf{The danger posed by the warrior didn't occur to you?}

Not in any real sense, no. He was just one of those clay guys they
enchanted in bulk and scattered around the entire pyramid. I guess he
could have taken one of them out, but the whole group? Not likely.

\textbf{I see. What measures did you take to make them believe they had
really been poisoned?}

Oh, man. It was really basic stuff. Like, just making them feel a little
dizzy, just enough to make them worry and wonder how bad it was gonna
get. A little bit of a headache. I could have done so much worse. Like,
I could have totally unraveled their perception of reality, but I'm not
that mean.

\textbf{Plus, then they probably wouldn't have been able to set you
free.}

Good point!

\textbf{Once they had defeated the warrior, what next?}

So, that meant they had ``proven their strength'' to me, so I figured
the next test should be something like a riddle. I told them that they'd
need to use their cleverest person's best tool to find the antidote in
the core of the crystal cylinder.

\textbf{And did you know how they would interpret that?}

I wasn't sure. It seemed obvious to me that their cleverest person was
the dragon, but I think they assumed that I didn't know he was really a
dragon in that little pig costume. So they thought I was referring to
the elf, which is kind of hilarious. But it worked out!

\textbf{So what would the dragon's best tool have been?}

Ehh, I don't know.

\textbf{Did you know what specifically they needed to accomplish in
order to open up the crystal cylinder?}

No.~I was hoping if I said something cryptic enough, they'd come up with
the answer themselves. It's kind of like fortune telling, or astrology,
right? The interpretation they came up with was that the elf's best tool
was her brain, so they had her just come up and look at the crystal and
think about it or something. And that's when she saw the keyhole, and it
just so happened that they had this magical key from some goblin friends
of theirs, and so she was all like, ``Eureka! I'll use that!''

\textbf{Did it work?}

Well, they didn't really need the key. They just had to notice the
keyhole. I'm honestly mad that that's how easy it was for someone to let
me out and it still took thousands of years to happen. But yeah, I
suppose it worked.

\textbf{What was their reaction when you emerged from the crystal?}

Surprised! And a little afraid, which I get. But they mellowed out as
soon as I started giving them treasure. Oids can be so predictable.

\textbf{Are you sure that word isn't rude?}

Hahahaha, don't worry about it.

\textbf{Okay. So you're out of the crystal, and you're giving them
treasure.}

Yup. And they're actually really sweet. They ask me my name, and I
realize I don't have one. Or if I did, I've forgotten it. Which
definitely threw me, I admit. It was a tough realization.

\textbf{Wow.}

Yeah. So two of the names they'd thrown out as suggestions are
``Frampton'' and ``Trogdor,'' and they're both so terrific, I had to
just do both.

\textbf{They are great names.}

Thanks, yeah.

\textbf{So, Frampton-Trogdor, what's next for you?}

What \emph{isn't} next for me? Hahahaha. No, but I'm happy to say I'm
returning to the celestial plane right after this interview to spend
some quality time with the kids. I also spent the last couple centuries
in that crystal thinking about starting my own brewery, too, so there's
that.

\textbf{Best of luck to you, sir, in all of your future endeavors.}

Same to you! Hey, any chance you can tell me what happened to those
guys? The ones who freed me, I mean?

\textbf{I'm afraid I can't.}

Aw. Bummer. Well, if you run into them, tell them I said thanks again
and what's up.

\textbf{I'll be sure to do that.}

Oh, man. They didn't die in the temple, did they?

\textbf{As I said, Mr.~Frampton-Trogdor, I don't---}

Ugh. Okay. But let me know when you learn the rest of their story, okay?

\textbf{I will.}


\chapter{The Lost Episodes: Part II}
\chapdesc{Phil tells his tale.}

The following is a transcript of an interview with Philtlanextli, an
ancient Olmen man who observed the Southside Chillers as they passed
through his chamber. Due to the nature of his enchantment, the reader
may find his answers evasive or otherwise unsatisfactory. Descriptions
of nonverbal communication have been included where helpful. Some
passages have been edited for clarity.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\textbf{For those at home who may not know you, would you mind
introducing yourself?}

Command me to answer and I shall.

\textbf{Oh, whoops, that's right. I have a spell scroll for this.}

Command me to answer and I shall.

\textbf{I speak one word; heed what I say.} \textbf{What I command, you
must obey.}

Command me to answer and I shall.

\textbf{Answer!}

Hey.

\textbf{Hello\ldots{} Philtlanextli?}

Yes.

\textbf{Did I say that right?}

You can call me \href{/characters/phil/}{Phil}.

\textbf{Great. Um, for those at home who may not know you, would you
mind---}

Introducing myself? Yeah, I heard you before. I just can't respond until
you Command me.

\textbf{Gotcha. Okay. So\ldots{} can you? Introduce yourself?}

Mmhmm. Well, I'm Phil, and I'm the one who lives in the black mirror.

\textbf{And can you tell us what the black mirror is?}

It's\ldots{} hmm. It's a mirror, and I guess its surface is black. I am
ninety-\emph{nine} percent certain it's hanging up on a wall.

\textbf{How did you get in there?}

I'm afraid I'm not sure of that either. Sorry.

\textbf{That's all right. Do you remember ever not being there?}

I think so.

\textbf{What was your life like?}

I was just\ldots{} a guy. You know? \emph{(he pauses)} You know.

\textbf{Okay. Let's see. What can you tell me about the last people to
come through your room?}

Hmm.

\emph{(moments pass)}

\textbf{Take your time.}

First, they dipped a lot of things in the tub.

\textbf{Set the scene for us, if you could.}

There's a tub in the room.

\textbf{Okay, continue.}

The first thing that happened was that the big one with the teeth dipped
a rod in there, and it turned to gold. He'll see.

\textbf{See what?}

Oh, just wait.

\textbf{No, but I haven't---I haven't dipped anything into the tub. Can
you just tell---}

I simply can't say. You'll have to wait and see. \emph{(he winks)}

\textbf{Fine. What next?}

The one with yellow hair dipped her shoe and a strand of her hair.
\emph{(he giggles)}

\textbf{And you won't tell me why that's funny?}

\emph{(he giggles)}

\textbf{Just assume I want you to continue describing what happened next
until I tell you otherwise, okay?}

That wasn't your command. (   )

\textbf{Please continue describing?}

They looked at the Water Mirror next, but the short and bearded one
resisted its power. And then the one with blue hair conjured a small
creature and banished it there. It has surely drowned.

\textbf{Oh dear. Did you get a look at the creature? Was it a prairie
dog, by any chance?}

It\ldots{} no.

\textbf{All right, then what happened?}

The yellow-haired one touched my neighbor. My good-smelling neighbor.

\textbf{Who is your neighbor?}

Who \emph{was} my neighbor!

\textbf{All right, who was your neighbor?}

I don't know! He smelled of spices! \emph{(he is visibly agitated)}

\textbf{What happened to him?}

She touched him, and he fell out of his home! His
\href{https://imgur.com/gallery/nUoaFR0}{wall home}, just next to mine!
And he was crushing her stupid---weak---little---stupid---stupid body
just fine until the other ones had to hack him to pieces!

\textbf{Are you all right?}

\emph{(he screams)}

\textbf{I'll let you have a minute to yourself.}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\textbf{FIG. 37-1:} \emph{Fragment of a hand-drawn map. A diamond-shaped
closet or annex is depicted adjoining to a larger room. The entire space
within the closet is devoted to a cartoonish drawing of a smiling
octopus.}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\textbf{Thanks for agreeing to continue speaking with me. I didn't mean
to upset you earlier.}

Mmm.

\textbf{All right, so, would you be comfortable telling me what the
Southside Chillers did next?}

They passed through my neighbor's home into the dance closet.

\textbf{And what is that?}

It's a closet where you have to dance the whole time with as many legs
as you have.

\textbf{Anything else?}

They came back soon enough. Nobody likes it in there. And after that, it
was all about the mirrors with these folks.

\textbf{Did they speak to you?}

Yes, but they didn't understand that they had to Command me, even though
that is the first thing I say. It's like\ldots{} no one listens.

\textbf{But they figured it out eventually, right?}

Eventually. First they looked into the Fire Mirror and saw death.

\textbf{Can you be more specific?}

They looked inside it and it showed them some different ways to die.

\textbf{Are these visions rooted in any kind of divination, or are they
just illusory?}

\emph{(he giggles)} You'll see.

\textbf{Ah, that again. Well, all right. Tell me about the conversation
you had with them.}

The priest was the one who Commanded me to answer. The rest of them
wanted to do silly things. One of them made my glass frosty. Some of
them wanted to proceed without talking to me.

\textbf{Would that have affected their quest in some way?}

I gave them good information. I told them that the object they were
seeking is in the room beyond this one.

\textbf{But that's where they were going anyway, right? So they would
have found it whether or not you said that.}

Do you want to know what else I said or not?

\textbf{Yes, yes, sorry. Go ahead.}

I told them the final chamber would exploit their strengths. And that
the thing inside was sealed away for a reason. I warned them not to go
in.

\textbf{But were you vague about it? Because I can see that not being
very persuasive, especially after they'd gotten this far.}

Yes, I was very vague.

\textbf{Okay. Did they ask anything else of you?}

They wanted to know if they had what they needed to succeed, and I told
them they had \emph{more} than they needed. Because I do like to lift
people up sometimes.

\textbf{But you still didn't want them to go in, right?}

I mean, I told them that my own civilization destroyed itself wielding
this powerful item they were seeking. Not in any amount of useful
detail. But I did tell them that.

\textbf{Can you give me any useful detail?}

No.~Just ominous proclamations.

\textbf{Like what?}

My people made many mistakes with this item. We used it too many times.
Brought things from distant lands that gave us great wealth and power.
But things came that should not have come. I could tell that these dumb
oxen would meet a similar fate if they were to succeed in finding this
item.

\textbf{All right. But they went through anyway?}

They sure did, I tell you what.

\textbf{And were their strengths used against them, as you predicted?}

I don't know what ultimately happened to them. They left two of their
party behind in the dance closet. A terrible horned woman and a pig.

\textbf{Was this based on your warning, do you think?}

Maybe. The woman was strong. I don't know about the pig. Would have to
be a strong pig.

\textbf{He is.}

You know the pig?

\textbf{I do.}

How is the smallest one the strongest? Tell me more.

\textbf{He's a really special guy.}

I get it! I see what you're doing! You wanted me to be more specific,
and I wouldn't, so now you are doing the same to me! Ha! Ha ha ha!

\textbf{Guilty. Thanks again, Phil. I wish you the best.}

Leave me now. Ha! Ha ha ha ha ha!


\chapter{The Many-Eyed God}
\chapdesc{With the quiznos in sight, the adventurers must keep their cool, lest things get toasty.}

\emph{(Broadcast test tone abruptly ends)}

We now return to the Tale of the Southside Chillers, already in
progress. At this moment, our heroes stand before a door with twin
inscriptions, one in Elvish, one in Draconic. They each translate,
roughly, to the following:

\emph{Lost soules wanderinge withoute cause}\\
\emph{Looking to bende immortall laws}\\
\emph{Heede theese words \& taeke pause}\\
\emph{Seek not the blade upon worlds divyde}

\emph{With theese words the laste of us atone}\\
\emph{Our treasure gods \& cursd throne}\\
\emph{For-ever seal'd in tombe of eternall stone}\\
\emph{Here our ultimatte pouere we seal insyde}

\emph{Ancient spiritte, we make our finall asque}\\
\emph{Protecte the ruinne of our past}\\
\emph{\& strongestte thronth the threshold passed}\\
\emph{Thronth that may your soule resyde.}

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

\href{/characters/galadriel/}{Galadriel} peers at the Elvish
inscription.

``Thronth?'' she says, frowning.

``I'm pretty sure it's supposed to be `through,'\,'' says
\href{/characters/hermione/}{Hermione}.

``All right, let's think about this before we proceed,'' says
\href{/characters/harlan/}{Harlan}. ``We've made it this far, against
all odds. Can't screw it up now.''

``I bet we can think through this logically,'' says
\href{/characters/hanamir/}{Hanamir}. ``Figure out a way to enter that
works to our advantage.''

``What is there to think through?'' says
\href{/characters/tannin/}{Tannin}, twirling his trident. ``It'll use
our strengths against us. \href{/characters/phil/}{Phil} said so. Let's
go!''

``Okay, who's the strongest, then? You, right?'' says Harlan. ``Or
Hanamir?''

``Hmm. We're both really strong,'' says Tannin. He flexes a bicep.
``Hey! What if you tied us together before we go in? So we're not as
much of a threat?''

``Are we to take it to mean \emph{literal} strength\ldots?'' murmurs
Hanamir.

``It says, `through that, may your soul reside'---is it going to possess
one of you?'' says Hermione.

``For real, at least tie \emph{me} up,'' Tannin says, enthused. ``I'll
be disappointed not to fight the final boss\ldots{} but what if I
\emph{am} the final boss?''

``Are we assuming that `it' is the `many-eyed god' that all the temple
guardians have been talking about?'' says Harlan.

``Or---hear me out---tie \emph{everyone} together so that all of us are
the final boss, and we're all as weak as possible,'' Tannin continues.

The adventurers stack their ideas on top of one another until Galadriel
holds up a hand.

``Wait,'' she says. ``You're not the strongest, Tannin. And neither is
Hanamir. It's \href{/characters/buddy/}{Buddy}. He's the strongest.''

Their eyes turn in unison to the pig at Galadriel's feet. He sniffs at
the air and licks his snout, utterly adorable.

``Okay,'' says Hermione. ``So we don't bring him in.''

``And what about \href{/characters/magick/}{Magick}? She's powerful too,
and unpredictable even when she's not possessed,'' says Harlan. ``Maybe
we don't bring her in either.''

They glance at each other in silence for a moment, waiting for
objections to be raised, but there are none.

``So, is that the plan, then? We leave Buddy and Magick outside?'' says
Harlan. ``Should someone\ldots{} stay behind and keep an eye on
Magick?''

All of them look at Hermione.

``No!'' she sputters. ``Come on, guys! I've been saddled with Magick
duty this entire time!''

``No, no, you're right, Hermione,'' says Galadriel. ``And we need you in
there with us if we're going to get out of here alive. Let's find a
place we can leave Magick that's safe.''

``Maybe the octopus closet?'' says Hanamir.

``And we could ask Phil to keep an eye on that door!'' says Tannin.

``What can he do?'' says Harlan. ``He's stuck in the mirror.''

``Buddy can watch her,'' says Hermione. ``She's already scared of him.''

She nods at Magick, who is hunched against the wall behind her,
wide-eyed, shivering, and pale.

``Yeah, this little dude can handle her,'' says Tannin. ``Worst-case
scenario, he just blasts her with dragon breath, right?''

Galadriel kneels down to Buddy's eye level.

\emph{Are you going to be all right if we leave you alone with Magick
again?}

Buddy oinks noncommittally.

I DON'T LOOK FORWARD TO IT. BUT I THINK YOU'RE RIGHT THAT I'D GET
POSSESSED IF I WENT IN WITH YOU. IT'S SAFER FOR ALL OF US IF I STAY
OUTSIDE.

``He says okay,'' says Galadriel.

They lead Magick back through the mirror room to the octopus closet and
transfer one of her shackles to the octopus statue itself.

``Don't leave me!'' she whimpers, articulating a complete thought for
the first time since the incident in the oni room. ``Please!''

``I'm sorry, Magick,'' says Harlan. He tugs at the shackles. ``We have
to. We can't take the risk that the spirit will possess you.''

``No! Don't---don't---chain me up like an animal!''

Harlan sighs with a mixture of guilt and resolve.

``What choice do we have?'' he asks.

``You could let me fight for once!'' rasps Magick. ``Let me help!''

``I'm sorry. I really am. But this foe we're about to face might be able
to possess you and use your considerable powers against us. And we just
can't take that gamble.''

Magick goes silent, sulking furiously.

``We will come back for you,'' says Harlan. ``I promise. We are not
leaving you here forever.''

He tries to make eye contact with her, but she stares at the ground.

``You'll regret this,'' says Magick.

``Why's that?''

She turns away and doesn't respond.

``Okay. See you soon, Magick.''

As the adventurers leave the octopus closet, Harlan looks back one more
time at the tiefling chained to the statue, her shoulders shaking with
noiseless sobs. His throat tightens. He turns away.

``It's for the best,'' whispers Hermione.

They return to the doors engraved with a final warning, one they never
had any intention of heeding. Hanamir pushes against the stone lightly.
It's not locked.

``I expect that there will be a set of stairs behind these doors that
lead us up to the highest level of the pyramid,'' he says. ``And in
there, we'll face the guardian of the quiznos.''

They look at one another, waiting for someone to make the next move.
There is the sense in the stale air that they ought to be saying their
goodbyes, but no one wants to be the first to turn that idea into sound.

In the silence, Galadriel kneels down and kisses Buddy's head.

\emph{Whatever happens in there, I want you to know I love you,} she
thinks. \emph{So much.} She blinks back tears. \emph{And if I don't come
back, I want you to change back to your true form and fly away, okay?}

HEY, NONE OF THAT.

A tear escapes down her cheek. She brushes it away. Buddy rests his
snout against her knee and waits for her to look him in the eye.

I'LL BE OUT HERE LISTENING IF YOU NEED ME.

Galadriel nods, sniffling, and stands up. She sees Tannin looking
pleased at Harlan's begrudging agreement to tie his hands behind his
back.

Without further chatter, they assume initiative order.

``Ready, team?'' says Hanamir.

He pushes the door open.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

The lower levels of the temple bear the scuff marks of centuries of
boots, but the broad staircase to the top level is pristine. Its steps
of polished stone are slippery with dust. The adventurers tiptoe like
mice up to the single wide room that comprises the temple's apex. There
they stand, half waiting to be vaporized on the spot, half memorizing
their surroundings in nervous awe.

From the staircase, the footpath branches across the floor, dividing the
room into visually distinct zones: a sandy dune, a marsh spotted with
ribbonweed and lily pads, a frozen tundra, a gorge of indeterminate
depth, and a single grassy hillock beneath a circular portal in the
ceiling.

After a minute of stillness, a voice echoes softly from nowhere in
particular.

``Have you come to take the quiznos?''

The air is strung tight with tension in the silence that follows.
Galadriel steps forward.

``Yeah,'' she announces.

Hermione grabs her elbow and pulls her back.

``No! We're not here to take anything!'' she says, waving a hand too
fervently to pass for a gesture of dismissal. ``We're, uh, we're lost!''

The energy in the air curdles.

``Nah, we're here to take the quiznos though,'' says Galadriel. To
Hermione, she adds, ``I've lied to gods before, and I'd rather not do it
again.''

The room seems to vibrate as if laughing softly. The voice returns, but
as a whisper. They each feel its gentle breath against their ears.

``They call me the Many-Eyed God,'' it says. ``Do you want to know
why?''

Over top of one another, Harlan and Tannin say ``No, thank you,'' and
``Kinda, yeah,'' respectively.

``Let me show you,'' whispers the voice.

They watch as Galadriel turns rigid and levitates a few inches off the
ground. Her neck bends unnaturally as she peers back at the others, and
they see that her eyes are not her own.

``Because your eyes are my eyes,'' the terrible voice whispers from
Galadriel's mouth.

``My sincere apologies! As I said before, we are hopelessly lost!''
Hermione tries again. ``Would you be so kind as to direct us toward the
way out?''

Galadriel's floating body shudders with laughter.

``So fragile, this vessel,'' she says, looking down at herself, then
back at the group, scanning their faces. ``I wonder if I might have more
fun with this one?''

Her eyes lose focus and roll back into her head and her body collapses
to the ground. Hermione jumps back as Hanamir is the next to rise into
the air like an oversized marionette.

``Better!'' the voice sneers, twisting Hanamir's face in a malevolent
grin. ``But still a meager offering. No, no, this won't do.'' Hanamir's
irises move erratically back and forth as if dreaming with his eyes
open. The voice diminishes to a hiss. ``None of you will do.''

Hanamir falls in a heap next to Galadriel, who is scrambling to her
feet. She helps him up. A rumbling noise comes from underground, and
with a force that sends cattails and swamp water splattering to the
walls, a massive snake emerges from the marsh. It is partly decomposed,
with patches of scales missing to reveal the skeleton inside.

``Untie me! Untie me! Untie me!'' Tannin whispers.

``All right, all right, hold on,'' says Harlan. He fumbles with his
dagger.

The voice returns, resounding against every surface of the room, from
the giant snake's rotting mouth.

``Since you didn't bring me anything to play with,'' it says, ``I'll
have to make my own fun.''

``Now! Come on, Harlan!'' says Tannin. He bounces from one foot to
another like a child waiting in line for the bathroom.

``On it, on it, on it,'' says Harlan. He saws at the ropes around
Tannin's wrists.

Galadriel dusts herself off and readies an arrow.

``I am \emph{so} glad we didn't bring Buddy in here,'' she says,
wide-eyed.

``Yes! And Magick too!'' says Harlan, finally slicing through Tannin's
bonds. ``Good job, everyone.''

``At Drephis State, we'd have earned an A in History for our
interpretation of a primary source back there,'' notes Hanamir. ``Or
perhaps in Comparative Poetry.''

Meanwhile, Hermione is flipping through her notebook.

``Okay, I've never seen a snake of this size before,'' she says,
stopping at a page of notes interspersed with detailed anatomical
drawings of serpents. ``But in general, we'll want to aim for the head,
especially if it's venomous, and we shouldn't stop until it's
\href{http://www.247wildlife.com/snakekill.html}{completely
decapitated}.''

Tannin, not absorbing this advice at all, has already flown into a rage.
He launches himself forward in an Olympic-style long jump and stabs the
snake in its belly.

``Oh, wow, ew,'' says Harlan. Tannin's trident catches on some decaying
snake innards and rips them out like a forkful of overcooked ramen
noodles.

Simultaneously, Hanamir folds himself into an elegant monkish pose for a
hot second and then beans the snake right in the face with one of his
darts. It's not a particularly damaging hit on its own, but the
meditative pose has a magical effect on the snake. Its eyes turn into
cartoon spirals, and it sways in place, unable to react to the dual
attacks on its face and guts.

``What did you do to it?'' asks Hermione, stuffing her notebook back in
her bag.

``That was a Stunning Strike,'' says Hanamir proudly. ``It can't speak
or move. Should be much easier to hit.''

``Let's give it a try!'' she says. Hermione readies a set of Magic
Missiles to launch at the snake, but she catches a glimpse at the pit
and sees two undead soldiers climbing out onto the path. ``Or not!'' She
shoots the projectiles at them instead, and they fall back into the
abyss.

``No worries, let me,'' says Galadriel. She casts Cloud of Daggers at
the snake, and her usual flurry of tiny blades slices through several
more scales on the snake's hide.

Tannin, meanwhile, has loosened the snake's noodly intestines up again
with another stab of the trident. The foul pile of offal is almost
taller than he is.

``Guys!'' shouts Harlan, raising his hammer for a swing. ``Is it just
me, or is this going \emph{too} well?!''

At that moment, the snake breaks free from its stunned state. Its eyes
narrow into furious slits of bright yellow in its dull green face.
Tannin and Harlan, whose melee weapons have forced them to come the
closest, do not have time to get out of the way before a spinning column
of fire descends upon them from an unseen source.

The flames expand, wrapping wider and wider circles around the two of
them. The entire room's temperature rises. After a long two seconds,
Tannin somersaults free, looking like a well-done steak. It takes
another three seconds for the divine fire to disappear, and by that
time, all that's left of Harlan is a lump of coal holding a hammer.
Remarkably, he is not deceased.

``Never mind!'' says Harlan's voice from the smoky chipotle-flavored
ashes of his human form. ``The thing about it going too well! I take it
back.''

``Aha,'' says Hanamir. ``That must be the aforementioned `fiery death'
referenced by more than one temple inscription.''

``I'm going to try and get a better vantage point from that hill,'' says
Hermione. She darts down the path toward the hill, and when she gets
there, the ground tries to shake her off. Its surface rolls like a pot
of boiling water, but she clings on and makes it to the top.

``I think the quiznos must be up there!'' she yells, looking up at the
hole in the ceiling. ``It looks like a room full of treasure!''

``I'll try and get in,'' says Galadriel, climbing up a wall and creeping
toward the hole in the ceiling.

Hermione refocuses her attention on the snake. She conjures a sphere of
flames in her hand and lobs it at the putrid creature.

``Since you like fire so much!'' she says with a grin. More and more of
the snake's skeleton reveals itself as the Fireball blasts a hole in
what Hermione knows to be its trachea but what the other adventurers
would call its ``snake chest,'' or ``snest.''

From the gem-lined opening in the ceiling, Galadriel fires off an arrow
at the snake.

``Right in the snest!'' she crows, then pauses, frowning. ``Hey, do you
think this is the right approach? I mean, is the Many-Eyed God just
going to move to a different host once we destroy this one?''

``What else are we supposed to do?'' shouts charcoal briquette Harlan,
landing a hit with his hammer on the snake's back.

``We could try and trap it!'' says Tannin.

The snake roars at Tannin, and with a zap from its eyes, the dwarf
disappears from view.

``It didn't like that idea,'' Hermione observes. She casts Fireball
again at the snake. Another hole is burned into its abdomen, revealing
several more ribs. Tannin reappears in the marsh, unharmed. It's
honestly perfect timing.

``I was in a pocket dimension, I think!'' he announces. ``What'd I
miss?''

Hanamir charges into the marsh and plunges his sword into the gaping
wound in the snake's snest. It groans, retreating under the water and
reappearing in the desert area, covered in sand like a breaded chicken
cutlet. As it emerges from the dune, it catches sight of Galadriel
peeking into the treasure room in the ceiling. Another pillar of flame
erupts from thin air and swallows the two adventurers nearest the
hill---Galadriel and Hermione.

``It's angry,'' says Harlan. ``We're close!''

He casts Sacred Flame at the snake, and the holy fire exposes its
mottled heart. Without wasting a second, Tannin hurls a javelin that
pierces the bloated muscle and pins the snake against the wall. From the
ceiling, a seared and crispy Galadriel casts Cloud of Daggers, and the
knives sever the remaining connections between the snake's head and
body. Its head rolls to the ground, landing upside down in a drift of
sand.

The adventurers, battered but victorious, cheer.

``Hold on,'' says Galadriel. ``I'm still not sure we're done here.''

From the snake's detached head, a dark shape emerges. It takes the form
of an Olmen king wearing a crown of jewels and feathers. His face is
blurred, as if obscured by a shadow that never moves.

``You have passed the final trial,'' says the king. ``You are free to
proceed and take the treasure.''

``Uhhh,'' says Tannin. ``Really?''

``How does it work?'' says Hermione. ``Explain how the quiznos works,
please!''

The spirit king gestures toward the hole in the ceiling, saying nothing.

``You gonna roast us again if I climb in there?'' says Galadriel.

``No,'' he says. ``You have proven yourselves worthy.''

``I can't tell if you're bullshitting me or not,'' she says. ``But we've
come too far for me to chicken out now.''

She climbs up.


\chapter{So Long, For Now}
\chapdesc{An arc nears its conclusion, but will loose ends trip them up?}

\href{/characters/galadriel/}{Galadriel} hoists herself up and lies flat
on the floor, her chin pressed against the cool quartzite. For a few
breaths, she rests there without moving. The walls are a mosaic of
gemstones, and their multicolored haloes reflect on the silver-white
stone beneath her. She closes her eyes, waiting for some kind of
catch---a hidden assailant, one last guardian of the quiznos to take out
anyone who makes it this far\ldots{} but none appears.

``Do you see it?'' comes \href{/characters/harlan/}{Harlan}'s voice from
below.

Warily, she lifts her head. The only features of the room other than the
jewel-encrusted walls are a simple wooden ladder resting in a corner,
leading up to a hatch in the ceiling, and a cracked wheel on a pedestal
in the center of the room. A small dagger is embedded in the hub of the
wheel. \emph{Seek not the blade upon worlds divyde.} She knows what it
is.

``Yeah,'' says Galadriel. ``Yeah, I think I do.''

She rises to her knees and slides her backpack from her shoulder. She
unrolls a length of rope and ties it to the pedestal so the others can
climb up.

``Get up here,'' she calls down to them, testing the knot, then tossing
the length down through the circular hole in the floor. ``You're going
to want to see this.''

A flash of blue, just out of the range of her periphery, makes her
breath catch. She turns and sees it: a phase spider, all caviar eyes and
bulbous abdomen, its velvet blue legs folded like origami in the corner
of the room. Her stomach hits the floor. In the next instant, the spider
is gone.

\href{/characters/hanamir/}{Hanamir} is the first to emerge, hauling
himself up the rope with athletic ease.

``You all right, Gals?'' he asks, springing to his feet and looking
around. ``You look spooked.''

``I thought I just saw\ldots{}'' she starts. She shakes her head. ``I
saw a phase spider, but it disappeared. Keep your eyes open.''

``Hard not to,'' says Hanamir. He whistles through his tusk-like fangs.
``Whole lot of nice rocks in these walls, huh?''

Harlan clambers up through the opening in the floor next.

``All right, nobody touch anything yet,'' he says. ``We've been told how
dangerous the quiznos is. Let's try to use some caution.''

\href{/characters/tannin/}{Tannin} pops through next. His eyes go wide
at the sight of the dagger stuck in the wheel, and he stumbles as he
rushes over to get a closer look.

``Is that the thing?'' he says. He reaches for it. ``Can we use it?''

``Just a second!'' says Harlan. He swats Tannin's hand away. ``We'll
want to do some magic detection first---''

``You could also help me get up there before you start splitting
planes!'' calls \href{/characters/hermione/}{Hermione}. Hanamir pulls
the rope through the floor portal and lifts her into the room. ``Thank
you!''

``All right, I'm going to sense the dagger's spiritual properties,''
says Harlan. ``Hermione, would you mind doing the same for its arcana?''

``Actually,'' says Hanamir, ``we found something a few rooms back that I
think would be perfect to use on the dagger, if we're hoping to verify
that it is indeed the quiznos, and perhaps learn some more about its
history.''

He motions to Tannin, who passes him the Bag of Holding. Hanamir's
entire arm disappears inside the bag for a moment and reemerges holding
a small silver hand mirror.

``The Mirror of the Past,'' he says. ``Someone looks in here while
thinking of the dagger, and they'll be gifted visions of its past.''

``Any volunteers?'' says Harlan. Ignoring Tannin's enthusiastic hand
raising, he continues. ``All right, I'll do it.'' He takes the mirror
from Hanamir and walks to the central wheel. ``Maybe I need to show it
the target first.'' He moves the mirror through the air around the
dagger from all possible angles. ``Okay, that's the item---uh, Mirror,
can you show me anything about---''

The tarnished surface of the mirror glows. The adventurers huddle closer
around its tiny viewport.

Generations of Olmen kings, dressed in crocodile skin robes and ruby-red
feathers, pass the dagger to their sons in a solemn coronation ceremony.
Each father presents it to his son on a cloth embroidered with golden
thread.

A king confronts a foe on a battlefield. He looks at both armies, then
plunges the dagger into his opponent's chest. The rival king disappears
from reality in plain view of his own army; his men retreat in
bewilderment and terror. This happens hundreds more times, on hundreds
more battlefields.

One king takes the dagger to his blacksmith. A shaman with a painted
face chants while the blacksmith dips the blade into an oven of unholy
flames. The king looks pleased.

Orcs approach from the sea in barges, hordes upon hordes, enough to wipe
out the city. The king raises the dagger into the sky, and the entire
bay is cleared. The kingdom is untouchable.

A terrible blight has killed the fruit trees that sustain the
population, causing a famine. A king is seen twisting the dagger,
summoning tentacular beasts of unnatural origin, which the people
harvest and turn into life-sustaining calamari.

More beasts, winged and demonic, appear in the sky from nowhere. The
king twists and turns the knife to no avail. The creatures swoop from
the sky and swallow entire homes. They raze villages. The king and his
council argue, and the dagger is sealed away in the highest room of the
sacred temple.

``Wow,'' says Harlan. The mirror's surface goes dark.

``It looks like it stopped working by the end,'' says Hermione. ``Did we
come all this way for a knife that doesn't work?''

``We could still use it to cut up our food and stuff,'' says Tannin,
scratching his chin. ``But nah, we don't know the whole story. I bet it
still works. Just gotta give it a try.''

``So we're taking it?'' says Hanamir. ``And\ldots{} bringing it back to
Aberith?''

``We're still about a half a day from when the Amber Guard said they'd
pick us up,'' says Hermione. ``We can make our way down to the beach and
be there with plenty of time.''

``No!'' says Tannin. ``No, if we get on that boat, they're going to take
it from us.'' He narrows his eyes. ``And we need this thing to defeat
the Lich. I haven't forgotten about that guy. He's why we went to
Aberith in the first place.''

``We can still take the ship back to Aberith,'' says Galadriel. ``I'll
just lie and say we didn't find it.''

``You think they won't search us?'' says Harlan. ``You'll just lie, and
they'll be like `oh, okay, bummer, thanks for checking'\ldots?''

``The other reason we maybe shouldn't get on their ship is
\href{/characters/magick/}{Magick},'' says Hanamir. ``We did promise to
keep her away from Aberith.''

``We could ask them to make a stop somewhere else before returning to
the city,'' says Hermione. Her eyes brighten. ``And then we can be rid
of her forever!''

``So are we extending this lie to King \href{/characters/slee/}{Slee}?''
asks Harlan. ``I think we should at least do him the courtesy of telling
the truth.''

``It'll be on a need-to-know basis,'' says Galadriel. ``But honestly,
don't you think the council would tear themselves apart if they knew we
had it? Especially \href{/characters/kandir/}{Kandir}. I'd trust Slee,
and probably no one else.''

``What about \href{/characters/mirama/}{Mirama}?'' says Tannin.

``Not her either,'' says Galadriel.

Their eyes turn to the knife embedded in the old wooden wheel. Harlan
extends a tentative hand toward its hilt.

``Objections?'' he says. He waits. ``Now or never.''

No one speaks. With a few wiggles of the blade, he frees it from the
cracked wood. He blinks rapidly.

``Whoa!''

His eyes dart around the room.

``I think\ldots{} I think I'm seeing to another plane,'' he says. He
points to a corner. ``There's a phase spider over there.''

``I knew it!'' says Galadriel. ``What else?''

``Nothing,'' says Harlan. ``It mostly just looks like the same room
superimposed on itself. Still lots of gems and gold in the walls.''

``This could get inconvenient if it's a factor in holding the quiznos,''
says Hanamir. ``Would you like to put it in that custom concealed dagger
holster I commissioned from a leatherworker back in Eillin?''

``That sounds like the perfect place for it,'' says Harlan, with a
nervous laugh. ``Just don't confuse it with a regular dagger.''

``No, no, I'll give the holster to you,'' says Hanamir. ``My reflexes
are such that I often draw a weapon before my mind has time to think
about it. I don't trust myself with the quiznos.''

``Ah,'' says Harlan.

``What now?'' asks Tannin. He glances at the ladder in the corner of the
room. ``Peace out?''

``As irritating as she is, even I'm not callous enough to leave Magick
behind,'' says Harlan. ``We should go collect her from the octopus
closet.''

``First, let's help ourselves to some treasure, shall we?'' says
Hanamir. He smiles and twirls his crowbar like a baton.

After prying as many precious gems from the walls as they can reasonably
fit in the Bag of Holding, they file back through the portal in the
floor to the battle room. The spirit king is gone, as far as anyone can
tell. The door at the bottom of the staircase remains locked shut.

``All right, what's our plan to get out of here? Force or magic?'' says
Hermione. She flips through her notebook and scans for helpful spells.

Hanamir leans against the door.

``Hard to say how strong this door is,'' he says. ``Feels heavy. We'd
have to chip away at it and then calibrate\ldots{}''

``Hold up, I'll just ask \href{/characters/buddy/}{Buddy}!'' says
Galadriel. Telepathically, she asks him. \emph{What do you think? Wanna
break down the door from the other side and let us out?}

HAHA, OKAY, SURE, says Buddy. YOU KNOW, IT'S FUNNY. NOW THAT I'M REALLY
ABOUT TO TURN BACK INTO A DRAGON IN FRONT OF YOU ALL, I'M KIND OF
NERVOUS.

``Stand back, everyone!'' Galadriel says.

They all jump backward a few paces into the room, but not far enough to
avoid the hail of rock and dust that blasts into the air. When the
coughing and sneezing dies down, the clouds of pulverized stone part
around the smiling face of a truly massive Copper Dragon.

His armored skull takes up the entire space of what was once the
doorway. The rest of his body cannot be seen, but surely extends down
the hallway and around the corner; the continuing noises of collapsing
stone indicate further destruction in his wake. His teeth alone are
taller than Tannin. He inhales with a sound like tectonic plates
grinding out a magnitude six earthquake.

``HI EVERYONE,'' says Buddy, aloud, for the first time. His voice is
what an upright bass would sound like if it were forty feet tall and
made of liquid magma. ``GOOD TO FINALLY MEET YOU GUYS FOR REAL. SORRY
FOR ALL THE DECEPTION.''

``No worries,'' says Harlan, wiping a layer of dust from his face. ``It
was definitely a good prank. Sorry I talked about killing and eating you
all those times.''

``HAHAHAHAHA,'' says Buddy. ``CLASSIC HARLAN.''

``Buddy!'' cries Hermione. She has dropped her notebook on the ground,
as if surrendered to the futility of capturing his majesty in words and
sketches. ``You're beautiful!''

``OH, STOP,'' says Buddy. He chuckles, shaking the entire room.

``Thanks for busting down the door, dude,'' says Tannin.

``Yes, much respect,'' says Hanamir.

``NO PROBLEM AT ALL,'' says Buddy. ``IT FEELS GOOD TO BE MYSELF, IF ONLY
FOR A SHORT WHILE.''

``You're going to turn back into a pig?'' asks Hermione.

``YEAH, WELL, I HEARD YOU ALL ARE GOING TO GO PICK UP THE TIEFLING, AND
THE LAST TIME SHE SAW ME SHE GOT REALLY UPSET,'' says Buddy. ``PLUS,
IT'S JUST\ldots{} CRAMPED IN HERE.'' He tilts his head slightly and more
potentially load-bearing stone blocks topple to the floor. ``HAHA,
YIKES.''

``Galadriel? You all right over there?'' says Harlan, giving her a
gentle nudge.

She nods, beaming.

``Just admiring my sweet boy,'' she says.

``AW, COME HERE, YOU.''

She approaches his enormous face and rests her cheek on his snout, just
next to a nostril larger than her head.

``I'm sorry you've had to be a pig for so long,'' she says. ``I promise
we'll be out of here soon.''

``NAH, I'VE LEARNED TO ENJOY BEING A PIG,'' says Buddy. ``AND BESIDES,
IT MAKES THE TIMES WHEN I TURN INTO A DRAGON OUT OF NOWHERE MUCH
FUNNIER, AND WAY MORE SURPRISING FOR ALL THE FARM ANIMALS I ATE.''

``That's a good point, sweetie,'' says Galadriel. She strokes his scales
lovingly.

``We should probably pay Elris for damages when we go back to pick up
Zotz,'' mutters Harlan.

``PIG TIME AGAIN, I THINK,'' says Buddy. ``I'M STARTING TO FEEL A LITTLE
CLAUSTROPHOBIC.''

Galadriel gives him a soft kiss on the snout, and in a sort of
reverse-Frog-Prince moment, he turns back into a pig---if possible, even
rounder, fuzzier, and cuter than before. Another cascade of rubble falls
in the absence of its dragon scaffolding, but Galadriel shields him from
the debris.

They proceed down the wrecked hallway toward the mirror room and its
adjoining octopus closet.

``How mad do you think she's gonna be?'' whispers Tannin. ``I'd bet my
remaining hand she's gonna try to kill you right away, bro.''

``Guess we're about to find out,'' says Harlan. ``And stop gambling with
your appendages.'' He sighs deeply, then strides into the cramped room
with the oversized statue feature. Magick is right where they left her,
shackled to one of the stone octopus's tentacles. ``Hi, Magick. We're
back.''

``Did you find it?!'' she says breathlessly.

``It was already gone,'' says Galadriel. ``Someone else had gotten there
first. I'm sorry, Magick.''

``What?!'' Magick's face falls. ``You're kidding. No, you---you
must've---you just didn't look in the right place! It has to be here!''

Harlan unshackles her from the statue and helps her to her feet.

``We can go back there now and show you,'' he says. ``It certainly looks
like the right place. We're as disappointed as you are.''

``I doubt \emph{that},'' she drawls, but she appears eager to inspect
the treasure room herself, and follows the adventurers back through the
battle room and up into the heavily bedazzled attic of the pyramid.

Galadriel has the uncanny feeling of being watched as she reenters the
room. The memory of the phase spider prickles at the back of her neck,
very much like the physical sensation of an insect creeping down her
spine. \emph{Maybe I'm just being dramatic,} she thinks. \emph{But maybe
not.}

``Let's not linger here,'' she says. It really does feel like her
gauntlet is tighter on her wrist than usual, the skin underneath itchy
and clammy. It reminds her of something she hasn't felt in a long time.
Her blood buzzes.

``What's wrong?'' asks Hanamir. He pries a baseball-sized emerald from
the wall and tosses it from hand to hand a few times.

``Kind of a bad feeling,'' says Galadriel. She can't tell if she's the
only one who can hear a faint laughter\ldots{} a familiar laughter,
too\ldots{} is it just a trick of their voices echoing off the chamber's
walls?

Magick circles around the room touching every gem in turn, waiting for
one of them to be a secret compartment containing the quiznos, while
Harlan and Hermione hover next to her like the anxious parents of a
toddler. Meanwhile, Tannin grips the rickety wooden wheel on a pedestal
in the center of the room, pretending to be a ship's captain.

``What kind of bad feeling?'' says Hanamir, alert. ``A spidery
feeling?''

Before Galadriel can reply, a disembodied giggle makes the hair on
Hanamir's arms stand on end. He recognizes the laughter, cold as a
moonless night.

``Hello,'' says \href{/characters/cazna/}{Cazna}. ``It's good to see you
all again.''

The late High Priestess of Lolth stands face-to-face with Galadriel. Her
entire lower half has been replaced with a set of eight long, black
legs. The adventurers stare at her, frozen in shock.

``Cazna,'' says Galadriel, unable to hide the question in her voice.
``We killed you.''

Cazna's full-throated laugh rings in their ears.

``Yes,'' she says. ``Yes, I failed Lolth's test.'' She gestures at
herself, smiling coolly. ``This is what becomes of those who disappoint
the Mother. It's a fate you'll know about soon enough.''

``Oh, you think so?'' snorts Galadriel. The surprise has begun to wear
off, and she feels a surge of power from her gauntleted wrist. ``I think
you're just jealous that I'm better than you were at serving Her.''

``It's time for your test now,'' says Cazna.

``Oh, good!'' says Galadriel. ``I love tests. Even pop quizzes, like
this. I perform very well under pressure.'' She strums a sequence of
power chords on her lute. ``It's probably why Lolth blessed me, and why
she continues to favor me. And why I defeated you.''

Cazna's face drains of its pretense of humor. With a wave of her palm,
she casts Command.

``Give me the item,'' she hisses.

Galadriel begins emptying her pockets onto the floor as if seeking
something urgently.

``What item do you want?'' she says, in earnest. She holds up the flask
of goop from the oni's well. ``This?'' She holds up her crossbow.
``This?'' Her lute.

``Don't play games with me,'' says Cazna. ``The quiznos. Give it to
me.''

``I don't have that,'' says Galadriel. ``I desperately want to obey your
Command, though. Can you pick something else?'' She holds up a tiny
sweater she knit for Buddy. It has ducks on it. ``This?''

Behind Cazna, she sees Harlan climbing up the ladder to the hatch in the
ceiling. He pulls Magick after himself by the hand. Hermione and Tannin
wait below. Hanamir, she notices, is in a meditative pose similar to the
one that initiated the Stunning Strike against the giant snake in their
last battle.

``Is this situation funny to you?'' asks Cazna, throwing the proffered
pig sweater to the floor.

``Honestly, yes, a little bit,'' says Galadriel, pelting Cazna with
every item she has on hand, including a wadded-up granola bar wrapper
that's been in her pocket for months.

Hanamir completes his meditation and punches Cazna in the kidneys. She
doubles over, and appears injured, but then seems somehow revitalized by
the attack. She starts to laugh again, turning to Hanamir.

``No need for that,'' she says. ``I'm not here to fight. Just here to
have a conversation with this one.'' She raises a hideous foreleg and
points at Galadriel.

``Please accept one of my items,'' Galadriel begs, head bowed.

``Fine,'' says Cazna, picking up the granola bar wrapper and tossing it
in her mouth, which has noticeably more teeth than it needs to have. ``I
see that you do not have the quiznos. Very well. You will tell me which
one of your friends has it before we're through here.''

``Sure,'' says Galadriel, jumping to her feet. ``But before that, we
have some catching up to do!''

``We don't, actually,'' says Cazna. ``I've been checking in you all from
time to time since our last meeting. Watching from another plane. I know
what you've been up to.''

``Oh, don't worry,'' says Galadriel, ``I'm not actually interested in
hearing what's been going on for you after the footage of your death won
first place on Aberith's Funniest Home Videos.''

Cazna doesn't laugh, but Tannin, from midway up the ladder to the roof,
guffaws.

``Thanks Tannin. But seriously, Cazna, I only said that because I was
going to ask if you wanted to hear another joke, since you liked my last
one so much,'' says Galadriel. She grins. ``And then I was going to do
this.''

She casts Tasha's Hideous Laughter. But---as she should have perhaps
foreseen, after Hanamir's attack---Cazna deflects the spell like a
senior varsity player blocking a freshman's attempt at a slam dunk.

``Not as funny as last time,'' says Cazna.

``Ah, you're right,'' sighs Galadriel. ``It wasn't my best work.''

Behind them, Hermione disappears onto the roof, followed by Hanamir
holding Buddy in his arms. Galadriel can't help but feel a mild panic
rising in her throat.

``So, are we done here?'' she asks.

A small object covered in cloth---which Galadriel recognizes, in alarm,
as one of Tannin's loincloths---hurtles down from the hatch and hits
Cazna in the back of the head. The object falls to the floor and tumbles
out of its wrapping. It's the gem from the octopus closet, the one that
makes you dance uncontrollably if you touch it.

``Good one, bud!'' she calls up at him.

``Did she do it?'' comes Tannin's voice.

``No, but it was funny anyway!'' She collects herself and clears her
throat. ``Sorry,'' she says. ``Please---are we done? Is it time for my
test, or what?''

Cazna purses her lips in an odd smile.

``I can tell it's not the right time,'' she says. She fixes Galadriel
with a flat stare. ``So long, for now.''

She disappears. Galadriel feels her gauntlet humming with energy,
slightly painful now, like a series of weak electric shocks. She shakes
her arm, willing it away.

Tannin's face appears in the hatch.

``Come on, Moonwater!'' he says. ``And bring back my loincloth!''

Galadriel grabs the corner of the ``garment'' gingerly and picks up the
dance gem with it, depositing both in a small bag at her hip. Heart
pounding, she sprints to the ladder and climbs as fast as she can,
before her fellow Servant of Lolth decides to change her mind.

The air outside is clean and surprisingly cool. She gulps it in by the
lungful, marveling at how good it feels to no longer breathe dust and
thousand-year-old catacomb air. She's greeted by a shrieking hug from
Hermione and an abundance of enthusiastic licks to her cheek from Buddy,
who is held out to her by Hanamir. Harlan and Tannin throw up their arms
and join the group hug, all of them laughing with incredulous relief.

``We did it,'' says Harlan. He pats his chest, where the quiznos lies
concealed in its holster, and glances behind himself at Magick, who is
busy kicking rocks down the stepped sides of the pyramid. ``Praise
\href{/characters/kord/}{Kord}, we really pulled it off.''

``And would you look at that view?'' says Hanamir, shading his eyes.
``That's quite a view, folks.''

From here, they can see the partial collapse of the jungle room beneath
them, the remains of the mudslide that swept them into the temple in the
first place, the vast canopy of the island's greenery beyond, and
farther still, the glittering ocean.

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

The adventurers trudge seaward.

``Ooh! I can see the Amber Guard ship!'' says Hermione. ``At least, I
think that's what it is---a little bit fuzzy---but something's on the
horizon.''

As they approach the shoreline, Hermione's updates regarding the ship
become more and more frequent.

``Looks like a brigantine rather than a full-rigged ship,'' she says.
``Interesting. Wonder if that means they expected to be picking up fewer
of us, or none at all.''

``We can ask them when they get here,'' says Harlan, ``which will
probably still be awhile.''

``Of course, of course. I just, you know, as the only full-blooded elf
here, I take my responsibility regarding long-distance sight \emph{very}
seriously,'' she reminds them. ``I just want the entire group to stay
informed.''

``Thank you,'' says Harlan. ``So, Magick, have you thought at all about
where you'd like the ship to drop you off? You remember that you're not
allowed to go back to Aberith, right?''

``Yes,'' says Magick. ``I'm not an \emph{idiot}, even though you insist
on treating me like one.''

Her opinion of the adventurers has soured dramatically since her
painstaking search of the treasure room did not yield the quiznos. She
has taken to muttering offensive things under her breath and feigning
innocence when someone asks her to repeat herself.

``All right, where to, then?'' Harlan asks.

``Nowhere,'' she says. ``Just leave me here. I'm serious! I know the
quiznos is still here---I can \emph{feel} it---and my life has no
purpose unless I can find it and---and---\emph{complete my quest}.''

She spits these last words with a venomous look at Buddy, who is digging
contentedly in the sand.

``Well?'' says Harlan, looking at the others. ``I'm open to it. It might
not be such a bad idea.''

``Really?'' Hermione raises her eyebrows. ``Don't you think she's going
to do something, um, no offense, but something \emph{evil} as soon as we
let her out of our sight?''

``Annoyingelfdorksayswhat,'' mumbles Magick.

``What?'' says Hermione.

``Nothing, jeez! Leave me alone!''

``So was it your assumption that we'd be babysitting her forever,
then?'' asks Harlan.

``No, but we did talk about getting her some kind of rehabilitation,
right?'' says Hermione. ``Someone experienced with cases like hers who
could help her get her power back under control, or at least\ldots{}
someone wise? And responsible?''

``We did discuss it,'' says Hanamir. ``But was that part of the deal?
Are we doing right by our word to Slee if we simply leave her here, so
long as she never returns to Aberith?''

``Oh! Oh! You know who'd be perfect?'' says Tannin. ``That guy, that
smart guy with the observatory!''

``\href{/characters/bryn/}{Bryn}?'' says Galadriel.

``Yeah! That guy,'' says Tannin. It dawns on him. ``Oh, wait, dang.''

``Magick, are you sure you can fend for yourself if you're alone here?''
says Harlan.

``I did it for years, in the burning forest, before you all showed up,''
says Magick.

``That's a good point,'' says Harlan. He thinks for a moment. ``All
right, Magick. We'll leave you here if that's what you want. But we'll
check in on you every once in awhile to see how you're doing.''

``Do it or don't, see if I care,'' says Magick.

``And you understand that if you attempt to return to Aberith, you will
undoubtedly be executed?''

``Yes! I am never going back there!'' She pauses, then for good measure:
``I hate it there!''

``Good,'' says Harlan, rolling his eyes.

``Exile, I think, is the most humane punishment she could have gotten,
anyway,'' says Hanamir. ``And exile to a place one finds fascinating is
barely punishment at all.''

\begin{center}\rule{0.5\linewidth}{\linethickness}\end{center}

When the Amber Guard ship lands on the beach, the guardsmen look frankly
stunned to see them.

``I had my money on \emph{all} of you being dead,'' one of them says,
scowling. ``Thanks a lot.''

They hike up the gangplank to the ship (``Only a brigantine, as I
said!'' chirps Hermione) while some other dejected-looking soldiers pass
fistfuls of coins to one elated young man who went out on a limb and
thought only two of them would die.

``How about that Mirama wine, am I right, guys?'' says Tannin, summoning
it from the Bag of Holding as soon as he's fully on board. He uses his
trident to uncork it and pours them each a glass, passing one to each of
them as they step onto the deck. ``Cheers.''

``None for me, thanks,'' says Hanamir. ``Vows are vows.''

``Are you sure?'' says Hermione, tasting it. ``This is a very good
wine.''

``I \emph{knew} it,'' says Tannin, his glass empty and his teeth purple.
``I knew it was good.''

``To victory!'' says Galadriel, her glass outstretched. Her arm still
stings beneath the gauntlet, but the wine dulls the sensation.

From the ship's hull, they wave down at Magick while sipping their wine,
which is indeed quite excellent. Magick makes a sarcastic wave back and
then stomps off into the jungle.

``Remember,'' calls Harlan, as she disappears from view, ``this isn't
goodbye forever!''

\end{document}